### 2025-05-17 bio.qmd
Initial commit.

---
title: Biography
---

# Biography

<img src="images/bio1.jpg" alt="Bin Yu speaking" style="float:right; margin:0 0 1em 2em; width:200px; border-radius:8px;" />

Bin Yu is CDSS Chancellor's Distinguished Professor in the Departments of statistics and EECS, and Center for Computational Biology, and serves as a scientific advisor at the Simons Institute for the Theory of Computing, all at UC Berkeley.

She obtained her BS Degree in Mathematics from Peking University, and MS and PhD Degrees in Statistics from UC Berkeley. She was Assistant Professor at UW-Madison, Visiting Assistant Professor at Yale University, Member of Technical Staff at Lucent Bell-Labs, and Miller Research Professor at Berkeley. She was a Visiting Faculty at MIT, ETH, Poincare Institute, Peking University, INRIA-Paris, Fields Institute at University of Toronto, Newton Institute at Cambridge University, and the Flatiron Institute in NYC. She was Chair of the Department of Statistics at UC Berkeley from 2009 to 2012. Recently, she was a 50% consultant researcher in the deep learning group of MSR at Redmond (2022-2023).

She is a Member of the U.S. National Academy of Sciences and of the American Academy of Arts and Sciences. She was President of the Institute of Mathematical Statistics (IMS), Guggenheim Fellow, Tukey Memorial Lecturer of the Bernoulli Society, Rietz Lecturer of IMS, and a COPSS E. L. Scott Prize winner. Recently, she delivered the Wald Memorial Lectures of IMS and COPSS Distinguished Achievement Award and Lecture (DAAL) (formerly Fisher Award and Lecture) at JSM in 2023. She served on the Inaugural Scientific Committee of the UK Turing Institute for Data Science and AI. She holds an Honorary Doctorate from the University of Lausanne in Switzerland. She is serving on the Editorial Board of Proceedings of National Academy of Sciences (PNAS).

She has published more than 170 papers in premier venues on statistical machine learning including deep learning and the Predictability-Computability-Stability (PCS) framework and documentation for [veridical (truthful) data science](https://vdsbook.com/) and these papers not only investigate a wide range of research topics from practice to algorithms and to theory, but also seek deep insights. The breadth and depth of her research experience enabled unique and novel solutions to interdisciplinary data problems in audio and image compression, network tomography, remote sensing, climate science, neuroscience, genomics, and precision medicine.

Currently, she is championing "in-context" research with experts in the subject knowledge and leading research in interpretable machine learning (e.g. tree-based methods and deep learning) and causal inference to design algorithms such as [iterative random forests (iRF)](https://www.pnas.org/doi/10.1073/pnas.1711236115), [Efficient Automated Circuit Discovery in Transformers using Contextual Decomposition (CD-T)](https://openreview.net/forum?id=41HlN8XYM5) and [adaptive wavelet distillation (AWD)](https://proceedings.neurips.cc/paper/2021/file/acaa23f71f963e96c8847585e71352d6-Paper.pdf) for interpreting deep neural networks and [X-learner for heterogeneous treatment effect estimation in causal inference](https://www.pnas.org/doi/10.1073/pnas.1804597116). Recently, she and her collaborators developed PCS-guided [low-signal signed iterative random forests (lo-siRF)](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v2) that recommends genetic targets for high-yield follow-up experiments with a case study showing epistasis regulation controls cardiac hypertrophy through gene-silencing experiment (4 out of 5 sets of experiments found causal genes or gene-gene interactions). She is also working on relevant deep learning theory and practical algorithms with her team (e.g. the development of [LoRA+ algorithm](https://github.com/nikhil-ghosh-berkeley/loraplus) for fine-tuning large language models).

Previously, she pioneered Vapnik-Chervonenkis (VC) type theory needed for asymptotic analysis of time series and spatio-temporal processes, and made fundamental contributions to information theory and statistics through work on minimum description length (MDL) and entropy estimation, and through theory on sparse modeling, boosting and spectral clustering, EM algorithm, and MCMC convergence analysis. With her students and collaborators, she developed a highly cited spatially adaptive wavelet image denoising method and a low-complexity low-delay perceptually lossless audio coder that was incorporated in Bose wireless speakers, and developed a fast and well-validated Arctic cloud detection algorithm using NASA's MISR data. With the Jack Gallant Lab and her students, she developed predictive models of fMRI brain activity in vision neuroscience that made "mind-reading" possible (or reconstruction of movies using only fMRI signals).

Moreover, she served on editorial boards including Annals of Statistics, Journal of American Statistical Association, and Journal of Machine Learning Research. Her leadership roles included co-chairing the National Scientific Committee of the Statistical and Applied Mathematical Sciences Institute (SAMSI), and serving on the scientific advisory committee of SAMSI and IPAM, and on the board of trustees of ICERM and the Board of Governors of IEEE-IT Society. She recently served on the scientific advisory committee for the IAS Special Year on optimization, statistics and theoretical machine learning, the Scientific Advisory Boards of Canadian Statistical Sciences Institute (CANSSI). She is serving on the advisory board of the AI Policy Hub at UC Berkeley, the Scientific Advisory Committee of the Department of Quantitative and Computational Biology at USC, and on the External Advisory Committee, Learning the Earth with Artificial Intelligence and Physics (LEAP), an NSF Science and Technology Center (STC), at Columbia University.

### 2025-05-17 index.qmd
Initial commit.

---
title: Home
title-block: false
format:
  html:
    css: styles.css
---

<div style="text-align:center">
# Bin Yu
</div>

<img src="images/binyu.jpg" alt="Bin Yu" style="float:right; margin:0 0 1em 2em; width:200px; border-radius:8px;" />

CDSS Chancellor's Distinguished Professor

Departments of [Statistics](https://statistics.berkeley.edu/) and [Electrical Engineering and Computer Sciences](https://eecs.berkeley.edu/), Center for Computational Biology

[UC Berkeley](https://www.berkeley.edu/)

[Chan-Zuckerberg Biohub](https://www.czbiohub.org/) Investigator Alumnus • [Weill Neurohub](https://www.weillneurohub.org/) Investigator

*mail: 367 Evans Hall #3860 • Berkeley, CA 94720*

*phone: 510-642-2781 • fax: 510-642-7892 • [binyu@berkeley.edu](mailto:binyu@berkeley.edu)*

## Welcome

Professor Bin Yu is the head of the [Yu Group](https://www.stat.berkeley.edu/~yugroup/) at Berkeley, which consists of 12-15 students and postdocs from Statistics and EECS. She was formally trained as a statistician, but her research interests and achievements extend beyond the realm of statistics. Together with her group, Bin Yu has leveraged new computational developments to solve important scientific problems by combining novel and often interpretable statistical machine learning approaches with the domain expertise of her many collaborators in neuroscience, genomics and precision medicine. She also develops relevant theory to understand random forests and deep learning for insight into and guidance for practice. Her work has been recognized by many awards. In particular, she was inducted to the National Academy of Sciences in 2014 and to the American Academy of Arts and Sciences in 2013. She delivered the IMS Wald Lectures and COPSS Distinguished Achievement and Award Lecture (DAAL, formerly Fisher Award and Lecture) in 2023.

She and her team have developed the PCS framework for veridical data science (or responsible, reliable, and transparent data analysis and decision-making). PCS stands for predictability, computability and stability, and it unifies, streamlines, and expands on ideas and best practices of machine learning and statistics.

In order to augment empirical evidence for decision-making, they are investigating statistical machine learning methods/algorithms (and associated statistical inference problems) such as dictionary learning, non-negative matrix factorization (NMF), EM and deep learning (CNNs and LSTMs), and heterogeneous effect estimation in randomized experiments (X-learner). Their recent algorithms include staNMF for unsupervised learning, iterative Random Forests (iRF) and signed iRF (s-iRF) for discovering predictive and stable high-order interactions in supervised learning, next generation tree-based methods (e.g. fast and interpretable greedy-tree sums (FIGS) and hierarchical shrinked (HS) trees, and RF+ ), contextual decomposition (CD), aggregated contextual decomposition (ACD), and adaptive wavelet distillation (AWD) for interpretation of Deep Neural Networks (DNNs).

## My vision for data science - papers & talks

- [Rome Workshop on Veridical Data Science, June 20, 2025](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html) (New)
- [Veridical data science and medical foundation models](https://arxiv.org/abs/2409.10580) on arXiv by Alaa and Yu.
- [VDS book review](https://hdsr.mitpress.mit.edu/pub/5322mn1e/release/3) by Yuval and Yoav Benjamini in Harvard Data Science Review (HDSR)-- "pedagogical excellence, diverse examples, and projects make Veridical Data Science a suitable textbook for students of all levels, in addition to being a valuable resource for data scientists in general" (review summary in HDSR Editor-in-Chief's note), June, 2024.
- [Inaugural Berkeley-Stanford Workshop on Veridical Data Science at UC Berkeley](https://na.eventscloud.com/website/69057/) (May 31, 2024) ([talk videos available](https://www.youtube.com/playlist?list=PLKW2Azk23ZtSrg4jwLSioaV1bwmFnQ1Bx))
- My co-author [Rebecca Barter](https://rebeccabarter.com/) and I are thrilled to announce the [online release](http://vdsbook.com/) of our MIT Press book ["Veridical Data Science: The Practice of Responsible Data Analysis and Decision Making"](https://mitpress.mit.edu/9780262049191/veridical-data-science/), an essential source for producing trustworthy data-driven results (Feb. 28, 2024).
- ["Veridical data science towards trustworthy AI"](https://ww2.amstat.org/meetings/jsm/2023/webcasts/index.cfm) (Talk video of COPSS DAAL (formerly Fisher Award and Lecture), scroll down), Aug. JSM in Toronto, 2023.
- [What is uncertainty in today's practice of data science?](https://www.sciencedirect.com/science/article/pii/S030440762300235X?dgcid=author) (Yu, 2023). Journal of Econometrics.
- [Building trust in medical AI algorithms with veridical data science](https://link.springer.com/epdf/10.1007/s13218-023-00803-y?sharing_token=ebI2N15qM6XZUegMth-Quve4RwlQNchNByi7wbcMAY7HhSJ5V2qZIFNLqxQFZ-zTvebYYHuYBEDcXzQl7eRE1JVsvjcy_eFebw0xZW9UU9CqWdFLLGd22GvHmjiyaKtyaRMQToSpZQruTneGX1KD5rV1I5kdcOMfqUq47TrVW5E%3D) (interview of Bin Yu by Dr. Merle Behr for the German scientific journal [KI - Künstliche Intelligenz](https://www.springer.com/journal/13218)), 2023
- [Veridical data science](https://www.pnas.org/content/117/8/3920) (PCS framework: [v-flow code](https://github.com/Yu-Group/veridical-flow) and [documentation template](https://yu-group.github.io/vdocs/PCSDoc-Template.html)), PNAS, 2020 ([QnAs with Bin Yu](https://www.pnas.org/content/117/8/3893))
- [Breiman Lecture (video) at NeurIPS "Veridical data Science"](https://slideslive.com/38922599/veridical-data-science) ([PCS framework](https://www.pnas.org/content/117/8/3920) and iterative random forests ([iRF](https://www.pnas.org/content/115/8/1943))), 2019; [updated slides](https://www.stat.berkeley.edu/~binyu/ps/papers2020/Breiman19-NeurIPS-yu.pdf), 2020
- [Stability](https://projecteuclid.org/euclid.bj/1377612862), Bernoulli, 2013
- [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/2), Harvard Data Science Review (HDSR), 2020.
- [Data science process: one culture.](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20) JASA, 2020.
- [Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y), Nature Medicine, 2020.
- [Definitions, methods and applications in interpretable machine learning](https://www.pnas.org/content/116/44/22071), PNAS, 2019
- [Data wisdom for data science (blog)](http://www.odbms.org/2015/04/data-wisdom-for-data-science/), 2015
- [IMS Presidential Address "Let us own data science"](https://imstat.org/2014/10/01/ims-presidential-address-let-us-own-data-science/), IMS Bulletin, 2014
- [Embracing statistical challenges in the IT age](https://www.tandfonline.com/doi/abs/10.1198/004017007000000254), Technometrics, 2007

## In the news

- IMS Wald [Lecture I](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1029) and [Lecture II](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1031), and [COPSS Distinguished Award and Lecture (DAAL)](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1374) delivered at [Joint Statistical Meeting (JSM)](https://ww2.amstat.org/meetings/jsm/2023/) in Toronto, August 2023
- UC Berkeley team part of the new NSF AI Center for Cybersecurity [ACTION](https://action.ucsb.edu/) led by UCSB.
- [CDSS news: Statistics-Computer Science team reflects on tackling covid outbreaks](https://data.berkeley.edu/news/statistics-computer-sciences-team-reflects-tackling-covid-outbreaks), May, 2022
- Honorary Doctorate, University of Lausanne (UNIL) (Faculty of Business and Economics), June 4, 2021 ([Interview of Bin Yu](https://www.youtube.com/watch?v=1JRGPGhcYzU) by journalist Nathalie Randin, with an introduction by Dean Jean-Philippe Bonardi of UNIL in French ([English translation](https://www.stat.berkeley.edu/~binyu/Intro-DeanBonardi-UNIL.pdf)))
- [CDSS news on our PCS framework: "A better framework for more robust, trustworthy data science"](https://data.berkeley.edu/people/bin-yu), Oct. 2020
- [UC Berkeley to lead $10M NSF/Simons Foundation program to investigate theoretical underpinnings of deep learning](https://data.berkeley.edu/news/uc-berkeley-lead-10m-nsfsimons-foundation-program-investigate-theoretical-underpinnings-deep), Aug. 25, 2020
- [Curating COVID-19 data repository and forecasting county-level death counts in the US](https://engineering.berkeley.edu/news/2020/04/getting-the-right-equipment-to-the-right-people/), 2020
- [Interviewed by PBS Nova about AlphaZero](https://www.pbs.org/wgbh/nova/article/google-alphazero-artificial-intelligence/), 2018
- [Mapping a cell's destiny](https://newscenter.lbl.gov/2016/05/04/mapping-cells-destiny/), 2016
- [Seeking Data Wisdom](https://vcresearch.berkeley.edu/news/seeking-data-wisdom), 2015
- [Member, National Academy of Sciences](http://www.dcd.zju.edu.cn/Hsu-conference/pr.htm), 2014
- [Fellow, American Academy of Arts and Sciences](http://www.dcd.zju.edu.cn/Hsu-conference/pr.htm), 2013
- [One of the 50 best inventions of 2011 by Time Magazine](http://content.time.com/time/magazine/article/0,9171,2099708,00.html), 2011
- [The Economist Article](http://www.economist.com/node/21534748), 2011
- [ScienceMatters @ Berkeley. Dealing with Cloudy Data](https://www.stat.berkeley.edu/~binyu/ps/dealingwithcloudydata.pdf), 2004

### 2025-05-17 papers.qmd
Initial commit.

---
title: Papers
---

# Papers

## Recent Papers by Area

- [Deep Learning and Machine Learning](papers/deep-learning-and-machine-learning.qmd)
- [Veridical Data Science (PCS)](papers/veridical-data-science-pcs.qmd)
- [Interpretable Machine Learning](papers/interpretable-machine-learning.qmd)
- [Interdisciplinary Research in Biomedicine](papers/interdisciplinary-research-in-biomedicine.qmd)
- [Tree-based Methods](papers/tree-based-methods.qmd)

---

## Complete List by Reverse Chronological Order

*For the most up-to-date and complete list, see [Google Scholar](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en) or [arXiv](https://arxiv.org/search/?query=bin+yu&searchtype=author).*

### Publications

1. A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contextual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886)
1. Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958)
1. O. Ronen, A. I. Humayun, R. Balestriero, R. Baraniuk, B. Yu (2024). [ScaLES: Scalable Latent Exploration Score for Pre-Trained Generative Networks](https://arxiv.org/pdf/2406.09657)
1. S. Hayou, N. Ghosh, B. Yu (2024). [The Impact of Initialization on LoRA Fineuning Dynamics.](https://arxiv.org/pdf/2406.08447)
1. B. Yu (2024). [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (Harvard Data Science Review)
1. S. Hayou, N. Ghosh, B. Yu (2024). [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) (Proc. ICML)
1. C. F. Elliott, J. Duncan, T. M. Tang, M. Behr, K. Kumbier, B. Yu (2024). [Designing a data science simulation with MERITS: a primer.](https://arxiv.org/abs/2403.08971)
1. Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). [Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986)
1. N. R. Mallinar, A. Zane, S. Frei, B. Yu (2024). Minimum-Norm Interpolation Under Covariate Shift. (Proc. ICML) [arXiv](https://arxiv.org/pdf/2404.00522)
1. L. Sun, A. Agarwal, A. Kornblith, B. Yu, C. Xiong (2024). ED-Copilot: Reduce Emergency Department Wait Time with Language Model Diagnostic Assistance. (Proc. ICML) [arXiv](https://arxiv.org/abs/2402.13448)
1. C. Singh*, A. R. Hsu*, R. Antonello, S. Jain, A. G. Huth, B. Yu, J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
1. Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262)
1. Q. Wang*, T. M. Tang*, N. Youlton, C. S. Weldy, A. M. Kenney, O. Ronen, J. W. Hughes, E. T. Chin, S. C. Sutton, A. Agarwal, X. Li, M. Behr, K. Kumbier, C. S. Moravec, W. H. W. Tang, K. B. Margulies, T. P. Cappola, A. J. Buitte, R. Arnaout, J. B. Brown, J. R. Priest, V. N. Parikh, B. Yu*, E. Ashley* (2023). Epistasis regulates genetic control of cardiac hypertrophy. [medRxiv](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
1. R. Cahill, Y. Wang, R. P. Xian, A. J. Lee, H. Zeng, B. Yu, B. Tasic, R. Abbasi-Asl (2023). Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology. [bioRxiv](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
1. E. Irajizad, A. Kenney, T. Tang, J. Vykoukal, R. Wu, E. Murage, J. B. Dennison, M. Sans, J. P. Long, M. Loftus, J. A. Chabot, M. D. Kluger, F. Kastrinos, L. Brais, A. Babic, K. Jajoo, L. S. Lee, T. E. Clancy, K. Ng, A. Bullock, J. M. Genkinger, A. Maitra, K. A. Do, B. Yu, B. W. Wolpin, S. Hanash, J. F. Fahrmann. (2023). [A blood-based metabolomic signature predictive of risk for pancreatic cancer](https://pubmed.ncbi.nlm.nih.gov/37729870/). Cell Reports Medicine 4(9): 101194. doi: 10.1016/j.xcrm.2023.101194. (PCS related) ([Editorial](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10518497/))
1. R. Dwivedi, C. Singh, B. Yu, M. Wainwright (2023). [Revisiting miniumu description length complexity in overparametrized models.](https://jmlr.org/papers/v24/21-1133.html) JMLR, 24(268): 1-59.
1. K. Wu, Y. Chen, W. Ha, B. Yu (2023). [Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms.](https://arxiv.org/abs/2309.10301) JMLR (accepted). [https://arxiv.org/abs/2309.10301](https://arxiv.org/abs/2309.10301)
1. N. Ghosh, S. Frei, W. Ha, B. Yu (2023). The effect of SGD batch size on autoencoder learning: sparsity, sharpness and feature learning. [https://arxiv.org/abs/2308.03215](https://arxiv.org/abs/2308.03215)
1. R. Netzorg, J. Li, B. Yu (2024). Improving prototypical part networks with reward reweighting, reselection, and retraining. Proc. ICML. [https://arxiv.org/abs/2307.03887](https://arxiv.org/abs/2307.03887)
1. A. Agarwal, A. M. Kenny, Y. S. Tan, T. M. Tang, B. Yu (2023). MDI+: a flexible random forest-based feature importance framework. [https://arxiv.org/abs/2307.01932](https://arxiv.org/abs/2307.01932) (PCS related)
1. A. R. Hsu, Y. Cherapanamjeri, B. Park, T. Naumann, A. Odisho, and B. Yu (2023). Diagnosing transformers: illuminating feature space for clinical decison-making. Proc. ICLR. [https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)
1. C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). Explaining black box text modules in natural language with language models. [https://arxiv.org/abs/2305.09863](https://arxiv.org/abs/2305.09863)
1. D. Shen, P. Ding, J. Sekhon, B. Yu (2022). Same root different leaves: time series and cross-sectional methods in panel data. Econometrica (accepted). [https://arxiv.org/abs/2207.14481](https://arxiv.org/abs/2207.14481)
1. B. Park, X. Wu, B. Yu, A. Zhou (2022). [Offline evaluation in RL: soft stability weighting to combine fitted Q-learning and model-based methods.](https://openreview.net/forum?id=R3h3-bt0mq) NeurIPS 3rd Offline Reinforcement Learning Workshop.
1. Y. S. Tan, C. Singh, K. Nasseri, A. Agarwal, J. Duncan, O. Ronen, M. Epland, A. Kornblith, B. Yu (2022). [Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931). ([imodels 🔎](https://github.com/csinva/imodels) contains code for FIGS)
1. A. Agarwal, Y. S. Tan, O. Ronen, C. Singh, B. Yu (2022). [Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.](https://arxiv.org/abs/2202.00858) Proc. ICML ([imodels 🔎](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS)).
1. B. Yu and C. Singh (2022). [Seven principles for rapid-response data science: lessons learned from covid-19 forecasting](https://projecteuclid.org/journals/statistical-science/volume-37/issue-2/Seven-Principles-for-Rapid-Response-Data-Science--Lessons-Learned/10.1214/22-STS855.full). Statistical Science, 36(2):266-269.
1. N. Ghosh, S. Mei, and B. Yu (2022). [The three stages of dynamics in high-dimensional kernel methods.](https://arxiv.org/abs/2111.07167) Proc. ICLR, 2022.
1. Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS.
1. N. Altieri, B. Park, J. DeNero, A. Odisho, B. Yu. (2021). [Improving natural language information extraction from cancer pathology reports using transfer learning and zero-shot string similarity.](https://pubmed.ncbi.nlm.nih.gov/34604711/) JAMIA Open. 2021 Sept. 30 4(3).
1. C. Singh, W. Ha and B. Yu (2021). [Interpreting and Improving Deep-Learning Models with Reality Checks](https://arxiv.org/abs/2108.06847). To appear in "xxAI - Beyond Explainable AI" (eds. Holzinger et al.).
1. W. Ha, C. Singh, F. Lanusse, S. Upadhyayula, and B. Yu (2021). [Adaptive Wavelet Distillation from Neural Networks through Interpretation.](https://nips.cc/Conferences/2021/ScheduleMultitrack?event=28027) Proc. NeurIPS 2021. ([code](https://github.com/Yu-Group/adaptive-wavelets))
1. M. Behr, Y. Wang, X. Li, B. Yu (2022). [Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.](https://arxiv.org/abs/2102.11800) PNAS. ([theory for iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS-related)
1. N. Altieri, B. Park, M. Olson, J. DeNero, A. Odisho, B. Yu. (2021). Supervised line attention for tumor attribute classification from pathology reports: Higher performance with less data. Journal of Biomedical Informatics. 122 (2021) 103872. [arXiv version](https://arxiv.org/abs/2012.08113)
1. M. Behr*, K. Kumbier*, A. Cordova-Palomera, M. Aguirre, E. Ashley, A. Butte, R. Arnaout, J. B. Brown, J. Preist*, B. Yu* (2020). [Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
1. B. Norgeot*, G. Quer, B. K. Beaulieu-Jones, A. Torkamani, R. Dias, M. Gianfrancesco, R. Arnaout, I. S. Kohane, S. Saria, E. Topol, Z. Obermeyer, B. Yu & A. Butte* (2020). [Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y), Nature Medicine, 26, 1320–1324.
1. B. Yu (2020). [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/1). Harvard Data Science Review (PCS related)
1. B. Yu and R. Barter (2020). [Data science process: one culture.](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20) JASA. (PCS related)
1. R. Dwivedi, Y. Tan, B. Park, M. Wei, K. Horgan, D. Madigan, B. Yu (2020). [Stable discovery of interpretable subgroups via calibration in causal studies (staDISC).](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427) International Statistical Review ([code](https://github.com/Yu-Group/stadisc)) (PCS case study for causal inference)
1. X. Li, T. M. Tang, X. Wang, J. A. Kocher, B. Yu (2020). [A stability-driven protocol for drug response interpretable prediction (staDRIP)](https://arxiv.org/abs/2011.06593). NeurISP workshop on ML4H (Machine learning for Health) Extended Abstract.
1. A. Y. Odisho, B. Park, N. Altieri, J. DeNero, M. R Cooperberg, P. R .Carroll, B. Yu (2020). [Natural language processing systems for pathology parsing in limited data environments with uncertainty estimation.](https://academic.oup.com/jamiaopen/article/3/3/431/5922788) JAMIA Open.
1. L. Reiger, J. W. Murdoch, S. Singh, B. Yu (2020). [Interpretations are Useful: Penalizing Explanations to Align Neural Networks with Prior Knowledge](https://proceedings.icml.cc/static/paper_files/icml/2020/992-Paper.pdf). ICML Proceedings. ([code](https://github.com/laura-rieger/deep-explanation-penalization))
1. C. Singh, W. Ha, F. Lanusse, V. Boehm, J. Liu, B. Yu (2020). [Transformation Importance with Applications to Cosmology](https://arxiv.org/pdf/2003.01926.pdf) ICLR Workshop paper. ([code](https://github.com/csinva/transformation-importance))
1. N. Altieri, R. Barter, J. Duncan, R. Dwivedi, K. Kumbier, X. Li, R. Netzorg, B. Park, C. Singh*, Y. Tan, T.Tang, Y. Wang, C. Zhang, B. Yu*. (2020) [Curating a COVID-19 data repository and forecasting county-level death counts in the United States.](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1) Harvard Data Science Review ([code](https://github.com/Yu-Group/covid19-severity-prediction)) [7-day prediction results](https://covidseverity.com/) [Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4)
1. B. Yu and K. Kumbier (2020) [Veridical data science](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf) (PCS framework), PNAS. 117 (8), 3920-3929. [QnAs with Bin Yu.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf)
1. R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) [Sharp Analysis of Expectation-Maximization for Weakly Identifiable Mixture Models](https://arxiv.org/abs/1902.00194) AISTATS.
1. R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) [Singularity, Misspecification and the Convergence Rate of EM](https://arxiv.org/abs/1810.00828) Annals of Statistics.
1. Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients,](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, [arXiv](https://arxiv.org/abs/1905.12247)
1. R. Dwivedi, Y. Chen, M. J. Wainwright and B. Yu (2019) [Log-concave Sampling: Metropolis Hastings Algorithms are Fast](http://jmlr.org/papers/v20/19-306.html) JMLR.
1. D. Rothenhäusler and B. Yu (2019). [Incremental causal effects](https://arxiv.org/abs/1907.13258).
1. Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes](http://jmlr.org/papers/v19/18-158.html). JMLR . http://jmlr.org/papers/v19/18-158.html
1. Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2020) [Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier](https://ieeexplore.ieee.org/abstract/document/8262876/) Allerton Conference 2017 https://ieeexplore.ieee.org/abstract/document/8262876/
1. W. J. Murdoch, C. Singh, K. Kumbier, R. Abbasi-Asl, and B. Yu* (2019) [Definitions, methods, and applications in interpretable machine learning.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) PNAS, 116 (44) 22071-22080.
1. W. J. Murdoch, C. Sign, and B. Yu (2019). [Hierarchical interpretations for neural network predictions.](https://openreview.net/pdf?id=SkEqro0ctQ) ICLR. ([code](https://github.com/csinva/hierarchical-dnn-interpretations))
1. Y. Wang, S. Wu and B. Yu (2020) [Unique Sharp Local Minimum in l1-minimization Complete Dictionary Learning.](https://jmlr.org/papers/volume21/19-169/19-169.pdf) JMLR. 21(63), pp. 1-52. Also at https://arxiv.org/abs/1902.08380
1. Y. Chen, R. Abbasi-Asl, A. Bloniarz, M. Oliver, B. Willmore, J. Gallant*, and B. Yu* (2018) [The DeepTune framework for modeling and characterizing neurons in visual cortex area V4](https://www.biorxiv.org/content/10.1101/465534v1) https://www.biorxiv.org/content/10.1101/465534v1
1. K. Kumbier, S. Sumanta, J. B. Brown, S. Celniker, and B. Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
1. Y. Chen C. Jin, and B. Yu (2018) [Stability and Convergence Trade-off of Iterative Optimization Algorithms.](https://arxiv.org/abs/1804.01619) https://arxiv.org/abs/1804.01619
1. J. Murdoch, P. Liu, and B. Yu (2018) [Beyond word importance: contextual decomposition to extract interactions from LSTMs.](https://arxiv.org/abs/1801.05453) Proc. ICLR 2018. [https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code)](https://github.com/csinva/hierarchical-dnn-interpretations)
1. R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309) https://arxiv.org/abs/1801.02309.
1. Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) [Fast MCMC sampling algorithms on polytopes](https://arxiv.org/abs/1710.08165) https://arxiv.org/abs/1710.08165.
1. B. Yu and K. Kumbier (2018) [Artificial Intelligence and Statistics](https://www.stat.berkeley.edu/~binyu/ps/papers2018/AI+Stat18.pdf) Frontiers of Information Technology and Electronic Engineering. 19(1), 6-9.
1. R. Abbasi-Asl and B. Yu (2017) [Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning](https://arxiv.org/abs/1705.07356) https://arxiv.org/abs/1705.07356
1. R. Abbasi-Asl and B. Yu (2017) [Interpreting Convolutional Neural Networks Through Compression.](https://arxiv.org/abs/1711.02329) NIPS 2017. Symposium on Interpretable Machine Learning. (also https://arxiv.org/abs/1711.02329)
1. S. Kunzel, J. Sekhon, P. Bickel, and B. Yu* (2019) [Meta-learners for Estimating Heterogeneous Treatment Effects using Machine Learning,](https://www.pnas.org/content/116/10/4156) PNAS. 116 (10) 4156-4165.  https://arxiv.org/abs/1706.03461. [(code](https://github.com/soerenkuenzel/hte))
1. S. Basu, K. Kumbier, J. B. Brown*, and B. Yu* (2018) [iterative Random Forests to discover predictive and stable high-order interactions](https://www.stat.berkeley.edu/~binyu/ps/papers2018/iRF+SI18.pdf) PNAS, 115 (8), 1943-1948. ([code](https://github.com/Yu-Group/iterative-Random-Forest)) (PCS related)
1. S. Balakrishnan, M. Wainwright, B. Yu (2017) [Statistical Guarantees for the EM algorithm: from population to sample-based analysis.](https://www.stat.berkeley.edu/~binyu/ps/papers2017/EM17.pdf) Annals of Statistics, 45(1), 77 - 120.
1. R. Barter and B. Yu (2017) [Superheat: An R package for creating beautiful and extendable heatmaps for visualizing complex data](https://www.stat.berkeley.edu/~binyu/ps/papers2017/superheat17.pdf) JCGS (revised). https://github.com/rlbarter/superheat
1. H. Liu and B. Yu (2017) [Comments on: High-dimensional simultaneous inference with the bootstrap by Dezeure et al](https://www.stat.berkeley.edu/~binyu/ps/papers2017/LiuYu-test17.pdf) Test. 26: 740-750.
1. C. Carson et al (2016). [UC Berkeley Data Science Planning Initiative Faculty Advisory Board (FAB) Report.](https://www.stat.berkeley.edu/~binyu/ps/FAB2016.pdf) [FAB Report Executive Summary](https://www.stat.berkeley.edu/~binyu/ps/FAB-Summary2016.pdf)
1. S. Wu and B. Yu (2018). [Local identifiability of l1-minimization dictionary learning: a sufficient and almost necessary condition.](https://www.stat.berkeley.edu/~binyu/ps/papers2018/local-iden18.pdf) JMLR. 18, 1 - 56.
1. K. Rohe, T. Qin and B. Yu* (2016). [Co-clustering directed graphs to discover asymmetries and directional communities.](http://www.pnas.org/content/113/45/12679.full.pdf?with-ds=yes) Proc. National Academy of Sciences (PNAS), 113(45), 12679 - 12684.
1. R. E. Kass, B. S. Caffo, M. Davidian, X. Meng, B. Yu, Nancy Reid* (2016). [Ten simple rules for effective statistical practice.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/Ten-Simple-Rules.pdf) PLoS Comput. Biol., 12(6): e1004961. doi:10.1371/journal.pcbi.1004961
1. Siqi Wu, Antony Joseph, Ann S. Hammonds, Susan E. Celniker, Bin Yu*, and Erwin Frise* (2016). [Stability-driven nonnegative matrix factorization to interpret spatial gene expression and build local gene networks (with support information).](https://www.stat.berkeley.edu/~binyu/ps/papers2016/staNMF+SI.pdf) PNAS, pp. 4290 - 4295. ([code](https://github.com/yu-group/stanmf)) (PCS related)
1. A. Bloniarz, C. Wu, B. Yu, A. Talwalkar (2016). [Supervised neighborhoods for distributed nonparametric regression.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/AISTATS16.pdf) Proc. of AISTATS, Barcelona, Spain.
1. B. Yu (2015). [Data wisdom for data science.](http://www.odbms.org/2015/04/data-wisdom-for-data-science/) Operational Database Management Systems (ODBMS.ORG).
1. A. Bloniarz, H. Liu, C. Zhang, J. Sekhon, and B. Yu* (2015). [Lasso adjustments of treatment effect estimates in randomized experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/lasso-adj+SI16.pdf) PNAS. 113, 7383 - 7390.
1. P. Ma, M. W. Mahoney and B. Yu (2015). [A Statistical Perspective on Algorithmic Leveraging.](https://www.stat.berkeley.edu/~binyu/ps/papers2015/MaMahoneyYu2015.pdf) Journal of Machine Learning Research, 16, (2015), 861-911.
1. T. Moon, Y. Wang, Y. Liu, and B. Yu (2015). [Evaluation of a MISR-based high-resolution aerosol retrieval method using AERONET DRAGON campaign data.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=7047927) IEEE Transactions on Geoscience and Remote Sensing, 53, 4328-4339.
1. B. Yu (2014). [Let us own data science.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/IMS-pres-address14-yu.pdf) [video](https://www.youtube.com/watch?v=92OjsYQJC1U) [IMS Bulletin](http://bulletin.imstat.org/2014/10/ims-presidential-address-let-us-own-data-science/) Institute of Mathematical Statistics (IMS) Presidental Address, ASC-IMS Joint Conference, Sydney, July, 2014.
1. G. Schiebinger, M. J. Wainwright and B. Yu (2014). [The geometry of kernelized spectral clustering.](http://arxiv.org/pdf/1404.7552v3.pdf) Annals of Statistics, 43, 819-846.
1. L. Miratrix, J. Jia, B. Yu, B. Gawalt, L. El Ghaoui, L. Barnesmoore, S. Clavier (2014). [Concise comparative summaries (CCS) of large text corpora with a human experiment.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/CCS14.pdf) Ann. Applied Statist., 8, 499-529.
1. Y. Benjamini and B. Yu (2014). [The shuttle estimator for explainable variance in fMRI experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/BenjaminiY12.pdf) Annals of Applied Statistics, 7, 2007-2033.
1. D. Bean, P. Bickel, N. El Karoui and B. Yu (2014). [Optimal M-estimation in high-dimensional regression.](http://www.pnas.org/content/early/2013/08/08/1307845110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1456314568.
1. N. El Karoui, D. Bean, P. Bickel, C. Lim, and B. Yu (2014). [On robust regression with high-dimensional predictors.](http://www.pnas.org/content/early/2013/08/15/1307842110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1455714562.
1. P. Ma, M. W. Mahoney, B. Yu (2014). [A Statistical Perspective on Algorithmic Leveraging.](http://arxiv.org/abs/1306.5362) Proc. of International Conference on Machine Learning (ICML) (This conference paper contains some of preliminary results of the journal submission Ma et al. (2015))
1. A. Bloniarz, A. Talwalkar, J. Terhorst, M. Jordan, D. Patterson, B. Yu and Y. Song (2014). [Changepoint Analysis for Efficient Variant Calling.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/Bloniarzetal14.pdf) Proc. of RECOMB 2014 (to appear).
1. Tao Shi (2013), [A conversation with Professor Bin Yu](http://www.yufamily.org/src/ShiTao_AnInterviewWithProfessorBinYu.php?xref=YuFamily_YuBin_interview_cn) International Chinese Statistical Association (ICSA) Bulletin, Vol 25, Issue 2, pp 85-98. ([Selected Parts in Statblogs](http://www.statsblogs.com/2013/07/09/a-conversation-with-professor-bin-yu/))
1. A. Joseph and B. Yu (2016). [The impact of regularization on spectral clustering.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/reg-spectral16.pdf) Annals of Statistics. 4, 1765 - 1791.
1. C. Lim and B. Yu (2016). [Estimation Stability with Cross Validation (ESCV)](https://www.stat.berkeley.edu/~binyu/ps/papers2016/ESCV16.pdf) Journal of Computational and Graphical Statistics. 25, 464 - 492. (First paper towards PCS)
1. A. S. Hammonds, C. A. Bristow, W. W. Fisher, R. Weiszmann, S. Wu, V. Hartenstein, M. Kellis, B. Yu, E. Frise, and S. E. Celniker (2013). [Spatial expression of transcription factors in Drosophila embryonic organ development.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Hammondsetal13.pdf) Genome Biology, 14(12), R140.
1. H. Liu and B. Yu (2013). [Asymptotic properties of Lasso+mLS and Lasso+Ridge in sparse high-dimensional linear regression.](https://www.stat.berkeley.edu/~binyu/ps/LassoOLSBootstrap13.pdf) Electron. J. Statist., 7, 312-3169.
1. J. Mairal and B. Yu (2013). [Supervised Feature Selection in Graphs with Path Coding Penalties and Network Flows.](http://jmlr.org/papers/v14/mairal13a.html) Journal of Machine Learning Research, 14, 2449-2485.
1. Y. Wang, X. Jiang, B. Yu, M. Jiang (2013). [A Hierarchical Bayesian Approach for Aerosol Retrieval Using MISR Data.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/WangJiangYuJiang2013.pdf) J. American Statistical Association, 108, 483-493.
1. Y. He, J. Jia and B. Yu (2013). [Reversible MCMC on Markov equivalence classes of sparse directed acyclic graphs.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/rev-MCMC13.pdf) Annals of Statistics, 41(4), 1742-1779.
1. B. Yu (2013). [Stability.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Yu13.pdf) Bernoulli, 19 (4), 1484-1500. (Invited paper for the Special Issue commemorating the 300th anniversary of the publication of Jakob Bernoullis Ars Conjectandi in 1712) (Begining of PCS)
1. J. Mairal and B. Yu (2013). Discussion on Grouping Strategies and Thresholding for High Dimensional Linear Models Journal of Statistical Planning and Inference, 143, 1451-1453.
1. C. Uhler, G. Raskutti, and P. Buhlmann and B. Yu (2013). [Geometry of faithfulness assumption in causal inference.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/faithfulness13.pdf) Annals of Statistics, 41, 436-463.
1. L. Miratrix, J. Sehkon, and B. Yu (2013). [Adjusting Treatment Effect Estimates by Post-Stratification in Randomized Experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/post-stratification13.pdf) Journal of Royal Statistical Society, Series B, 75 (part 2), 369-396.
1. J. Jia, K. Rohe and B. Yu (2013) [The Lasso under Poisson-like Heteroscadecity.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/lasso-poisson13.pdf) Statistica Sinica, 23, 99-118.
1. S. Negahban, P. Ravikumar, M. Wainwrigt, and B. Yu (2012) [A unified framework for high-dimensional analysis of M-estimators with decomposable regularizers.](https://www.stat.berkeley.edu/~binyu/ps/unified-797.pdf) Statistical Science, 27, 538-557.
1. G. Raskutti, M. Wainwrigt, and B. Yu (2012) [Minimax-optimal rates for sparse additive models over kernel classes via convex programming.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/RaskuttiWY12.pdf) J. Machine Learning Research, 13, 389-427.
1. J. Mairal and B. Yu (2012). [Complexity analysis of the Lasso regularization path.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/MairalY12.pdf) Proc. of International Conference on Machine Learning (ICML).
1. Yanfeng Gu, Shizhe Wang, Tao Shi, Yinghui Lu, Eugene E. Clothiaux, and Bin Yu (2012). [Multiple-kernel learning-based unmixing algorithm for estimation of cloud fractions with MODIS and CLOUDSAT data.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GuWSLCY12.pdf) Proc. of IEEE International Geoscience and Remote Sensing Symposium (IGRSS).
1. S. Nishimoto, A. T. Vu, T. Naselaris, Y. Benjamini, B. Yu, J. L. Gallant (2011). [Reconstructing visual experiences from brain activity evoked by natural movies.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/NishimotoVNBYG11.pdf) Current Biology, 21(19), 1641-1646. [related videos](https://sites.google.com/site/gallantlabucb/publications/nishimoto-et-al-2011)
1. P. Ravikumar, M. Wainwright, G. Raskutti, B. Yu (2011). [High-dimensional covariance estimation by minimizing l1-penalized log-determinant divergence.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RavikumarWRY11.pdf) Electronic Journal of Statistics, 5, 935-980.
1. G. Raskutti, M. Wainwright, B. Yu (2011). [Minimax rates of estimation for high-dimensional linear regression over lq-balls.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RaskuttiWainwrightYu2011.pdf) IEEE Trans. Inform. Th., 57(10), 6976-6994.
1. K. Rohe, S. Chatterjee, and B. Yu (2011). [Spectral clustering and the high-dimensional Stochastic Block Model.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RoheCY11.pdf) Annals of Statistics, 39 (4), 1878-1915
1. V. Q. Vu, P. Ravikumar, T. Naselaris, K. N. Kay, J. L. Gallant, B. Yu* (2011). [Encoding and decoding V1 fMRI responses to natural images with sparse nonparametric models.](http://arxiv.org/pdf/1104.2805.pdf) Annals of Applied Statistics, 5, 1150-1182. (*First senior author as last author in biology tradition)
1. S. N. Pakzad, G. Rocha, and B. Yu (2011). Distributed modal identification by regularized auto regressive models. International Journal of Systems Science, 42, 1473-1489.
1. J. Yousafzai, P. Sollich, Z. Cvetkovic, and B. Yu (2011). [Combined Features and Kernel Design for Robust Phoneme Classification Using Support Vector Machines.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=5618550) IEEE Trans. Audio, Speech and Language Processing (to appear). 64.
1. X. Dai, J. Jia, B. Yu, El Ghaoui (2011) [SBA-term: Sparse Bilingual Association for terms.](http://www.eecs.berkeley.edu/~elghaoui/Pubs/icsc2011.pdf) Proc. International Conference on Semantic Computing.
1. B. Yu (2011). [Asymptotics and Coding Theory: One of the n - 1 Dimensions of Terry.](http://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/Yu11.pdf) In Selected Works of Terry Speed (ed. S. Duoit), pp. 33-36, Springer.
1. B. Yu (2010). [Remembering Leo.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/Yu10.pdf) Annals of Applied Statistics, 4(4), 1657-1659.
1. J. Jia, Y. Benjamini, C. Lim, G. Raskutti, B. Yu (2010). [Comment on "Envelope models for parsimonious and efficient multivariate linear regression" by R. D. Cook, B. Li, and F. Chiaromonte.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaBLRY10.pdf) Statistica Sinica, 20, 961-967.
1. G. Raskutti, M. Wainwrigt, and B. Yu (2010) [Restricted Eigenvalue Properties for Correlated Gaussian Designs.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/RaskuttiWY10.pdf) Journal of Machine Learning Research, 11, 2241-2259.
1. J. Jia and B. Yu (2010). [On model selection consistency of elastic net when p >>n.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaY10.pdf) Statistica Sinica, 10, 595-611.
1. P. Buhlmann and B. Yu (2010). [Boosting.](http://onlinelibrary.wiley.com/doi/10.1002/wics.55/abstract) Wiley Interdisciplinary Reviews: Computational Statistics, 2, 69-74.
1. L. Huang, J. Jia, B. Yu, B. Chun, P. Maniatis, M. Naik (2010). [Predicting Execution Time of Computer Programs Using Sparse Polynomial Regression.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HuangJYCMN10.pdf) Proc. NIPS 2010.
1. Y. Han, F. Wu, J. Jia, Y. Zhuang and B. Yu (2010). [Multi-task Sparse Discriminant Analysis (MtSDA) with Overlapping Categories.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HanWJZY10.pdf) Proc. of The 24th AAAI Conference on Artificial Intelligence, July 11-15, Atlanta, GA.
1. B. Gawalt, J. Jia, L. Miratrix, L. El Ghaoui, B. Yu, and S. Clavier (2010). [Discovering Word Associations in News Media via Feature Selection and Sparse Classification.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GawaltJMGYC10.pdf) Proc. 11th ACM SIGMM International Confernece on Multimedia Information Retrieval (MIR).
1. E. Anderes, B. Yu, V. Jovanovic, C. Moroney, M. Garay, A. Braverman, E. Clothiaux (2009) [Maximum Likelihood Estimation of Cloud Height from Multi-Angle Satellite Imagery.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/AnderesYJMGBC09.pdf) Annals of Applied Statistics, 3, 902-921
1. T. Shi, M. Belkin, and B. Yu, (2009) [Data Spectroscopy: Eigenspace of Convolution Operator and Clustering](https://www.stat.berkeley.edu/~binyu/ps/shi.aos09.pdf) Annals of Statistics, 37 (6B), 3960-3984.
1. Vincent Q. Vu, Bin Yu, Robert E. Kass (2009) [Information In The Non-Stationary Case](https://www.stat.berkeley.edu/~binyu/ps/papers2009/VuYK09.pdf) Neural computation 21, 688-703.
1. N. Meinshausen and B. Yu (2009). [Lasso-type recovery of sparse representations for high-dimensional data.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/MeinshausenY09.pdf) Annals of Statistics 37, 246-270.
1. P. Zhao, G. Rocha, and B. Yu (2009). [The composite absolute penalties family for grouped and hierarchical variable selection](https://www.stat.berkeley.edu/~binyu/ps/papers2009/ZhaoRY09.pdf) Annals of Statistics 37, 3468-3497. (An earlier version 'appeared as Grouped and hierarchical model selection through composite absolute penalties' by P. Zhao, G. Rocha and B. Yu, Department of Statistics, UC Berkeley, Tech. Rep 703.)
1. S. Negahban, P. Ravikumar, M. Wainwright, and B. Yu (2009). [A unified framework for high-dimensional analysis of $M$-estimators with decomposable regularizers](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/NegahbanRWY09.pdf) Proc. NIPS, 2009. (This conference paper contains preliminary results of the journal submission Negahban et al. 2012).
1. G. Raskutti, M. Wainwright, B. Yu (2009) [High-dimensional regression under lq-ball sparsity: Optimal rates of convergence.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09b.pdf) Proc. of Allerton Conference on Communication, Control, and Computing. (This conference paper contains some of preliminary results of the journal submission Ravikumar et al. 2011).
1. G. Raskutti, M. Wainwrigt, and B. Yu (2009) [Lower bounds on minimax rates for nonparametric regression with additive sparsity and smoothness.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09a.pdf) Proc. NIPS, 2009. (This conference paper contains some of preliminary results of the journal submission Ravikumar et al. 2011).
1. T. Shi, B. Yu, E. Clothiaux, and A. Braverman (2008). [Daytime Arctic Cloud Detection based on Multi-angle Satellite Data with Case Studies.](https://www.stat.berkeley.edu/~binyu/ps/jasa_resub.pdf) Journal of American Statistical Association. 103( 482), 584-593.
1. Peter Buhlmann and Bin Yu (2008) Invited discussion on "Evidence contrary to the statistical view of boosting (D. Mease and A. Wyner)". [(paper with discussion) ](https://www.stat.berkeley.edu/~binyu/ps/Mease08a_with_discussion.pdf) Journal of Machine Learning Research 9, 187-194.
1. P. Ravikumer, V. Vu, B. Yu, T. Naselaris, K. Kay, J. Gallant (2008). [Nonparametric sparse hiearchical models describe V1 fMRI responses to natural images](https://www.stat.berkeley.edu/~binyu/ps/rocha.pseudo.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008). (This conference paper contains some preliminary results of journal paper Vu et al. (2011) on encoding models, but also contains an encoding model that is not in Vu et al. (2011). It does not contain decoding results.)
1. P. Ravikumar, G. Raskutti, M. Wainwright, B. Yu (2008) [Model selection in Gaussian graphical models: high-dimensional consistency of l1-regularized MLE.](https://www.stat.berkeley.edu/~binyu/ps/covsel.nips08.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
1. T. Shi, M. Belkin, and B. Yu (2008). [Data spectroscopy: learning mixture models using eigenspaces of convolution operators.](https://www.stat.berkeley.edu/~binyu/ps/ICML08.pdf) Proc. of ICML 2008.
1. M. Ager, Z. Cvetkovic, P. Pollich, and B. Yu (2008). [Towards Robust Phoneme Classification Augmentation of PLP Models with Acoustic Waveforms.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=7080758) Proceedings of EUSIPCO.
1. J. Yousafzai, Z. Cvetković, P. Pollich, and B. Yu (2008). [Combined PLP-Acoustic Waveform Classification for Robust Phoneme Recognition using Support Vector Machines.](http://www.eurasip.org/Proceedings/Eusipco/Eusipco2008/papers/1569105546.pdf) Proceedings of EUSIPCO.
1. N. Meinshausen, G. Rocha, and B. Yu (2007). [A tale of three cousins: Lasso, L2Boosting, and Danzig](https://www.stat.berkeley.edu/~binyu/ps/aos.dis07.pdf) Annals of Statistics (invited discussion on Candes and Tao's Danzig Selector paper)
1. V. Vu, B. Yu, and R. Kass (2007). [Coverage Adjusted Entropy Estimation.](https://www.stat.berkeley.edu/~binyu/ps/entropy.sub.pdf) Statistics and Medicine, 26(21), 4039-4060.
1. B. Yu (2007). [Embracing Statistical Challenges in the Information Technology Age](https://www.stat.berkeley.edu/~binyu/ps/embracing.pdf) Technometrics (special issue on statistics and information technologies). vol. 49 (3), 237-248.
1. X. Jiang, Y. Liu, B. Yu and M. Jiang (2007). [Comparison of MISR aerosol optical thickness with AERONET measurements in Beijing metropolitan area.](https://www.stat.berkeley.edu/~binyu/ps/xin.pdf) Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol. 107, pp. 45-53.
1. T. Shi, E. E. Clothiaux, B. Yu, A. J. Braverman, and G. N. Groff (2007). [Detection of Daytime Arctic Clouds using MISR and MODIS Data.](https://www.stat.berkeley.edu/~binyu/ps/misr-modis.pdf) Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol. 107, pp. 172-184.
1. Peng Zhao and Bin Yu (2006). [On Model Selection Consistency of Lasso.](https://www.stat.berkeley.edu/~binyu/ps/LassoConsi.pdf) J. Machine Learning Research, 7 (nov), 2541-2567.
1. B. Yu (2006). [Comments on: Monitoring networked applications with incremental quantile estimation by Chambers et al.](http://arxiv.org/pdf/0708.0338.pdf) Statist. Sci., 21, 483-485.
1. B. Yu (2006). [Comments on: Regularization in Statistics, by P. J. Bickel and B. Li.](https://www.stat.berkeley.edu/~binyu/ps/test06.pdf) Test, vol. 15 (2), pages 314-316.
1. P. Buhlmann and B. Yu (2006). [Sparse Boosing](https://www.stat.berkeley.edu/~binyu/ps/rev.pdf) Journal of Machine Learning Research ( 7 (June), 1001-1024). This is a shortened and more focused version of Buhlmann and Yu "Boosting, Model Selection, Lasso and Nonnegative Garotte" given below.
1. J. Gao, H. Suzuki, and B. Yu (2006). [Approximation Lasso Methods for Language Modeling.](https://www.stat.berkeley.edu/~binyu/ps/acl.06.pdf) Proceedings of the 21st International Conference on Computational Linguistics and 44th Annual Meeting of the ACL, pp. 225-232, Sydney.
1. T. Shi and B. Yu (2005). [Binning in Gaussian Kernel Regularization.](https://www.stat.berkeley.edu/~binyu/ps/binning.final.pdf) Statistica Sinica (special issue on machine learning), 16, 541-567.
1. G. Liang, N. Taft, and B. Yu (2005). [A fast lightweight approach to origin-destination IP traffic estimation using partial measurements.](https://www.stat.berkeley.edu/~binyu/ps/pamtram.final.pdf) Tech Report 687, Statistics Department, UCB (accepted for Special Issue of IEEE-IT and ACM Networks on data networks, Jan. 2006)
1. Tong Zhang and B. Yu (2005). [Boosting with early stopping: convergence and consistency.](https://www.stat.berkeley.edu/~binyu/ps/zhang.final.ps) The Annals of Statistics. Vol. 33, 1538-1579.
1. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2005) [Network tomography: recent developments.](http://nowak.ece.wisc.edu/StatSci04.pdf) Statistical Science, 19, 499-517.
1. C. D. Giurcaneanu and B. Yu (2005). [Efficient algorithms for discrete universal denoising for channels with memeory.](https://www.stat.berkeley.edu/~binyu/ps/isit05.pdf) Proceedings of International Symposium on Information Theory, Australia. (Also as Tech. Report 686, Statistics Department, UCB (Proc. ISIT, Sept. 2005))
1. P. Zhao and B. Yu (2004). [Stagewise Lasso (old title: Boosted Lasso)](https://www.stat.berkeley.edu/~binyu/ps/StagewiseLasso.pdf) Journal of Machine Learning Research, 8, 2701-2726. (An earlier version appeared as Tech. Report #678, Statistics Department, UC Berkeley (December, 2004; revised in April, 2005)
1. D. J. Diner et al (2004). [PARAGON: A Systematic, Integrated Approach to Aerosol Observation and Modeling.](https://www.stat.berkeley.edu/~binyu/ps/paragon.pdf) American Meterological Society, Oct., 1491-1501.
1. P. Buhlmann and B. Yu (2004). [Discussion on three boosting papers by Jiang, Lugosi and Vayatis, and Zhang](https://www.stat.berkeley.edu/~binyu/ps/disc2.ps) Annals of Statistics. 32 (1): 96-101.
1. R. Jorsten and B. Yu (2004). [Compressing genomic and proteomic array images for statistical analyses.](https://www.stat.berkeley.edu/~binyu/ps/sig.chapter.ps) Invited chapter in a book on Genomic signal processing and statistics, edited by E. R. Dougherty, I. Shmulevich, J. Chen, and Z. J. Wang, pp. 341 - 366.
1. G. Liang, B. Yu, and N. Taft (2004). [Maximum entropy models: convergence rates and application in dynamic system monitoring.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=1365207&sortType%3Dasc_p_Sequence%26filter%3DAND%28p_IS_Number%3A29909%29%26pageNumber%3D4%26rowsPerPage%3D50) International Symposium on Information Theory, Chicago.
1. R. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2003). [Internet Tomography: Recent Developments](https://www.stat.berkeley.edu/~binyu/ps/cny.pdf) Statistical Science. Vol. 19(3), 499-517.
1. G. Liang and B. Yu (2003). [Maximum Pseudo Likelihood Estimation in Network Tomography.](https://www.stat.berkeley.edu/~binyu/ps/pseudo-ieee.ps) IEEE Trans. on Signal Processing (Special Issue on Data Networks). 51(8), 2043-2053
1. Rebecka Jornsten and Bin Yu (2003). [Simultaneous Gene Clustering and Subset Selection for Classification via MDL.](https://www.stat.berkeley.edu/~binyu/ps/bioinformatics.ps) Bioinformatics. 19(9): 1100-1109.
1. Peter Buhlmann and Bin Yu (2003). [Boosting with the L2 Loss: Regression and Classification.](https://www.stat.berkeley.edu/~binyu/ps/boostingl2.ps) J. Amer. Statist. Assoc. 98, 324-340.
1. R. Jornsten, W. Wang, B. Yu, and K. Ramchandran (2003). [Microarray image compression: SLOCO and the effects of information loss.](https://www.stat.berkeley.edu/~binyu/ps/spj.ps) Signal Processing Journal (Special Issue on Genomic Signal Processing). 83, 859-869.
1. G. Liang and B. Yu (2003). [Pseudo Likelihood Estimation in Network Tomography.](http://infocom2003.ieee-infocom.org/papers/51_03.PDF) Proceedings of of Infocom, San Francisco.
1. Peter Buhlmann and Bin Yu (2002). [Analyzing Bagging.](https://www.stat.berkeley.edu/~binyu/ps/bagging.ps) Annals of Statistics vol. 30, 927-961.
1. R. Jornsten, M. Hansen, and B. Yu (2002). Adaptive Minimum Description Length (MDL) criteria with applications to microarray data. In Advances in Minimum Description Length: Theory and Applications, edited by P. Grunwald, I.J. Myung and M.A. Pitt. The MIT Press, pp. 295-321.
1. Mark Hansen and Bin Yu (2002). [Minimum Description Length Model Selection Criteria for Generalized Linear Models.](https://www.stat.berkeley.edu/~binyu/ps/mdl_glm.ps){\em Science and Statistics: Festschrift for Terry Speed}, IMS Lecture Notes -- Monograph Series, Vol. 40.
1. Rebecka Jornsten, and Bin Yu (2002). [Multiterminal Estimation: Extensions and a Geometric interpretation.](https://www.stat.berkeley.edu/~binyu/ps/isit02.ps) Proceedings of International Symposium on Information Theory (ISIT), June, 2002.
1. Gerald Schuller, Bin Yu, Dawei Huang, and Bern Edler (2002). [Perceptual Audio Coding using Pre- and Poster- Filters and Lossless Compression.](https://www.stat.berkeley.edu/~binyu/ps/coding.ps) IEEE Trans. Speech and Audio Processing. Vol. 10 (6), 379-390
1. Mark Coates, Alfred Hero, Robert Nowak, and Bin Yu (2002). [Internet Tomography.](https://www.stat.berkeley.edu/~binyu/ps/spmag.ps) Signal Processing Magazine. vol. 19, No. 3 (May issue), 47-65.
1. M. Hansen and B. Yu (2001). [Model selection and the principle of Minimum Description Length.](https://www.stat.berkeley.edu/~binyu/ps/mdl.ps) Journal of American Statistical Association. 96, 746-774.
1. Jin Cao, Drew Davis, Scott Vander Wiel and Bin Yu (2000). [[ PDF ](https://www.stat.berkeley.edu/~binyu/Site/ps/net.pdf)| [Time-varying network tomography: router link data.](https://www.stat.berkeley.edu/~binyu/ps/net.ps) J. Amer. Statist. Assoc. vol. 95, 1063-1075.
1. Peter Buhlmann and Bin Yu (2000a). [Discussion. Additive logistic regression: a statistical view of boosting, by Friedman, J., Hastie, T. and Tibshirani, R.](https://www.stat.berkeley.edu/~binyu/ps/disc.ps) Annals of Statistics. Vol. 28, 377-386
1. Mark Hansen and Bin Yu (2000). [Wavelet thresholding via MDL for natural images.](https://www.stat.berkeley.edu/~binyu/ps/lmdl.ps) IEEE Trans. Inform. Theory (Special Issue on Information Theoretic Imaging). vol. 46, 1778-1788.
1. Jorma Rissanen and Bin Yu (2000). [Coding and compression: a happy union of theory and practice.](https://www.stat.berkeley.edu/~binyu/ps/vig.ps) J. Amer. Statist. Assoc. (Year 2000 Commemorative Vignette on Engineering and Physical Sciences). vol. 95, 986-988.
1. Lei Li and Bin Yu (2000). [Iterated logarithm expansions of the pathwise code lengths for exponential families.](https://www.stat.berkeley.edu/~binyu/ps/pred.ps) IEEE Trans. Inform. Theory. vol. 46, 2683-2689.
1. G. Chang, B. Yu and M. Vetterli (2000). [Adaptive wavelet thresholding for image denoising and compression.](https://www.stat.berkeley.edu/~binyu/ps/jMDLQ.ps) IEEE Trans. Image Processing, vol. 9, 1532-1546.
1. G. Chang, B. Yu and M. Vetterli (2000). [Spatially adaptive wavelet thresholding based on context modeling for image denoising.](https://www.stat.berkeley.edu/~binyu/ps/spatThr.ps) IEEE Trans. Image Processing, vol. 9, 1522-1531.
1. G. Chang, B. Yu and M. Vetterli (2000). [Wavelet thresholding for multiple noisy image copies.](https://www.stat.berkeley.edu/~binyu/ps/mt.ps) IEEE Trans. Image Processing, vol. 9, 1631-1635.
1. Y. Yoo, A. Ortega, and B. Yu (1999). [Image subband coding using context-based classification and adaptive quantization.](https://www.stat.berkeley.edu/~binyu/ps/yoo.ps) IEEE Trans. Image Processing, vol. 8, 1702-1215.
1. B. Yu, M. Ostland, P. Gong and R. Pu (1999). Penalized discriminant analysis of in situ hyperspectral data for conifer species recognition. IEEE Trans. Geoscience and Remote Sensing, in press.
1. A. Barron, J. Rissanen, and B. Yu (1998). The Minimum Description Length principle in coding and modeling. (Special Commemorative Issue: Information Theory: 1948-1998) IEEE. Trans. Inform. Th., 44, 2743-2760. Reprinted in Information 50 Years of Discovery, Theory: S. Verdu and S. McLaughlin (eds), IEEE Press , 1999.
1. B. Yu and P. Mykland (1998). Looking at Markov samplers through cusum path plots: a simple diagnostic idea. Statistics and Computing , 8, 275-286.
1. P. Gong, R. Pu and B. Yu (1998) Conifer species recognition: effects of data transformation and band width (in Chinese) Journal of Remote Sensing, 2(3), 211-217.
1. G. Chang, B. Yu and M. Vetterli (1998). [Spatially adaptive wavelet thresholding for image denoising.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=862630) Proceedings of IEEE International Conference on Image Processing, October, Chicago.
1. S. G. Chang, B. Yu, and M. Vetterli (1998). [Image denoising via lossy compression and wavelet thresholding.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=647985) Proceedings of International Conference on Image Processing. Santa Barbara, California, vol. 1, pp. 604-607.
1. M. Ostland and B. Yu (1997). [Exploring quasi Monte Carlo for marginal density approximation.](https://www.stat.berkeley.edu/~binyu/ps/quasiMC.pdf) Statistics and Computing, 7, 217-228.
1. P. Gong, R. Pu, and B. Yu (1997). Conifer species recognition with in Situ hyperspectral data. Remote Sensing of Environment, 62, 189-200.
1. B. Yu and T. P. Speed (1997). [Information and the clone mapping of chromosomes.](https://www.stat.berkeley.edu/~binyu/ps/clone.pdf) Ann. Statist. 25, 169-185.
1. D. Nelson, T. Speed, and B. Yu (1997). The limits of random fingerprinting. Genomics, 40, 1-12.
1. B. Yu (1997). [Assouad, Fano, and Le Cam.](https://www.stat.berkeley.edu/~binyu/ps/LeCam.pdf) Festschrift for Lucien Le Cam . D. Pollard, E. Torgersen, and G. Yang (eds), pp. 423-435, Springer-Verlag.
1. B. Yu (1996). Lower bounds on expected redundancy for nonparametric classes. IEEE Trans. on Information Theory, 42, 272-275.
1. Y. Yoo, A. Ortega, and B. Yu (1996). Adaptive quantization of image subbands with efficient overhead rate selection. In Proceedings of IEEE International Conference on Image Processing, Lausanne, Switzerland.
1. B. Yu (1996). [A Statistical analysis of adaptive scalar quantization based on quantized past data.](https://www.stat.berkeley.edu/~binyu/ps/quan.ps) In Proceedings of International Symposium on Information Theory and its Applications (ISITA96), Victoria, Canada.
1. B. Yu (1995). Comment: Extracting more diagnostic information from a single run using cusum path plot. Statist. Sci., 10, 54-58.
1. J. Rissanen and B. Yu (1995). MDL learning. In Learning and Geometry: Computational Approaches, Progress in Computer Science and Applied Logic, 14, David Kueker and Carl Smith (eds), Birkhäuser, Boston, pp. 3-19.
1. P. Mykland, L. Tierney, and B. Yu (1995). Regeneration in Markov Chain samplers. J. Amer. Statist. Assoc., 90, 233-241.
1. B. Yu (1994a). Rates of convergence for empirical processes of stationary mixing sequences. Ann. Probab. 22, 94-116.
1. M. Arcones and B. Yu (1994). Central limit theorems for empirical and U-processes of stationary mixing sequences. J. Theor. Probab. 7, 47-71.
1. B. Yu (1994). Lower bound on the expected redundancy for classes of continuous Markov sources. In Statistical Decision Theory and Related Topics V, S. S. Gupta and J. O. Berger (eds), 453-466.
1. M. Arcones and B. Yu (1994). Limit theorems for empirical processes under dependence. In Proceedings in Chaos expansions, multiple Wiener integrals and their applications. 205-221.
1. A. R. Barron, Y. Yang and B. Yu (1994). Asymptotically optimal function estimation by minimum complexity criteria. In Proceedings of 1994 International Symposium on Information Theory, pp. 38, Trondheim, Norway.
1. B. Yu and T. Speed (1993). A rate of convergence result for a universal D-semifaithful code. IEEE Trans. on Information Theory 39, 8813-820.
1. B. Yu (1993). Density estimation in the L∞ norm for dependent data with applications to the Gibbs sampler. Ann. Statist. 21, 711-735.
1. T. Speed and B. Yu (1993). Model selection and prediction: normal regression. J. Inst. Statist. Math. 45, 35-54.
1. J. Rissanen, T. Speed and B. Yu (1992). Density estimation by stochastic complexity. IEEE Trans. on Information Theory, 38, 315-323.
1. B. Yu and T. Speed (1992) Data compression and histograms. Probability Theory and Related Fields, 92, 195-229.

---

### 2025-05-17 papers/deep-learning-and-machine-learning.qmd
Initial commit.

--- 2025-05-17 papers.qmd
@@
 ---
-title: Papers
+title: "Deep Learning and Machine Learning"
 ---
 
-# Papers
+[Complete Paper List in Reverse Chronological Order](../papers.qmd)
 
-## Recent Papers by Area
+## Selected Recent Papers in Deep Learning and Machine Learning
 
-- [Deep Learning and Machine Learning](papers/deep-learning-and-machine-learning.qmd)
-- [Veridical Data Science (PCS)](papers/veridical-data-science-pcs.qmd)
-- [Interpretable Machine Learning](papers/interpretable-machine-learning.qmd)
-- [Interdisciplinary Research in Biomedicine](papers/interdisciplinary-research-in-biomedicine.qmd)
-- [Tree-based Methods](papers/tree-based-methods.qmd)
-
----
-
-## Complete List by Reverse Chronological Order
-
-*For the most up-to-date and complete list, see [Google Scholar](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en) or [arXiv](https://arxiv.org/search/?query=bin+yu&searchtype=author).*
-
-### Publications
-
-1. A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contextual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886)
-1. Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958)
-1. O. Ronen, A. I. Humayun, R. Balestriero, R. Baraniuk, B. Yu (2024). [ScaLES: Scalable Latent Exploration Score for Pre-Trained Generative Networks](https://arxiv.org/pdf/2406.09657)
-1. S. Hayou, N. Ghosh, B. Yu (2024). [The Impact of Initialization on LoRA Fineuning Dynamics.](https://arxiv.org/pdf/2406.08447)
-1. B. Yu (2024). [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (Harvard Data Science Review)
-1. S. Hayou, N. Ghosh, B. Yu (2024). [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) (Proc. ICML)
-1. C. F. Elliott, J. Duncan, T. M. Tang, M. Behr, K. Kumbier, B. Yu (2024). [Designing a data science simulation with MERITS: a primer.](https://arxiv.org/abs/2403.08971)
-1. Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). [Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986)
-1. N. R. Mallinar, A. Zane, S. Frei, B. Yu (2024). Minimum-Norm Interpolation Under Covariate Shift. (Proc. ICML) [arXiv](https://arxiv.org/pdf/2404.00522)
+1.
+A.
+R.
+Hsu, Y.
+Cherapanamjeri, A.
+Y.
+Odisho, P.
+R.
+Carroll, B.
+Yu (2024).
+[Mechanistic Interpretation through Contexual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886) [https://arxiv.org/pdf/2407.00886](https://arxiv.org/pdf/2407.00886).
+1.
+O.
+Ronen, A.
+I.
+Humayun, R.
+Balestriero, R.
+Baraniuk, B.
+Yu (2024).
+[ScaLES: Scalable Latent Exploration Score for Pre-Trained Generative Networks](https://arxiv.org/pdf/2406.09657).
+[https://arxiv.org/pdf/2406.09657](https://arxiv.org/pdf/2406.09657)
+1. S. Hayou, N. Ghosh, B. Yu (2024). [The Impact of Initialization on LoRA Fineuning Dynamics.](https://arxiv.org/pdf/2406.08447) [https://arxiv.org/pdf/2406.08447](https://arxiv.org/pdf/2406.08447)
+1.
+B.
+Yu (2024).
+[After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (discussion of Donoho's paper "Data Science at the Singularity") Harvard Data Science Review (HDSR).
+1. N. R. Mallinar, A. Zane, S. Frei, B. Yu (2024). Minimum-Norm Interpolation Under Covariate Shift. Proc. ICML. [https://arxiv.org/pdf/2404.00522](https://arxiv.org/pdf/2404.00522)
 1.
@@
 ED-Copilot: Reduce Emergency Department Wait Time with Language Model Diagnostic Assistance.
-(Proc.
-ICML) [arXiv](https://arxiv.org/abs/2402.13448)
-1. C. Singh*, A. R. Hsu*, R. Antonello, S. Jain, A. G. Huth, B. Yu, J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
-1. Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262)
+Proc.
+ICML.
+[https://arxiv.org/abs/2402.13448](https://arxiv.org/abs/2402.13448)
 1.
-Q.
-Wang*, T.
-M.
-Tang*, N.
-Youlton, C.
 S.
-Weldy, A.
-M.
-Kenney, O.
-Ronen, J.
-W.
-Hughes, E.
-T.
-Chin, S.
-C.
-Sutton, A.
-Agarwal, X.
-Li, M.
-Behr, K.
-Kumbier, C.
-S.
-Moravec, W.
-H.
-W.
-Tang, K.
-B.
-Margulies, T.
-P.
-Cappola, A.
-J.
-Buitte, R.
-Arnaout, J.
-B.
-Brown, J.
-R.
-Priest, V.
-N.
-Parikh, B.
-Yu*, E.
-Ashley* (2023).
-Epistasis regulates genetic control of cardiac hypertrophy.
-[medRxiv](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
-1.
-R.
-Cahill, Y.
-Wang, R.
-P.
-Xian, A.
-J.
-Lee, H.
-Zeng, B.
-Yu, B.
-Tasic, R.
-Abbasi-Asl (2023).
-Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology.
-[bioRxiv](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
-1.
-E.
-Irajizad, A.
-Kenney, T.
-Tang, J.
-Vykoukal, R.
-Wu, E.
-Murage, J.
-B.
-Dennison, M.
-Sans, J.
-P.
-Long, M.
-Loftus, J.
-A.
-Chabot, M.
-D.
-Kluger, F.
-Kastrinos, L.
-Brais, A.
-Babic, K.
-Jajoo, L.
-S.
-Lee, T.
-E.
-Clancy, K.
-Ng, A.
-Bullock, J.
-M.
-Genkinger, A.
-Maitra, K.
-A.
-Do, B.
-Yu, B.
-W.
-Wolpin, S.
-Hanash, J.
-F.
-Fahrmann.
-(2023).
-[A blood-based metabolomic signature predictive of risk for pancreatic cancer](https://pubmed.ncbi.nlm.nih.gov/37729870/).
-Cell Reports Medicine 4(9): 101194.
-doi: 10.1016/j.xcrm.2023.101194.
-(PCS related) ([Editorial](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10518497/))
-1. R. Dwivedi, C. Singh, B. Yu, M. Wainwright (2023). [Revisiting miniumu description length complexity in overparametrized models.](https://jmlr.org/papers/v24/21-1133.html) JMLR, 24(268): 1-59.
-1.
-K.
-Wu, Y.
-Chen, W.
-Ha, B.
-Yu (2023).
-[Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms.](https://arxiv.org/abs/2309.10301) JMLR (accepted).
-[https://arxiv.org/abs/2309.10301](https://arxiv.org/abs/2309.10301)
+Hayou, N.
+Ghosh, B.
+Yu (2024).
+[LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354).
+Proc.
+ICML.
+[https://arxiv.org/abs/2402.12354](https://arxiv.org/abs/2402.12354)
 1.
@@
 1.
-R.
-Netzorg, J.
-Li, B.
-Yu (2024).
-Improving prototypical part networks with reward reweighting, reselection, and retraining.
-Proc.
-ICML.
-[https://arxiv.org/abs/2307.03887](https://arxiv.org/abs/2307.03887)
-1.
-A.
-Agarwal, A.
-M.
-Kenny, Y.
-S.
-Tan, T.
-M.
-Tang, B.
-Yu (2023).
-MDI+: a flexible random forest-based feature importance framework.
-[https://arxiv.org/abs/2307.01932](https://arxiv.org/abs/2307.01932) (PCS related)
-1.
 A.
@@
 Yu (2023).
-Diagnosing transformers: illuminating feature space for clinical decison-making.
-Proc.
-ICLR.
+[Diagnosing transformers: illuminating feature space for clinical decison-making.](https://arxiv.org/abs/2305.17588) ICLR 2023.
 [https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)
-1.
-C.
-Singh, A.
-R.
-Hsu, R.
-Antonello, S.
-Jain, A.
-G.
-Huth, B.
-Yu and J.
-Gao (2023).
-Explaining black box text modules in natural language with language models.
-[https://arxiv.org/abs/2305.09863](https://arxiv.org/abs/2305.09863)
-1.
-D.
-Shen, P.
-Ding, J.
-Sekhon, B.
-Yu (2022).
-Same root different leaves: time series and cross-sectional methods in panel data.
-Econometrica (accepted).
-[https://arxiv.org/abs/2207.14481](https://arxiv.org/abs/2207.14481)
-1.
-B.
-Park, X.
-Wu, B.
-Yu, A.
-Zhou (2022).
-[Offline evaluation in RL: soft stability weighting to combine fitted Q-learning and model-based methods.](https://openreview.net/forum?id=R3h3-bt0mq) NeurIPS 3rd Offline Reinforcement Learning Workshop.
-1.
-Y.
-S.
-Tan, C.
-Singh, K.
-Nasseri, A.
-Agarwal, J.
-Duncan, O.
-Ronen, M.
-Epland, A.
-Kornblith, B.
-Yu (2022).
-[Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931).
-([imodels 🔎](https://github.com/csinva/imodels) contains code for FIGS)
-1.
-A.
-Agarwal, Y.
-S.
-Tan, O.
-Ronen, C.
-Singh, B.
-Yu (2022).
-[Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.](https://arxiv.org/abs/2202.00858) Proc.
-ICML ([imodels 🔎](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS)).
-1.
-B.
-Yu and C.
-Singh (2022).
-[Seven principles for rapid-response data science: lessons learned from covid-19 forecasting](https://projecteuclid.org/journals/statistical-science/volume-37/issue-2/Seven-Principles-for-Rapid-Response-Data-Science--Lessons-Learned/10.1214/22-STS855.full).
-Statistical Science, 36(2):266-269.
-1. N. Ghosh, S. Mei, and B. Yu (2022). [The three stages of dynamics in high-dimensional kernel methods.](https://arxiv.org/abs/2111.07167) Proc. ICLR, 2022.
-1. Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS.
+1. C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
 1.
 N.
-Altieri, B.
-Park, J.
-DeNero, A.
-Odisho, B.
-Yu.
-(2021).
-[Improving natural language information extraction from cancer pathology reports using transfer learning and zero-shot string similarity.](https://pubmed.ncbi.nlm.nih.gov/34604711/) JAMIA Open.
-2021 Sept.
-30 4(3).
-1.
-C.
-Singh, W.
-Ha and B.
-Yu (2021).
-[Interpreting and Improving Deep-Learning Models with Reality Checks](https://arxiv.org/abs/2108.06847).
-To appear in "xxAI - Beyond Explainable AI" (eds.
-Holzinger et al.).
+Ghosh, S.
+Mei, and B.
+Yu (2022).
+[The three stages of dynamics in high-dimensional kernel methods.](https://arxiv.org/abs/2111.07167) Proc.
+ICLR, 2022.
+[https://arxiv.org/abs/2111.07167](https://arxiv.org/abs/2111.07167)
 1.
@@
 ([code](https://github.com/Yu-Group/adaptive-wavelets))
-1.
-M.
-Behr, Y.
-Wang, X.
-Li, B.
-Yu (2022).
-[Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.](https://arxiv.org/abs/2102.11800) PNAS.
-([theory for iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS-related)
-1.
-N.
-Altieri, B.
-Park, M.
-Olson, J.
-DeNero, A.
-Odisho, B.
-Yu.
-(2021).
-Supervised line attention for tumor attribute classification from pathology reports: Higher performance with less data.
-Journal of Biomedical Informatics.
-122 (2021) 103872.
-[arXiv version](https://arxiv.org/abs/2012.08113)
-1.
-M.
-Behr*, K.
-Kumbier*, A.
-Cordova-Palomera, M.
-Aguirre, E.
-Ashley, A.
-Butte, R.
-Arnaout, J.
-B.
-Brown, J.
-Preist*, B.
-Yu* (2020).
-[Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
-1.
-B.
-Norgeot*, G.
-Quer, B.
-K.
-Beaulieu-Jones, A.
-Torkamani, R.
-Dias, M.
-Gianfrancesco, R.
-Arnaout, I.
-S.
-Kohane, S.
-Saria, E.
-Topol, Z.
-Obermeyer, B.
-Yu & A.
-Butte* (2020).
-[Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y), Nature Medicine, 26, 1320–1324.
-1. B. Yu (2020). [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/1). Harvard Data Science Review (PCS related)
-1. B. Yu and R. Barter (2020). [Data science process: one culture.](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20) JASA. (PCS related)
-1.
-R.
-Dwivedi, Y.
-Tan, B.
-Park, M.
-Wei, K.
-Horgan, D.
-Madigan, B.
-Yu (2020).
-[Stable discovery of interpretable subgroups via calibration in causal studies (staDISC).](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427) International Statistical Review ([code](https://github.com/Yu-Group/stadisc)) (PCS case study for causal inference)
-1.
-X.
-Li, T.
-M.
-Tang, X.
-Wang, J.
-A.
-Kocher, B.
-Yu (2020).
-[A stability-driven protocol for drug response interpretable prediction (staDRIP)](https://arxiv.org/abs/2011.06593).
-NeurISP workshop on ML4H (Machine learning for Health) Extended Abstract.
-1.
-A.
-Y.
-Odisho, B.
-Park, N.
-Altieri, J.
-DeNero, M.
-R Cooperberg, P.
-R .Carroll, B.
-Yu (2020).
-[Natural language processing systems for pathology parsing in limited data environments with uncertainty estimation.](https://academic.oup.com/jamiaopen/article/3/3/431/5922788) JAMIA Open.
 1.
@@
 Lanusse, V.
-Boehm, J.
+Boehm , J.
 Liu, B.
@@
 ([code](https://github.com/csinva/transformation-importance))
-1.
-N.
-Altieri, R.
-Barter, J.
-Duncan, R.
-Dwivedi, K.
-Kumbier, X.
-Li, R.
-Netzorg, B.
-Park, C.
-Singh*, Y.
-Tan, T.Tang, Y.
-Wang, C.
-Zhang, B.
-Yu*.
-(2020) [Curating a COVID-19 data repository and forecasting county-level death counts in the United States.](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1) Harvard Data Science Review ([code](https://github.com/Yu-Group/covid19-severity-prediction)) [7-day prediction results](https://covidseverity.com/) [Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4)
-1.
-B.
-Yu and K.
-Kumbier (2020) [Veridical data science](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf) (PCS framework), PNAS.
-117 (8), 3920-3929.
-[QnAs with Bin Yu.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf)
-1.
-R.
-Dwivedi, N.
-Ho, K.
-Khamaru, M.
-J.
-Wainwright, M.
-I.
-Jordan and B.
-Yu (2020) [Sharp Analysis of Expectation-Maximization for Weakly Identifiable Mixture Models](https://arxiv.org/abs/1902.00194) AISTATS.
-1. R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) [Singularity, Misspecification and the Convergence Rate of EM](https://arxiv.org/abs/1810.00828) Annals of Statistics.
 1.
@@
 Wainwright and B.
-Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients,](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, [arXiv](https://arxiv.org/abs/1905.12247)
-1. R. Dwivedi, Y. Chen, M. J. Wainwright and B. Yu (2019) [Log-concave Sampling: Metropolis Hastings Algorithms are Fast](http://jmlr.org/papers/v20/19-306.html) JMLR.
-1. D. Rothenhäusler and B. Yu (2019). [Incremental causal effects](https://arxiv.org/abs/1907.13258).
-1. Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes](http://jmlr.org/papers/v19/18-158.html). JMLR . http://jmlr.org/papers/v19/18-158.html
+Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients,](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, [https://arxiv.org/abs/1905.12247](https://arxiv.org/abs/1905.12247)
 1.
-Y.
-Chen, R.
-Dwivedi, M.
+R.
+Dwivedi, Y.
+Chen, M.
 J.
 Wainwright and B.
-Yu (2020) [Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier](https://ieeexplore.ieee.org/abstract/document/8262876/) Allerton Conference 2017 https://ieeexplore.ieee.org/abstract/document/8262876/
-1.
-W.
-J.
-Murdoch, C.
-Singh, K.
-Kumbier, R.
-Abbasi-Asl, and B.
-Yu* (2019) [Definitions, methods, and applications in interpretable machine learning.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) PNAS, 116 (44) 22071-22080.
-1.
-W.
-J.
-Murdoch, C.
-Sign, and B.
-Yu (2019).
-[Hierarchical interpretations for neural network predictions.](https://openreview.net/pdf?id=SkEqro0ctQ) ICLR.
-([code](https://github.com/csinva/hierarchical-dnn-interpretations))
-1.
-Y.
-Wang, S.
-Wu and B.
-Yu (2020) [Unique Sharp Local Minimum in l1-minimization Complete Dictionary Learning.](https://jmlr.org/papers/volume21/19-169/19-169.pdf) JMLR.
-21(63), pp.
-1-52.
-Also at https://arxiv.org/abs/1902.08380
+Yu (2019) [Log-concave Sampling: Metropolis Hastings Algorithms are Fast](http://jmlr.org/papers/v20/19-306.html) JMLR.
+[http://jmlr.org/papers/v20/19-306.html](http://jmlr.org/papers/v20/19-306.html)
+1. Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes](http://jmlr.org/papers/v19/18-158.html). JMLR. http://jmlr.org/papers/v19/18-158.html
 1.
@@
 Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
-1. Y. Chen C. Jin, and B. Yu (2018) [Stability and Convergence Trade-off of Iterative Optimization Algorithms.](https://arxiv.org/abs/1804.01619) https://arxiv.org/abs/1804.01619
 1.
@@
 ICLR 2018.
-[https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code)](https://github.com/csinva/hierarchical-dnn-interpretations)
-1. R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309) https://arxiv.org/abs/1801.02309.
-1. Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) [Fast MCMC sampling algorithms on polytopes](https://arxiv.org/abs/1710.08165) https://arxiv.org/abs/1710.08165.
-1.
-B.
-Yu and K.
-Kumbier (2018) [Artificial Intelligence and Statistics](https://www.stat.berkeley.edu/~binyu/ps/papers2018/AI+Stat18.pdf) Frontiers of Information Technology and Electronic Engineering.
-19(1), 6-9.
-1. R. Abbasi-Asl and B. Yu (2017) [Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning](https://arxiv.org/abs/1705.07356) https://arxiv.org/abs/1705.07356
-1.
-R.
-Abbasi-Asl and B.
-Yu (2017) [Interpreting Convolutional Neural Networks Through Compression.](https://arxiv.org/abs/1711.02329) NIPS 2017.
-Symposium on Interpretable Machine Learning.
-(also https://arxiv.org/abs/1711.02329)
+[https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code](https://github.com/csinva/hierarchical-dnn-interpretations))
 1.
@@
 116 (10) 4156-4165.
-https://arxiv.org/abs/1706.03461.
-[(code](https://github.com/soerenkuenzel/hte))
+[https://arxiv.org/abs/1706.03461](https://arxiv.org/abs/1706.03461) ([code](https://github.com/soerenkuenzel/hte))
 1.
@@
 1.
-R.
-Barter and B.
-Yu (2017) [Superheat: An R package for creating beautiful and extendable heatmaps for visualizing complex data](https://www.stat.berkeley.edu/~binyu/ps/papers2017/superheat17.pdf) JCGS (revised).
-https://github.com/rlbarter/superheat
-1.
-H.
-Liu and B.
-Yu (2017) [Comments on: High-dimensional simultaneous inference with the bootstrap by Dezeure et al](https://www.stat.berkeley.edu/~binyu/ps/papers2017/LiuYu-test17.pdf) Test.
-26: 740-750.
-1.
-C.
-Carson et al (2016).
-[UC Berkeley Data Science Planning Initiative Faculty Advisory Board (FAB) Report.](https://www.stat.berkeley.edu/~binyu/ps/FAB2016.pdf) [FAB Report Executive Summary](https://www.stat.berkeley.edu/~binyu/ps/FAB-Summary2016.pdf)
-1.
 S.
@@
 1.
-R.
-E.
-Kass, B.
-S.
-Caffo, M.
-Davidian, X.
-Meng, B.
-Yu, Nancy Reid* (2016).
-[Ten simple rules for effective statistical practice.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/Ten-Simple-Rules.pdf) PLoS Comput.
-Biol., 12(6): e1004961.
-doi:10.1371/journal.pcbi.1004961
-1.
 Siqi Wu, Antony Joseph, Ann S.
@@
 ([code](https://github.com/yu-group/stanmf)) (PCS related)
-1.
-A.
-Bloniarz, C.
-Wu, B.
-Yu, A.
-Talwalkar (2016).
-[Supervised neighborhoods for distributed nonparametric regression.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/AISTATS16.pdf) Proc.
-of AISTATS, Barcelona, Spain.
-1. B. Yu (2015). [Data wisdom for data science.](http://www.odbms.org/2015/04/data-wisdom-for-data-science/) Operational Database Management Systems (ODBMS.ORG).
 1.
@@
 113, 7383 - 7390.
-1.
-P.
-Ma, M.
-W.
-Mahoney and B.
-Yu (2015).
-[A Statistical Perspective on Algorithmic Leveraging.](https://www.stat.berkeley.edu/~binyu/ps/papers2015/MaMahoneyYu2015.pdf) Journal of Machine Learning Research, 16, (2015), 861-911.
-1.
-T.
-Moon, Y.
-Wang, Y.
-Liu, and B.
-Yu (2015).
-[Evaluation of a MISR-based high-resolution aerosol retrieval method using AERONET DRAGON campaign data.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=7047927) IEEE Transactions on Geoscience and Remote Sensing, 53, 4328-4339.
-1.
-B.
-Yu (2014).
-[Let us own data science.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/IMS-pres-address14-yu.pdf) [video](https://www.youtube.com/watch?v=92OjsYQJC1U) [IMS Bulletin](http://bulletin.imstat.org/2014/10/ims-presidential-address-let-us-own-data-science/) Institute of Mathematical Statistics (IMS) Presidental Address, ASC-IMS Joint Conference, Sydney, July, 2014.
-1. G. Schiebinger, M. J. Wainwright and B. Yu (2014). [The geometry of kernelized spectral clustering.](http://arxiv.org/pdf/1404.7552v3.pdf) Annals of Statistics, 43, 819-846.
-1.
-L.
-Miratrix, J.
-Jia, B.
-Yu, B.
-Gawalt, L.
-El Ghaoui, L.
-Barnesmoore, S.
-Clavier (2014).
-[Concise comparative summaries (CCS) of large text corpora with a human experiment.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/CCS14.pdf) Ann.
-Applied Statist., 8, 499-529.
-1.
-Y.
-Benjamini and B.
-Yu (2014).
-[The shuttle estimator for explainable variance in fMRI experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/BenjaminiY12.pdf) Annals of Applied Statistics, 7, 2007-2033.
-1.
-D.
-Bean, P.
-Bickel, N.
-El Karoui and B.
-Yu (2014).
-[Optimal M-estimation in high-dimensional regression.](http://www.pnas.org/content/early/2013/08/08/1307845110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1456314568.
-1.
-N.
-El Karoui, D.
-Bean, P.
-Bickel, C.
-Lim, and B.
-Yu (2014).
-[On robust regression with high-dimensional predictors.](http://www.pnas.org/content/early/2013/08/15/1307842110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1455714562.
-1.
-P.
-Ma, M.
-W.
-Mahoney, B.
-Yu (2014).
-[A Statistical Perspective on Algorithmic Leveraging.](http://arxiv.org/abs/1306.5362) Proc.
-of International Conference on Machine Learning (ICML) (This conference paper contains some of preliminary results of the journal submission Ma et al.
-(2015))
-1.
-A.
-Bloniarz, A.
-Talwalkar, J.
-Terhorst, M.
-Jordan, D.
-Patterson, B.
-Yu and Y.
-Song (2014).
-[Changepoint Analysis for Efficient Variant Calling.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/Bloniarzetal14.pdf) Proc.
-of RECOMB 2014 (to appear).
-1.
-Tao Shi (2013), [A conversation with Professor Bin Yu](http://www.yufamily.org/src/ShiTao_AnInterviewWithProfessorBinYu.php?xref=YuFamily_YuBin_interview_cn) International Chinese Statistical Association (ICSA) Bulletin, Vol 25, Issue 2, pp 85-98.
-([Selected Parts in Statblogs](http://www.statsblogs.com/2013/07/09/a-conversation-with-professor-bin-yu/))
-1. A. Joseph and B. Yu (2016). [The impact of regularization on spectral clustering.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/reg-spectral16.pdf) Annals of Statistics. 4, 1765 - 1791.
-1.
-C.
-Lim and B.
-Yu (2016).
-[Estimation Stability with Cross Validation (ESCV)](https://www.stat.berkeley.edu/~binyu/ps/papers2016/ESCV16.pdf) Journal of Computational and Graphical Statistics.
-25, 464 - 492.
-(First paper towards PCS)
-1.
-A.
-S.
-Hammonds, C.
-A.
-Bristow, W.
-W.
-Fisher, R.
-Weiszmann, S.
-Wu, V.
-Hartenstein, M.
-Kellis, B.
-Yu, E.
-Frise, and S.
-E.
-Celniker (2013).
-[Spatial expression of transcription factors in Drosophila embryonic organ development.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Hammondsetal13.pdf) Genome Biology, 14(12), R140.
-1.
-H.
-Liu and B.
-Yu (2013).
-[Asymptotic properties of Lasso+mLS and Lasso+Ridge in sparse high-dimensional linear regression.](https://www.stat.berkeley.edu/~binyu/ps/LassoOLSBootstrap13.pdf) Electron.
-J.
-Statist., 7, 312-3169.
-1.
-J.
-Mairal and B.
-Yu (2013).
-[Supervised Feature Selection in Graphs with Path Coding Penalties and Network Flows.](http://jmlr.org/papers/v14/mairal13a.html) Journal of Machine Learning Research, 14, 2449-2485.
-1.
-Y.
-Wang, X.
-Jiang, B.
-Yu, M.
-Jiang (2013).
-[A Hierarchical Bayesian Approach for Aerosol Retrieval Using MISR Data.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/WangJiangYuJiang2013.pdf) J.
-American Statistical Association, 108, 483-493.
-1.
-Y.
-He, J.
-Jia and B.
-Yu (2013).
-[Reversible MCMC on Markov equivalence classes of sparse directed acyclic graphs.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/rev-MCMC13.pdf) Annals of Statistics, 41(4), 1742-1779.
-1.
-B.
-Yu (2013).
-[Stability.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Yu13.pdf) Bernoulli, 19 (4), 1484-1500.
-(Invited paper for the Special Issue commemorating the 300th anniversary of the publication of Jakob Bernoullis Ars Conjectandi in 1712) (Begining of PCS)
-1. J. Mairal and B. Yu (2013). Discussion on Grouping Strategies and Thresholding for High Dimensional Linear Models Journal of Statistical Planning and Inference, 143, 1451-1453.
-1.
-C.
-Uhler, G.
-Raskutti, and P.
-Buhlmann and B.
-Yu (2013).
-[Geometry of faithfulness assumption in causal inference.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/faithfulness13.pdf) Annals of Statistics, 41, 436-463.
-1.
-L.
-Miratrix, J.
-Sehkon, and B.
-Yu (2013).
-[Adjusting Treatment Effect Estimates by Post-Stratification in Randomized Experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/post-stratification13.pdf) Journal of Royal Statistical Society, Series B, 75 (part 2), 369-396.
-1. J. Jia, K. Rohe and B. Yu (2013) [The Lasso under Poisson-like Heteroscadecity.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/lasso-poisson13.pdf) Statistica Sinica, 23, 99-118.
-1.
-S.
-Negahban, P.
-Ravikumar, M.
-Wainwrigt, and B.
-Yu (2012) [A unified framework for high-dimensional analysis of M-estimators with decomposable regularizers.](https://www.stat.berkeley.edu/~binyu/ps/unified-797.pdf) Statistical Science, 27, 538-557.
-1.
-G.
-Raskutti, M.
-Wainwrigt, and B.
-Yu (2012) [Minimax-optimal rates for sparse additive models over kernel classes via convex programming.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/RaskuttiWY12.pdf) J.
-Machine Learning Research, 13, 389-427.
-1.
-J.
-Mairal and B.
-Yu (2012).
-[Complexity analysis of the Lasso regularization path.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/MairalY12.pdf) Proc.
-of International Conference on Machine Learning (ICML).
-1.
-Yanfeng Gu, Shizhe Wang, Tao Shi, Yinghui Lu, Eugene E.
-Clothiaux, and Bin Yu (2012).
-[Multiple-kernel learning-based unmixing algorithm for estimation of cloud fractions with MODIS and CLOUDSAT data.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GuWSLCY12.pdf) Proc.
-of IEEE International Geoscience and Remote Sensing Symposium (IGRSS).
-1.
-S.
-Nishimoto, A.
-T.
-Vu, T.
-Naselaris, Y.
-Benjamini, B.
-Yu, J.
-L.
-Gallant (2011).
-[Reconstructing visual experiences from brain activity evoked by natural movies.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/NishimotoVNBYG11.pdf) Current Biology, 21(19), 1641-1646.
-[related videos](https://sites.google.com/site/gallantlabucb/publications/nishimoto-et-al-2011)
-1.
-P.
-Ravikumar, M.
-Wainwright, G.
-Raskutti, B.
-Yu (2011).
-[High-dimensional covariance estimation by minimizing l1-penalized log-determinant divergence.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RavikumarWRY11.pdf) Electronic Journal of Statistics, 5, 935-980.
-1.
-G.
-Raskutti, M.
-Wainwright, B.
-Yu (2011).
-[Minimax rates of estimation for high-dimensional linear regression over lq-balls.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RaskuttiWainwrightYu2011.pdf) IEEE Trans.
-Inform.
-Th., 57(10), 6976-6994.
-1.
-K.
-Rohe, S.
-Chatterjee, and B.
-Yu (2011).
-[Spectral clustering and the high-dimensional Stochastic Block Model.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RoheCY11.pdf) Annals of Statistics, 39 (4), 1878-1915
-1.
-V.
-Q.
-Vu, P.
-Ravikumar, T.
-Naselaris, K.
-N.
-Kay, J.
-L.
-Gallant, B.
-Yu* (2011).
-[Encoding and decoding V1 fMRI responses to natural images with sparse nonparametric models.](http://arxiv.org/pdf/1104.2805.pdf) Annals of Applied Statistics, 5, 1150-1182.
-(*First senior author as last author in biology tradition)
-1. S. N. Pakzad, G. Rocha, and B. Yu (2011). Distributed modal identification by regularized auto regressive models. International Journal of Systems Science, 42, 1473-1489.
-1.
-J.
-Yousafzai, P.
-Sollich, Z.
-Cvetkovic, and B.
-Yu (2011).
-[Combined Features and Kernel Design for Robust Phoneme Classification Using Support Vector Machines.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=5618550) IEEE Trans.
-Audio, Speech and Language Processing (to appear).
-64.
-1.
-X.
-Dai, J.
-Jia, B.
-Yu, El Ghaoui (2011) [SBA-term: Sparse Bilingual Association for terms.](http://www.eecs.berkeley.edu/~elghaoui/Pubs/icsc2011.pdf) Proc.
-International Conference on Semantic Computing.
-1.
-B.
-Yu (2011).
-[Asymptotics and Coding Theory: One of the n - 1 Dimensions of Terry.](http://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/Yu11.pdf) In Selected Works of Terry Speed (ed.
-S.
-Duoit), pp.
-33-36, Springer.
-1. B. Yu (2010). [Remembering Leo.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/Yu10.pdf) Annals of Applied Statistics, 4(4), 1657-1659.
-1.
-J.
-Jia, Y.
-Benjamini, C.
-Lim, G.
-Raskutti, B.
-Yu (2010).
-[Comment on "Envelope models for parsimonious and efficient multivariate linear regression" by R.
-D.
-Cook, B.
-Li, and F.
-Chiaromonte.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaBLRY10.pdf) Statistica Sinica, 20, 961-967.
-1.
-G.
-Raskutti, M.
-Wainwrigt, and B.
-Yu (2010) [Restricted Eigenvalue Properties for Correlated Gaussian Designs.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/RaskuttiWY10.pdf) Journal of Machine Learning Research, 11, 2241-2259.
-1. J. Jia and B. Yu (2010). [On model selection consistency of elastic net when p >>n.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaY10.pdf) Statistica Sinica, 10, 595-611.
-1. P. Buhlmann and B. Yu (2010). [Boosting.](http://onlinelibrary.wiley.com/doi/10.1002/wics.55/abstract) Wiley Interdisciplinary Reviews: Computational Statistics, 2, 69-74.
-1.
-L.
-Huang, J.
-Jia, B.
-Yu, B.
-Chun, P.
-Maniatis, M.
-Naik (2010).
-[Predicting Execution Time of Computer Programs Using Sparse Polynomial Regression.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HuangJYCMN10.pdf) Proc.
-NIPS 2010.
-1.
-Y.
-Han, F.
-Wu, J.
-Jia, Y.
-Zhuang and B.
-Yu (2010).
-[Multi-task Sparse Discriminant Analysis (MtSDA) with Overlapping Categories.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HanWJZY10.pdf) Proc.
-of The 24th AAAI Conference on Artificial Intelligence, July 11-15, Atlanta, GA.
-1.
-B.
-Gawalt, J.
-Jia, L.
-Miratrix, L.
-El Ghaoui, B.
-Yu, and S.
-Clavier (2010).
-[Discovering Word Associations in News Media via Feature Selection and Sparse Classification.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GawaltJMGYC10.pdf) Proc.
-11th ACM SIGMM International Confernece on Multimedia Information Retrieval (MIR).
-1.
-E.
-Anderes, B.
-Yu, V.
-Jovanovic, C.
-Moroney, M.
-Garay, A.
-Braverman, E.
-Clothiaux (2009) [Maximum Likelihood Estimation of Cloud Height from Multi-Angle Satellite Imagery.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/AnderesYJMGBC09.pdf) Annals of Applied Statistics, 3, 902-921
-1.
-T.
-Shi, M.
-Belkin, and B.
-Yu, (2009) [Data Spectroscopy: Eigenspace of Convolution Operator and Clustering](https://www.stat.berkeley.edu/~binyu/ps/shi.aos09.pdf) Annals of Statistics, 37 (6B), 3960-3984.
-1. Vincent Q. Vu, Bin Yu, Robert E. Kass (2009) [Information In The Non-Stationary Case](https://www.stat.berkeley.edu/~binyu/ps/papers2009/VuYK09.pdf) Neural computation 21, 688-703.
-1.
-N.
-Meinshausen and B.
-Yu (2009).
-[Lasso-type recovery of sparse representations for high-dimensional data.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/MeinshausenY09.pdf) Annals of Statistics 37, 246-270.
-1.
-P.
-Zhao, G.
-Rocha, and B.
-Yu (2009).
-[The composite absolute penalties family for grouped and hierarchical variable selection](https://www.stat.berkeley.edu/~binyu/ps/papers2009/ZhaoRY09.pdf) Annals of Statistics 37, 3468-3497.
-(An earlier version 'appeared as Grouped and hierarchical model selection through composite absolute penalties' by P.
-Zhao, G.
-Rocha and B.
-Yu, Department of Statistics, UC Berkeley, Tech.
-Rep 703.)
-1.
-S.
-Negahban, P.
-Ravikumar, M.
-Wainwright, and B.
-Yu (2009).
-[A unified framework for high-dimensional analysis of $M$-estimators with decomposable regularizers](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/NegahbanRWY09.pdf) Proc.
-NIPS, 2009.
-(This conference paper contains preliminary results of the journal submission Negahban et al.
-2012).
-1.
-G.
-Raskutti, M.
-Wainwright, B.
-Yu (2009) [High-dimensional regression under lq-ball sparsity: Optimal rates of convergence.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09b.pdf) Proc.
-of Allerton Conference on Communication, Control, and Computing.
-(This conference paper contains some of preliminary results of the journal submission Ravikumar et al.
-2011).
-1.
-G.
-Raskutti, M.
-Wainwrigt, and B.
-Yu (2009) [Lower bounds on minimax rates for nonparametric regression with additive sparsity and smoothness.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09a.pdf) Proc.
-NIPS, 2009.
-(This conference paper contains some of preliminary results of the journal submission Ravikumar et al.
-2011).
-1.
-T.
-Shi, B.
-Yu, E.
-Clothiaux, and A.
-Braverman (2008).
-[Daytime Arctic Cloud Detection based on Multi-angle Satellite Data with Case Studies.](https://www.stat.berkeley.edu/~binyu/ps/jasa_resub.pdf) Journal of American Statistical Association.
-103( 482), 584-593.
-1.
-Peter Buhlmann and Bin Yu (2008) Invited discussion on "Evidence contrary to the statistical view of boosting (D.
-Mease and A.
-Wyner)".
-[(paper with discussion) ](https://www.stat.berkeley.edu/~binyu/ps/Mease08a_with_discussion.pdf) Journal of Machine Learning Research 9, 187-194.
-1.
-P.
-Ravikumer, V.
-Vu, B.
-Yu, T.
-Naselaris, K.
-Kay, J.
-Gallant (2008).
-[Nonparametric sparse hiearchical models describe V1 fMRI responses to natural images](https://www.stat.berkeley.edu/~binyu/ps/rocha.pseudo.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
-(This conference paper contains some preliminary results of journal paper Vu et al.
-(2011) on encoding models, but also contains an encoding model that is not in Vu et al.
-(2011).
-It does not contain decoding results.)
-1.
-P.
-Ravikumar, G.
-Raskutti, M.
-Wainwright, B.
-Yu (2008) [Model selection in Gaussian graphical models: high-dimensional consistency of l1-regularized MLE.](https://www.stat.berkeley.edu/~binyu/ps/covsel.nips08.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
-1. T. Shi, M. Belkin, and B. Yu (2008). [Data spectroscopy: learning mixture models using eigenspaces of convolution operators.](https://www.stat.berkeley.edu/~binyu/ps/ICML08.pdf) Proc. of ICML 2008.
-1.
-M.
-Ager, Z.
-Cvetkovic, P.
-Pollich, and B.
-Yu (2008).
-[Towards Robust Phoneme Classification Augmentation of PLP Models with Acoustic Waveforms.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=7080758) Proceedings of EUSIPCO.
-1.
-J.
-Yousafzai, Z.
-Cvetković, P.
-Pollich, and B.
-Yu (2008).
-[Combined PLP-Acoustic Waveform Classification for Robust Phoneme Recognition using Support Vector Machines.](http://www.eurasip.org/Proceedings/Eusipco/Eusipco2008/papers/1569105546.pdf) Proceedings of EUSIPCO.
-1.
-N.
-Meinshausen, G.
-Rocha, and B.
-Yu (2007).
-[A tale of three cousins: Lasso, L2Boosting, and Danzig](https://www.stat.berkeley.edu/~binyu/ps/aos.dis07.pdf) Annals of Statistics (invited discussion on Candes and Tao's Danzig Selector paper)
-1. V. Vu, B. Yu, and R. Kass (2007). [Coverage Adjusted Entropy Estimation.](https://www.stat.berkeley.edu/~binyu/ps/entropy.sub.pdf) Statistics and Medicine, 26(21), 4039-4060.
-1.
-B.
-Yu (2007).
-[Embracing Statistical Challenges in the Information Technology Age](https://www.stat.berkeley.edu/~binyu/ps/embracing.pdf) Technometrics (special issue on statistics and information technologies).
-vol.
-49 (3), 237-248.
-1.
-X.
-Jiang, Y.
-Liu, B.
-Yu and M.
-Jiang (2007).
-[Comparison of MISR aerosol optical thickness with AERONET measurements in Beijing metropolitan area.](https://www.stat.berkeley.edu/~binyu/ps/xin.pdf) Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol.
-107, pp.
-45-53.
-1.
-T.
-Shi, E.
-E.
-Clothiaux, B.
-Yu, A.
-J.
-Braverman, and G.
-N.
-Groff (2007).
-[Detection of Daytime Arctic Clouds using MISR and MODIS Data.](https://www.stat.berkeley.edu/~binyu/ps/misr-modis.pdf) Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol.
-107, pp.
-172-184.
-1. Peng Zhao and Bin Yu (2006). [On Model Selection Consistency of Lasso.](https://www.stat.berkeley.edu/~binyu/ps/LassoConsi.pdf) J. Machine Learning Research, 7 (nov), 2541-2567.
-1. B. Yu (2006). [Comments on: Monitoring networked applications with incremental quantile estimation by Chambers et al.](http://arxiv.org/pdf/0708.0338.pdf) Statist. Sci., 21, 483-485.
-1. B. Yu (2006). [Comments on: Regularization in Statistics, by P. J. Bickel and B. Li.](https://www.stat.berkeley.edu/~binyu/ps/test06.pdf) Test, vol. 15 (2), pages 314-316.
-1.
-P.
-Buhlmann and B.
-Yu (2006).
-[Sparse Boosing](https://www.stat.berkeley.edu/~binyu/ps/rev.pdf) Journal of Machine Learning Research ( 7 (June), 1001-1024).
-This is a shortened and more focused version of Buhlmann and Yu "Boosting, Model Selection, Lasso and Nonnegative Garotte" given below.
-1.
-J.
-Gao, H.
-Suzuki, and B.
-Yu (2006).
-[Approximation Lasso Methods for Language Modeling.](https://www.stat.berkeley.edu/~binyu/ps/acl.06.pdf) Proceedings of the 21st International Conference on Computational Linguistics and 44th Annual Meeting of the ACL, pp.
-225-232, Sydney.
-1. T. Shi and B. Yu (2005). [Binning in Gaussian Kernel Regularization.](https://www.stat.berkeley.edu/~binyu/ps/binning.final.pdf) Statistica Sinica (special issue on machine learning), 16, 541-567.
-1.
-G.
-Liang, N.
-Taft, and B.
-Yu (2005).
-[A fast lightweight approach to origin-destination IP traffic estimation using partial measurements.](https://www.stat.berkeley.edu/~binyu/ps/pamtram.final.pdf) Tech Report 687, Statistics Department, UCB (accepted for Special Issue of IEEE-IT and ACM Networks on data networks, Jan.
-2006)
-1. Tong Zhang and B. Yu (2005). [Boosting with early stopping: convergence and consistency.](https://www.stat.berkeley.edu/~binyu/ps/zhang.final.ps) The Annals of Statistics. Vol. 33, 1538-1579.
-1. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2005) [Network tomography: recent developments.](http://nowak.ece.wisc.edu/StatSci04.pdf) Statistical Science, 19, 499-517.
-1.
-C.
-D.
-Giurcaneanu and B.
-Yu (2005).
-[Efficient algorithms for discrete universal denoising for channels with memeory.](https://www.stat.berkeley.edu/~binyu/ps/isit05.pdf) Proceedings of International Symposium on Information Theory, Australia.
-(Also as Tech.
-Report 686, Statistics Department, UCB (Proc.
-ISIT, Sept.
-2005))
-1.
-P.
-Zhao and B.
-Yu (2004).
-[Stagewise Lasso (old title: Boosted Lasso)](https://www.stat.berkeley.edu/~binyu/ps/StagewiseLasso.pdf) Journal of Machine Learning Research, 8, 2701-2726.
-(An earlier version appeared as Tech.
-Report #678, Statistics Department, UC Berkeley (December, 2004; revised in April, 2005)
-1.
-D.
-J.
-Diner et al (2004).
-[PARAGON: A Systematic, Integrated Approach to Aerosol Observation and Modeling.](https://www.stat.berkeley.edu/~binyu/ps/paragon.pdf) American Meterological Society, Oct., 1491-1501.
-1. P. Buhlmann and B. Yu (2004). [Discussion on three boosting papers by Jiang, Lugosi and Vayatis, and Zhang](https://www.stat.berkeley.edu/~binyu/ps/disc2.ps) Annals of Statistics. 32 (1): 96-101.
-1.
-R.
-Jorsten and B.
-Yu (2004).
-[Compressing genomic and proteomic array images for statistical analyses.](https://www.stat.berkeley.edu/~binyu/ps/sig.chapter.ps) Invited chapter in a book on Genomic signal processing and statistics, edited by E.
-R.
-Dougherty, I.
-Shmulevich, J.
-Chen, and Z.
-J.
-Wang, pp.
-341 - 366.
-1.
-G.
-Liang, B.
-Yu, and N.
-Taft (2004).
-[Maximum entropy models: convergence rates and application in dynamic system monitoring.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=1365207&sortType%3Dasc_p_Sequence%26filter%3DAND%28p_IS_Number%3A29909%29%26pageNumber%3D4%26rowsPerPage%3D50) International Symposium on Information Theory, Chicago.
-1. R. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2003). [Internet Tomography: Recent Developments](https://www.stat.berkeley.edu/~binyu/ps/cny.pdf) Statistical Science. Vol. 19(3), 499-517.
-1.
-G.
-Liang and B.
-Yu (2003).
-[Maximum Pseudo Likelihood Estimation in Network Tomography.](https://www.stat.berkeley.edu/~binyu/ps/pseudo-ieee.ps) IEEE Trans.
-on Signal Processing (Special Issue on Data Networks).
-51(8), 2043-2053
-1.
-Rebecka Jornsten and Bin Yu (2003).
-[Simultaneous Gene Clustering and Subset Selection for Classification via MDL.](https://www.stat.berkeley.edu/~binyu/ps/bioinformatics.ps) Bioinformatics.
-19(9): 1100-1109.
-1. Peter Buhlmann and Bin Yu (2003). [Boosting with the L2 Loss: Regression and Classification.](https://www.stat.berkeley.edu/~binyu/ps/boostingl2.ps) J. Amer. Statist. Assoc. 98, 324-340.
-1.
-R.
-Jornsten, W.
-Wang, B.
-Yu, and K.
-Ramchandran (2003).
-[Microarray image compression: SLOCO and the effects of information loss.](https://www.stat.berkeley.edu/~binyu/ps/spj.ps) Signal Processing Journal (Special Issue on Genomic Signal Processing).
-83, 859-869.
-1. G. Liang and B. Yu (2003). [Pseudo Likelihood Estimation in Network Tomography.](http://infocom2003.ieee-infocom.org/papers/51_03.PDF) Proceedings of of Infocom, San Francisco.
-1. Peter Buhlmann and Bin Yu (2002). [Analyzing Bagging.](https://www.stat.berkeley.edu/~binyu/ps/bagging.ps) Annals of Statistics vol. 30, 927-961.
-1.
-R.
-Jornsten, M.
-Hansen, and B.
-Yu (2002).
-Adaptive Minimum Description Length (MDL) criteria with applications to microarray data.
-In Advances in Minimum Description Length: Theory and Applications, edited by P.
-Grunwald, I.J.
-Myung and M.A.
-Pitt.
-The MIT Press, pp.
-295-321.
-1.
-Mark Hansen and Bin Yu (2002).
-[Minimum Description Length Model Selection Criteria for Generalized Linear Models.](https://www.stat.berkeley.edu/~binyu/ps/mdl_glm.ps){\em Science and Statistics: Festschrift for Terry Speed}, IMS Lecture Notes -- Monograph Series, Vol.
-40.
-1.
-Rebecka Jornsten, and Bin Yu (2002).
-[Multiterminal Estimation: Extensions and a Geometric interpretation.](https://www.stat.berkeley.edu/~binyu/ps/isit02.ps) Proceedings of International Symposium on Information Theory (ISIT), June, 2002.
-1.
-Gerald Schuller, Bin Yu, Dawei Huang, and Bern Edler (2002).
-[Perceptual Audio Coding using Pre- and Poster- Filters and Lossless Compression.](https://www.stat.berkeley.edu/~binyu/ps/coding.ps) IEEE Trans.
-Speech and Audio Processing.
-Vol.
-10 (6), 379-390
-1. Mark Coates, Alfred Hero, Robert Nowak, and Bin Yu (2002). [Internet Tomography.](https://www.stat.berkeley.edu/~binyu/ps/spmag.ps) Signal Processing Magazine. vol. 19, No. 3 (May issue), 47-65.
-1.
-M.
-Hansen and B.
-Yu (2001).
-[Model selection and the principle of Minimum Description Length.](https://www.stat.berkeley.edu/~binyu/ps/mdl.ps) Journal of American Statistical Association.
-96, 746-774.
-1.
-Jin Cao, Drew Davis, Scott Vander Wiel and Bin Yu (2000).
-[[ PDF ](https://www.stat.berkeley.edu/~binyu/Site/ps/net.pdf)| [Time-varying network tomography: router link data.](https://www.stat.berkeley.edu/~binyu/ps/net.ps) J.
-Amer.
-Statist.
-Assoc.
-vol.
-95, 1063-1075.
-1.
-Peter Buhlmann and Bin Yu (2000a).
-[Discussion.
-Additive logistic regression: a statistical view of boosting, by Friedman, J., Hastie, T.
-and Tibshirani, R.](https://www.stat.berkeley.edu/~binyu/ps/disc.ps) Annals of Statistics.
-Vol.
-28, 377-386
-1.
-Mark Hansen and Bin Yu (2000).
-[Wavelet thresholding via MDL for natural images.](https://www.stat.berkeley.edu/~binyu/ps/lmdl.ps) IEEE Trans.
-Inform.
-Theory (Special Issue on Information Theoretic Imaging).
-vol.
-46, 1778-1788.
-1.
-Jorma Rissanen and Bin Yu (2000).
-[Coding and compression: a happy union of theory and practice.](https://www.stat.berkeley.edu/~binyu/ps/vig.ps) J.
-Amer.
-Statist.
-Assoc.
-(Year 2000 Commemorative Vignette on Engineering and Physical Sciences).
-vol.
-95, 986-988.
-1.
-Lei Li and Bin Yu (2000).
-[Iterated logarithm expansions of the pathwise code lengths for exponential families.](https://www.stat.berkeley.edu/~binyu/ps/pred.ps) IEEE Trans.
-Inform.
-Theory.
-vol.
-46, 2683-2689.
-1.
-G.
-Chang, B.
-Yu and M.
-Vetterli (2000).
-[Adaptive wavelet thresholding for image denoising and compression.](https://www.stat.berkeley.edu/~binyu/ps/jMDLQ.ps) IEEE Trans.
-Image Processing, vol.
-9, 1532-1546.
-1.
-G.
-Chang, B.
-Yu and M.
-Vetterli (2000).
-[Spatially adaptive wavelet thresholding based on context modeling for image denoising.](https://www.stat.berkeley.edu/~binyu/ps/spatThr.ps) IEEE Trans.
-Image Processing, vol.
-9, 1522-1531.
-1. G. Chang, B. Yu and M. Vetterli (2000). [Wavelet thresholding for multiple noisy image copies.](https://www.stat.berkeley.edu/~binyu/ps/mt.ps) IEEE Trans. Image Processing, vol. 9, 1631-1635.
-1.
-Y.
-Yoo, A.
-Ortega, and B.
-Yu (1999).
-[Image subband coding using context-based classification and adaptive quantization.](https://www.stat.berkeley.edu/~binyu/ps/yoo.ps) IEEE Trans.
-Image Processing, vol.
-8, 1702-1215.
-1. B. Yu, M. Ostland, P. Gong and R. Pu (1999). Penalized discriminant analysis of in situ hyperspectral data for conifer species recognition. IEEE Trans. Geoscience and Remote Sensing, in press.
-1.
-A.
-Barron, J.
-Rissanen, and B.
-Yu (1998).
-The Minimum Description Length principle in coding and modeling.
-(Special Commemorative Issue: Information Theory: 1948-1998) IEEE.
-Trans.
-Inform.
-Th., 44, 2743-2760.
-Reprinted in Information 50 Years of Discovery, Theory: S.
-Verdu and S.
-McLaughlin (eds), IEEE Press , 1999.
-1. B. Yu and P. Mykland (1998). Looking at Markov samplers through cusum path plots: a simple diagnostic idea. Statistics and Computing , 8, 275-286.
-1. P. Gong, R. Pu and B. Yu (1998) Conifer species recognition: effects of data transformation and band width (in Chinese) Journal of Remote Sensing, 2(3), 211-217.
-1.
-G.
-Chang, B.
-Yu and M.
-Vetterli (1998).
-[Spatially adaptive wavelet thresholding for image denoising.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=862630) Proceedings of IEEE International Conference on Image Processing, October, Chicago.
-1.
-S.
-G.
-Chang, B.
-Yu, and M.
-Vetterli (1998).
-[Image denoising via lossy compression and wavelet thresholding.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=647985) Proceedings of International Conference on Image Processing.
-Santa Barbara, California, vol.
-1, pp.
-604-607.
-1. M. Ostland and B. Yu (1997). [Exploring quasi Monte Carlo for marginal density approximation.](https://www.stat.berkeley.edu/~binyu/ps/quasiMC.pdf) Statistics and Computing, 7, 217-228.
-1. P. Gong, R. Pu, and B. Yu (1997). Conifer species recognition with in Situ hyperspectral data. Remote Sensing of Environment, 62, 189-200.
-1. B. Yu and T. P. Speed (1997). [Information and the clone mapping of chromosomes.](https://www.stat.berkeley.edu/~binyu/ps/clone.pdf) Ann. Statist. 25, 169-185.
-1. D. Nelson, T. Speed, and B. Yu (1997). The limits of random fingerprinting. Genomics, 40, 1-12.
-1.
-B.
-Yu (1997).
-[Assouad, Fano, and Le Cam.](https://www.stat.berkeley.edu/~binyu/ps/LeCam.pdf) Festschrift for Lucien Le Cam .
-D.
-Pollard, E.
-Torgersen, and G.
-Yang (eds), pp.
-423-435, Springer-Verlag.
-1. B. Yu (1996). Lower bounds on expected redundancy for nonparametric classes. IEEE Trans. on Information Theory, 42, 272-275.
-1.
-Y.
-Yoo, A.
-Ortega, and B.
-Yu (1996).
-Adaptive quantization of image subbands with efficient overhead rate selection.
-In Proceedings of IEEE International Conference on Image Processing, Lausanne, Switzerland.
-1.
-B.
-Yu (1996).
-[A Statistical analysis of adaptive scalar quantization based on quantized past data.](https://www.stat.berkeley.edu/~binyu/ps/quan.ps) In Proceedings of International Symposium on Information Theory and its Applications (ISITA96), Victoria, Canada.
-1. B. Yu (1995). Comment: Extracting more diagnostic information from a single run using cusum path plot. Statist. Sci., 10, 54-58.
-1.
-J.
-Rissanen and B.
-Yu (1995).
-MDL learning.
-In Learning and Geometry: Computational Approaches, Progress in Computer Science and Applied Logic, 14, David Kueker and Carl Smith (eds), Birkhäuser, Boston, pp.
-3-19.
-1. P. Mykland, L. Tierney, and B. Yu (1995). Regeneration in Markov Chain samplers. J. Amer. Statist. Assoc., 90, 233-241.
-1. B. Yu (1994a). Rates of convergence for empirical processes of stationary mixing sequences. Ann. Probab. 22, 94-116.
-1. M. Arcones and B. Yu (1994). Central limit theorems for empirical and U-processes of stationary mixing sequences. J. Theor. Probab. 7, 47-71.
-1. B. Yu (1994). Lower bound on the expected redundancy for classes of continuous Markov sources. In Statistical Decision Theory and Related Topics V, S. S. Gupta and J. O. Berger (eds), 453-466.
-1. M. Arcones and B. Yu (1994). Limit theorems for empirical processes under dependence. In Proceedings in Chaos expansions, multiple Wiener integrals and their applications. 205-221.
-1.
-A.
-R.
-Barron, Y.
-Yang and B.
-Yu (1994).
-Asymptotically optimal function estimation by minimum complexity criteria.
-In Proceedings of 1994 International Symposium on Information Theory, pp.
-38, Trondheim, Norway.
-1. B. Yu and T. Speed (1993). A rate of convergence result for a universal D-semifaithful code. IEEE Trans. on Information Theory 39, 8813-820.
-1. B. Yu (1993). Density estimation in the L∞ norm for dependent data with applications to the Gibbs sampler. Ann. Statist. 21, 711-735.
-1. T. Speed and B. Yu (1993). Model selection and prediction: normal regression. J. Inst. Statist. Math. 45, 35-54.
-1. J. Rissanen, T. Speed and B. Yu (1992). Density estimation by stochastic complexity. IEEE Trans. on Information Theory, 38, 315-323.
-1. B. Yu and T. Speed (1992) Data compression and histograms. Probability Theory and Related Fields, 92, 195-229.
-
----

### 2025-05-17 papers/interdisciplinary-research-in-biomedicine.qmd
Initial commit.

--- 2025-05-17 papers.qmd
@@
 ---
-title: Papers
+title: "Interdisciplinary Research in Biomedicine"
 ---
 
-# Papers
+[Complete Paper List in Reverse Chronological Order](../papers.qmd)
 
-## Recent Papers by Area
+## Selected Recent Papers in Biomedicine
 
-- [Deep Learning and Machine Learning](papers/deep-learning-and-machine-learning.qmd)
-- [Veridical Data Science (PCS)](papers/veridical-data-science-pcs.qmd)
-- [Interpretable Machine Learning](papers/interpretable-machine-learning.qmd)
-- [Interdisciplinary Research in Biomedicine](papers/interdisciplinary-research-in-biomedicine.qmd)
-- [Tree-based Methods](papers/tree-based-methods.qmd)
-
----
-
-## Complete List by Reverse Chronological Order
-
-*For the most up-to-date and complete list, see [Google Scholar](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en) or [arXiv](https://arxiv.org/search/?query=bin+yu&searchtype=author).*
-
-### Publications
-
-1. A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contextual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886)
-1. Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958)
-1. O. Ronen, A. I. Humayun, R. Balestriero, R. Baraniuk, B. Yu (2024). [ScaLES: Scalable Latent Exploration Score for Pre-Trained Generative Networks](https://arxiv.org/pdf/2406.09657)
-1. S. Hayou, N. Ghosh, B. Yu (2024). [The Impact of Initialization on LoRA Fineuning Dynamics.](https://arxiv.org/pdf/2406.08447)
-1. B. Yu (2024). [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (Harvard Data Science Review)
-1. S. Hayou, N. Ghosh, B. Yu (2024). [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) (Proc. ICML)
-1. C. F. Elliott, J. Duncan, T. M. Tang, M. Behr, K. Kumbier, B. Yu (2024). [Designing a data science simulation with MERITS: a primer.](https://arxiv.org/abs/2403.08971)
-1. Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). [Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986)
-1. N. R. Mallinar, A. Zane, S. Frei, B. Yu (2024). Minimum-Norm Interpolation Under Covariate Shift. (Proc. ICML) [arXiv](https://arxiv.org/pdf/2404.00522)
-1.
-L.
-Sun, A.
-Agarwal, A.
-Kornblith, B.
-Yu, C.
-Xiong (2024).
-ED-Copilot: Reduce Emergency Department Wait Time with Language Model Diagnostic Assistance.
-(Proc.
-ICML) [arXiv](https://arxiv.org/abs/2402.13448)
-1. C. Singh*, A. R. Hsu*, R. Antonello, S. Jain, A. G. Huth, B. Yu, J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
-1. Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262)
 1.
 Q.
-Wang*, T.
+Wang,* T.
 M.
@@
 C.
-Sutton, A.
+Sutton.
+A.
 Agarwal, X.
@@
 Epistasis regulates genetic control of cardiac hypertrophy.
-[medRxiv](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
+[https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
 1.
@@
 Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology.
-[bioRxiv](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
+[https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
 1.
@@
 doi: 10.1016/j.xcrm.2023.101194.
-(PCS related) ([Editorial](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10518497/))
-1. R. Dwivedi, C. Singh, B. Yu, M. Wainwright (2023). [Revisiting miniumu description length complexity in overparametrized models.](https://jmlr.org/papers/v24/21-1133.html) JMLR, 24(268): 1-59.
-1.
-K.
-Wu, Y.
-Chen, W.
-Ha, B.
-Yu (2023).
-[Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms.](https://arxiv.org/abs/2309.10301) JMLR (accepted).
-[https://arxiv.org/abs/2309.10301](https://arxiv.org/abs/2309.10301)
-1.
-N.
-Ghosh, S.
-Frei, W.
-Ha, B.
-Yu (2023).
-The effect of SGD batch size on autoencoder learning: sparsity, sharpness and feature learning.
-[https://arxiv.org/abs/2308.03215](https://arxiv.org/abs/2308.03215)
-1.
-R.
-Netzorg, J.
-Li, B.
-Yu (2024).
-Improving prototypical part networks with reward reweighting, reselection, and retraining.
-Proc.
-ICML.
-[https://arxiv.org/abs/2307.03887](https://arxiv.org/abs/2307.03887)
-1.
-A.
-Agarwal, A.
-M.
-Kenny, Y.
-S.
-Tan, T.
-M.
-Tang, B.
-Yu (2023).
-MDI+: a flexible random forest-based feature importance framework.
-[https://arxiv.org/abs/2307.01932](https://arxiv.org/abs/2307.01932) (PCS related)
+(PCS related) ([Editorial in Cell Reports Medicine](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10518497/) by L.
+Oldfield and E.
+Costello on Erajizad et al.
+(2023))
 1.
@@
 Diagnosing transformers: illuminating feature space for clinical decison-making.
-Proc.
-ICLR.
 [https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)
-1.
-C.
-Singh, A.
-R.
-Hsu, R.
-Antonello, S.
-Jain, A.
-G.
-Huth, B.
-Yu and J.
-Gao (2023).
-Explaining black box text modules in natural language with language models.
-[https://arxiv.org/abs/2305.09863](https://arxiv.org/abs/2305.09863)
-1.
-D.
-Shen, P.
-Ding, J.
-Sekhon, B.
-Yu (2022).
-Same root different leaves: time series and cross-sectional methods in panel data.
-Econometrica (accepted).
-[https://arxiv.org/abs/2207.14481](https://arxiv.org/abs/2207.14481)
-1.
-B.
-Park, X.
-Wu, B.
-Yu, A.
-Zhou (2022).
-[Offline evaluation in RL: soft stability weighting to combine fitted Q-learning and model-based methods.](https://openreview.net/forum?id=R3h3-bt0mq) NeurIPS 3rd Offline Reinforcement Learning Workshop.
-1.
-Y.
-S.
-Tan, C.
-Singh, K.
-Nasseri, A.
-Agarwal, J.
-Duncan, O.
-Ronen, M.
-Epland, A.
-Kornblith, B.
-Yu (2022).
-[Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931).
-([imodels 🔎](https://github.com/csinva/imodels) contains code for FIGS)
-1.
-A.
-Agarwal, Y.
-S.
-Tan, O.
-Ronen, C.
-Singh, B.
-Yu (2022).
-[Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.](https://arxiv.org/abs/2202.00858) Proc.
-ICML ([imodels 🔎](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS)).
-1.
-B.
-Yu and C.
-Singh (2022).
-[Seven principles for rapid-response data science: lessons learned from covid-19 forecasting](https://projecteuclid.org/journals/statistical-science/volume-37/issue-2/Seven-Principles-for-Rapid-Response-Data-Science--Lessons-Learned/10.1214/22-STS855.full).
-Statistical Science, 36(2):266-269.
-1. N. Ghosh, S. Mei, and B. Yu (2022). [The three stages of dynamics in high-dimensional kernel methods.](https://arxiv.org/abs/2111.07167) Proc. ICLR, 2022.
-1. Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS.
 1.
@@
 30 4(3).
-1.
-C.
-Singh, W.
-Ha and B.
-Yu (2021).
-[Interpreting and Improving Deep-Learning Models with Reality Checks](https://arxiv.org/abs/2108.06847).
-To appear in "xxAI - Beyond Explainable AI" (eds.
-Holzinger et al.).
-1.
-W.
-Ha, C.
-Singh, F.
-Lanusse, S.
-Upadhyayula, and B.
-Yu (2021).
-[Adaptive Wavelet Distillation from Neural Networks through Interpretation.](https://nips.cc/Conferences/2021/ScheduleMultitrack?event=28027) Proc.
-NeurIPS 2021.
-([code](https://github.com/Yu-Group/adaptive-wavelets))
-1.
-M.
-Behr, Y.
-Wang, X.
-Li, B.
-Yu (2022).
-[Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.](https://arxiv.org/abs/2102.11800) PNAS.
-([theory for iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS-related)
-1.
-N.
-Altieri, B.
-Park, M.
-Olson, J.
-DeNero, A.
-Odisho, B.
-Yu.
-(2021).
-Supervised line attention for tumor attribute classification from pathology reports: Higher performance with less data.
-Journal of Biomedical Informatics.
-122 (2021) 103872.
-[arXiv version](https://arxiv.org/abs/2012.08113)
-1.
-M.
-Behr*, K.
-Kumbier*, A.
-Cordova-Palomera, M.
-Aguirre, E.
-Ashley, A.
-Butte, R.
-Arnaout, J.
-B.
-Brown, J.
-Preist*, B.
-Yu* (2020).
-[Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
 1.
@@
 [Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y), Nature Medicine, 26, 1320–1324.
-1. B. Yu (2020). [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/1). Harvard Data Science Review (PCS related)
-1. B. Yu and R. Barter (2020). [Data science process: one culture.](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20) JASA. (PCS related)
-1.
-R.
-Dwivedi, Y.
-Tan, B.
-Park, M.
-Wei, K.
-Horgan, D.
-Madigan, B.
-Yu (2020).
-[Stable discovery of interpretable subgroups via calibration in causal studies (staDISC).](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427) International Statistical Review ([code](https://github.com/Yu-Group/stadisc)) (PCS case study for causal inference)
-1.
-X.
-Li, T.
-M.
-Tang, X.
-Wang, J.
-A.
-Kocher, B.
-Yu (2020).
-[A stability-driven protocol for drug response interpretable prediction (staDRIP)](https://arxiv.org/abs/2011.06593).
-NeurISP workshop on ML4H (Machine learning for Health) Extended Abstract.
-1.
-A.
-Y.
-Odisho, B.
-Park, N.
-Altieri, J.
-DeNero, M.
-R Cooperberg, P.
-R .Carroll, B.
-Yu (2020).
-[Natural language processing systems for pathology parsing in limited data environments with uncertainty estimation.](https://academic.oup.com/jamiaopen/article/3/3/431/5922788) JAMIA Open.
-1.
-L.
-Reiger, J.
-W.
-Murdoch, S.
-Singh, B.
-Yu (2020).
-[Interpretations are Useful: Penalizing Explanations to Align Neural Networks with Prior Knowledge](https://proceedings.icml.cc/static/paper_files/icml/2020/992-Paper.pdf).
-ICML Proceedings.
-([code](https://github.com/laura-rieger/deep-explanation-penalization))
-1.
-C.
-Singh, W.
-Ha, F.
-Lanusse, V.
-Boehm, J.
-Liu, B.
-Yu (2020).
-[Transformation Importance with Applications to Cosmology](https://arxiv.org/pdf/2003.01926.pdf) ICLR Workshop paper.
-([code](https://github.com/csinva/transformation-importance))
-1.
-N.
-Altieri, R.
-Barter, J.
-Duncan, R.
-Dwivedi, K.
-Kumbier, X.
-Li, R.
-Netzorg, B.
-Park, C.
-Singh*, Y.
-Tan, T.Tang, Y.
-Wang, C.
-Zhang, B.
-Yu*.
-(2020) [Curating a COVID-19 data repository and forecasting county-level death counts in the United States.](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1) Harvard Data Science Review ([code](https://github.com/Yu-Group/covid19-severity-prediction)) [7-day prediction results](https://covidseverity.com/) [Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4)
-1.
-B.
-Yu and K.
-Kumbier (2020) [Veridical data science](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf) (PCS framework), PNAS.
-117 (8), 3920-3929.
-[QnAs with Bin Yu.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf)
-1.
-R.
-Dwivedi, N.
-Ho, K.
-Khamaru, M.
-J.
-Wainwright, M.
-I.
-Jordan and B.
-Yu (2020) [Sharp Analysis of Expectation-Maximization for Weakly Identifiable Mixture Models](https://arxiv.org/abs/1902.00194) AISTATS.
-1. R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) [Singularity, Misspecification and the Convergence Rate of EM](https://arxiv.org/abs/1810.00828) Annals of Statistics.
-1.
-Y.
-Chen, R.
-Dwivedi, M.
-J.
-Wainwright and B.
-Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients,](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, [arXiv](https://arxiv.org/abs/1905.12247)
-1. R. Dwivedi, Y. Chen, M. J. Wainwright and B. Yu (2019) [Log-concave Sampling: Metropolis Hastings Algorithms are Fast](http://jmlr.org/papers/v20/19-306.html) JMLR.
-1. D. Rothenhäusler and B. Yu (2019). [Incremental causal effects](https://arxiv.org/abs/1907.13258).
-1. Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes](http://jmlr.org/papers/v19/18-158.html). JMLR . http://jmlr.org/papers/v19/18-158.html
-1.
-Y.
-Chen, R.
-Dwivedi, M.
-J.
-Wainwright and B.
-Yu (2020) [Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier](https://ieeexplore.ieee.org/abstract/document/8262876/) Allerton Conference 2017 https://ieeexplore.ieee.org/abstract/document/8262876/
-1.
-W.
-J.
-Murdoch, C.
-Singh, K.
-Kumbier, R.
-Abbasi-Asl, and B.
-Yu* (2019) [Definitions, methods, and applications in interpretable machine learning.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) PNAS, 116 (44) 22071-22080.
-1.
-W.
-J.
-Murdoch, C.
-Sign, and B.
-Yu (2019).
-[Hierarchical interpretations for neural network predictions.](https://openreview.net/pdf?id=SkEqro0ctQ) ICLR.
-([code](https://github.com/csinva/hierarchical-dnn-interpretations))
-1.
-Y.
-Wang, S.
-Wu and B.
-Yu (2020) [Unique Sharp Local Minimum in l1-minimization Complete Dictionary Learning.](https://jmlr.org/papers/volume21/19-169/19-169.pdf) JMLR.
-21(63), pp.
-1-52.
-Also at https://arxiv.org/abs/1902.08380
-1.
-Y.
-Chen, R.
-Abbasi-Asl, A.
-Bloniarz, M.
-Oliver, B.
-Willmore, J.
-Gallant*, and B.
-Yu* (2018) [The DeepTune framework for modeling and characterizing neurons in visual cortex area V4](https://www.biorxiv.org/content/10.1101/465534v1) https://www.biorxiv.org/content/10.1101/465534v1
-1.
-K.
-Kumbier, S.
-Sumanta, J.
-B.
-Brown, S.
-Celniker, and B.
-Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
-1. Y. Chen C. Jin, and B. Yu (2018) [Stability and Convergence Trade-off of Iterative Optimization Algorithms.](https://arxiv.org/abs/1804.01619) https://arxiv.org/abs/1804.01619
-1.
-J.
-Murdoch, P.
-Liu, and B.
-Yu (2018) [Beyond word importance: contextual decomposition to extract interactions from LSTMs.](https://arxiv.org/abs/1801.05453) Proc.
-ICLR 2018.
-[https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code)](https://github.com/csinva/hierarchical-dnn-interpretations)
-1. R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309) https://arxiv.org/abs/1801.02309.
-1. Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) [Fast MCMC sampling algorithms on polytopes](https://arxiv.org/abs/1710.08165) https://arxiv.org/abs/1710.08165.
-1.
-B.
-Yu and K.
-Kumbier (2018) [Artificial Intelligence and Statistics](https://www.stat.berkeley.edu/~binyu/ps/papers2018/AI+Stat18.pdf) Frontiers of Information Technology and Electronic Engineering.
-19(1), 6-9.
-1. R. Abbasi-Asl and B. Yu (2017) [Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning](https://arxiv.org/abs/1705.07356) https://arxiv.org/abs/1705.07356
-1.
-R.
-Abbasi-Asl and B.
-Yu (2017) [Interpreting Convolutional Neural Networks Through Compression.](https://arxiv.org/abs/1711.02329) NIPS 2017.
-Symposium on Interpretable Machine Learning.
-(also https://arxiv.org/abs/1711.02329)
-1.
-S.
-Kunzel, J.
-Sekhon, P.
-Bickel, and B.
-Yu* (2019) [Meta-learners for Estimating Heterogeneous Treatment Effects using Machine Learning,](https://www.pnas.org/content/116/10/4156) PNAS.
-116 (10) 4156-4165.
-https://arxiv.org/abs/1706.03461.
-[(code](https://github.com/soerenkuenzel/hte))
-1.
-S.
-Basu, K.
-Kumbier, J.
-B.
-Brown*, and B.
-Yu* (2018) [iterative Random Forests to discover predictive and stable high-order interactions](https://www.stat.berkeley.edu/~binyu/ps/papers2018/iRF+SI18.pdf) PNAS, 115 (8), 1943-1948.
-([code](https://github.com/Yu-Group/iterative-Random-Forest)) (PCS related)
-1.
-S.
-Balakrishnan, M.
-Wainwright, B.
-Yu (2017) [Statistical Guarantees for the EM algorithm: from population to sample-based analysis.](https://www.stat.berkeley.edu/~binyu/ps/papers2017/EM17.pdf) Annals of Statistics, 45(1), 77 - 120.
-1.
-R.
-Barter and B.
-Yu (2017) [Superheat: An R package for creating beautiful and extendable heatmaps for visualizing complex data](https://www.stat.berkeley.edu/~binyu/ps/papers2017/superheat17.pdf) JCGS (revised).
-https://github.com/rlbarter/superheat
-1.
-H.
-Liu and B.
-Yu (2017) [Comments on: High-dimensional simultaneous inference with the bootstrap by Dezeure et al](https://www.stat.berkeley.edu/~binyu/ps/papers2017/LiuYu-test17.pdf) Test.
-26: 740-750.
-1.
-C.
-Carson et al (2016).
-[UC Berkeley Data Science Planning Initiative Faculty Advisory Board (FAB) Report.](https://www.stat.berkeley.edu/~binyu/ps/FAB2016.pdf) [FAB Report Executive Summary](https://www.stat.berkeley.edu/~binyu/ps/FAB-Summary2016.pdf)
-1.
-S.
-Wu and B.
-Yu (2018).
-[Local identifiability of l1-minimization dictionary learning: a sufficient and almost necessary condition.](https://www.stat.berkeley.edu/~binyu/ps/papers2018/local-iden18.pdf) JMLR.
-18, 1 - 56.
-1.
-K.
-Rohe, T.
-Qin and B.
-Yu* (2016).
-[Co-clustering directed graphs to discover asymmetries and directional communities.](http://www.pnas.org/content/113/45/12679.full.pdf?with-ds=yes) Proc.
-National Academy of Sciences (PNAS), 113(45), 12679 - 12684.
-1.
-R.
-E.
-Kass, B.
-S.
-Caffo, M.
-Davidian, X.
-Meng, B.
-Yu, Nancy Reid* (2016).
-[Ten simple rules for effective statistical practice.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/Ten-Simple-Rules.pdf) PLoS Comput.
-Biol., 12(6): e1004961.
-doi:10.1371/journal.pcbi.1004961
-1.
-Siqi Wu, Antony Joseph, Ann S.
-Hammonds, Susan E.
-Celniker, Bin Yu*, and Erwin Frise* (2016).
-[Stability-driven nonnegative matrix factorization to interpret spatial gene expression and build local gene networks (with support information).](https://www.stat.berkeley.edu/~binyu/ps/papers2016/staNMF+SI.pdf) PNAS, pp.
-4290 - 4295.
-([code](https://github.com/yu-group/stanmf)) (PCS related)
-1.
-A.
-Bloniarz, C.
-Wu, B.
-Yu, A.
-Talwalkar (2016).
-[Supervised neighborhoods for distributed nonparametric regression.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/AISTATS16.pdf) Proc.
-of AISTATS, Barcelona, Spain.
-1. B. Yu (2015). [Data wisdom for data science.](http://www.odbms.org/2015/04/data-wisdom-for-data-science/) Operational Database Management Systems (ODBMS.ORG).
-1.
-A.
-Bloniarz, H.
-Liu, C.
-Zhang, J.
-Sekhon, and B.
-Yu* (2015).
-[Lasso adjustments of treatment effect estimates in randomized experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/lasso-adj+SI16.pdf) PNAS.
-113, 7383 - 7390.
-1.
-P.
-Ma, M.
-W.
-Mahoney and B.
-Yu (2015).
-[A Statistical Perspective on Algorithmic Leveraging.](https://www.stat.berkeley.edu/~binyu/ps/papers2015/MaMahoneyYu2015.pdf) Journal of Machine Learning Research, 16, (2015), 861-911.
-1.
-T.
-Moon, Y.
-Wang, Y.
-Liu, and B.
-Yu (2015).
-[Evaluation of a MISR-based high-resolution aerosol retrieval method using AERONET DRAGON campaign data.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=7047927) IEEE Transactions on Geoscience and Remote Sensing, 53, 4328-4339.
-1.
-B.
-Yu (2014).
-[Let us own data science.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/IMS-pres-address14-yu.pdf) [video](https://www.youtube.com/watch?v=92OjsYQJC1U) [IMS Bulletin](http://bulletin.imstat.org/2014/10/ims-presidential-address-let-us-own-data-science/) Institute of Mathematical Statistics (IMS) Presidental Address, ASC-IMS Joint Conference, Sydney, July, 2014.
-1. G. Schiebinger, M. J. Wainwright and B. Yu (2014). [The geometry of kernelized spectral clustering.](http://arxiv.org/pdf/1404.7552v3.pdf) Annals of Statistics, 43, 819-846.
-1.
-L.
-Miratrix, J.
-Jia, B.
-Yu, B.
-Gawalt, L.
-El Ghaoui, L.
-Barnesmoore, S.
-Clavier (2014).
-[Concise comparative summaries (CCS) of large text corpora with a human experiment.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/CCS14.pdf) Ann.
-Applied Statist., 8, 499-529.
-1.
-Y.
-Benjamini and B.
-Yu (2014).
-[The shuttle estimator for explainable variance in fMRI experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/BenjaminiY12.pdf) Annals of Applied Statistics, 7, 2007-2033.
-1.
-D.
-Bean, P.
-Bickel, N.
-El Karoui and B.
-Yu (2014).
-[Optimal M-estimation in high-dimensional regression.](http://www.pnas.org/content/early/2013/08/08/1307845110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1456314568.
-1.
-N.
-El Karoui, D.
-Bean, P.
-Bickel, C.
-Lim, and B.
-Yu (2014).
-[On robust regression with high-dimensional predictors.](http://www.pnas.org/content/early/2013/08/15/1307842110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1455714562.
-1.
-P.
-Ma, M.
-W.
-Mahoney, B.
-Yu (2014).
-[A Statistical Perspective on Algorithmic Leveraging.](http://arxiv.org/abs/1306.5362) Proc.
-of International Conference on Machine Learning (ICML) (This conference paper contains some of preliminary results of the journal submission Ma et al.
-(2015))
-1.
-A.
-Bloniarz, A.
-Talwalkar, J.
-Terhorst, M.
-Jordan, D.
-Patterson, B.
-Yu and Y.
-Song (2014).
-[Changepoint Analysis for Efficient Variant Calling.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/Bloniarzetal14.pdf) Proc.
-of RECOMB 2014 (to appear).
-1.
-Tao Shi (2013), [A conversation with Professor Bin Yu](http://www.yufamily.org/src/ShiTao_AnInterviewWithProfessorBinYu.php?xref=YuFamily_YuBin_interview_cn) International Chinese Statistical Association (ICSA) Bulletin, Vol 25, Issue 2, pp 85-98.
-([Selected Parts in Statblogs](http://www.statsblogs.com/2013/07/09/a-conversation-with-professor-bin-yu/))
-1. A. Joseph and B. Yu (2016). [The impact of regularization on spectral clustering.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/reg-spectral16.pdf) Annals of Statistics. 4, 1765 - 1791.
-1.
-C.
-Lim and B.
-Yu (2016).
-[Estimation Stability with Cross Validation (ESCV)](https://www.stat.berkeley.edu/~binyu/ps/papers2016/ESCV16.pdf) Journal of Computational and Graphical Statistics.
-25, 464 - 492.
-(First paper towards PCS)
-1.
-A.
-S.
-Hammonds, C.
-A.
-Bristow, W.
-W.
-Fisher, R.
-Weiszmann, S.
-Wu, V.
-Hartenstein, M.
-Kellis, B.
-Yu, E.
-Frise, and S.
-E.
-Celniker (2013).
-[Spatial expression of transcription factors in Drosophila embryonic organ development.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Hammondsetal13.pdf) Genome Biology, 14(12), R140.
-1.
-H.
-Liu and B.
-Yu (2013).
-[Asymptotic properties of Lasso+mLS and Lasso+Ridge in sparse high-dimensional linear regression.](https://www.stat.berkeley.edu/~binyu/ps/LassoOLSBootstrap13.pdf) Electron.
-J.
-Statist., 7, 312-3169.
-1.
-J.
-Mairal and B.
-Yu (2013).
-[Supervised Feature Selection in Graphs with Path Coding Penalties and Network Flows.](http://jmlr.org/papers/v14/mairal13a.html) Journal of Machine Learning Research, 14, 2449-2485.
-1.
-Y.
-Wang, X.
-Jiang, B.
-Yu, M.
-Jiang (2013).
-[A Hierarchical Bayesian Approach for Aerosol Retrieval Using MISR Data.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/WangJiangYuJiang2013.pdf) J.
-American Statistical Association, 108, 483-493.
-1.
-Y.
-He, J.
-Jia and B.
-Yu (2013).
-[Reversible MCMC on Markov equivalence classes of sparse directed acyclic graphs.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/rev-MCMC13.pdf) Annals of Statistics, 41(4), 1742-1779.
-1.
-B.
-Yu (2013).
-[Stability.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Yu13.pdf) Bernoulli, 19 (4), 1484-1500.
-(Invited paper for the Special Issue commemorating the 300th anniversary of the publication of Jakob Bernoullis Ars Conjectandi in 1712) (Begining of PCS)
-1. J. Mairal and B. Yu (2013). Discussion on Grouping Strategies and Thresholding for High Dimensional Linear Models Journal of Statistical Planning and Inference, 143, 1451-1453.
-1.
-C.
-Uhler, G.
-Raskutti, and P.
-Buhlmann and B.
-Yu (2013).
-[Geometry of faithfulness assumption in causal inference.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/faithfulness13.pdf) Annals of Statistics, 41, 436-463.
-1.
-L.
-Miratrix, J.
-Sehkon, and B.
-Yu (2013).
-[Adjusting Treatment Effect Estimates by Post-Stratification in Randomized Experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/post-stratification13.pdf) Journal of Royal Statistical Society, Series B, 75 (part 2), 369-396.
-1. J. Jia, K. Rohe and B. Yu (2013) [The Lasso under Poisson-like Heteroscadecity.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/lasso-poisson13.pdf) Statistica Sinica, 23, 99-118.
-1.
-S.
-Negahban, P.
-Ravikumar, M.
-Wainwrigt, and B.
-Yu (2012) [A unified framework for high-dimensional analysis of M-estimators with decomposable regularizers.](https://www.stat.berkeley.edu/~binyu/ps/unified-797.pdf) Statistical Science, 27, 538-557.
-1.
-G.
-Raskutti, M.
-Wainwrigt, and B.
-Yu (2012) [Minimax-optimal rates for sparse additive models over kernel classes via convex programming.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/RaskuttiWY12.pdf) J.
-Machine Learning Research, 13, 389-427.
-1.
-J.
-Mairal and B.
-Yu (2012).
-[Complexity analysis of the Lasso regularization path.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/MairalY12.pdf) Proc.
-of International Conference on Machine Learning (ICML).
-1.
-Yanfeng Gu, Shizhe Wang, Tao Shi, Yinghui Lu, Eugene E.
-Clothiaux, and Bin Yu (2012).
-[Multiple-kernel learning-based unmixing algorithm for estimation of cloud fractions with MODIS and CLOUDSAT data.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GuWSLCY12.pdf) Proc.
-of IEEE International Geoscience and Remote Sensing Symposium (IGRSS).
-1.
-S.
-Nishimoto, A.
-T.
-Vu, T.
-Naselaris, Y.
-Benjamini, B.
-Yu, J.
-L.
-Gallant (2011).
-[Reconstructing visual experiences from brain activity evoked by natural movies.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/NishimotoVNBYG11.pdf) Current Biology, 21(19), 1641-1646.
-[related videos](https://sites.google.com/site/gallantlabucb/publications/nishimoto-et-al-2011)
-1.
-P.
-Ravikumar, M.
-Wainwright, G.
-Raskutti, B.
-Yu (2011).
-[High-dimensional covariance estimation by minimizing l1-penalized log-determinant divergence.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RavikumarWRY11.pdf) Electronic Journal of Statistics, 5, 935-980.
-1.
-G.
-Raskutti, M.
-Wainwright, B.
-Yu (2011).
-[Minimax rates of estimation for high-dimensional linear regression over lq-balls.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RaskuttiWainwrightYu2011.pdf) IEEE Trans.
-Inform.
-Th., 57(10), 6976-6994.
-1.
-K.
-Rohe, S.
-Chatterjee, and B.
-Yu (2011).
-[Spectral clustering and the high-dimensional Stochastic Block Model.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RoheCY11.pdf) Annals of Statistics, 39 (4), 1878-1915
-1.
-V.
-Q.
-Vu, P.
-Ravikumar, T.
-Naselaris, K.
-N.
-Kay, J.
-L.
-Gallant, B.
-Yu* (2011).
-[Encoding and decoding V1 fMRI responses to natural images with sparse nonparametric models.](http://arxiv.org/pdf/1104.2805.pdf) Annals of Applied Statistics, 5, 1150-1182.
-(*First senior author as last author in biology tradition)
-1. S. N. Pakzad, G. Rocha, and B. Yu (2011). Distributed modal identification by regularized auto regressive models. International Journal of Systems Science, 42, 1473-1489.
-1.
-J.
-Yousafzai, P.
-Sollich, Z.
-Cvetkovic, and B.
-Yu (2011).
-[Combined Features and Kernel Design for Robust Phoneme Classification Using Support Vector Machines.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=5618550) IEEE Trans.
-Audio, Speech and Language Processing (to appear).
-64.
-1.
-X.
-Dai, J.
-Jia, B.
-Yu, El Ghaoui (2011) [SBA-term: Sparse Bilingual Association for terms.](http://www.eecs.berkeley.edu/~elghaoui/Pubs/icsc2011.pdf) Proc.
-International Conference on Semantic Computing.
-1.
-B.
-Yu (2011).
-[Asymptotics and Coding Theory: One of the n - 1 Dimensions of Terry.](http://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/Yu11.pdf) In Selected Works of Terry Speed (ed.
-S.
-Duoit), pp.
-33-36, Springer.
-1. B. Yu (2010). [Remembering Leo.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/Yu10.pdf) Annals of Applied Statistics, 4(4), 1657-1659.
-1.
-J.
-Jia, Y.
-Benjamini, C.
-Lim, G.
-Raskutti, B.
-Yu (2010).
-[Comment on "Envelope models for parsimonious and efficient multivariate linear regression" by R.
-D.
-Cook, B.
-Li, and F.
-Chiaromonte.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaBLRY10.pdf) Statistica Sinica, 20, 961-967.
-1.
-G.
-Raskutti, M.
-Wainwrigt, and B.
-Yu (2010) [Restricted Eigenvalue Properties for Correlated Gaussian Designs.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/RaskuttiWY10.pdf) Journal of Machine Learning Research, 11, 2241-2259.
-1. J. Jia and B. Yu (2010). [On model selection consistency of elastic net when p >>n.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaY10.pdf) Statistica Sinica, 10, 595-611.
-1. P. Buhlmann and B. Yu (2010). [Boosting.](http://onlinelibrary.wiley.com/doi/10.1002/wics.55/abstract) Wiley Interdisciplinary Reviews: Computational Statistics, 2, 69-74.
-1.
-L.
-Huang, J.
-Jia, B.
-Yu, B.
-Chun, P.
-Maniatis, M.
-Naik (2010).
-[Predicting Execution Time of Computer Programs Using Sparse Polynomial Regression.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HuangJYCMN10.pdf) Proc.
-NIPS 2010.
-1.
-Y.
-Han, F.
-Wu, J.
-Jia, Y.
-Zhuang and B.
-Yu (2010).
-[Multi-task Sparse Discriminant Analysis (MtSDA) with Overlapping Categories.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HanWJZY10.pdf) Proc.
-of The 24th AAAI Conference on Artificial Intelligence, July 11-15, Atlanta, GA.
-1.
-B.
-Gawalt, J.
-Jia, L.
-Miratrix, L.
-El Ghaoui, B.
-Yu, and S.
-Clavier (2010).
-[Discovering Word Associations in News Media via Feature Selection and Sparse Classification.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GawaltJMGYC10.pdf) Proc.
-11th ACM SIGMM International Confernece on Multimedia Information Retrieval (MIR).
-1.
-E.
-Anderes, B.
-Yu, V.
-Jovanovic, C.
-Moroney, M.
-Garay, A.
-Braverman, E.
-Clothiaux (2009) [Maximum Likelihood Estimation of Cloud Height from Multi-Angle Satellite Imagery.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/AnderesYJMGBC09.pdf) Annals of Applied Statistics, 3, 902-921
-1.
-T.
-Shi, M.
-Belkin, and B.
-Yu, (2009) [Data Spectroscopy: Eigenspace of Convolution Operator and Clustering](https://www.stat.berkeley.edu/~binyu/ps/shi.aos09.pdf) Annals of Statistics, 37 (6B), 3960-3984.
-1. Vincent Q. Vu, Bin Yu, Robert E. Kass (2009) [Information In The Non-Stationary Case](https://www.stat.berkeley.edu/~binyu/ps/papers2009/VuYK09.pdf) Neural computation 21, 688-703.
-1.
-N.
-Meinshausen and B.
-Yu (2009).
-[Lasso-type recovery of sparse representations for high-dimensional data.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/MeinshausenY09.pdf) Annals of Statistics 37, 246-270.
-1.
-P.
-Zhao, G.
-Rocha, and B.
-Yu (2009).
-[The composite absolute penalties family for grouped and hierarchical variable selection](https://www.stat.berkeley.edu/~binyu/ps/papers2009/ZhaoRY09.pdf) Annals of Statistics 37, 3468-3497.
-(An earlier version 'appeared as Grouped and hierarchical model selection through composite absolute penalties' by P.
-Zhao, G.
-Rocha and B.
-Yu, Department of Statistics, UC Berkeley, Tech.
-Rep 703.)
-1.
-S.
-Negahban, P.
-Ravikumar, M.
-Wainwright, and B.
-Yu (2009).
-[A unified framework for high-dimensional analysis of $M$-estimators with decomposable regularizers](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/NegahbanRWY09.pdf) Proc.
-NIPS, 2009.
-(This conference paper contains preliminary results of the journal submission Negahban et al.
-2012).
-1.
-G.
-Raskutti, M.
-Wainwright, B.
-Yu (2009) [High-dimensional regression under lq-ball sparsity: Optimal rates of convergence.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09b.pdf) Proc.
-of Allerton Conference on Communication, Control, and Computing.
-(This conference paper contains some of preliminary results of the journal submission Ravikumar et al.
-2011).
-1.
-G.
-Raskutti, M.
-Wainwrigt, and B.
-Yu (2009) [Lower bounds on minimax rates for nonparametric regression with additive sparsity and smoothness.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09a.pdf) Proc.
-NIPS, 2009.
-(This conference paper contains some of preliminary results of the journal submission Ravikumar et al.
-2011).
-1.
-T.
-Shi, B.
-Yu, E.
-Clothiaux, and A.
-Braverman (2008).
-[Daytime Arctic Cloud Detection based on Multi-angle Satellite Data with Case Studies.](https://www.stat.berkeley.edu/~binyu/ps/jasa_resub.pdf) Journal of American Statistical Association.
-103( 482), 584-593.
-1.
-Peter Buhlmann and Bin Yu (2008) Invited discussion on "Evidence contrary to the statistical view of boosting (D.
-Mease and A.
-Wyner)".
-[(paper with discussion) ](https://www.stat.berkeley.edu/~binyu/ps/Mease08a_with_discussion.pdf) Journal of Machine Learning Research 9, 187-194.
-1.
-P.
-Ravikumer, V.
-Vu, B.
-Yu, T.
-Naselaris, K.
-Kay, J.
-Gallant (2008).
-[Nonparametric sparse hiearchical models describe V1 fMRI responses to natural images](https://www.stat.berkeley.edu/~binyu/ps/rocha.pseudo.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
-(This conference paper contains some preliminary results of journal paper Vu et al.
-(2011) on encoding models, but also contains an encoding model that is not in Vu et al.
-(2011).
-It does not contain decoding results.)
-1.
-P.
-Ravikumar, G.
-Raskutti, M.
-Wainwright, B.
-Yu (2008) [Model selection in Gaussian graphical models: high-dimensional consistency of l1-regularized MLE.](https://www.stat.berkeley.edu/~binyu/ps/covsel.nips08.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
-1. T. Shi, M. Belkin, and B. Yu (2008). [Data spectroscopy: learning mixture models using eigenspaces of convolution operators.](https://www.stat.berkeley.edu/~binyu/ps/ICML08.pdf) Proc. of ICML 2008.
-1.
-M.
-Ager, Z.
-Cvetkovic, P.
-Pollich, and B.
-Yu (2008).
-[Towards Robust Phoneme Classification Augmentation of PLP Models with Acoustic Waveforms.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=7080758) Proceedings of EUSIPCO.
-1.
-J.
-Yousafzai, Z.
-Cvetković, P.
-Pollich, and B.
-Yu (2008).
-[Combined PLP-Acoustic Waveform Classification for Robust Phoneme Recognition using Support Vector Machines.](http://www.eurasip.org/Proceedings/Eusipco/Eusipco2008/papers/1569105546.pdf) Proceedings of EUSIPCO.
-1.
-N.
-Meinshausen, G.
-Rocha, and B.
-Yu (2007).
-[A tale of three cousins: Lasso, L2Boosting, and Danzig](https://www.stat.berkeley.edu/~binyu/ps/aos.dis07.pdf) Annals of Statistics (invited discussion on Candes and Tao's Danzig Selector paper)
-1. V. Vu, B. Yu, and R. Kass (2007). [Coverage Adjusted Entropy Estimation.](https://www.stat.berkeley.edu/~binyu/ps/entropy.sub.pdf) Statistics and Medicine, 26(21), 4039-4060.
-1.
-B.
-Yu (2007).
-[Embracing Statistical Challenges in the Information Technology Age](https://www.stat.berkeley.edu/~binyu/ps/embracing.pdf) Technometrics (special issue on statistics and information technologies).
-vol.
-49 (3), 237-248.
-1.
-X.
-Jiang, Y.
-Liu, B.
-Yu and M.
-Jiang (2007).
-[Comparison of MISR aerosol optical thickness with AERONET measurements in Beijing metropolitan area.](https://www.stat.berkeley.edu/~binyu/ps/xin.pdf) Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol.
-107, pp.
-45-53.
-1.
-T.
-Shi, E.
-E.
-Clothiaux, B.
-Yu, A.
-J.
-Braverman, and G.
-N.
-Groff (2007).
-[Detection of Daytime Arctic Clouds using MISR and MODIS Data.](https://www.stat.berkeley.edu/~binyu/ps/misr-modis.pdf) Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol.
-107, pp.
-172-184.
-1. Peng Zhao and Bin Yu (2006). [On Model Selection Consistency of Lasso.](https://www.stat.berkeley.edu/~binyu/ps/LassoConsi.pdf) J. Machine Learning Research, 7 (nov), 2541-2567.
-1. B. Yu (2006). [Comments on: Monitoring networked applications with incremental quantile estimation by Chambers et al.](http://arxiv.org/pdf/0708.0338.pdf) Statist. Sci., 21, 483-485.
-1. B. Yu (2006). [Comments on: Regularization in Statistics, by P. J. Bickel and B. Li.](https://www.stat.berkeley.edu/~binyu/ps/test06.pdf) Test, vol. 15 (2), pages 314-316.
-1.
-P.
-Buhlmann and B.
-Yu (2006).
-[Sparse Boosing](https://www.stat.berkeley.edu/~binyu/ps/rev.pdf) Journal of Machine Learning Research ( 7 (June), 1001-1024).
-This is a shortened and more focused version of Buhlmann and Yu "Boosting, Model Selection, Lasso and Nonnegative Garotte" given below.
-1.
-J.
-Gao, H.
-Suzuki, and B.
-Yu (2006).
-[Approximation Lasso Methods for Language Modeling.](https://www.stat.berkeley.edu/~binyu/ps/acl.06.pdf) Proceedings of the 21st International Conference on Computational Linguistics and 44th Annual Meeting of the ACL, pp.
-225-232, Sydney.
-1. T. Shi and B. Yu (2005). [Binning in Gaussian Kernel Regularization.](https://www.stat.berkeley.edu/~binyu/ps/binning.final.pdf) Statistica Sinica (special issue on machine learning), 16, 541-567.
-1.
-G.
-Liang, N.
-Taft, and B.
-Yu (2005).
-[A fast lightweight approach to origin-destination IP traffic estimation using partial measurements.](https://www.stat.berkeley.edu/~binyu/ps/pamtram.final.pdf) Tech Report 687, Statistics Department, UCB (accepted for Special Issue of IEEE-IT and ACM Networks on data networks, Jan.
-2006)
-1. Tong Zhang and B. Yu (2005). [Boosting with early stopping: convergence and consistency.](https://www.stat.berkeley.edu/~binyu/ps/zhang.final.ps) The Annals of Statistics. Vol. 33, 1538-1579.
-1. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2005) [Network tomography: recent developments.](http://nowak.ece.wisc.edu/StatSci04.pdf) Statistical Science, 19, 499-517.
-1.
-C.
-D.
-Giurcaneanu and B.
-Yu (2005).
-[Efficient algorithms for discrete universal denoising for channels with memeory.](https://www.stat.berkeley.edu/~binyu/ps/isit05.pdf) Proceedings of International Symposium on Information Theory, Australia.
-(Also as Tech.
-Report 686, Statistics Department, UCB (Proc.
-ISIT, Sept.
-2005))
-1.
-P.
-Zhao and B.
-Yu (2004).
-[Stagewise Lasso (old title: Boosted Lasso)](https://www.stat.berkeley.edu/~binyu/ps/StagewiseLasso.pdf) Journal of Machine Learning Research, 8, 2701-2726.
-(An earlier version appeared as Tech.
-Report #678, Statistics Department, UC Berkeley (December, 2004; revised in April, 2005)
-1.
-D.
-J.
-Diner et al (2004).
-[PARAGON: A Systematic, Integrated Approach to Aerosol Observation and Modeling.](https://www.stat.berkeley.edu/~binyu/ps/paragon.pdf) American Meterological Society, Oct., 1491-1501.
-1. P. Buhlmann and B. Yu (2004). [Discussion on three boosting papers by Jiang, Lugosi and Vayatis, and Zhang](https://www.stat.berkeley.edu/~binyu/ps/disc2.ps) Annals of Statistics. 32 (1): 96-101.
-1.
-R.
-Jorsten and B.
-Yu (2004).
-[Compressing genomic and proteomic array images for statistical analyses.](https://www.stat.berkeley.edu/~binyu/ps/sig.chapter.ps) Invited chapter in a book on Genomic signal processing and statistics, edited by E.
-R.
-Dougherty, I.
-Shmulevich, J.
-Chen, and Z.
-J.
-Wang, pp.
-341 - 366.
-1.
-G.
-Liang, B.
-Yu, and N.
-Taft (2004).
-[Maximum entropy models: convergence rates and application in dynamic system monitoring.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=1365207&sortType%3Dasc_p_Sequence%26filter%3DAND%28p_IS_Number%3A29909%29%26pageNumber%3D4%26rowsPerPage%3D50) International Symposium on Information Theory, Chicago.
-1. R. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2003). [Internet Tomography: Recent Developments](https://www.stat.berkeley.edu/~binyu/ps/cny.pdf) Statistical Science. Vol. 19(3), 499-517.
-1.
-G.
-Liang and B.
-Yu (2003).
-[Maximum Pseudo Likelihood Estimation in Network Tomography.](https://www.stat.berkeley.edu/~binyu/ps/pseudo-ieee.ps) IEEE Trans.
-on Signal Processing (Special Issue on Data Networks).
-51(8), 2043-2053
-1.
-Rebecka Jornsten and Bin Yu (2003).
-[Simultaneous Gene Clustering and Subset Selection for Classification via MDL.](https://www.stat.berkeley.edu/~binyu/ps/bioinformatics.ps) Bioinformatics.
-19(9): 1100-1109.
-1. Peter Buhlmann and Bin Yu (2003). [Boosting with the L2 Loss: Regression and Classification.](https://www.stat.berkeley.edu/~binyu/ps/boostingl2.ps) J. Amer. Statist. Assoc. 98, 324-340.
-1.
-R.
-Jornsten, W.
-Wang, B.
-Yu, and K.
-Ramchandran (2003).
-[Microarray image compression: SLOCO and the effects of information loss.](https://www.stat.berkeley.edu/~binyu/ps/spj.ps) Signal Processing Journal (Special Issue on Genomic Signal Processing).
-83, 859-869.
-1. G. Liang and B. Yu (2003). [Pseudo Likelihood Estimation in Network Tomography.](http://infocom2003.ieee-infocom.org/papers/51_03.PDF) Proceedings of of Infocom, San Francisco.
-1. Peter Buhlmann and Bin Yu (2002). [Analyzing Bagging.](https://www.stat.berkeley.edu/~binyu/ps/bagging.ps) Annals of Statistics vol. 30, 927-961.
-1.
-R.
-Jornsten, M.
-Hansen, and B.
-Yu (2002).
-Adaptive Minimum Description Length (MDL) criteria with applications to microarray data.
-In Advances in Minimum Description Length: Theory and Applications, edited by P.
-Grunwald, I.J.
-Myung and M.A.
-Pitt.
-The MIT Press, pp.
-295-321.
-1.
-Mark Hansen and Bin Yu (2002).
-[Minimum Description Length Model Selection Criteria for Generalized Linear Models.](https://www.stat.berkeley.edu/~binyu/ps/mdl_glm.ps){\em Science and Statistics: Festschrift for Terry Speed}, IMS Lecture Notes -- Monograph Series, Vol.
-40.
-1.
-Rebecka Jornsten, and Bin Yu (2002).
-[Multiterminal Estimation: Extensions and a Geometric interpretation.](https://www.stat.berkeley.edu/~binyu/ps/isit02.ps) Proceedings of International Symposium on Information Theory (ISIT), June, 2002.
-1.
-Gerald Schuller, Bin Yu, Dawei Huang, and Bern Edler (2002).
-[Perceptual Audio Coding using Pre- and Poster- Filters and Lossless Compression.](https://www.stat.berkeley.edu/~binyu/ps/coding.ps) IEEE Trans.
-Speech and Audio Processing.
-Vol.
-10 (6), 379-390
-1. Mark Coates, Alfred Hero, Robert Nowak, and Bin Yu (2002). [Internet Tomography.](https://www.stat.berkeley.edu/~binyu/ps/spmag.ps) Signal Processing Magazine. vol. 19, No. 3 (May issue), 47-65.
-1.
-M.
-Hansen and B.
-Yu (2001).
-[Model selection and the principle of Minimum Description Length.](https://www.stat.berkeley.edu/~binyu/ps/mdl.ps) Journal of American Statistical Association.
-96, 746-774.
-1.
-Jin Cao, Drew Davis, Scott Vander Wiel and Bin Yu (2000).
-[[ PDF ](https://www.stat.berkeley.edu/~binyu/Site/ps/net.pdf)| [Time-varying network tomography: router link data.](https://www.stat.berkeley.edu/~binyu/ps/net.ps) J.
-Amer.
-Statist.
-Assoc.
-vol.
-95, 1063-1075.
-1.
-Peter Buhlmann and Bin Yu (2000a).
-[Discussion.
-Additive logistic regression: a statistical view of boosting, by Friedman, J., Hastie, T.
-and Tibshirani, R.](https://www.stat.berkeley.edu/~binyu/ps/disc.ps) Annals of Statistics.
-Vol.
-28, 377-386
-1.
-Mark Hansen and Bin Yu (2000).
-[Wavelet thresholding via MDL for natural images.](https://www.stat.berkeley.edu/~binyu/ps/lmdl.ps) IEEE Trans.
-Inform.
-Theory (Special Issue on Information Theoretic Imaging).
-vol.
-46, 1778-1788.
-1.
-Jorma Rissanen and Bin Yu (2000).
-[Coding and compression: a happy union of theory and practice.](https://www.stat.berkeley.edu/~binyu/ps/vig.ps) J.
-Amer.
-Statist.
-Assoc.
-(Year 2000 Commemorative Vignette on Engineering and Physical Sciences).
-vol.
-95, 986-988.
-1.
-Lei Li and Bin Yu (2000).
-[Iterated logarithm expansions of the pathwise code lengths for exponential families.](https://www.stat.berkeley.edu/~binyu/ps/pred.ps) IEEE Trans.
-Inform.
-Theory.
-vol.
-46, 2683-2689.
-1.
-G.
-Chang, B.
-Yu and M.
-Vetterli (2000).
-[Adaptive wavelet thresholding for image denoising and compression.](https://www.stat.berkeley.edu/~binyu/ps/jMDLQ.ps) IEEE Trans.
-Image Processing, vol.
-9, 1532-1546.
-1.
-G.
-Chang, B.
-Yu and M.
-Vetterli (2000).
-[Spatially adaptive wavelet thresholding based on context modeling for image denoising.](https://www.stat.berkeley.edu/~binyu/ps/spatThr.ps) IEEE Trans.
-Image Processing, vol.
-9, 1522-1531.
-1. G. Chang, B. Yu and M. Vetterli (2000). [Wavelet thresholding for multiple noisy image copies.](https://www.stat.berkeley.edu/~binyu/ps/mt.ps) IEEE Trans. Image Processing, vol. 9, 1631-1635.
-1.
-Y.
-Yoo, A.
-Ortega, and B.
-Yu (1999).
-[Image subband coding using context-based classification and adaptive quantization.](https://www.stat.berkeley.edu/~binyu/ps/yoo.ps) IEEE Trans.
-Image Processing, vol.
-8, 1702-1215.
-1. B. Yu, M. Ostland, P. Gong and R. Pu (1999). Penalized discriminant analysis of in situ hyperspectral data for conifer species recognition. IEEE Trans. Geoscience and Remote Sensing, in press.
-1.
-A.
-Barron, J.
-Rissanen, and B.
-Yu (1998).
-The Minimum Description Length principle in coding and modeling.
-(Special Commemorative Issue: Information Theory: 1948-1998) IEEE.
-Trans.
-Inform.
-Th., 44, 2743-2760.
-Reprinted in Information 50 Years of Discovery, Theory: S.
-Verdu and S.
-McLaughlin (eds), IEEE Press , 1999.
-1. B. Yu and P. Mykland (1998). Looking at Markov samplers through cusum path plots: a simple diagnostic idea. Statistics and Computing , 8, 275-286.
-1. P. Gong, R. Pu and B. Yu (1998) Conifer species recognition: effects of data transformation and band width (in Chinese) Journal of Remote Sensing, 2(3), 211-217.
-1.
-G.
-Chang, B.
-Yu and M.
-Vetterli (1998).
-[Spatially adaptive wavelet thresholding for image denoising.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=862630) Proceedings of IEEE International Conference on Image Processing, October, Chicago.
-1.
-S.
-G.
-Chang, B.
-Yu, and M.
-Vetterli (1998).
-[Image denoising via lossy compression and wavelet thresholding.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=647985) Proceedings of International Conference on Image Processing.
-Santa Barbara, California, vol.
-1, pp.
-604-607.
-1. M. Ostland and B. Yu (1997). [Exploring quasi Monte Carlo for marginal density approximation.](https://www.stat.berkeley.edu/~binyu/ps/quasiMC.pdf) Statistics and Computing, 7, 217-228.
-1. P. Gong, R. Pu, and B. Yu (1997). Conifer species recognition with in Situ hyperspectral data. Remote Sensing of Environment, 62, 189-200.
-1. B. Yu and T. P. Speed (1997). [Information and the clone mapping of chromosomes.](https://www.stat.berkeley.edu/~binyu/ps/clone.pdf) Ann. Statist. 25, 169-185.
-1. D. Nelson, T. Speed, and B. Yu (1997). The limits of random fingerprinting. Genomics, 40, 1-12.
-1.
-B.
-Yu (1997).
-[Assouad, Fano, and Le Cam.](https://www.stat.berkeley.edu/~binyu/ps/LeCam.pdf) Festschrift for Lucien Le Cam .
-D.
-Pollard, E.
-Torgersen, and G.
-Yang (eds), pp.
-423-435, Springer-Verlag.
-1. B. Yu (1996). Lower bounds on expected redundancy for nonparametric classes. IEEE Trans. on Information Theory, 42, 272-275.
-1.
-Y.
-Yoo, A.
-Ortega, and B.
-Yu (1996).
-Adaptive quantization of image subbands with efficient overhead rate selection.
-In Proceedings of IEEE International Conference on Image Processing, Lausanne, Switzerland.
-1.
-B.
-Yu (1996).
-[A Statistical analysis of adaptive scalar quantization based on quantized past data.](https://www.stat.berkeley.edu/~binyu/ps/quan.ps) In Proceedings of International Symposium on Information Theory and its Applications (ISITA96), Victoria, Canada.
-1. B. Yu (1995). Comment: Extracting more diagnostic information from a single run using cusum path plot. Statist. Sci., 10, 54-58.
-1.
-J.
-Rissanen and B.
-Yu (1995).
-MDL learning.
-In Learning and Geometry: Computational Approaches, Progress in Computer Science and Applied Logic, 14, David Kueker and Carl Smith (eds), Birkhäuser, Boston, pp.
-3-19.
-1. P. Mykland, L. Tierney, and B. Yu (1995). Regeneration in Markov Chain samplers. J. Amer. Statist. Assoc., 90, 233-241.
-1. B. Yu (1994a). Rates of convergence for empirical processes of stationary mixing sequences. Ann. Probab. 22, 94-116.
-1. M. Arcones and B. Yu (1994). Central limit theorems for empirical and U-processes of stationary mixing sequences. J. Theor. Probab. 7, 47-71.
-1. B. Yu (1994). Lower bound on the expected redundancy for classes of continuous Markov sources. In Statistical Decision Theory and Related Topics V, S. S. Gupta and J. O. Berger (eds), 453-466.
-1. M. Arcones and B. Yu (1994). Limit theorems for empirical processes under dependence. In Proceedings in Chaos expansions, multiple Wiener integrals and their applications. 205-221.
-1.
-A.
-R.
-Barron, Y.
-Yang and B.
-Yu (1994).
-Asymptotically optimal function estimation by minimum complexity criteria.
-In Proceedings of 1994 International Symposium on Information Theory, pp.
-38, Trondheim, Norway.
-1. B. Yu and T. Speed (1993). A rate of convergence result for a universal D-semifaithful code. IEEE Trans. on Information Theory 39, 8813-820.
-1. B. Yu (1993). Density estimation in the L∞ norm for dependent data with applications to the Gibbs sampler. Ann. Statist. 21, 711-735.
-1. T. Speed and B. Yu (1993). Model selection and prediction: normal regression. J. Inst. Statist. Math. 45, 35-54.
-1. J. Rissanen, T. Speed and B. Yu (1992). Density estimation by stochastic complexity. IEEE Trans. on Information Theory, 38, 315-323.
-1. B. Yu and T. Speed (1992) Data compression and histograms. Probability Theory and Related Fields, 92, 195-229.
-
----

### 2025-05-17 papers/interpretable-machine-learning.qmd
Initial commit.

--- 2025-05-17 papers.qmd
@@
 ---
-title: Papers
+title: "Interpretable Machine Learning"
 ---
 
-# Papers
+[Complete Paper List in Reverse Chronological Order](../papers.qmd)
 
-## Recent Papers by Area
+## Selected Recent Papers on Interpretable Machine Learning
 
-- [Deep Learning and Machine Learning](papers/deep-learning-and-machine-learning.qmd)
-- [Veridical Data Science (PCS)](papers/veridical-data-science-pcs.qmd)
-- [Interpretable Machine Learning](papers/interpretable-machine-learning.qmd)
-- [Interdisciplinary Research in Biomedicine](papers/interdisciplinary-research-in-biomedicine.qmd)
-- [Tree-based Methods](papers/tree-based-methods.qmd)
-
----
-
-## Complete List by Reverse Chronological Order
-
-*For the most up-to-date and complete list, see [Google Scholar](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en) or [arXiv](https://arxiv.org/search/?query=bin+yu&searchtype=author).*
-
-### Publications
-
-1. A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contextual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886)
-1. Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958)
-1. O. Ronen, A. I. Humayun, R. Balestriero, R. Baraniuk, B. Yu (2024). [ScaLES: Scalable Latent Exploration Score for Pre-Trained Generative Networks](https://arxiv.org/pdf/2406.09657)
-1. S. Hayou, N. Ghosh, B. Yu (2024). [The Impact of Initialization on LoRA Fineuning Dynamics.](https://arxiv.org/pdf/2406.08447)
-1. B. Yu (2024). [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (Harvard Data Science Review)
-1. S. Hayou, N. Ghosh, B. Yu (2024). [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) (Proc. ICML)
-1. C. F. Elliott, J. Duncan, T. M. Tang, M. Behr, K. Kumbier, B. Yu (2024). [Designing a data science simulation with MERITS: a primer.](https://arxiv.org/abs/2403.08971)
-1. Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). [Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986)
-1. N. R. Mallinar, A. Zane, S. Frei, B. Yu (2024). Minimum-Norm Interpolation Under Covariate Shift. (Proc. ICML) [arXiv](https://arxiv.org/pdf/2404.00522)
 1.
-L.
-Sun, A.
-Agarwal, A.
-Kornblith, B.
-Yu, C.
-Xiong (2024).
-ED-Copilot: Reduce Emergency Department Wait Time with Language Model Diagnostic Assistance.
-(Proc.
-ICML) [arXiv](https://arxiv.org/abs/2402.13448)
-1. C. Singh*, A. R. Hsu*, R. Antonello, S. Jain, A. G. Huth, B. Yu, J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
-1. Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262)
+A.
+R.
+Hsu, Y.
+Cherapanamjeri, A.
+Y.
+Odisho, P.
+R.
+Carroll, B.
+Yu (2024).
+[Mechanistic Interpretation through Contexual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886) [https://arxiv.org/pdf/2407.00886](https://arxiv.org/pdf/2407.00886).
+1.
+Y.
+Chen, C.
+Singh, X.
+Liu, S.
+Zuo, B.
+Yu, H.
+He, J.
+Gao (2024).
+[Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986) [https://arxiv.org/abs/2401.13986](https://arxiv.org/abs/2401.13986)
 1.
 Q.
-Wang*, T.
-M.
-Tang*, N.
-Youlton, C.
-S.
-Weldy, A.
-M.
-Kenney, O.
-Ronen, J.
-W.
-Hughes, E.
-T.
-Chin, S.
-C.
-Sutton, A.
-Agarwal, X.
-Li, M.
-Behr, K.
-Kumbier, C.
-S.
-Moravec, W.
-H.
-W.
-Tang, K.
-B.
-Margulies, T.
-P.
-Cappola, A.
-J.
-Buitte, R.
-Arnaout, J.
-B.
-Brown, J.
-R.
-Priest, V.
-N.
-Parikh, B.
-Yu*, E.
-Ashley* (2023).
-Epistasis regulates genetic control of cardiac hypertrophy.
-[medRxiv](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
-1.
-R.
-Cahill, Y.
-Wang, R.
-P.
-Xian, A.
-J.
-Lee, H.
-Zeng, B.
-Yu, B.
-Tasic, R.
-Abbasi-Asl (2023).
-Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology.
-[bioRxiv](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
-1.
-E.
-Irajizad, A.
-Kenney, T.
-Tang, J.
-Vykoukal, R.
-Wu, E.
-Murage, J.
-B.
-Dennison, M.
-Sans, J.
-P.
-Long, M.
-Loftus, J.
-A.
-Chabot, M.
-D.
-Kluger, F.
-Kastrinos, L.
-Brais, A.
-Babic, K.
-Jajoo, L.
-S.
-Lee, T.
-E.
-Clancy, K.
-Ng, A.
-Bullock, J.
-M.
-Genkinger, A.
-Maitra, K.
-A.
-Do, B.
-Yu, B.
-W.
-Wolpin, S.
-Hanash, J.
-F.
-Fahrmann.
-(2023).
-[A blood-based metabolomic signature predictive of risk for pancreatic cancer](https://pubmed.ncbi.nlm.nih.gov/37729870/).
-Cell Reports Medicine 4(9): 101194.
-doi: 10.1016/j.xcrm.2023.101194.
-(PCS related) ([Editorial](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10518497/))
-1. R. Dwivedi, C. Singh, B. Yu, M. Wainwright (2023). [Revisiting miniumu description length complexity in overparametrized models.](https://jmlr.org/papers/v24/21-1133.html) JMLR, 24(268): 1-59.
-1.
-K.
-Wu, Y.
-Chen, W.
-Ha, B.
-Yu (2023).
-[Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms.](https://arxiv.org/abs/2309.10301) JMLR (accepted).
-[https://arxiv.org/abs/2309.10301](https://arxiv.org/abs/2309.10301)
-1.
-N.
-Ghosh, S.
-Frei, W.
-Ha, B.
-Yu (2023).
-The effect of SGD batch size on autoencoder learning: sparsity, sharpness and feature learning.
-[https://arxiv.org/abs/2308.03215](https://arxiv.org/abs/2308.03215)
-1.
-R.
-Netzorg, J.
-Li, B.
-Yu (2024).
-Improving prototypical part networks with reward reweighting, reselection, and retraining.
-Proc.
-ICML.
-[https://arxiv.org/abs/2307.03887](https://arxiv.org/abs/2307.03887)
+Zhang, C.
+Singh, L.
+Liu, X.
+Liu, B.
+Yu, J.
+Gao, T.
+Zhao (2023).
+[Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262) ICLR 2024.
+https://arxiv.org/abs/2311.02262
 1.
@@
 Yu (2023).
-Diagnosing transformers: illuminating feature space for clinical decison-making.
-Proc.
-ICLR.
-[https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)
-1.
-C.
-Singh, A.
-R.
-Hsu, R.
-Antonello, S.
-Jain, A.
-G.
-Huth, B.
-Yu and J.
-Gao (2023).
-Explaining black box text modules in natural language with language models.
-[https://arxiv.org/abs/2305.09863](https://arxiv.org/abs/2305.09863)
-1.
-D.
-Shen, P.
-Ding, J.
-Sekhon, B.
-Yu (2022).
-Same root different leaves: time series and cross-sectional methods in panel data.
-Econometrica (accepted).
-[https://arxiv.org/abs/2207.14481](https://arxiv.org/abs/2207.14481)
-1.
-B.
-Park, X.
-Wu, B.
-Yu, A.
-Zhou (2022).
-[Offline evaluation in RL: soft stability weighting to combine fitted Q-learning and model-based methods.](https://openreview.net/forum?id=R3h3-bt0mq) NeurIPS 3rd Offline Reinforcement Learning Workshop.
-1.
-Y.
-S.
-Tan, C.
-Singh, K.
-Nasseri, A.
-Agarwal, J.
-Duncan, O.
-Ronen, M.
-Epland, A.
-Kornblith, B.
-Yu (2022).
-[Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931).
-([imodels 🔎](https://github.com/csinva/imodels) contains code for FIGS)
-1.
-A.
-Agarwal, Y.
-S.
-Tan, O.
-Ronen, C.
-Singh, B.
-Yu (2022).
-[Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.](https://arxiv.org/abs/2202.00858) Proc.
-ICML ([imodels 🔎](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS)).
-1.
-B.
-Yu and C.
-Singh (2022).
-[Seven principles for rapid-response data science: lessons learned from covid-19 forecasting](https://projecteuclid.org/journals/statistical-science/volume-37/issue-2/Seven-Principles-for-Rapid-Response-Data-Science--Lessons-Learned/10.1214/22-STS855.full).
-Statistical Science, 36(2):266-269.
-1. N. Ghosh, S. Mei, and B. Yu (2022). [The three stages of dynamics in high-dimensional kernel methods.](https://arxiv.org/abs/2111.07167) Proc. ICLR, 2022.
-1. Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS.
-1.
-N.
-Altieri, B.
-Park, J.
-DeNero, A.
-Odisho, B.
-Yu.
-(2021).
-[Improving natural language information extraction from cancer pathology reports using transfer learning and zero-shot string similarity.](https://pubmed.ncbi.nlm.nih.gov/34604711/) JAMIA Open.
-2021 Sept.
-30 4(3).
+[Diagnosing transformers: illuminating feature space for clinical decison-making.](https://arxiv.org/abs/2305.17588) ICLR (2024) [https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)
+1. C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
 1.
@@
 [Interpreting and Improving Deep-Learning Models with Reality Checks](https://arxiv.org/abs/2108.06847).
-To appear in "xxAI - Beyond Explainable AI" (eds.
-Holzinger et al.).
+[https://arxiv.org/abs/2108.06847](https://arxiv.org/abs/2108.06847) to appear in the book entitled "xxAI - Beyond Explainable AI" (eds.
+Andreas Holzinger, Randy Goebel, Ruth Fong, Taesup Moon, Klaus-Robert Müller, and Wojciech Samek).
 1.
@@
 ([code](https://github.com/csinva/transformation-importance))
-1.
-N.
-Altieri, R.
-Barter, J.
-Duncan, R.
-Dwivedi, K.
-Kumbier, X.
-Li, R.
-Netzorg, B.
-Park, C.
-Singh*, Y.
-Tan, T.Tang, Y.
-Wang, C.
-Zhang, B.
-Yu*.
-(2020) [Curating a COVID-19 data repository and forecasting county-level death counts in the United States.](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1) Harvard Data Science Review ([code](https://github.com/Yu-Group/covid19-severity-prediction)) [7-day prediction results](https://covidseverity.com/) [Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4)
-1.
-B.
-Yu and K.
-Kumbier (2020) [Veridical data science](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf) (PCS framework), PNAS.
-117 (8), 3920-3929.
-[QnAs with Bin Yu.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf)
-1.
-R.
-Dwivedi, N.
-Ho, K.
-Khamaru, M.
-J.
-Wainwright, M.
-I.
-Jordan and B.
-Yu (2020) [Sharp Analysis of Expectation-Maximization for Weakly Identifiable Mixture Models](https://arxiv.org/abs/1902.00194) AISTATS.
-1. R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) [Singularity, Misspecification and the Convergence Rate of EM](https://arxiv.org/abs/1810.00828) Annals of Statistics.
-1.
-Y.
-Chen, R.
-Dwivedi, M.
-J.
-Wainwright and B.
-Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients,](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, [arXiv](https://arxiv.org/abs/1905.12247)
-1. R. Dwivedi, Y. Chen, M. J. Wainwright and B. Yu (2019) [Log-concave Sampling: Metropolis Hastings Algorithms are Fast](http://jmlr.org/papers/v20/19-306.html) JMLR.
-1. D. Rothenhäusler and B. Yu (2019). [Incremental causal effects](https://arxiv.org/abs/1907.13258).
-1. Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes](http://jmlr.org/papers/v19/18-158.html). JMLR . http://jmlr.org/papers/v19/18-158.html
-1.
-Y.
-Chen, R.
-Dwivedi, M.
-J.
-Wainwright and B.
-Yu (2020) [Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier](https://ieeexplore.ieee.org/abstract/document/8262876/) Allerton Conference 2017 https://ieeexplore.ieee.org/abstract/document/8262876/
 1.
@@
 1.
-Y.
-Wang, S.
-Wu and B.
-Yu (2020) [Unique Sharp Local Minimum in l1-minimization Complete Dictionary Learning.](https://jmlr.org/papers/volume21/19-169/19-169.pdf) JMLR.
-21(63), pp.
-1-52.
-Also at https://arxiv.org/abs/1902.08380
-1.
-Y.
-Chen, R.
-Abbasi-Asl, A.
-Bloniarz, M.
-Oliver, B.
-Willmore, J.
-Gallant*, and B.
-Yu* (2018) [The DeepTune framework for modeling and characterizing neurons in visual cortex area V4](https://www.biorxiv.org/content/10.1101/465534v1) https://www.biorxiv.org/content/10.1101/465534v1
-1.
-K.
-Kumbier, S.
-Sumanta, J.
-B.
-Brown, S.
-Celniker, and B.
-Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
-1. Y. Chen C. Jin, and B. Yu (2018) [Stability and Convergence Trade-off of Iterative Optimization Algorithms.](https://arxiv.org/abs/1804.01619) https://arxiv.org/abs/1804.01619
-1.
 J.
@@
 ICLR 2018.
-[https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code)](https://github.com/csinva/hierarchical-dnn-interpretations)
-1. R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309) https://arxiv.org/abs/1801.02309.
-1. Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) [Fast MCMC sampling algorithms on polytopes](https://arxiv.org/abs/1710.08165) https://arxiv.org/abs/1710.08165.
-1.
-B.
-Yu and K.
-Kumbier (2018) [Artificial Intelligence and Statistics](https://www.stat.berkeley.edu/~binyu/ps/papers2018/AI+Stat18.pdf) Frontiers of Information Technology and Electronic Engineering.
-19(1), 6-9.
-1. R. Abbasi-Asl and B. Yu (2017) [Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning](https://arxiv.org/abs/1705.07356) https://arxiv.org/abs/1705.07356
-1.
-R.
-Abbasi-Asl and B.
-Yu (2017) [Interpreting Convolutional Neural Networks Through Compression.](https://arxiv.org/abs/1711.02329) NIPS 2017.
-Symposium on Interpretable Machine Learning.
-(also https://arxiv.org/abs/1711.02329)
-1.
-S.
-Kunzel, J.
-Sekhon, P.
-Bickel, and B.
-Yu* (2019) [Meta-learners for Estimating Heterogeneous Treatment Effects using Machine Learning,](https://www.pnas.org/content/116/10/4156) PNAS.
-116 (10) 4156-4165.
-https://arxiv.org/abs/1706.03461.
-[(code](https://github.com/soerenkuenzel/hte))
-1.
-S.
-Basu, K.
-Kumbier, J.
-B.
-Brown*, and B.
-Yu* (2018) [iterative Random Forests to discover predictive and stable high-order interactions](https://www.stat.berkeley.edu/~binyu/ps/papers2018/iRF+SI18.pdf) PNAS, 115 (8), 1943-1948.
-([code](https://github.com/Yu-Group/iterative-Random-Forest)) (PCS related)
-1.
-S.
-Balakrishnan, M.
-Wainwright, B.
-Yu (2017) [Statistical Guarantees for the EM algorithm: from population to sample-based analysis.](https://www.stat.berkeley.edu/~binyu/ps/papers2017/EM17.pdf) Annals of Statistics, 45(1), 77 - 120.
-1.
-R.
-Barter and B.
-Yu (2017) [Superheat: An R package for creating beautiful and extendable heatmaps for visualizing complex data](https://www.stat.berkeley.edu/~binyu/ps/papers2017/superheat17.pdf) JCGS (revised).
-https://github.com/rlbarter/superheat
-1.
-H.
-Liu and B.
-Yu (2017) [Comments on: High-dimensional simultaneous inference with the bootstrap by Dezeure et al](https://www.stat.berkeley.edu/~binyu/ps/papers2017/LiuYu-test17.pdf) Test.
-26: 740-750.
-1.
-C.
-Carson et al (2016).
-[UC Berkeley Data Science Planning Initiative Faculty Advisory Board (FAB) Report.](https://www.stat.berkeley.edu/~binyu/ps/FAB2016.pdf) [FAB Report Executive Summary](https://www.stat.berkeley.edu/~binyu/ps/FAB-Summary2016.pdf)
-1.
-S.
-Wu and B.
-Yu (2018).
-[Local identifiability of l1-minimization dictionary learning: a sufficient and almost necessary condition.](https://www.stat.berkeley.edu/~binyu/ps/papers2018/local-iden18.pdf) JMLR.
-18, 1 - 56.
-1.
-K.
-Rohe, T.
-Qin and B.
-Yu* (2016).
-[Co-clustering directed graphs to discover asymmetries and directional communities.](http://www.pnas.org/content/113/45/12679.full.pdf?with-ds=yes) Proc.
-National Academy of Sciences (PNAS), 113(45), 12679 - 12684.
-1.
-R.
-E.
-Kass, B.
-S.
-Caffo, M.
-Davidian, X.
-Meng, B.
-Yu, Nancy Reid* (2016).
-[Ten simple rules for effective statistical practice.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/Ten-Simple-Rules.pdf) PLoS Comput.
-Biol., 12(6): e1004961.
-doi:10.1371/journal.pcbi.1004961
-1.
-Siqi Wu, Antony Joseph, Ann S.
-Hammonds, Susan E.
-Celniker, Bin Yu*, and Erwin Frise* (2016).
-[Stability-driven nonnegative matrix factorization to interpret spatial gene expression and build local gene networks (with support information).](https://www.stat.berkeley.edu/~binyu/ps/papers2016/staNMF+SI.pdf) PNAS, pp.
-4290 - 4295.
-([code](https://github.com/yu-group/stanmf)) (PCS related)
-1.
-A.
-Bloniarz, C.
-Wu, B.
-Yu, A.
-Talwalkar (2016).
-[Supervised neighborhoods for distributed nonparametric regression.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/AISTATS16.pdf) Proc.
-of AISTATS, Barcelona, Spain.
-1. B. Yu (2015). [Data wisdom for data science.](http://www.odbms.org/2015/04/data-wisdom-for-data-science/) Operational Database Management Systems (ODBMS.ORG).
-1.
-A.
-Bloniarz, H.
-Liu, C.
-Zhang, J.
-Sekhon, and B.
-Yu* (2015).
-[Lasso adjustments of treatment effect estimates in randomized experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/lasso-adj+SI16.pdf) PNAS.
-113, 7383 - 7390.
-1.
-P.
-Ma, M.
-W.
-Mahoney and B.
-Yu (2015).
-[A Statistical Perspective on Algorithmic Leveraging.](https://www.stat.berkeley.edu/~binyu/ps/papers2015/MaMahoneyYu2015.pdf) Journal of Machine Learning Research, 16, (2015), 861-911.
-1.
-T.
-Moon, Y.
-Wang, Y.
-Liu, and B.
-Yu (2015).
-[Evaluation of a MISR-based high-resolution aerosol retrieval method using AERONET DRAGON campaign data.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=7047927) IEEE Transactions on Geoscience and Remote Sensing, 53, 4328-4339.
-1.
-B.
-Yu (2014).
-[Let us own data science.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/IMS-pres-address14-yu.pdf) [video](https://www.youtube.com/watch?v=92OjsYQJC1U) [IMS Bulletin](http://bulletin.imstat.org/2014/10/ims-presidential-address-let-us-own-data-science/) Institute of Mathematical Statistics (IMS) Presidental Address, ASC-IMS Joint Conference, Sydney, July, 2014.
-1. G. Schiebinger, M. J. Wainwright and B. Yu (2014). [The geometry of kernelized spectral clustering.](http://arxiv.org/pdf/1404.7552v3.pdf) Annals of Statistics, 43, 819-846.
-1.
-L.
-Miratrix, J.
-Jia, B.
-Yu, B.
-Gawalt, L.
-El Ghaoui, L.
-Barnesmoore, S.
-Clavier (2014).
-[Concise comparative summaries (CCS) of large text corpora with a human experiment.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/CCS14.pdf) Ann.
-Applied Statist., 8, 499-529.
-1.
-Y.
-Benjamini and B.
-Yu (2014).
-[The shuttle estimator for explainable variance in fMRI experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/BenjaminiY12.pdf) Annals of Applied Statistics, 7, 2007-2033.
-1.
-D.
-Bean, P.
-Bickel, N.
-El Karoui and B.
-Yu (2014).
-[Optimal M-estimation in high-dimensional regression.](http://www.pnas.org/content/early/2013/08/08/1307845110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1456314568.
-1.
-N.
-El Karoui, D.
-Bean, P.
-Bickel, C.
-Lim, and B.
-Yu (2014).
-[On robust regression with high-dimensional predictors.](http://www.pnas.org/content/early/2013/08/15/1307842110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1455714562.
-1.
-P.
-Ma, M.
-W.
-Mahoney, B.
-Yu (2014).
-[A Statistical Perspective on Algorithmic Leveraging.](http://arxiv.org/abs/1306.5362) Proc.
-of International Conference on Machine Learning (ICML) (This conference paper contains some of preliminary results of the journal submission Ma et al.
-(2015))
-1.
-A.
-Bloniarz, A.
-Talwalkar, J.
-Terhorst, M.
-Jordan, D.
-Patterson, B.
-Yu and Y.
-Song (2014).
-[Changepoint Analysis for Efficient Variant Calling.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/Bloniarzetal14.pdf) Proc.
-of RECOMB 2014 (to appear).
-1.
-Tao Shi (2013), [A conversation with Professor Bin Yu](http://www.yufamily.org/src/ShiTao_AnInterviewWithProfessorBinYu.php?xref=YuFamily_YuBin_interview_cn) International Chinese Statistical Association (ICSA) Bulletin, Vol 25, Issue 2, pp 85-98.
-([Selected Parts in Statblogs](http://www.statsblogs.com/2013/07/09/a-conversation-with-professor-bin-yu/))
-1. A. Joseph and B. Yu (2016). [The impact of regularization on spectral clustering.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/reg-spectral16.pdf) Annals of Statistics. 4, 1765 - 1791.
-1.
-C.
-Lim and B.
-Yu (2016).
-[Estimation Stability with Cross Validation (ESCV)](https://www.stat.berkeley.edu/~binyu/ps/papers2016/ESCV16.pdf) Journal of Computational and Graphical Statistics.
-25, 464 - 492.
-(First paper towards PCS)
-1.
-A.
-S.
-Hammonds, C.
-A.
-Bristow, W.
-W.
-Fisher, R.
-Weiszmann, S.
-Wu, V.
-Hartenstein, M.
-Kellis, B.
-Yu, E.
-Frise, and S.
-E.
-Celniker (2013).
-[Spatial expression of transcription factors in Drosophila embryonic organ development.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Hammondsetal13.pdf) Genome Biology, 14(12), R140.
-1.
-H.
-Liu and B.
-Yu (2013).
-[Asymptotic properties of Lasso+mLS and Lasso+Ridge in sparse high-dimensional linear regression.](https://www.stat.berkeley.edu/~binyu/ps/LassoOLSBootstrap13.pdf) Electron.
-J.
-Statist., 7, 312-3169.
-1.
-J.
-Mairal and B.
-Yu (2013).
-[Supervised Feature Selection in Graphs with Path Coding Penalties and Network Flows.](http://jmlr.org/papers/v14/mairal13a.html) Journal of Machine Learning Research, 14, 2449-2485.
-1.
-Y.
-Wang, X.
-Jiang, B.
-Yu, M.
-Jiang (2013).
-[A Hierarchical Bayesian Approach for Aerosol Retrieval Using MISR Data.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/WangJiangYuJiang2013.pdf) J.
-American Statistical Association, 108, 483-493.
-1.
-Y.
-He, J.
-Jia and B.
-Yu (2013).
-[Reversible MCMC on Markov equivalence classes of sparse directed acyclic graphs.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/rev-MCMC13.pdf) Annals of Statistics, 41(4), 1742-1779.
-1.
-B.
-Yu (2013).
-[Stability.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Yu13.pdf) Bernoulli, 19 (4), 1484-1500.
-(Invited paper for the Special Issue commemorating the 300th anniversary of the publication of Jakob Bernoullis Ars Conjectandi in 1712) (Begining of PCS)
-1. J. Mairal and B. Yu (2013). Discussion on Grouping Strategies and Thresholding for High Dimensional Linear Models Journal of Statistical Planning and Inference, 143, 1451-1453.
-1.
-C.
-Uhler, G.
-Raskutti, and P.
-Buhlmann and B.
-Yu (2013).
-[Geometry of faithfulness assumption in causal inference.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/faithfulness13.pdf) Annals of Statistics, 41, 436-463.
-1.
-L.
-Miratrix, J.
-Sehkon, and B.
-Yu (2013).
-[Adjusting Treatment Effect Estimates by Post-Stratification in Randomized Experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/post-stratification13.pdf) Journal of Royal Statistical Society, Series B, 75 (part 2), 369-396.
-1. J. Jia, K. Rohe and B. Yu (2013) [The Lasso under Poisson-like Heteroscadecity.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/lasso-poisson13.pdf) Statistica Sinica, 23, 99-118.
-1.
-S.
-Negahban, P.
-Ravikumar, M.
-Wainwrigt, and B.
-Yu (2012) [A unified framework for high-dimensional analysis of M-estimators with decomposable regularizers.](https://www.stat.berkeley.edu/~binyu/ps/unified-797.pdf) Statistical Science, 27, 538-557.
-1.
-G.
-Raskutti, M.
-Wainwrigt, and B.
-Yu (2012) [Minimax-optimal rates for sparse additive models over kernel classes via convex programming.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/RaskuttiWY12.pdf) J.
-Machine Learning Research, 13, 389-427.
-1.
-J.
-Mairal and B.
-Yu (2012).
-[Complexity analysis of the Lasso regularization path.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/MairalY12.pdf) Proc.
-of International Conference on Machine Learning (ICML).
-1.
-Yanfeng Gu, Shizhe Wang, Tao Shi, Yinghui Lu, Eugene E.
-Clothiaux, and Bin Yu (2012).
-[Multiple-kernel learning-based unmixing algorithm for estimation of cloud fractions with MODIS and CLOUDSAT data.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GuWSLCY12.pdf) Proc.
-of IEEE International Geoscience and Remote Sensing Symposium (IGRSS).
-1.
-S.
-Nishimoto, A.
-T.
-Vu, T.
-Naselaris, Y.
-Benjamini, B.
-Yu, J.
-L.
-Gallant (2011).
-[Reconstructing visual experiences from brain activity evoked by natural movies.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/NishimotoVNBYG11.pdf) Current Biology, 21(19), 1641-1646.
-[related videos](https://sites.google.com/site/gallantlabucb/publications/nishimoto-et-al-2011)
-1.
-P.
-Ravikumar, M.
-Wainwright, G.
-Raskutti, B.
-Yu (2011).
-[High-dimensional covariance estimation by minimizing l1-penalized log-determinant divergence.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RavikumarWRY11.pdf) Electronic Journal of Statistics, 5, 935-980.
-1.
-G.
-Raskutti, M.
-Wainwright, B.
-Yu (2011).
-[Minimax rates of estimation for high-dimensional linear regression over lq-balls.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RaskuttiWainwrightYu2011.pdf) IEEE Trans.
-Inform.
-Th., 57(10), 6976-6994.
-1.
-K.
-Rohe, S.
-Chatterjee, and B.
-Yu (2011).
-[Spectral clustering and the high-dimensional Stochastic Block Model.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RoheCY11.pdf) Annals of Statistics, 39 (4), 1878-1915
-1.
-V.
-Q.
-Vu, P.
-Ravikumar, T.
-Naselaris, K.
-N.
-Kay, J.
-L.
-Gallant, B.
-Yu* (2011).
-[Encoding and decoding V1 fMRI responses to natural images with sparse nonparametric models.](http://arxiv.org/pdf/1104.2805.pdf) Annals of Applied Statistics, 5, 1150-1182.
-(*First senior author as last author in biology tradition)
-1. S. N. Pakzad, G. Rocha, and B. Yu (2011). Distributed modal identification by regularized auto regressive models. International Journal of Systems Science, 42, 1473-1489.
-1.
-J.
-Yousafzai, P.
-Sollich, Z.
-Cvetkovic, and B.
-Yu (2011).
-[Combined Features and Kernel Design for Robust Phoneme Classification Using Support Vector Machines.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=5618550) IEEE Trans.
-Audio, Speech and Language Processing (to appear).
-64.
-1.
-X.
-Dai, J.
-Jia, B.
-Yu, El Ghaoui (2011) [SBA-term: Sparse Bilingual Association for terms.](http://www.eecs.berkeley.edu/~elghaoui/Pubs/icsc2011.pdf) Proc.
-International Conference on Semantic Computing.
-1.
-B.
-Yu (2011).
-[Asymptotics and Coding Theory: One of the n - 1 Dimensions of Terry.](http://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/Yu11.pdf) In Selected Works of Terry Speed (ed.
-S.
-Duoit), pp.
-33-36, Springer.
-1. B. Yu (2010). [Remembering Leo.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/Yu10.pdf) Annals of Applied Statistics, 4(4), 1657-1659.
-1.
-J.
-Jia, Y.
-Benjamini, C.
-Lim, G.
-Raskutti, B.
-Yu (2010).
-[Comment on "Envelope models for parsimonious and efficient multivariate linear regression" by R.
-D.
-Cook, B.
-Li, and F.
-Chiaromonte.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaBLRY10.pdf) Statistica Sinica, 20, 961-967.
-1.
-G.
-Raskutti, M.
-Wainwrigt, and B.
-Yu (2010) [Restricted Eigenvalue Properties for Correlated Gaussian Designs.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/RaskuttiWY10.pdf) Journal of Machine Learning Research, 11, 2241-2259.
-1. J. Jia and B. Yu (2010). [On model selection consistency of elastic net when p >>n.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaY10.pdf) Statistica Sinica, 10, 595-611.
-1. P. Buhlmann and B. Yu (2010). [Boosting.](http://onlinelibrary.wiley.com/doi/10.1002/wics.55/abstract) Wiley Interdisciplinary Reviews: Computational Statistics, 2, 69-74.
-1.
-L.
-Huang, J.
-Jia, B.
-Yu, B.
-Chun, P.
-Maniatis, M.
-Naik (2010).
-[Predicting Execution Time of Computer Programs Using Sparse Polynomial Regression.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HuangJYCMN10.pdf) Proc.
-NIPS 2010.
-1.
-Y.
-Han, F.
-Wu, J.
-Jia, Y.
-Zhuang and B.
-Yu (2010).
-[Multi-task Sparse Discriminant Analysis (MtSDA) with Overlapping Categories.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HanWJZY10.pdf) Proc.
-of The 24th AAAI Conference on Artificial Intelligence, July 11-15, Atlanta, GA.
-1.
-B.
-Gawalt, J.
-Jia, L.
-Miratrix, L.
-El Ghaoui, B.
-Yu, and S.
-Clavier (2010).
-[Discovering Word Associations in News Media via Feature Selection and Sparse Classification.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GawaltJMGYC10.pdf) Proc.
-11th ACM SIGMM International Confernece on Multimedia Information Retrieval (MIR).
-1.
-E.
-Anderes, B.
-Yu, V.
-Jovanovic, C.
-Moroney, M.
-Garay, A.
-Braverman, E.
-Clothiaux (2009) [Maximum Likelihood Estimation of Cloud Height from Multi-Angle Satellite Imagery.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/AnderesYJMGBC09.pdf) Annals of Applied Statistics, 3, 902-921
-1.
-T.
-Shi, M.
-Belkin, and B.
-Yu, (2009) [Data Spectroscopy: Eigenspace of Convolution Operator and Clustering](https://www.stat.berkeley.edu/~binyu/ps/shi.aos09.pdf) Annals of Statistics, 37 (6B), 3960-3984.
-1. Vincent Q. Vu, Bin Yu, Robert E. Kass (2009) [Information In The Non-Stationary Case](https://www.stat.berkeley.edu/~binyu/ps/papers2009/VuYK09.pdf) Neural computation 21, 688-703.
-1.
-N.
-Meinshausen and B.
-Yu (2009).
-[Lasso-type recovery of sparse representations for high-dimensional data.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/MeinshausenY09.pdf) Annals of Statistics 37, 246-270.
-1.
-P.
-Zhao, G.
-Rocha, and B.
-Yu (2009).
-[The composite absolute penalties family for grouped and hierarchical variable selection](https://www.stat.berkeley.edu/~binyu/ps/papers2009/ZhaoRY09.pdf) Annals of Statistics 37, 3468-3497.
-(An earlier version 'appeared as Grouped and hierarchical model selection through composite absolute penalties' by P.
-Zhao, G.
-Rocha and B.
-Yu, Department of Statistics, UC Berkeley, Tech.
-Rep 703.)
-1.
-S.
-Negahban, P.
-Ravikumar, M.
-Wainwright, and B.
-Yu (2009).
-[A unified framework for high-dimensional analysis of $M$-estimators with decomposable regularizers](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/NegahbanRWY09.pdf) Proc.
-NIPS, 2009.
-(This conference paper contains preliminary results of the journal submission Negahban et al.
-2012).
-1.
-G.
-Raskutti, M.
-Wainwright, B.
-Yu (2009) [High-dimensional regression under lq-ball sparsity: Optimal rates of convergence.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09b.pdf) Proc.
-of Allerton Conference on Communication, Control, and Computing.
-(This conference paper contains some of preliminary results of the journal submission Ravikumar et al.
-2011).
-1.
-G.
-Raskutti, M.
-Wainwrigt, and B.
-Yu (2009) [Lower bounds on minimax rates for nonparametric regression with additive sparsity and smoothness.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09a.pdf) Proc.
-NIPS, 2009.
-(This conference paper contains some of preliminary results of the journal submission Ravikumar et al.
-2011).
-1.
-T.
-Shi, B.
-Yu, E.
-Clothiaux, and A.
-Braverman (2008).
-[Daytime Arctic Cloud Detection based on Multi-angle Satellite Data with Case Studies.](https://www.stat.berkeley.edu/~binyu/ps/jasa_resub.pdf) Journal of American Statistical Association.
-103( 482), 584-593.
-1.
-Peter Buhlmann and Bin Yu (2008) Invited discussion on "Evidence contrary to the statistical view of boosting (D.
-Mease and A.
-Wyner)".
-[(paper with discussion) ](https://www.stat.berkeley.edu/~binyu/ps/Mease08a_with_discussion.pdf) Journal of Machine Learning Research 9, 187-194.
-1.
-P.
-Ravikumer, V.
-Vu, B.
-Yu, T.
-Naselaris, K.
-Kay, J.
-Gallant (2008).
-[Nonparametric sparse hiearchical models describe V1 fMRI responses to natural images](https://www.stat.berkeley.edu/~binyu/ps/rocha.pseudo.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
-(This conference paper contains some preliminary results of journal paper Vu et al.
-(2011) on encoding models, but also contains an encoding model that is not in Vu et al.
-(2011).
-It does not contain decoding results.)
-1.
-P.
-Ravikumar, G.
-Raskutti, M.
-Wainwright, B.
-Yu (2008) [Model selection in Gaussian graphical models: high-dimensional consistency of l1-regularized MLE.](https://www.stat.berkeley.edu/~binyu/ps/covsel.nips08.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
-1. T. Shi, M. Belkin, and B. Yu (2008). [Data spectroscopy: learning mixture models using eigenspaces of convolution operators.](https://www.stat.berkeley.edu/~binyu/ps/ICML08.pdf) Proc. of ICML 2008.
-1.
-M.
-Ager, Z.
-Cvetkovic, P.
-Pollich, and B.
-Yu (2008).
-[Towards Robust Phoneme Classification Augmentation of PLP Models with Acoustic Waveforms.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=7080758) Proceedings of EUSIPCO.
-1.
-J.
-Yousafzai, Z.
-Cvetković, P.
-Pollich, and B.
-Yu (2008).
-[Combined PLP-Acoustic Waveform Classification for Robust Phoneme Recognition using Support Vector Machines.](http://www.eurasip.org/Proceedings/Eusipco/Eusipco2008/papers/1569105546.pdf) Proceedings of EUSIPCO.
-1.
-N.
-Meinshausen, G.
-Rocha, and B.
-Yu (2007).
-[A tale of three cousins: Lasso, L2Boosting, and Danzig](https://www.stat.berkeley.edu/~binyu/ps/aos.dis07.pdf) Annals of Statistics (invited discussion on Candes and Tao's Danzig Selector paper)
-1. V. Vu, B. Yu, and R. Kass (2007). [Coverage Adjusted Entropy Estimation.](https://www.stat.berkeley.edu/~binyu/ps/entropy.sub.pdf) Statistics and Medicine, 26(21), 4039-4060.
-1.
-B.
-Yu (2007).
-[Embracing Statistical Challenges in the Information Technology Age](https://www.stat.berkeley.edu/~binyu/ps/embracing.pdf) Technometrics (special issue on statistics and information technologies).
-vol.
-49 (3), 237-248.
-1.
-X.
-Jiang, Y.
-Liu, B.
-Yu and M.
-Jiang (2007).
-[Comparison of MISR aerosol optical thickness with AERONET measurements in Beijing metropolitan area.](https://www.stat.berkeley.edu/~binyu/ps/xin.pdf) Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol.
-107, pp.
-45-53.
-1.
-T.
-Shi, E.
-E.
-Clothiaux, B.
-Yu, A.
-J.
-Braverman, and G.
-N.
-Groff (2007).
-[Detection of Daytime Arctic Clouds using MISR and MODIS Data.](https://www.stat.berkeley.edu/~binyu/ps/misr-modis.pdf) Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol.
-107, pp.
-172-184.
-1. Peng Zhao and Bin Yu (2006). [On Model Selection Consistency of Lasso.](https://www.stat.berkeley.edu/~binyu/ps/LassoConsi.pdf) J. Machine Learning Research, 7 (nov), 2541-2567.
-1. B. Yu (2006). [Comments on: Monitoring networked applications with incremental quantile estimation by Chambers et al.](http://arxiv.org/pdf/0708.0338.pdf) Statist. Sci., 21, 483-485.
-1. B. Yu (2006). [Comments on: Regularization in Statistics, by P. J. Bickel and B. Li.](https://www.stat.berkeley.edu/~binyu/ps/test06.pdf) Test, vol. 15 (2), pages 314-316.
-1.
-P.
-Buhlmann and B.
-Yu (2006).
-[Sparse Boosing](https://www.stat.berkeley.edu/~binyu/ps/rev.pdf) Journal of Machine Learning Research ( 7 (June), 1001-1024).
-This is a shortened and more focused version of Buhlmann and Yu "Boosting, Model Selection, Lasso and Nonnegative Garotte" given below.
-1.
-J.
-Gao, H.
-Suzuki, and B.
-Yu (2006).
-[Approximation Lasso Methods for Language Modeling.](https://www.stat.berkeley.edu/~binyu/ps/acl.06.pdf) Proceedings of the 21st International Conference on Computational Linguistics and 44th Annual Meeting of the ACL, pp.
-225-232, Sydney.
-1. T. Shi and B. Yu (2005). [Binning in Gaussian Kernel Regularization.](https://www.stat.berkeley.edu/~binyu/ps/binning.final.pdf) Statistica Sinica (special issue on machine learning), 16, 541-567.
-1.
-G.
-Liang, N.
-Taft, and B.
-Yu (2005).
-[A fast lightweight approach to origin-destination IP traffic estimation using partial measurements.](https://www.stat.berkeley.edu/~binyu/ps/pamtram.final.pdf) Tech Report 687, Statistics Department, UCB (accepted for Special Issue of IEEE-IT and ACM Networks on data networks, Jan.
-2006)
-1. Tong Zhang and B. Yu (2005). [Boosting with early stopping: convergence and consistency.](https://www.stat.berkeley.edu/~binyu/ps/zhang.final.ps) The Annals of Statistics. Vol. 33, 1538-1579.
-1. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2005) [Network tomography: recent developments.](http://nowak.ece.wisc.edu/StatSci04.pdf) Statistical Science, 19, 499-517.
-1.
-C.
-D.
-Giurcaneanu and B.
-Yu (2005).
-[Efficient algorithms for discrete universal denoising for channels with memeory.](https://www.stat.berkeley.edu/~binyu/ps/isit05.pdf) Proceedings of International Symposium on Information Theory, Australia.
-(Also as Tech.
-Report 686, Statistics Department, UCB (Proc.
-ISIT, Sept.
-2005))
-1.
-P.
-Zhao and B.
-Yu (2004).
-[Stagewise Lasso (old title: Boosted Lasso)](https://www.stat.berkeley.edu/~binyu/ps/StagewiseLasso.pdf) Journal of Machine Learning Research, 8, 2701-2726.
-(An earlier version appeared as Tech.
-Report #678, Statistics Department, UC Berkeley (December, 2004; revised in April, 2005)
-1.
-D.
-J.
-Diner et al (2004).
-[PARAGON: A Systematic, Integrated Approach to Aerosol Observation and Modeling.](https://www.stat.berkeley.edu/~binyu/ps/paragon.pdf) American Meterological Society, Oct., 1491-1501.
-1. P. Buhlmann and B. Yu (2004). [Discussion on three boosting papers by Jiang, Lugosi and Vayatis, and Zhang](https://www.stat.berkeley.edu/~binyu/ps/disc2.ps) Annals of Statistics. 32 (1): 96-101.
-1.
-R.
-Jorsten and B.
-Yu (2004).
-[Compressing genomic and proteomic array images for statistical analyses.](https://www.stat.berkeley.edu/~binyu/ps/sig.chapter.ps) Invited chapter in a book on Genomic signal processing and statistics, edited by E.
-R.
-Dougherty, I.
-Shmulevich, J.
-Chen, and Z.
-J.
-Wang, pp.
-341 - 366.
-1.
-G.
-Liang, B.
-Yu, and N.
-Taft (2004).
-[Maximum entropy models: convergence rates and application in dynamic system monitoring.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=1365207&sortType%3Dasc_p_Sequence%26filter%3DAND%28p_IS_Number%3A29909%29%26pageNumber%3D4%26rowsPerPage%3D50) International Symposium on Information Theory, Chicago.
-1. R. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2003). [Internet Tomography: Recent Developments](https://www.stat.berkeley.edu/~binyu/ps/cny.pdf) Statistical Science. Vol. 19(3), 499-517.
-1.
-G.
-Liang and B.
-Yu (2003).
-[Maximum Pseudo Likelihood Estimation in Network Tomography.](https://www.stat.berkeley.edu/~binyu/ps/pseudo-ieee.ps) IEEE Trans.
-on Signal Processing (Special Issue on Data Networks).
-51(8), 2043-2053
-1.
-Rebecka Jornsten and Bin Yu (2003).
-[Simultaneous Gene Clustering and Subset Selection for Classification via MDL.](https://www.stat.berkeley.edu/~binyu/ps/bioinformatics.ps) Bioinformatics.
-19(9): 1100-1109.
-1. Peter Buhlmann and Bin Yu (2003). [Boosting with the L2 Loss: Regression and Classification.](https://www.stat.berkeley.edu/~binyu/ps/boostingl2.ps) J. Amer. Statist. Assoc. 98, 324-340.
-1.
-R.
-Jornsten, W.
-Wang, B.
-Yu, and K.
-Ramchandran (2003).
-[Microarray image compression: SLOCO and the effects of information loss.](https://www.stat.berkeley.edu/~binyu/ps/spj.ps) Signal Processing Journal (Special Issue on Genomic Signal Processing).
-83, 859-869.
-1. G. Liang and B. Yu (2003). [Pseudo Likelihood Estimation in Network Tomography.](http://infocom2003.ieee-infocom.org/papers/51_03.PDF) Proceedings of of Infocom, San Francisco.
-1. Peter Buhlmann and Bin Yu (2002). [Analyzing Bagging.](https://www.stat.berkeley.edu/~binyu/ps/bagging.ps) Annals of Statistics vol. 30, 927-961.
-1.
-R.
-Jornsten, M.
-Hansen, and B.
-Yu (2002).
-Adaptive Minimum Description Length (MDL) criteria with applications to microarray data.
-In Advances in Minimum Description Length: Theory and Applications, edited by P.
-Grunwald, I.J.
-Myung and M.A.
-Pitt.
-The MIT Press, pp.
-295-321.
-1.
-Mark Hansen and Bin Yu (2002).
-[Minimum Description Length Model Selection Criteria for Generalized Linear Models.](https://www.stat.berkeley.edu/~binyu/ps/mdl_glm.ps){\em Science and Statistics: Festschrift for Terry Speed}, IMS Lecture Notes -- Monograph Series, Vol.
-40.
-1.
-Rebecka Jornsten, and Bin Yu (2002).
-[Multiterminal Estimation: Extensions and a Geometric interpretation.](https://www.stat.berkeley.edu/~binyu/ps/isit02.ps) Proceedings of International Symposium on Information Theory (ISIT), June, 2002.
-1.
-Gerald Schuller, Bin Yu, Dawei Huang, and Bern Edler (2002).
-[Perceptual Audio Coding using Pre- and Poster- Filters and Lossless Compression.](https://www.stat.berkeley.edu/~binyu/ps/coding.ps) IEEE Trans.
-Speech and Audio Processing.
-Vol.
-10 (6), 379-390
-1. Mark Coates, Alfred Hero, Robert Nowak, and Bin Yu (2002). [Internet Tomography.](https://www.stat.berkeley.edu/~binyu/ps/spmag.ps) Signal Processing Magazine. vol. 19, No. 3 (May issue), 47-65.
-1.
-M.
-Hansen and B.
-Yu (2001).
-[Model selection and the principle of Minimum Description Length.](https://www.stat.berkeley.edu/~binyu/ps/mdl.ps) Journal of American Statistical Association.
-96, 746-774.
-1.
-Jin Cao, Drew Davis, Scott Vander Wiel and Bin Yu (2000).
-[[ PDF ](https://www.stat.berkeley.edu/~binyu/Site/ps/net.pdf)| [Time-varying network tomography: router link data.](https://www.stat.berkeley.edu/~binyu/ps/net.ps) J.
-Amer.
-Statist.
-Assoc.
-vol.
-95, 1063-1075.
-1.
-Peter Buhlmann and Bin Yu (2000a).
-[Discussion.
-Additive logistic regression: a statistical view of boosting, by Friedman, J., Hastie, T.
-and Tibshirani, R.](https://www.stat.berkeley.edu/~binyu/ps/disc.ps) Annals of Statistics.
-Vol.
-28, 377-386
-1.
-Mark Hansen and Bin Yu (2000).
-[Wavelet thresholding via MDL for natural images.](https://www.stat.berkeley.edu/~binyu/ps/lmdl.ps) IEEE Trans.
-Inform.
-Theory (Special Issue on Information Theoretic Imaging).
-vol.
-46, 1778-1788.
-1.
-Jorma Rissanen and Bin Yu (2000).
-[Coding and compression: a happy union of theory and practice.](https://www.stat.berkeley.edu/~binyu/ps/vig.ps) J.
-Amer.
-Statist.
-Assoc.
-(Year 2000 Commemorative Vignette on Engineering and Physical Sciences).
-vol.
-95, 986-988.
-1.
-Lei Li and Bin Yu (2000).
-[Iterated logarithm expansions of the pathwise code lengths for exponential families.](https://www.stat.berkeley.edu/~binyu/ps/pred.ps) IEEE Trans.
-Inform.
-Theory.
-vol.
-46, 2683-2689.
-1.
-G.
-Chang, B.
-Yu and M.
-Vetterli (2000).
-[Adaptive wavelet thresholding for image denoising and compression.](https://www.stat.berkeley.edu/~binyu/ps/jMDLQ.ps) IEEE Trans.
-Image Processing, vol.
-9, 1532-1546.
-1.
-G.
-Chang, B.
-Yu and M.
-Vetterli (2000).
-[Spatially adaptive wavelet thresholding based on context modeling for image denoising.](https://www.stat.berkeley.edu/~binyu/ps/spatThr.ps) IEEE Trans.
-Image Processing, vol.
-9, 1522-1531.
-1. G. Chang, B. Yu and M. Vetterli (2000). [Wavelet thresholding for multiple noisy image copies.](https://www.stat.berkeley.edu/~binyu/ps/mt.ps) IEEE Trans. Image Processing, vol. 9, 1631-1635.
-1.
-Y.
-Yoo, A.
-Ortega, and B.
-Yu (1999).
-[Image subband coding using context-based classification and adaptive quantization.](https://www.stat.berkeley.edu/~binyu/ps/yoo.ps) IEEE Trans.
-Image Processing, vol.
-8, 1702-1215.
-1. B. Yu, M. Ostland, P. Gong and R. Pu (1999). Penalized discriminant analysis of in situ hyperspectral data for conifer species recognition. IEEE Trans. Geoscience and Remote Sensing, in press.
-1.
-A.
-Barron, J.
-Rissanen, and B.
-Yu (1998).
-The Minimum Description Length principle in coding and modeling.
-(Special Commemorative Issue: Information Theory: 1948-1998) IEEE.
-Trans.
-Inform.
-Th., 44, 2743-2760.
-Reprinted in Information 50 Years of Discovery, Theory: S.
-Verdu and S.
-McLaughlin (eds), IEEE Press , 1999.
-1. B. Yu and P. Mykland (1998). Looking at Markov samplers through cusum path plots: a simple diagnostic idea. Statistics and Computing , 8, 275-286.
-1. P. Gong, R. Pu and B. Yu (1998) Conifer species recognition: effects of data transformation and band width (in Chinese) Journal of Remote Sensing, 2(3), 211-217.
-1.
-G.
-Chang, B.
-Yu and M.
-Vetterli (1998).
-[Spatially adaptive wavelet thresholding for image denoising.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=862630) Proceedings of IEEE International Conference on Image Processing, October, Chicago.
-1.
-S.
-G.
-Chang, B.
-Yu, and M.
-Vetterli (1998).
-[Image denoising via lossy compression and wavelet thresholding.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=647985) Proceedings of International Conference on Image Processing.
-Santa Barbara, California, vol.
-1, pp.
-604-607.
-1. M. Ostland and B. Yu (1997). [Exploring quasi Monte Carlo for marginal density approximation.](https://www.stat.berkeley.edu/~binyu/ps/quasiMC.pdf) Statistics and Computing, 7, 217-228.
-1. P. Gong, R. Pu, and B. Yu (1997). Conifer species recognition with in Situ hyperspectral data. Remote Sensing of Environment, 62, 189-200.
-1. B. Yu and T. P. Speed (1997). [Information and the clone mapping of chromosomes.](https://www.stat.berkeley.edu/~binyu/ps/clone.pdf) Ann. Statist. 25, 169-185.
-1. D. Nelson, T. Speed, and B. Yu (1997). The limits of random fingerprinting. Genomics, 40, 1-12.
-1.
-B.
-Yu (1997).
-[Assouad, Fano, and Le Cam.](https://www.stat.berkeley.edu/~binyu/ps/LeCam.pdf) Festschrift for Lucien Le Cam .
-D.
-Pollard, E.
-Torgersen, and G.
-Yang (eds), pp.
-423-435, Springer-Verlag.
-1. B. Yu (1996). Lower bounds on expected redundancy for nonparametric classes. IEEE Trans. on Information Theory, 42, 272-275.
-1.
-Y.
-Yoo, A.
-Ortega, and B.
-Yu (1996).
-Adaptive quantization of image subbands with efficient overhead rate selection.
-In Proceedings of IEEE International Conference on Image Processing, Lausanne, Switzerland.
-1.
-B.
-Yu (1996).
-[A Statistical analysis of adaptive scalar quantization based on quantized past data.](https://www.stat.berkeley.edu/~binyu/ps/quan.ps) In Proceedings of International Symposium on Information Theory and its Applications (ISITA96), Victoria, Canada.
-1. B. Yu (1995). Comment: Extracting more diagnostic information from a single run using cusum path plot. Statist. Sci., 10, 54-58.
-1.
-J.
-Rissanen and B.
-Yu (1995).
-MDL learning.
-In Learning and Geometry: Computational Approaches, Progress in Computer Science and Applied Logic, 14, David Kueker and Carl Smith (eds), Birkhäuser, Boston, pp.
-3-19.
-1. P. Mykland, L. Tierney, and B. Yu (1995). Regeneration in Markov Chain samplers. J. Amer. Statist. Assoc., 90, 233-241.
-1. B. Yu (1994a). Rates of convergence for empirical processes of stationary mixing sequences. Ann. Probab. 22, 94-116.
-1. M. Arcones and B. Yu (1994). Central limit theorems for empirical and U-processes of stationary mixing sequences. J. Theor. Probab. 7, 47-71.
-1. B. Yu (1994). Lower bound on the expected redundancy for classes of continuous Markov sources. In Statistical Decision Theory and Related Topics V, S. S. Gupta and J. O. Berger (eds), 453-466.
-1. M. Arcones and B. Yu (1994). Limit theorems for empirical processes under dependence. In Proceedings in Chaos expansions, multiple Wiener integrals and their applications. 205-221.
-1.
-A.
-R.
-Barron, Y.
-Yang and B.
-Yu (1994).
-Asymptotically optimal function estimation by minimum complexity criteria.
-In Proceedings of 1994 International Symposium on Information Theory, pp.
-38, Trondheim, Norway.
-1. B. Yu and T. Speed (1993). A rate of convergence result for a universal D-semifaithful code. IEEE Trans. on Information Theory 39, 8813-820.
-1. B. Yu (1993). Density estimation in the L∞ norm for dependent data with applications to the Gibbs sampler. Ann. Statist. 21, 711-735.
-1. T. Speed and B. Yu (1993). Model selection and prediction: normal regression. J. Inst. Statist. Math. 45, 35-54.
-1. J. Rissanen, T. Speed and B. Yu (1992). Density estimation by stochastic complexity. IEEE Trans. on Information Theory, 38, 315-323.
-1. B. Yu and T. Speed (1992) Data compression and histograms. Probability Theory and Related Fields, 92, 195-229.
-
----
+[https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code](https://github.com/csinva/hierarchical-dnn-interpretations))

### 2025-05-17 papers/tree-based-methods.qmd
Initial commit.

---
title: "Tree-based Methods"
---

[Complete Paper List in Reverse Chronological Order](../papers.qmd)

## Selected Recent Papers on Tree-based Methods

1. Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958) [https://arxiv.org/pdf/2406.19958](https://arxiv.org/pdf/2406.19958).
1. Y. S. Tan, C. Singh, K. Nasseri, A. Agarwal, J. Duncan, O. Ronen, M. Epland, A. Kornblith, B. Yu (2022). [Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931). https://arxiv.org/abs/2201.11931 ([imodels 🔎: a python package for fitting interpretable models](https://github.com/csinva/imodels) contains code for FIGS).
1. M. Behr, Y. Wang, X. Li, B. Yu (2022). [Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.](https://arxiv.org/abs/2102.11800) PNAS, [https://arxiv.org/abs/2102.11800](https://arxiv.org/abs/2102.11800) (theory for a tractable version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS-related)
1. A. Agarwal, Y. S. Tan, O. Ronen, C. Singh, B. Yu (2022). [Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.](https://arxiv.org/abs/2202.00858) Proc. ICML [https://arxiv.org/abs/2202.00858](https://arxiv.org/abs/2202.00858) ([imodels 🔎: a python package for fitting interpretable models](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS))
1. Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS, [https://arxiv.org/abs/2110.09626](https://arxiv.org/abs/2110.09626)
1. M. Behr*, K. Kumbier*, A. Cordova-Palomera, M. Aguirre, E. Ashley, A. Butte, R. Arnaout, J. B. Brown, J. Preist*, B. Yu* (2020). [Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) [https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
1. K. Kumbier, S. Sumanta, J. B. Brown, S. Celniker, and B. Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
1. S. Basu, K. Kumbier, J. B. Brown*, and B. Yu* (2018) [iterative Random Forests to discover predictive and stable high-order interactions](https://www.stat.berkeley.edu/~binyu/ps/papers2018/iRF+SI18.pdf) PNAS, 115 (8), 1943-1948. ([code](https://github.com/Yu-Group/iterative-Random-Forest)) (PCS related)

### 2025-05-17 papers/veridical-data-science-pcs.qmd
Initial commit.

--- 2025-05-17 papers.qmd
@@
 ---
-title: Papers
+title: "Veridical Data Science (PCS)"
 ---
 
-# Papers
+[Complete Paper List in Reverse Chronological Order](../papers.qmd)
 
-## Recent Papers by Area
+## Selected Recent Papers on Veridical Data Science (PCS)
 
-- [Deep Learning and Machine Learning](papers/deep-learning-and-machine-learning.qmd)
-- [Veridical Data Science (PCS)](papers/veridical-data-science-pcs.qmd)
-- [Interpretable Machine Learning](papers/interpretable-machine-learning.qmd)
-- [Interdisciplinary Research in Biomedicine](papers/interdisciplinary-research-in-biomedicine.qmd)
-- [Tree-based Methods](papers/tree-based-methods.qmd)
-
----
-
-## Complete List by Reverse Chronological Order
-
-*For the most up-to-date and complete list, see [Google Scholar](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en) or [arXiv](https://arxiv.org/search/?query=bin+yu&searchtype=author).*
-
-### Publications
-
-1. A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contextual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886)
-1. Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958)
-1. O. Ronen, A. I. Humayun, R. Balestriero, R. Baraniuk, B. Yu (2024). [ScaLES: Scalable Latent Exploration Score for Pre-Trained Generative Networks](https://arxiv.org/pdf/2406.09657)
-1. S. Hayou, N. Ghosh, B. Yu (2024). [The Impact of Initialization on LoRA Fineuning Dynamics.](https://arxiv.org/pdf/2406.08447)
-1. B. Yu (2024). [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (Harvard Data Science Review)
-1. S. Hayou, N. Ghosh, B. Yu (2024). [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) (Proc. ICML)
-1. C. F. Elliott, J. Duncan, T. M. Tang, M. Behr, K. Kumbier, B. Yu (2024). [Designing a data science simulation with MERITS: a primer.](https://arxiv.org/abs/2403.08971)
-1. Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). [Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986)
-1. N. R. Mallinar, A. Zane, S. Frei, B. Yu (2024). Minimum-Norm Interpolation Under Covariate Shift. (Proc. ICML) [arXiv](https://arxiv.org/pdf/2404.00522)
 1.
-L.
-Sun, A.
-Agarwal, A.
-Kornblith, B.
-Yu, C.
-Xiong (2024).
-ED-Copilot: Reduce Emergency Department Wait Time with Language Model Diagnostic Assistance.
-(Proc.
-ICML) [arXiv](https://arxiv.org/abs/2402.13448)
-1. C. Singh*, A. R. Hsu*, R. Antonello, S. Jain, A. G. Huth, B. Yu, J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
-1. Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262)
+B.
+Yu (2024).
+[After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (discussion of Donoho's paper "Data Science at the Singularity") Harvard Data Science Review (HDSR).
+1. B. Yu (2023). [What is uncertainty in today's practice of data science?](https://www.sciencedirect.com/science/article/abs/pii/S030440762300235X?dgcid=author) J. Econometrics. 237, 105519.
 1.
 Q.
-Wang*, T.
+Wang, T.
 M.
-Tang*, N.
+Tang, N.
 Youlton, C.
@@
 Parikh, B.
-Yu*, E.
-Ashley* (2023).
+Yu, E.
+Ashley (2023).
 Epistasis regulates genetic control of cardiac hypertrophy.
-[medRxiv](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
+[https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
 1.
@@
 Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology.
-[bioRxiv](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
-1.
-E.
-Irajizad, A.
-Kenney, T.
-Tang, J.
-Vykoukal, R.
-Wu, E.
-Murage, J.
-B.
-Dennison, M.
-Sans, J.
-P.
-Long, M.
-Loftus, J.
-A.
-Chabot, M.
-D.
-Kluger, F.
-Kastrinos, L.
-Brais, A.
-Babic, K.
-Jajoo, L.
-S.
-Lee, T.
-E.
-Clancy, K.
-Ng, A.
-Bullock, J.
-M.
-Genkinger, A.
-Maitra, K.
-A.
-Do, B.
-Yu, B.
-W.
-Wolpin, S.
-Hanash, J.
-F.
-Fahrmann.
-(2023).
-[A blood-based metabolomic signature predictive of risk for pancreatic cancer](https://pubmed.ncbi.nlm.nih.gov/37729870/).
-Cell Reports Medicine 4(9): 101194.
-doi: 10.1016/j.xcrm.2023.101194.
-(PCS related) ([Editorial](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10518497/))
-1. R. Dwivedi, C. Singh, B. Yu, M. Wainwright (2023). [Revisiting miniumu description length complexity in overparametrized models.](https://jmlr.org/papers/v24/21-1133.html) JMLR, 24(268): 1-59.
-1.
-K.
-Wu, Y.
-Chen, W.
-Ha, B.
-Yu (2023).
-[Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms.](https://arxiv.org/abs/2309.10301) JMLR (accepted).
-[https://arxiv.org/abs/2309.10301](https://arxiv.org/abs/2309.10301)
-1.
-N.
-Ghosh, S.
-Frei, W.
-Ha, B.
-Yu (2023).
-The effect of SGD batch size on autoencoder learning: sparsity, sharpness and feature learning.
-[https://arxiv.org/abs/2308.03215](https://arxiv.org/abs/2308.03215)
-1.
-R.
-Netzorg, J.
-Li, B.
-Yu (2024).
-Improving prototypical part networks with reward reweighting, reselection, and retraining.
-Proc.
-ICML.
-[https://arxiv.org/abs/2307.03887](https://arxiv.org/abs/2307.03887)
+[https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
 1.
@@
 1.
-A.
-R.
-Hsu, Y.
-Cherapanamjeri, B.
-Park, T.
-Naumann, A.
-Odisho, and B.
-Yu (2023).
-Diagnosing transformers: illuminating feature space for clinical decison-making.
-Proc.
-ICLR.
-[https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)
-1.
-C.
-Singh, A.
-R.
-Hsu, R.
-Antonello, S.
-Jain, A.
-G.
-Huth, B.
-Yu and J.
-Gao (2023).
-Explaining black box text modules in natural language with language models.
-[https://arxiv.org/abs/2305.09863](https://arxiv.org/abs/2305.09863)
-1.
-D.
-Shen, P.
-Ding, J.
-Sekhon, B.
-Yu (2022).
-Same root different leaves: time series and cross-sectional methods in panel data.
-Econometrica (accepted).
-[https://arxiv.org/abs/2207.14481](https://arxiv.org/abs/2207.14481)
-1.
-B.
-Park, X.
-Wu, B.
-Yu, A.
-Zhou (2022).
-[Offline evaluation in RL: soft stability weighting to combine fitted Q-learning and model-based methods.](https://openreview.net/forum?id=R3h3-bt0mq) NeurIPS 3rd Offline Reinforcement Learning Workshop.
-1.
-Y.
-S.
-Tan, C.
-Singh, K.
-Nasseri, A.
-Agarwal, J.
-Duncan, O.
-Ronen, M.
-Epland, A.
-Kornblith, B.
-Yu (2022).
-[Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931).
-([imodels 🔎](https://github.com/csinva/imodels) contains code for FIGS)
-1.
-A.
-Agarwal, Y.
-S.
-Tan, O.
-Ronen, C.
-Singh, B.
-Yu (2022).
-[Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.](https://arxiv.org/abs/2202.00858) Proc.
-ICML ([imodels 🔎](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS)).
-1.
-B.
-Yu and C.
-Singh (2022).
-[Seven principles for rapid-response data science: lessons learned from covid-19 forecasting](https://projecteuclid.org/journals/statistical-science/volume-37/issue-2/Seven-Principles-for-Rapid-Response-Data-Science--Lessons-Learned/10.1214/22-STS855.full).
-Statistical Science, 36(2):266-269.
-1. N. Ghosh, S. Mei, and B. Yu (2022). [The three stages of dynamics in high-dimensional kernel methods.](https://arxiv.org/abs/2111.07167) Proc. ICLR, 2022.
-1. Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS.
-1.
-N.
-Altieri, B.
-Park, J.
-DeNero, A.
-Odisho, B.
-Yu.
-(2021).
-[Improving natural language information extraction from cancer pathology reports using transfer learning and zero-shot string similarity.](https://pubmed.ncbi.nlm.nih.gov/34604711/) JAMIA Open.
-2021 Sept.
-30 4(3).
-1.
-C.
-Singh, W.
-Ha and B.
-Yu (2021).
-[Interpreting and Improving Deep-Learning Models with Reality Checks](https://arxiv.org/abs/2108.06847).
-To appear in "xxAI - Beyond Explainable AI" (eds.
-Holzinger et al.).
-1.
-W.
-Ha, C.
-Singh, F.
-Lanusse, S.
-Upadhyayula, and B.
-Yu (2021).
-[Adaptive Wavelet Distillation from Neural Networks through Interpretation.](https://nips.cc/Conferences/2021/ScheduleMultitrack?event=28027) Proc.
-NeurIPS 2021.
-([code](https://github.com/Yu-Group/adaptive-wavelets))
-1.
-M.
-Behr, Y.
-Wang, X.
-Li, B.
-Yu (2022).
-[Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.](https://arxiv.org/abs/2102.11800) PNAS.
-([theory for iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS-related)
-1.
-N.
-Altieri, B.
-Park, M.
-Olson, J.
-DeNero, A.
-Odisho, B.
-Yu.
-(2021).
-Supervised line attention for tumor attribute classification from pathology reports: Higher performance with less data.
-Journal of Biomedical Informatics.
-122 (2021) 103872.
-[arXiv version](https://arxiv.org/abs/2012.08113)
-1.
 M.
@@
 Yu* (2020).
-[Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
+[Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) [https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
 1.
@@
 [Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y), Nature Medicine, 26, 1320–1324.
-1. B. Yu (2020). [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/1). Harvard Data Science Review (PCS related)
+1. B. Yu (2020). [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/1). Harvard Data Science Review (HDSR). (PCS related)
 1. B. Yu and R. Barter (2020). [Data science process: one culture.](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20) JASA. (PCS related)
@@
 R.
-Dwivedi, Y.
-Tan, B.
+Dwivedi*, Y.
+Tan*, B.
 Park, M.
@@
 Horgan, D.
-Madigan, B.
-Yu (2020).
-[Stable discovery of interpretable subgroups via calibration in causal studies (staDISC).](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427) International Statistical Review ([code](https://github.com/Yu-Group/stadisc)) (PCS case study for causal inference)
+Madigan*, B.
+Yu* (2020).
+[Stable discovery of interpretable subgroups via calibration in causal studies (staDISC).](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427) International Statistical Review and also at [arxiv.org/abs/2008.10109](https://arxiv.org/abs/2008.10109) ([code](https://github.com/Yu-Group/stadisc)) (PCS case study for causal inference)
 1.
@@
 NeurISP workshop on ML4H (Machine learning for Health) Extended Abstract.
-1.
-A.
-Y.
-Odisho, B.
-Park, N.
-Altieri, J.
-DeNero, M.
-R Cooperberg, P.
-R .Carroll, B.
-Yu (2020).
-[Natural language processing systems for pathology parsing in limited data environments with uncertainty estimation.](https://academic.oup.com/jamiaopen/article/3/3/431/5922788) JAMIA Open.
-1.
-L.
-Reiger, J.
-W.
-Murdoch, S.
-Singh, B.
-Yu (2020).
-[Interpretations are Useful: Penalizing Explanations to Align Neural Networks with Prior Knowledge](https://proceedings.icml.cc/static/paper_files/icml/2020/992-Paper.pdf).
-ICML Proceedings.
-([code](https://github.com/laura-rieger/deep-explanation-penalization))
-1.
-C.
-Singh, W.
-Ha, F.
-Lanusse, V.
-Boehm, J.
-Liu, B.
-Yu (2020).
-[Transformation Importance with Applications to Cosmology](https://arxiv.org/pdf/2003.01926.pdf) ICLR Workshop paper.
-([code](https://github.com/csinva/transformation-importance))
-1.
-N.
-Altieri, R.
-Barter, J.
-Duncan, R.
-Dwivedi, K.
-Kumbier, X.
-Li, R.
-Netzorg, B.
-Park, C.
-Singh*, Y.
-Tan, T.Tang, Y.
-Wang, C.
-Zhang, B.
-Yu*.
-(2020) [Curating a COVID-19 data repository and forecasting county-level death counts in the United States.](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1) Harvard Data Science Review ([code](https://github.com/Yu-Group/covid19-severity-prediction)) [7-day prediction results](https://covidseverity.com/) [Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4)
+[drive link](https://drive.google.com/file/d/1QwQwQwQwQwQwQwQwQwQwQwQwQwQwQwQ/view)
 1.
@@
 [QnAs with Bin Yu.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf)
-1.
-R.
-Dwivedi, N.
-Ho, K.
-Khamaru, M.
-J.
-Wainwright, M.
-I.
-Jordan and B.
-Yu (2020) [Sharp Analysis of Expectation-Maximization for Weakly Identifiable Mixture Models](https://arxiv.org/abs/1902.00194) AISTATS.
-1. R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) [Singularity, Misspecification and the Convergence Rate of EM](https://arxiv.org/abs/1810.00828) Annals of Statistics.
-1.
-Y.
-Chen, R.
-Dwivedi, M.
-J.
-Wainwright and B.
-Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients,](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, [arXiv](https://arxiv.org/abs/1905.12247)
-1. R. Dwivedi, Y. Chen, M. J. Wainwright and B. Yu (2019) [Log-concave Sampling: Metropolis Hastings Algorithms are Fast](http://jmlr.org/papers/v20/19-306.html) JMLR.
-1. D. Rothenhäusler and B. Yu (2019). [Incremental causal effects](https://arxiv.org/abs/1907.13258).
-1. Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes](http://jmlr.org/papers/v19/18-158.html). JMLR . http://jmlr.org/papers/v19/18-158.html
-1.
-Y.
-Chen, R.
-Dwivedi, M.
-J.
-Wainwright and B.
-Yu (2020) [Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier](https://ieeexplore.ieee.org/abstract/document/8262876/) Allerton Conference 2017 https://ieeexplore.ieee.org/abstract/document/8262876/
-1.
-W.
-J.
-Murdoch, C.
-Singh, K.
-Kumbier, R.
-Abbasi-Asl, and B.
-Yu* (2019) [Definitions, methods, and applications in interpretable machine learning.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) PNAS, 116 (44) 22071-22080.
-1.
-W.
-J.
-Murdoch, C.
-Sign, and B.
-Yu (2019).
-[Hierarchical interpretations for neural network predictions.](https://openreview.net/pdf?id=SkEqro0ctQ) ICLR.
-([code](https://github.com/csinva/hierarchical-dnn-interpretations))
-1.
-Y.
-Wang, S.
-Wu and B.
-Yu (2020) [Unique Sharp Local Minimum in l1-minimization Complete Dictionary Learning.](https://jmlr.org/papers/volume21/19-169/19-169.pdf) JMLR.
-21(63), pp.
-1-52.
-Also at https://arxiv.org/abs/1902.08380
 1.
@@
 Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
-1. Y. Chen C. Jin, and B. Yu (2018) [Stability and Convergence Trade-off of Iterative Optimization Algorithms.](https://arxiv.org/abs/1804.01619) https://arxiv.org/abs/1804.01619
-1.
-J.
-Murdoch, P.
-Liu, and B.
-Yu (2018) [Beyond word importance: contextual decomposition to extract interactions from LSTMs.](https://arxiv.org/abs/1801.05453) Proc.
-ICLR 2018.
-[https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code)](https://github.com/csinva/hierarchical-dnn-interpretations)
-1. R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309) https://arxiv.org/abs/1801.02309.
-1. Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) [Fast MCMC sampling algorithms on polytopes](https://arxiv.org/abs/1710.08165) https://arxiv.org/abs/1710.08165.
-1.
-B.
-Yu and K.
-Kumbier (2018) [Artificial Intelligence and Statistics](https://www.stat.berkeley.edu/~binyu/ps/papers2018/AI+Stat18.pdf) Frontiers of Information Technology and Electronic Engineering.
-19(1), 6-9.
-1. R. Abbasi-Asl and B. Yu (2017) [Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning](https://arxiv.org/abs/1705.07356) https://arxiv.org/abs/1705.07356
-1.
-R.
-Abbasi-Asl and B.
-Yu (2017) [Interpreting Convolutional Neural Networks Through Compression.](https://arxiv.org/abs/1711.02329) NIPS 2017.
-Symposium on Interpretable Machine Learning.
-(also https://arxiv.org/abs/1711.02329)
-1.
-S.
-Kunzel, J.
-Sekhon, P.
-Bickel, and B.
-Yu* (2019) [Meta-learners for Estimating Heterogeneous Treatment Effects using Machine Learning,](https://www.pnas.org/content/116/10/4156) PNAS.
-116 (10) 4156-4165.
-https://arxiv.org/abs/1706.03461.
-[(code](https://github.com/soerenkuenzel/hte))
 1.
@@
 1.
-S.
-Balakrishnan, M.
-Wainwright, B.
-Yu (2017) [Statistical Guarantees for the EM algorithm: from population to sample-based analysis.](https://www.stat.berkeley.edu/~binyu/ps/papers2017/EM17.pdf) Annals of Statistics, 45(1), 77 - 120.
-1.
-R.
-Barter and B.
-Yu (2017) [Superheat: An R package for creating beautiful and extendable heatmaps for visualizing complex data](https://www.stat.berkeley.edu/~binyu/ps/papers2017/superheat17.pdf) JCGS (revised).
-https://github.com/rlbarter/superheat
-1.
-H.
-Liu and B.
-Yu (2017) [Comments on: High-dimensional simultaneous inference with the bootstrap by Dezeure et al](https://www.stat.berkeley.edu/~binyu/ps/papers2017/LiuYu-test17.pdf) Test.
-26: 740-750.
-1.
-C.
-Carson et al (2016).
-[UC Berkeley Data Science Planning Initiative Faculty Advisory Board (FAB) Report.](https://www.stat.berkeley.edu/~binyu/ps/FAB2016.pdf) [FAB Report Executive Summary](https://www.stat.berkeley.edu/~binyu/ps/FAB-Summary2016.pdf)
-1.
-S.
-Wu and B.
-Yu (2018).
-[Local identifiability of l1-minimization dictionary learning: a sufficient and almost necessary condition.](https://www.stat.berkeley.edu/~binyu/ps/papers2018/local-iden18.pdf) JMLR.
-18, 1 - 56.
-1.
-K.
-Rohe, T.
-Qin and B.
-Yu* (2016).
-[Co-clustering directed graphs to discover asymmetries and directional communities.](http://www.pnas.org/content/113/45/12679.full.pdf?with-ds=yes) Proc.
-National Academy of Sciences (PNAS), 113(45), 12679 - 12684.
-1.
-R.
-E.
-Kass, B.
-S.
-Caffo, M.
-Davidian, X.
-Meng, B.
-Yu, Nancy Reid* (2016).
-[Ten simple rules for effective statistical practice.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/Ten-Simple-Rules.pdf) PLoS Comput.
-Biol., 12(6): e1004961.
-doi:10.1371/journal.pcbi.1004961
-1.
 Siqi Wu, Antony Joseph, Ann S.
@@
 ([code](https://github.com/yu-group/stanmf)) (PCS related)
-1.
-A.
-Bloniarz, C.
-Wu, B.
-Yu, A.
-Talwalkar (2016).
-[Supervised neighborhoods for distributed nonparametric regression.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/AISTATS16.pdf) Proc.
-of AISTATS, Barcelona, Spain.
-1. B. Yu (2015). [Data wisdom for data science.](http://www.odbms.org/2015/04/data-wisdom-for-data-science/) Operational Database Management Systems (ODBMS.ORG).
-1.
-A.
-Bloniarz, H.
-Liu, C.
-Zhang, J.
-Sekhon, and B.
-Yu* (2015).
-[Lasso adjustments of treatment effect estimates in randomized experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/lasso-adj+SI16.pdf) PNAS.
-113, 7383 - 7390.
-1.
-P.
-Ma, M.
-W.
-Mahoney and B.
-Yu (2015).
-[A Statistical Perspective on Algorithmic Leveraging.](https://www.stat.berkeley.edu/~binyu/ps/papers2015/MaMahoneyYu2015.pdf) Journal of Machine Learning Research, 16, (2015), 861-911.
-1.
-T.
-Moon, Y.
-Wang, Y.
-Liu, and B.
-Yu (2015).
-[Evaluation of a MISR-based high-resolution aerosol retrieval method using AERONET DRAGON campaign data.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=7047927) IEEE Transactions on Geoscience and Remote Sensing, 53, 4328-4339.
-1.
-B.
-Yu (2014).
-[Let us own data science.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/IMS-pres-address14-yu.pdf) [video](https://www.youtube.com/watch?v=92OjsYQJC1U) [IMS Bulletin](http://bulletin.imstat.org/2014/10/ims-presidential-address-let-us-own-data-science/) Institute of Mathematical Statistics (IMS) Presidental Address, ASC-IMS Joint Conference, Sydney, July, 2014.
-1. G. Schiebinger, M. J. Wainwright and B. Yu (2014). [The geometry of kernelized spectral clustering.](http://arxiv.org/pdf/1404.7552v3.pdf) Annals of Statistics, 43, 819-846.
-1.
-L.
-Miratrix, J.
-Jia, B.
-Yu, B.
-Gawalt, L.
-El Ghaoui, L.
-Barnesmoore, S.
-Clavier (2014).
-[Concise comparative summaries (CCS) of large text corpora with a human experiment.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/CCS14.pdf) Ann.
-Applied Statist., 8, 499-529.
-1.
-Y.
-Benjamini and B.
-Yu (2014).
-[The shuttle estimator for explainable variance in fMRI experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/BenjaminiY12.pdf) Annals of Applied Statistics, 7, 2007-2033.
-1.
-D.
-Bean, P.
-Bickel, N.
-El Karoui and B.
-Yu (2014).
-[Optimal M-estimation in high-dimensional regression.](http://www.pnas.org/content/early/2013/08/08/1307845110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1456314568.
-1.
-N.
-El Karoui, D.
-Bean, P.
-Bickel, C.
-Lim, and B.
-Yu (2014).
-[On robust regression with high-dimensional predictors.](http://www.pnas.org/content/early/2013/08/15/1307842110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1455714562.
-1.
-P.
-Ma, M.
-W.
-Mahoney, B.
-Yu (2014).
-[A Statistical Perspective on Algorithmic Leveraging.](http://arxiv.org/abs/1306.5362) Proc.
-of International Conference on Machine Learning (ICML) (This conference paper contains some of preliminary results of the journal submission Ma et al.
-(2015))
-1.
-A.
-Bloniarz, A.
-Talwalkar, J.
-Terhorst, M.
-Jordan, D.
-Patterson, B.
-Yu and Y.
-Song (2014).
-[Changepoint Analysis for Efficient Variant Calling.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/Bloniarzetal14.pdf) Proc.
-of RECOMB 2014 (to appear).
-1.
-Tao Shi (2013), [A conversation with Professor Bin Yu](http://www.yufamily.org/src/ShiTao_AnInterviewWithProfessorBinYu.php?xref=YuFamily_YuBin_interview_cn) International Chinese Statistical Association (ICSA) Bulletin, Vol 25, Issue 2, pp 85-98.
-([Selected Parts in Statblogs](http://www.statsblogs.com/2013/07/09/a-conversation-with-professor-bin-yu/))
-1. A. Joseph and B. Yu (2016). [The impact of regularization on spectral clustering.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/reg-spectral16.pdf) Annals of Statistics. 4, 1765 - 1791.
-1.
-C.
-Lim and B.
-Yu (2016).
-[Estimation Stability with Cross Validation (ESCV)](https://www.stat.berkeley.edu/~binyu/ps/papers2016/ESCV16.pdf) Journal of Computational and Graphical Statistics.
-25, 464 - 492.
-(First paper towards PCS)
-1.
-A.
-S.
-Hammonds, C.
-A.
-Bristow, W.
-W.
-Fisher, R.
-Weiszmann, S.
-Wu, V.
-Hartenstein, M.
-Kellis, B.
-Yu, E.
-Frise, and S.
-E.
-Celniker (2013).
-[Spatial expression of transcription factors in Drosophila embryonic organ development.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Hammondsetal13.pdf) Genome Biology, 14(12), R140.
-1.
-H.
-Liu and B.
-Yu (2013).
-[Asymptotic properties of Lasso+mLS and Lasso+Ridge in sparse high-dimensional linear regression.](https://www.stat.berkeley.edu/~binyu/ps/LassoOLSBootstrap13.pdf) Electron.
-J.
-Statist., 7, 312-3169.
-1.
-J.
-Mairal and B.
-Yu (2013).
-[Supervised Feature Selection in Graphs with Path Coding Penalties and Network Flows.](http://jmlr.org/papers/v14/mairal13a.html) Journal of Machine Learning Research, 14, 2449-2485.
-1.
-Y.
-Wang, X.
-Jiang, B.
-Yu, M.
-Jiang (2013).
-[A Hierarchical Bayesian Approach for Aerosol Retrieval Using MISR Data.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/WangJiangYuJiang2013.pdf) J.
-American Statistical Association, 108, 483-493.
-1.
-Y.
-He, J.
-Jia and B.
-Yu (2013).
-[Reversible MCMC on Markov equivalence classes of sparse directed acyclic graphs.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/rev-MCMC13.pdf) Annals of Statistics, 41(4), 1742-1779.
-1.
-B.
-Yu (2013).
-[Stability.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Yu13.pdf) Bernoulli, 19 (4), 1484-1500.
-(Invited paper for the Special Issue commemorating the 300th anniversary of the publication of Jakob Bernoullis Ars Conjectandi in 1712) (Begining of PCS)
-1. J. Mairal and B. Yu (2013). Discussion on Grouping Strategies and Thresholding for High Dimensional Linear Models Journal of Statistical Planning and Inference, 143, 1451-1453.
-1.
-C.
-Uhler, G.
-Raskutti, and P.
-Buhlmann and B.
-Yu (2013).
-[Geometry of faithfulness assumption in causal inference.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/faithfulness13.pdf) Annals of Statistics, 41, 436-463.
-1.
-L.
-Miratrix, J.
-Sehkon, and B.
-Yu (2013).
-[Adjusting Treatment Effect Estimates by Post-Stratification in Randomized Experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/post-stratification13.pdf) Journal of Royal Statistical Society, Series B, 75 (part 2), 369-396.
-1. J. Jia, K. Rohe and B. Yu (2013) [The Lasso under Poisson-like Heteroscadecity.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/lasso-poisson13.pdf) Statistica Sinica, 23, 99-118.
-1.
-S.
-Negahban, P.
-Ravikumar, M.
-Wainwrigt, and B.
-Yu (2012) [A unified framework for high-dimensional analysis of M-estimators with decomposable regularizers.](https://www.stat.berkeley.edu/~binyu/ps/unified-797.pdf) Statistical Science, 27, 538-557.
-1.
-G.
-Raskutti, M.
-Wainwrigt, and B.
-Yu (2012) [Minimax-optimal rates for sparse additive models over kernel classes via convex programming.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/RaskuttiWY12.pdf) J.
-Machine Learning Research, 13, 389-427.
-1.
-J.
-Mairal and B.
-Yu (2012).
-[Complexity analysis of the Lasso regularization path.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/MairalY12.pdf) Proc.
-of International Conference on Machine Learning (ICML).
-1.
-Yanfeng Gu, Shizhe Wang, Tao Shi, Yinghui Lu, Eugene E.
-Clothiaux, and Bin Yu (2012).
-[Multiple-kernel learning-based unmixing algorithm for estimation of cloud fractions with MODIS and CLOUDSAT data.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GuWSLCY12.pdf) Proc.
-of IEEE International Geoscience and Remote Sensing Symposium (IGRSS).
-1.
-S.
-Nishimoto, A.
-T.
-Vu, T.
-Naselaris, Y.
-Benjamini, B.
-Yu, J.
-L.
-Gallant (2011).
-[Reconstructing visual experiences from brain activity evoked by natural movies.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/NishimotoVNBYG11.pdf) Current Biology, 21(19), 1641-1646.
-[related videos](https://sites.google.com/site/gallantlabucb/publications/nishimoto-et-al-2011)
-1.
-P.
-Ravikumar, M.
-Wainwright, G.
-Raskutti, B.
-Yu (2011).
-[High-dimensional covariance estimation by minimizing l1-penalized log-determinant divergence.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RavikumarWRY11.pdf) Electronic Journal of Statistics, 5, 935-980.
-1.
-G.
-Raskutti, M.
-Wainwright, B.
-Yu (2011).
-[Minimax rates of estimation for high-dimensional linear regression over lq-balls.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RaskuttiWainwrightYu2011.pdf) IEEE Trans.
-Inform.
-Th., 57(10), 6976-6994.
-1.
-K.
-Rohe, S.
-Chatterjee, and B.
-Yu (2011).
-[Spectral clustering and the high-dimensional Stochastic Block Model.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RoheCY11.pdf) Annals of Statistics, 39 (4), 1878-1915
-1.
-V.
-Q.
-Vu, P.
-Ravikumar, T.
-Naselaris, K.
-N.
-Kay, J.
-L.
-Gallant, B.
-Yu* (2011).
-[Encoding and decoding V1 fMRI responses to natural images with sparse nonparametric models.](http://arxiv.org/pdf/1104.2805.pdf) Annals of Applied Statistics, 5, 1150-1182.
-(*First senior author as last author in biology tradition)
-1. S. N. Pakzad, G. Rocha, and B. Yu (2011). Distributed modal identification by regularized auto regressive models. International Journal of Systems Science, 42, 1473-1489.
-1.
-J.
-Yousafzai, P.
-Sollich, Z.
-Cvetkovic, and B.
-Yu (2011).
-[Combined Features and Kernel Design for Robust Phoneme Classification Using Support Vector Machines.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=5618550) IEEE Trans.
-Audio, Speech and Language Processing (to appear).
-64.
-1.
-X.
-Dai, J.
-Jia, B.
-Yu, El Ghaoui (2011) [SBA-term: Sparse Bilingual Association for terms.](http://www.eecs.berkeley.edu/~elghaoui/Pubs/icsc2011.pdf) Proc.
-International Conference on Semantic Computing.
-1.
-B.
-Yu (2011).
-[Asymptotics and Coding Theory: One of the n - 1 Dimensions of Terry.](http://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/Yu11.pdf) In Selected Works of Terry Speed (ed.
-S.
-Duoit), pp.
-33-36, Springer.
-1. B. Yu (2010). [Remembering Leo.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/Yu10.pdf) Annals of Applied Statistics, 4(4), 1657-1659.
-1.
-J.
-Jia, Y.
-Benjamini, C.
-Lim, G.
-Raskutti, B.
-Yu (2010).
-[Comment on "Envelope models for parsimonious and efficient multivariate linear regression" by R.
-D.
-Cook, B.
-Li, and F.
-Chiaromonte.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaBLRY10.pdf) Statistica Sinica, 20, 961-967.
-1.
-G.
-Raskutti, M.
-Wainwrigt, and B.
-Yu (2010) [Restricted Eigenvalue Properties for Correlated Gaussian Designs.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/RaskuttiWY10.pdf) Journal of Machine Learning Research, 11, 2241-2259.
-1. J. Jia and B. Yu (2010). [On model selection consistency of elastic net when p >>n.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaY10.pdf) Statistica Sinica, 10, 595-611.
-1. P. Buhlmann and B. Yu (2010). [Boosting.](http://onlinelibrary.wiley.com/doi/10.1002/wics.55/abstract) Wiley Interdisciplinary Reviews: Computational Statistics, 2, 69-74.
-1.
-L.
-Huang, J.
-Jia, B.
-Yu, B.
-Chun, P.
-Maniatis, M.
-Naik (2010).
-[Predicting Execution Time of Computer Programs Using Sparse Polynomial Regression.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HuangJYCMN10.pdf) Proc.
-NIPS 2010.
-1.
-Y.
-Han, F.
-Wu, J.
-Jia, Y.
-Zhuang and B.
-Yu (2010).
-[Multi-task Sparse Discriminant Analysis (MtSDA) with Overlapping Categories.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HanWJZY10.pdf) Proc.
-of The 24th AAAI Conference on Artificial Intelligence, July 11-15, Atlanta, GA.
-1.
-B.
-Gawalt, J.
-Jia, L.
-Miratrix, L.
-El Ghaoui, B.
-Yu, and S.
-Clavier (2010).
-[Discovering Word Associations in News Media via Feature Selection and Sparse Classification.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GawaltJMGYC10.pdf) Proc.
-11th ACM SIGMM International Confernece on Multimedia Information Retrieval (MIR).
-1.
-E.
-Anderes, B.
-Yu, V.
-Jovanovic, C.
-Moroney, M.
-Garay, A.
-Braverman, E.
-Clothiaux (2009) [Maximum Likelihood Estimation of Cloud Height from Multi-Angle Satellite Imagery.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/AnderesYJMGBC09.pdf) Annals of Applied Statistics, 3, 902-921
-1.
-T.
-Shi, M.
-Belkin, and B.
-Yu, (2009) [Data Spectroscopy: Eigenspace of Convolution Operator and Clustering](https://www.stat.berkeley.edu/~binyu/ps/shi.aos09.pdf) Annals of Statistics, 37 (6B), 3960-3984.
-1. Vincent Q. Vu, Bin Yu, Robert E. Kass (2009) [Information In The Non-Stationary Case](https://www.stat.berkeley.edu/~binyu/ps/papers2009/VuYK09.pdf) Neural computation 21, 688-703.
-1.
-N.
-Meinshausen and B.
-Yu (2009).
-[Lasso-type recovery of sparse representations for high-dimensional data.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/MeinshausenY09.pdf) Annals of Statistics 37, 246-270.
-1.
-P.
-Zhao, G.
-Rocha, and B.
-Yu (2009).
-[The composite absolute penalties family for grouped and hierarchical variable selection](https://www.stat.berkeley.edu/~binyu/ps/papers2009/ZhaoRY09.pdf) Annals of Statistics 37, 3468-3497.
-(An earlier version 'appeared as Grouped and hierarchical model selection through composite absolute penalties' by P.
-Zhao, G.
-Rocha and B.
-Yu, Department of Statistics, UC Berkeley, Tech.
-Rep 703.)
-1.
-S.
-Negahban, P.
-Ravikumar, M.
-Wainwright, and B.
-Yu (2009).
-[A unified framework for high-dimensional analysis of $M$-estimators with decomposable regularizers](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/NegahbanRWY09.pdf) Proc.
-NIPS, 2009.
-(This conference paper contains preliminary results of the journal submission Negahban et al.
-2012).
-1.
-G.
-Raskutti, M.
-Wainwright, B.
-Yu (2009) [High-dimensional regression under lq-ball sparsity: Optimal rates of convergence.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09b.pdf) Proc.
-of Allerton Conference on Communication, Control, and Computing.
-(This conference paper contains some of preliminary results of the journal submission Ravikumar et al.
-2011).
-1.
-G.
-Raskutti, M.
-Wainwrigt, and B.
-Yu (2009) [Lower bounds on minimax rates for nonparametric regression with additive sparsity and smoothness.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09a.pdf) Proc.
-NIPS, 2009.
-(This conference paper contains some of preliminary results of the journal submission Ravikumar et al.
-2011).
-1.
-T.
-Shi, B.
-Yu, E.
-Clothiaux, and A.
-Braverman (2008).
-[Daytime Arctic Cloud Detection based on Multi-angle Satellite Data with Case Studies.](https://www.stat.berkeley.edu/~binyu/ps/jasa_resub.pdf) Journal of American Statistical Association.
-103( 482), 584-593.
-1.
-Peter Buhlmann and Bin Yu (2008) Invited discussion on "Evidence contrary to the statistical view of boosting (D.
-Mease and A.
-Wyner)".
-[(paper with discussion) ](https://www.stat.berkeley.edu/~binyu/ps/Mease08a_with_discussion.pdf) Journal of Machine Learning Research 9, 187-194.
-1.
-P.
-Ravikumer, V.
-Vu, B.
-Yu, T.
-Naselaris, K.
-Kay, J.
-Gallant (2008).
-[Nonparametric sparse hiearchical models describe V1 fMRI responses to natural images](https://www.stat.berkeley.edu/~binyu/ps/rocha.pseudo.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
-(This conference paper contains some preliminary results of journal paper Vu et al.
-(2011) on encoding models, but also contains an encoding model that is not in Vu et al.
-(2011).
-It does not contain decoding results.)
-1.
-P.
-Ravikumar, G.
-Raskutti, M.
-Wainwright, B.
-Yu (2008) [Model selection in Gaussian graphical models: high-dimensional consistency of l1-regularized MLE.](https://www.stat.berkeley.edu/~binyu/ps/covsel.nips08.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
-1. T. Shi, M. Belkin, and B. Yu (2008). [Data spectroscopy: learning mixture models using eigenspaces of convolution operators.](https://www.stat.berkeley.edu/~binyu/ps/ICML08.pdf) Proc. of ICML 2008.
-1.
-M.
-Ager, Z.
-Cvetkovic, P.
-Pollich, and B.
-Yu (2008).
-[Towards Robust Phoneme Classification Augmentation of PLP Models with Acoustic Waveforms.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=7080758) Proceedings of EUSIPCO.
-1.
-J.
-Yousafzai, Z.
-Cvetković, P.
-Pollich, and B.
-Yu (2008).
-[Combined PLP-Acoustic Waveform Classification for Robust Phoneme Recognition using Support Vector Machines.](http://www.eurasip.org/Proceedings/Eusipco/Eusipco2008/papers/1569105546.pdf) Proceedings of EUSIPCO.
-1.
-N.
-Meinshausen, G.
-Rocha, and B.
-Yu (2007).
-[A tale of three cousins: Lasso, L2Boosting, and Danzig](https://www.stat.berkeley.edu/~binyu/ps/aos.dis07.pdf) Annals of Statistics (invited discussion on Candes and Tao's Danzig Selector paper)
-1. V. Vu, B. Yu, and R. Kass (2007). [Coverage Adjusted Entropy Estimation.](https://www.stat.berkeley.edu/~binyu/ps/entropy.sub.pdf) Statistics and Medicine, 26(21), 4039-4060.
-1.
-B.
-Yu (2007).
-[Embracing Statistical Challenges in the Information Technology Age](https://www.stat.berkeley.edu/~binyu/ps/embracing.pdf) Technometrics (special issue on statistics and information technologies).
-vol.
-49 (3), 237-248.
-1.
-X.
-Jiang, Y.
-Liu, B.
-Yu and M.
-Jiang (2007).
-[Comparison of MISR aerosol optical thickness with AERONET measurements in Beijing metropolitan area.](https://www.stat.berkeley.edu/~binyu/ps/xin.pdf) Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol.
-107, pp.
-45-53.
-1.
-T.
-Shi, E.
-E.
-Clothiaux, B.
-Yu, A.
-J.
-Braverman, and G.
-N.
-Groff (2007).
-[Detection of Daytime Arctic Clouds using MISR and MODIS Data.](https://www.stat.berkeley.edu/~binyu/ps/misr-modis.pdf) Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol.
-107, pp.
-172-184.
-1. Peng Zhao and Bin Yu (2006). [On Model Selection Consistency of Lasso.](https://www.stat.berkeley.edu/~binyu/ps/LassoConsi.pdf) J. Machine Learning Research, 7 (nov), 2541-2567.
-1. B. Yu (2006). [Comments on: Monitoring networked applications with incremental quantile estimation by Chambers et al.](http://arxiv.org/pdf/0708.0338.pdf) Statist. Sci., 21, 483-485.
-1. B. Yu (2006). [Comments on: Regularization in Statistics, by P. J. Bickel and B. Li.](https://www.stat.berkeley.edu/~binyu/ps/test06.pdf) Test, vol. 15 (2), pages 314-316.
-1.
-P.
-Buhlmann and B.
-Yu (2006).
-[Sparse Boosing](https://www.stat.berkeley.edu/~binyu/ps/rev.pdf) Journal of Machine Learning Research ( 7 (June), 1001-1024).
-This is a shortened and more focused version of Buhlmann and Yu "Boosting, Model Selection, Lasso and Nonnegative Garotte" given below.
-1.
-J.
-Gao, H.
-Suzuki, and B.
-Yu (2006).
-[Approximation Lasso Methods for Language Modeling.](https://www.stat.berkeley.edu/~binyu/ps/acl.06.pdf) Proceedings of the 21st International Conference on Computational Linguistics and 44th Annual Meeting of the ACL, pp.
-225-232, Sydney.
-1. T. Shi and B. Yu (2005). [Binning in Gaussian Kernel Regularization.](https://www.stat.berkeley.edu/~binyu/ps/binning.final.pdf) Statistica Sinica (special issue on machine learning), 16, 541-567.
-1.
-G.
-Liang, N.
-Taft, and B.
-Yu (2005).
-[A fast lightweight approach to origin-destination IP traffic estimation using partial measurements.](https://www.stat.berkeley.edu/~binyu/ps/pamtram.final.pdf) Tech Report 687, Statistics Department, UCB (accepted for Special Issue of IEEE-IT and ACM Networks on data networks, Jan.
-2006)
-1. Tong Zhang and B. Yu (2005). [Boosting with early stopping: convergence and consistency.](https://www.stat.berkeley.edu/~binyu/ps/zhang.final.ps) The Annals of Statistics. Vol. 33, 1538-1579.
-1. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2005) [Network tomography: recent developments.](http://nowak.ece.wisc.edu/StatSci04.pdf) Statistical Science, 19, 499-517.
-1.
-C.
-D.
-Giurcaneanu and B.
-Yu (2005).
-[Efficient algorithms for discrete universal denoising for channels with memeory.](https://www.stat.berkeley.edu/~binyu/ps/isit05.pdf) Proceedings of International Symposium on Information Theory, Australia.
-(Also as Tech.
-Report 686, Statistics Department, UCB (Proc.
-ISIT, Sept.
-2005))
-1.
-P.
-Zhao and B.
-Yu (2004).
-[Stagewise Lasso (old title: Boosted Lasso)](https://www.stat.berkeley.edu/~binyu/ps/StagewiseLasso.pdf) Journal of Machine Learning Research, 8, 2701-2726.
-(An earlier version appeared as Tech.
-Report #678, Statistics Department, UC Berkeley (December, 2004; revised in April, 2005)
-1.
-D.
-J.
-Diner et al (2004).
-[PARAGON: A Systematic, Integrated Approach to Aerosol Observation and Modeling.](https://www.stat.berkeley.edu/~binyu/ps/paragon.pdf) American Meterological Society, Oct., 1491-1501.
-1. P. Buhlmann and B. Yu (2004). [Discussion on three boosting papers by Jiang, Lugosi and Vayatis, and Zhang](https://www.stat.berkeley.edu/~binyu/ps/disc2.ps) Annals of Statistics. 32 (1): 96-101.
-1.
-R.
-Jorsten and B.
-Yu (2004).
-[Compressing genomic and proteomic array images for statistical analyses.](https://www.stat.berkeley.edu/~binyu/ps/sig.chapter.ps) Invited chapter in a book on Genomic signal processing and statistics, edited by E.
-R.
-Dougherty, I.
-Shmulevich, J.
-Chen, and Z.
-J.
-Wang, pp.
-341 - 366.
-1.
-G.
-Liang, B.
-Yu, and N.
-Taft (2004).
-[Maximum entropy models: convergence rates and application in dynamic system monitoring.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=1365207&sortType%3Dasc_p_Sequence%26filter%3DAND%28p_IS_Number%3A29909%29%26pageNumber%3D4%26rowsPerPage%3D50) International Symposium on Information Theory, Chicago.
-1. R. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2003). [Internet Tomography: Recent Developments](https://www.stat.berkeley.edu/~binyu/ps/cny.pdf) Statistical Science. Vol. 19(3), 499-517.
-1.
-G.
-Liang and B.
-Yu (2003).
-[Maximum Pseudo Likelihood Estimation in Network Tomography.](https://www.stat.berkeley.edu/~binyu/ps/pseudo-ieee.ps) IEEE Trans.
-on Signal Processing (Special Issue on Data Networks).
-51(8), 2043-2053
-1.
-Rebecka Jornsten and Bin Yu (2003).
-[Simultaneous Gene Clustering and Subset Selection for Classification via MDL.](https://www.stat.berkeley.edu/~binyu/ps/bioinformatics.ps) Bioinformatics.
-19(9): 1100-1109.
-1. Peter Buhlmann and Bin Yu (2003). [Boosting with the L2 Loss: Regression and Classification.](https://www.stat.berkeley.edu/~binyu/ps/boostingl2.ps) J. Amer. Statist. Assoc. 98, 324-340.
-1.
-R.
-Jornsten, W.
-Wang, B.
-Yu, and K.
-Ramchandran (2003).
-[Microarray image compression: SLOCO and the effects of information loss.](https://www.stat.berkeley.edu/~binyu/ps/spj.ps) Signal Processing Journal (Special Issue on Genomic Signal Processing).
-83, 859-869.
-1. G. Liang and B. Yu (2003). [Pseudo Likelihood Estimation in Network Tomography.](http://infocom2003.ieee-infocom.org/papers/51_03.PDF) Proceedings of of Infocom, San Francisco.
-1. Peter Buhlmann and Bin Yu (2002). [Analyzing Bagging.](https://www.stat.berkeley.edu/~binyu/ps/bagging.ps) Annals of Statistics vol. 30, 927-961.
-1.
-R.
-Jornsten, M.
-Hansen, and B.
-Yu (2002).
-Adaptive Minimum Description Length (MDL) criteria with applications to microarray data.
-In Advances in Minimum Description Length: Theory and Applications, edited by P.
-Grunwald, I.J.
-Myung and M.A.
-Pitt.
-The MIT Press, pp.
-295-321.
-1.
-Mark Hansen and Bin Yu (2002).
-[Minimum Description Length Model Selection Criteria for Generalized Linear Models.](https://www.stat.berkeley.edu/~binyu/ps/mdl_glm.ps){\em Science and Statistics: Festschrift for Terry Speed}, IMS Lecture Notes -- Monograph Series, Vol.
-40.
-1.
-Rebecka Jornsten, and Bin Yu (2002).
-[Multiterminal Estimation: Extensions and a Geometric interpretation.](https://www.stat.berkeley.edu/~binyu/ps/isit02.ps) Proceedings of International Symposium on Information Theory (ISIT), June, 2002.
-1.
-Gerald Schuller, Bin Yu, Dawei Huang, and Bern Edler (2002).
-[Perceptual Audio Coding using Pre- and Poster- Filters and Lossless Compression.](https://www.stat.berkeley.edu/~binyu/ps/coding.ps) IEEE Trans.
-Speech and Audio Processing.
-Vol.
-10 (6), 379-390
-1. Mark Coates, Alfred Hero, Robert Nowak, and Bin Yu (2002). [Internet Tomography.](https://www.stat.berkeley.edu/~binyu/ps/spmag.ps) Signal Processing Magazine. vol. 19, No. 3 (May issue), 47-65.
-1.
-M.
-Hansen and B.
-Yu (2001).
-[Model selection and the principle of Minimum Description Length.](https://www.stat.berkeley.edu/~binyu/ps/mdl.ps) Journal of American Statistical Association.
-96, 746-774.
-1.
-Jin Cao, Drew Davis, Scott Vander Wiel and Bin Yu (2000).
-[[ PDF ](https://www.stat.berkeley.edu/~binyu/Site/ps/net.pdf)| [Time-varying network tomography: router link data.](https://www.stat.berkeley.edu/~binyu/ps/net.ps) J.
-Amer.
-Statist.
-Assoc.
-vol.
-95, 1063-1075.
-1.
-Peter Buhlmann and Bin Yu (2000a).
-[Discussion.
-Additive logistic regression: a statistical view of boosting, by Friedman, J., Hastie, T.
-and Tibshirani, R.](https://www.stat.berkeley.edu/~binyu/ps/disc.ps) Annals of Statistics.
-Vol.
-28, 377-386
-1.
-Mark Hansen and Bin Yu (2000).
-[Wavelet thresholding via MDL for natural images.](https://www.stat.berkeley.edu/~binyu/ps/lmdl.ps) IEEE Trans.
-Inform.
-Theory (Special Issue on Information Theoretic Imaging).
-vol.
-46, 1778-1788.
-1.
-Jorma Rissanen and Bin Yu (2000).
-[Coding and compression: a happy union of theory and practice.](https://www.stat.berkeley.edu/~binyu/ps/vig.ps) J.
-Amer.
-Statist.
-Assoc.
-(Year 2000 Commemorative Vignette on Engineering and Physical Sciences).
-vol.
-95, 986-988.
-1.
-Lei Li and Bin Yu (2000).
-[Iterated logarithm expansions of the pathwise code lengths for exponential families.](https://www.stat.berkeley.edu/~binyu/ps/pred.ps) IEEE Trans.
-Inform.
-Theory.
-vol.
-46, 2683-2689.
-1.
-G.
-Chang, B.
-Yu and M.
-Vetterli (2000).
-[Adaptive wavelet thresholding for image denoising and compression.](https://www.stat.berkeley.edu/~binyu/ps/jMDLQ.ps) IEEE Trans.
-Image Processing, vol.
-9, 1532-1546.
-1.
-G.
-Chang, B.
-Yu and M.
-Vetterli (2000).
-[Spatially adaptive wavelet thresholding based on context modeling for image denoising.](https://www.stat.berkeley.edu/~binyu/ps/spatThr.ps) IEEE Trans.
-Image Processing, vol.
-9, 1522-1531.
-1. G. Chang, B. Yu and M. Vetterli (2000). [Wavelet thresholding for multiple noisy image copies.](https://www.stat.berkeley.edu/~binyu/ps/mt.ps) IEEE Trans. Image Processing, vol. 9, 1631-1635.
-1.
-Y.
-Yoo, A.
-Ortega, and B.
-Yu (1999).
-[Image subband coding using context-based classification and adaptive quantization.](https://www.stat.berkeley.edu/~binyu/ps/yoo.ps) IEEE Trans.
-Image Processing, vol.
-8, 1702-1215.
-1. B. Yu, M. Ostland, P. Gong and R. Pu (1999). Penalized discriminant analysis of in situ hyperspectral data for conifer species recognition. IEEE Trans. Geoscience and Remote Sensing, in press.
-1.
-A.
-Barron, J.
-Rissanen, and B.
-Yu (1998).
-The Minimum Description Length principle in coding and modeling.
-(Special Commemorative Issue: Information Theory: 1948-1998) IEEE.
-Trans.
-Inform.
-Th., 44, 2743-2760.
-Reprinted in Information 50 Years of Discovery, Theory: S.
-Verdu and S.
-McLaughlin (eds), IEEE Press , 1999.
-1. B. Yu and P. Mykland (1998). Looking at Markov samplers through cusum path plots: a simple diagnostic idea. Statistics and Computing , 8, 275-286.
-1. P. Gong, R. Pu and B. Yu (1998) Conifer species recognition: effects of data transformation and band width (in Chinese) Journal of Remote Sensing, 2(3), 211-217.
-1.
-G.
-Chang, B.
-Yu and M.
-Vetterli (1998).
-[Spatially adaptive wavelet thresholding for image denoising.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=862630) Proceedings of IEEE International Conference on Image Processing, October, Chicago.
-1.
-S.
-G.
-Chang, B.
-Yu, and M.
-Vetterli (1998).
-[Image denoising via lossy compression and wavelet thresholding.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=647985) Proceedings of International Conference on Image Processing.
-Santa Barbara, California, vol.
-1, pp.
-604-607.
-1. M. Ostland and B. Yu (1997). [Exploring quasi Monte Carlo for marginal density approximation.](https://www.stat.berkeley.edu/~binyu/ps/quasiMC.pdf) Statistics and Computing, 7, 217-228.
-1. P. Gong, R. Pu, and B. Yu (1997). Conifer species recognition with in Situ hyperspectral data. Remote Sensing of Environment, 62, 189-200.
-1. B. Yu and T. P. Speed (1997). [Information and the clone mapping of chromosomes.](https://www.stat.berkeley.edu/~binyu/ps/clone.pdf) Ann. Statist. 25, 169-185.
-1. D. Nelson, T. Speed, and B. Yu (1997). The limits of random fingerprinting. Genomics, 40, 1-12.
-1.
-B.
-Yu (1997).
-[Assouad, Fano, and Le Cam.](https://www.stat.berkeley.edu/~binyu/ps/LeCam.pdf) Festschrift for Lucien Le Cam .
-D.
-Pollard, E.
-Torgersen, and G.
-Yang (eds), pp.
-423-435, Springer-Verlag.
-1. B. Yu (1996). Lower bounds on expected redundancy for nonparametric classes. IEEE Trans. on Information Theory, 42, 272-275.
-1.
-Y.
-Yoo, A.
-Ortega, and B.
-Yu (1996).
-Adaptive quantization of image subbands with efficient overhead rate selection.
-In Proceedings of IEEE International Conference on Image Processing, Lausanne, Switzerland.
-1.
-B.
-Yu (1996).
-[A Statistical analysis of adaptive scalar quantization based on quantized past data.](https://www.stat.berkeley.edu/~binyu/ps/quan.ps) In Proceedings of International Symposium on Information Theory and its Applications (ISITA96), Victoria, Canada.
-1. B. Yu (1995). Comment: Extracting more diagnostic information from a single run using cusum path plot. Statist. Sci., 10, 54-58.
-1.
-J.
-Rissanen and B.
-Yu (1995).
-MDL learning.
-In Learning and Geometry: Computational Approaches, Progress in Computer Science and Applied Logic, 14, David Kueker and Carl Smith (eds), Birkhäuser, Boston, pp.
-3-19.
-1. P. Mykland, L. Tierney, and B. Yu (1995). Regeneration in Markov Chain samplers. J. Amer. Statist. Assoc., 90, 233-241.
-1. B. Yu (1994a). Rates of convergence for empirical processes of stationary mixing sequences. Ann. Probab. 22, 94-116.
-1. M. Arcones and B. Yu (1994). Central limit theorems for empirical and U-processes of stationary mixing sequences. J. Theor. Probab. 7, 47-71.
-1. B. Yu (1994). Lower bound on the expected redundancy for classes of continuous Markov sources. In Statistical Decision Theory and Related Topics V, S. S. Gupta and J. O. Berger (eds), 453-466.
-1. M. Arcones and B. Yu (1994). Limit theorems for empirical processes under dependence. In Proceedings in Chaos expansions, multiple Wiener integrals and their applications. 205-221.
-1.
-A.
-R.
-Barron, Y.
-Yang and B.
-Yu (1994).
-Asymptotically optimal function estimation by minimum complexity criteria.
-In Proceedings of 1994 International Symposium on Information Theory, pp.
-38, Trondheim, Norway.
-1. B. Yu and T. Speed (1993). A rate of convergence result for a universal D-semifaithful code. IEEE Trans. on Information Theory 39, 8813-820.
-1. B. Yu (1993). Density estimation in the L∞ norm for dependent data with applications to the Gibbs sampler. Ann. Statist. 21, 711-735.
-1. T. Speed and B. Yu (1993). Model selection and prediction: normal regression. J. Inst. Statist. Math. 45, 35-54.
-1. J. Rissanen, T. Speed and B. Yu (1992). Density estimation by stochastic complexity. IEEE Trans. on Information Theory, 38, 315-323.
-1. B. Yu and T. Speed (1992) Data compression and histograms. Probability Theory and Related Fields, 92, 195-229.
-
----

### 2025-05-17 research.qmd
Initial commit.

---
title: Research
---

# Research

In 2014, I was elected to the National Academy of Sciences based on my statistical and scientific contributions, as well as my broad vision of data science best described in my article [Veridical Data Science](https://www.pnas.org/content/117/8/3920), written together with my former student Karl Kumbier. In this work, I introduced a framework based on three principles: predictability, computability and stability (abbreviated to PCS). This framework helps guide practitioners who solve domain data problems with data science tools to be creative in their analysis and properly validate their findings. I have written a book on the Veridical Data Science framework together with my former student [Rebecca Barter](https://www.rebeccabarter.com/). The book is being published by the MIT Press in 2024 with a free on-line copy available soon.

In my research group, I cultivate a strongly interdisciplinary and collaborative culture, solving data problems across fields such as neuroscience, genomics, remote sensing, and precision medicine. Through these projects we have successfully [mapped a cell's destiny](https://newscenter.lbl.gov/2016/05/04/mapping-cells-destiny/) using spatial gene expression images of Drosophila embryos, we have characterized V4 neurons through [DeepTune](https://www.biorxiv.org/content/10.1101/465534v1) images, and we are currently seeking genomic markers of heart disease using UK Biobank data. Recently, my group and I have developed approaches for [predicting county-level COVID-19 death counts](https://covidseverity.com/) in an effort to support the non-profit, [Response4Life](https://response4life.org/), who are working towards distributing PPE across the country to those who need it most.

The Yu Group and I have also developed an array of statistical and machine learning methods inspired by our interdisciplinary projects, including [stability-driven nonnegative matrix factorization (staNMF)](https://github.com/Yu-Group/staNMF) for unsupervised learning, [iterative Random Forests (iRF)](https://github.com/Yu-Group/iterative-Random-Forest) and [signed iRF (s-iRF)](https://github.com/karlkumbier/iRF2.0) for discovering predictive and stable high-order (Boolean) interactions in supervised learning, [contextual decomposition (CD)](https://github.com/jamie-murdoch/ContextualDecomposition) and [aggregated contextual decomposition (ACD)](https://github.com/csinva/hierarchical-dnn-interpretations) for phrase or patch importance extraction from Deep Neural Networks (DNNs).

Research is supported in part by grants from NSF, NIH, the Weill Neurohub, and the Simons Foundation.

- [Yu Group at Berkeley](https://www.stat.berkeley.edu/~yugroup/) for current group members and current projects
- [Papers](https://binyu.stat.berkeley.edu/papers)
- [Code](https://www.stat.berkeley.edu/~yugroup/code.html)
- [Statistical Machine Learning at Berkeley](http://www.stat.berkeley.edu/~statlearning/)

### 2025-05-17 teaching.qmd
Initial commit.

---
title: "Teaching"
---

# Teaching

## 2020 Fall

- Statistical Models: Theory and Application  [[STAT 215A](https://classes.berkeley.edu/content/2019-Fall-STAT-215A-001-LEC-001)]

## 2019 Fall

- Statistical Models: Theory and Application  [[STAT 215A](https://classes.berkeley.edu/content/2019-Fall-STAT-215A-001-LEC-001)]

## 2019 Spring

- [Modern Statistical Prediction and Machine Learning](https://stat154.github.io/logistics/)  [[STAT 154](https://classes.berkeley.edu/content/2019-Spring-STAT-154-001-LEC-001)]

### 2025-06-16 index.qmd
Add link.
Bin sent in a link by email.

@@
 
+- [Veridical Data Science in Biology on July 11, 2024 at UC Berkeley (Submission deadline July 4)](https://www.eventbrite.com/e/veridical-data-science-for-biology-2025-tickets-1384456339179)
 - [Rome Workshop on Veridical Data Science, June 20, 2025](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html) (New)

### 2025-07-10 index.qmd
Update index.qmd

@@
 
-- [Veridical Data Science in Biology on July 11, 2024 at UC Berkeley (Submission deadline July 4)](https://www.eventbrite.com/e/veridical-data-science-for-biology-2025-tickets-1384456339179)
+- [New paper: PCS workflow for veridical data science in the age of AI (Z. Rewolinski and B. Yu, 2025)](https://www.stat.berkeley.edu/~yugroup/pubs/pcs_workflow-6.pdf)
+- [Veridical Data Science in Biology on July 11, 2025 at UC Berkeley (Submission deadline July 4)](https://www.eventbrite.com/e/veridical-data-science-for-biology-2025-tickets-1384456339179)
 - [Rome Workshop on Veridical Data Science, June 20, 2025](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html) (New)

### 2025-07-19 about.qmd
Update website structure and content
Replaced the 'Research' section with a new 'About' page, detailing Professor Bin Yu's background and the Yu Group's research focus. Updated navigation links in _quarto.yml to reflect these changes, removing the old 'Research' link and adding 'About' and 'People' links. Enhanced the index.qmd layout for better presentation of recent publications and news, and added a responsive two-column layout in styles.css for improved readability.

--- 2025-05-17 bio.qmd
@@
 ---
-title: Biography
+title: About
 ---
 
-# Biography
+# About Bin
 
@@
 
+Professor Bin Yu was formally trained as a statistician, but her research interests and achievements extend beyond the realm of statistics.
+Together with her group, Bin Yu has leveraged new computational developments to solve important scientific problems by combining novel and often interpretable statistical machine learning approaches with the domain expertise of her many collaborators in neuroscience, genomics and precision medicine.
+She also develops relevant theory to understand random forests and deep learning for insight into and guidance for practice.
+Her work has been recognized by many awards.
+In particular, she was inducted to the National Academy of Sciences in 2014 and to the American Academy of Arts and Sciences in 2013.
+She delivered the IMS Wald Lectures and COPSS Distinguished Achievement and Award Lecture (DAAL, formerly Fisher Award and Lecture) in 2023.
+
 Currently, she is championing "in-context" research with experts in the subject knowledge and leading research in interpretable machine learning (e.g.
@@
 She is serving on the advisory board of the AI Policy Hub at UC Berkeley, the Scientific Advisory Committee of the Department of Quantitative and Computational Biology at USC, and on the External Advisory Committee, Learning the Earth with Artificial Intelligence and Physics (LEAP), an NSF Science and Technology Center (STC), at Columbia University.
+
+# About the Research Group
+
+The [Yu Group](https://www.stat.berkeley.edu/~yugroup/) at Berkeley consists of 12-15 students and postdocs from Statistics and EECS.
+In the research group, we cultivate a strongly interdisciplinary and collaborative culture, solving data problems across fields such as neuroscience, genomics, remote sensing, and precision medicine.
+
+Through these projects we have successfully [mapped a cell's destiny](https://newscenter.lbl.gov/2016/05/04/mapping-cells-destiny/) using spatial gene expression images of Drosophila embryos, we have characterized V4 neurons through [DeepTune](https://www.biorxiv.org/content/10.1101/465534v1) images, and we are currently seeking genomic markers of heart disease using UK Biobank data.
+Recently, my group and I have developed approaches for [predicting county-level COVID-19 death counts](https://covidseverity.com/) in an effort to support the non-profit, [Response4Life](https://response4life.org/), who are working towards distributing PPE across the country to those who need it most.
+
+The Yu Group and I have also developed an array of statistical and machine learning methods inspired by our interdisciplinary projects, including [stability-driven nonnegative matrix factorization (staNMF)](https://github.com/Yu-Group/staNMF) for unsupervised learning, [iterative Random Forests (iRF)](https://github.com/Yu-Group/iterative-Random-Forest) and [signed iRF (s-iRF)](https://github.com/karlkumbier/iRF2.0) for discovering predictive and stable high-order (Boolean) interactions in supervised learning, [contextual decomposition (CD)](https://github.com/jamie-murdoch/ContextualDecomposition) and [aggregated contextual decomposition (ACD)](https://github.com/csinva/hierarchical-dnn-interpretations) for phrase or patch importance extraction from Deep Neural Networks (DNNs).
+
+Research is supported in part by grants from NSF, NIH, the Weill Neurohub, and the Simons Foundation.
+
+- [Yu Group at Berkeley](https://www.stat.berkeley.edu/~yugroup/) for current group members and current projects
+- [Papers](https://binyu.stat.berkeley.edu/papers)
+- [Code](https://www.stat.berkeley.edu/~yugroup/code.html)
+- [Statistical Machine Learning at Berkeley](http://www.stat.berkeley.edu/~statlearning/)
+
+# Vision
+
+In 2014, I was elected to the National Academy of Sciences based on my statistical and scientific contributions, as well as my broad vision of data science best described in my article [Veridical Data Science](https://www.pnas.org/content/117/8/3920), written together with my former student Karl Kumbier.
+In this work, I introduced a framework based on three principles: predictability, computability and stability (abbreviated to PCS).
+This framework helps guide practitioners who solve domain data problems with data science tools to be creative in their analysis and properly validate their findings.
+I have written a book on the Veridical Data Science framework together with my former student [Rebecca Barter](https://www.rebeccabarter.com/).
+The book is being published by the MIT Press in 2024 with a free on-line copy available soon.
+
+She and her team have developed the PCS framework for veridical data science (or responsible, reliable, and transparent data analysis and decision-making).
+PCS stands for predictability, computability and stability, and it unifies, streamlines, and expands on ideas and best practices of machine learning and statistics.
+
+In order to augment empirical evidence for decision-making, they are investigating statistical machine learning methods/algorithms (and associated statistical inference problems) such as dictionary learning, non-negative matrix factorization (NMF), EM and deep learning (CNNs and LSTMs), and heterogeneous effect estimation in randomized experiments (X-learner).
+Their recent algorithms include staNMF for unsupervised learning, iterative Random Forests (iRF) and signed iRF (s-iRF) for discovering predictive and stable high-order interactions in supervised learning, next generation tree-based methods (e.g.
+fast and interpretable greedy-tree sums (FIGS) and hierarchical shrinked (HS) trees, and RF+ ), contextual decomposition (CD), aggregated contextual decomposition (ACD), and adaptive wavelet distillation (AWD) for interpretation of Deep Neural Networks (DNNs).

### 2025-07-19 index.qmd
Update index.qmd
Update website structure and content
Replaced the 'Research' section with a new 'About' page, detailing Professor Bin Yu's background and the Yu Group's research focus. Updated navigation links in _quarto.yml to reflect these changes, removing the old 'Research' link and adding 'About' and 'People' links. Enhanced the index.qmd layout for better presentation of recent publications and news, and added a responsive two-column layout in styles.css for improved readability.

--- 2025-05-17 index.qmd
@@
 
-## Welcome
+<div class="two-column-container">
 
-Professor Bin Yu is the head of the [Yu Group](https://www.stat.berkeley.edu/~yugroup/) at Berkeley, which consists of 12-15 students and postdocs from Statistics and EECS.
-She was formally trained as a statistician, but her research interests and achievements extend beyond the realm of statistics.
-Together with her group, Bin Yu has leveraged new computational developments to solve important scientific problems by combining novel and often interpretable statistical machine learning approaches with the domain expertise of her many collaborators in neuroscience, genomics and precision medicine.
-She also develops relevant theory to understand random forests and deep learning for insight into and guidance for practice.
-Her work has been recognized by many awards.
-In particular, she was inducted to the National Academy of Sciences in 2014 and to the American Academy of Arts and Sciences in 2013.
-She delivered the IMS Wald Lectures and COPSS Distinguished Achievement and Award Lecture (DAAL, formerly Fisher Award and Lecture) in 2023.
+<div class="column">
+## Recent Publications & Talks
 
-She and her team have developed the PCS framework for veridical data science (or responsible, reliable, and transparent data analysis and decision-making).
-PCS stands for predictability, computability and stability, and it unifies, streamlines, and expands on ideas and best practices of machine learning and statistics.
-
-In order to augment empirical evidence for decision-making, they are investigating statistical machine learning methods/algorithms (and associated statistical inference problems) such as dictionary learning, non-negative matrix factorization (NMF), EM and deep learning (CNNs and LSTMs), and heterogeneous effect estimation in randomized experiments (X-learner).
-Their recent algorithms include staNMF for unsupervised learning, iterative Random Forests (iRF) and signed iRF (s-iRF) for discovering predictive and stable high-order interactions in supervised learning, next generation tree-based methods (e.g.
-fast and interpretable greedy-tree sums (FIGS) and hierarchical shrinked (HS) trees, and RF+ ), contextual decomposition (CD), aggregated contextual decomposition (ACD), and adaptive wavelet distillation (AWD) for interpretation of Deep Neural Networks (DNNs).
-
-## My vision for data science - papers & talks
-
-- [Rome Workshop on Veridical Data Science, June 20, 2025](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html) (New)
+- [New paper: PCS workflow for veridical data science in the age of AI (Z. Rewolinski and B. Yu, 2025)](https://www.stat.berkeley.edu/~yugroup/pubs/pcs_workflow-6.pdf)
 - [Veridical data science and medical foundation models](https://arxiv.org/abs/2409.10580) on arXiv by Alaa and Yu.
 - [VDS book review](https://hdsr.mitpress.mit.edu/pub/5322mn1e/release/3) by Yuval and Yoav Benjamini in Harvard Data Science Review (HDSR)-- "pedagogical excellence, diverse examples, and projects make Veridical Data Science a suitable textbook for students of all levels, in addition to being a valuable resource for data scientists in general" (review summary in HDSR Editor-in-Chief's note), June, 2024.
-- [Inaugural Berkeley-Stanford Workshop on Veridical Data Science at UC Berkeley](https://na.eventscloud.com/website/69057/) (May 31, 2024) ([talk videos available](https://www.youtube.com/playlist?list=PLKW2Azk23ZtSrg4jwLSioaV1bwmFnQ1Bx))
+- ["Veridical data science towards trustworthy AI"](https://ww2.amstat.org/meetings/jsm/2023/webcasts/index.cfm) (Talk video of COPSS DAAL (formerly Fisher Award and Lecture), scroll down), Aug.
+JSM in Toronto, 2023.
+- [Veridical data science](https://www.pnas.org/content/117/8/3920) (PCS framework: [v-flow code](https://github.com/Yu-Group/veridical-flow) and [documentation template](https://yu-group.github.io/vdocs/PCSDoc-Template.html)), PNAS, 2020 ([QnAs with Bin Yu](https://www.pnas.org/content/117/8/3893))
 - My co-author [Rebecca Barter](https://rebeccabarter.com/) and I are thrilled to announce the [online release](http://vdsbook.com/) of our MIT Press book ["Veridical Data Science: The Practice of Responsible Data Analysis and Decision Making"](https://mitpress.mit.edu/9780262049191/veridical-data-science/), an essential source for producing trustworthy data-driven results (Feb.
 28, 2024).
-- ["Veridical data science towards trustworthy AI"](https://ww2.amstat.org/meetings/jsm/2023/webcasts/index.cfm) (Talk video of COPSS DAAL (formerly Fisher Award and Lecture), scroll down), Aug.
-JSM in Toronto, 2023.
-- [What is uncertainty in today's practice of data science?](https://www.sciencedirect.com/science/article/pii/S030440762300235X?dgcid=author) (Yu, 2023). Journal of Econometrics.
-- [Building trust in medical AI algorithms with veridical data science](https://link.springer.com/epdf/10.1007/s13218-023-00803-y?sharing_token=ebI2N15qM6XZUegMth-Quve4RwlQNchNByi7wbcMAY7HhSJ5V2qZIFNLqxQFZ-zTvebYYHuYBEDcXzQl7eRE1JVsvjcy_eFebw0xZW9UU9CqWdFLLGd22GvHmjiyaKtyaRMQToSpZQruTneGX1KD5rV1I5kdcOMfqUq47TrVW5E%3D) (interview of Bin Yu by Dr.
-Merle Behr for the German scientific journal [KI - Künstliche Intelligenz](https://www.springer.com/journal/13218)), 2023
-- [Veridical data science](https://www.pnas.org/content/117/8/3920) (PCS framework: [v-flow code](https://github.com/Yu-Group/veridical-flow) and [documentation template](https://yu-group.github.io/vdocs/PCSDoc-Template.html)), PNAS, 2020 ([QnAs with Bin Yu](https://www.pnas.org/content/117/8/3893))
-- [Breiman Lecture (video) at NeurIPS "Veridical data Science"](https://slideslive.com/38922599/veridical-data-science) ([PCS framework](https://www.pnas.org/content/117/8/3920) and iterative random forests ([iRF](https://www.pnas.org/content/115/8/1943))), 2019; [updated slides](https://www.stat.berkeley.edu/~binyu/ps/papers2020/Breiman19-NeurIPS-yu.pdf), 2020
-- [Stability](https://projecteuclid.org/euclid.bj/1377612862), Bernoulli, 2013
-- [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/2), Harvard Data Science Review (HDSR), 2020.
-- [Data science process: one culture.](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20) JASA, 2020.
-- [Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y), Nature Medicine, 2020.
-- [Definitions, methods and applications in interpretable machine learning](https://www.pnas.org/content/116/44/22071), PNAS, 2019
-- [Data wisdom for data science (blog)](http://www.odbms.org/2015/04/data-wisdom-for-data-science/), 2015
-- [IMS Presidential Address "Let us own data science"](https://imstat.org/2014/10/01/ims-presidential-address-let-us-own-data-science/), IMS Bulletin, 2014
-- [Embracing statistical challenges in the IT age](https://www.tandfonline.com/doi/abs/10.1198/004017007000000254), Technometrics, 2007
 
-## In the news
+[View all papers →](papers.qmd)
 
+</div>
+
+<div class="column">
+## Recent News
+
+- [Veridical Data Science in Biology on July 11, 2025 at UC Berkeley (Submission deadline July 4)](https://www.eventbrite.com/e/veridical-data-science-for-biology-2025-tickets-1384456339179)
+- [Rome Workshop on Veridical Data Science, June 20, 2025](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html)
 - IMS Wald [Lecture I](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1029) and [Lecture II](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1031), and [COPSS Distinguished Award and Lecture (DAAL)](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1374) delivered at [Joint Statistical Meeting (JSM)](https://ww2.amstat.org/meetings/jsm/2023/) in Toronto, August 2023
+- [Inaugural Berkeley-Stanford Workshop on Veridical Data Science at UC Berkeley](https://na.eventscloud.com/website/69057/) (May 31, 2024) ([talk videos available](https://www.youtube.com/playlist?list=PLKW2Azk23ZtSrg4jwLSioaV1bwmFnQ1Bx))
 - UC Berkeley team part of the new NSF AI Center for Cybersecurity [ACTION](https://action.ucsb.edu/) led by UCSB.
@@
 25, 2020
-- [Curating COVID-19 data repository and forecasting county-level death counts in the US](https://engineering.berkeley.edu/news/2020/04/getting-the-right-equipment-to-the-right-people/), 2020
-- [Interviewed by PBS Nova about AlphaZero](https://www.pbs.org/wgbh/nova/article/google-alphazero-artificial-intelligence/), 2018
-- [Mapping a cell's destiny](https://newscenter.lbl.gov/2016/05/04/mapping-cells-destiny/), 2016
-- [Seeking Data Wisdom](https://vcresearch.berkeley.edu/news/seeking-data-wisdom), 2015
-- [Member, National Academy of Sciences](http://www.dcd.zju.edu.cn/Hsu-conference/pr.htm), 2014
-- [Fellow, American Academy of Arts and Sciences](http://www.dcd.zju.edu.cn/Hsu-conference/pr.htm), 2013
-- [One of the 50 best inventions of 2011 by Time Magazine](http://content.time.com/time/magazine/article/0,9171,2099708,00.html), 2011
-- [The Economist Article](http://www.economist.com/node/21534748), 2011
-- [ScienceMatters @ Berkeley. Dealing with Cloudy Data](https://www.stat.berkeley.edu/~binyu/ps/dealingwithcloudydata.pdf), 2004
+
+</div>
+
+</div>

### 2025-07-20 about.qmd
Refactor website navigation and update content
Added a new 'People' link to the navigation in _quarto.yml and streamlined the 'Papers' section to a single link. Updated the 'About' page with a comprehensive overview of Professor Bin Yu's background and research focus, while enhancing the teaching section with detailed course descriptions for STAT 154 and STAT 215A. Adjusted styles.css to comment out the background color for the column class, improving layout consistency.

@@
 
-# About Bin
+# About Bin Yu
 
-<img src="images/bio1.jpg" alt="Bin Yu speaking" style="float:right; margin:0 0 1em 2em; width:200px; border-radius:8px;" />
-
-Bin Yu is CDSS Chancellor's Distinguished Professor in the Departments of statistics and EECS, and Center for Computational Biology, and serves as a scientific advisor at the Simons Institute for the Theory of Computing, all at UC Berkeley.
+Bin Yu is the Chancellor's Distinguished Professor in the UC Berkeley Departments of statistics and EECS.
+She was Chair of the Department of Statistics at UC Berkeley from 2009 to 2012.
+She has been elected to the National Academy of Sciences and Academy of Arts and Sciences.
+She was President of the Institute of Mathematical Statistics (IMS), Guggenheim Fellow, Tukey Memorial Lecturer of the Bernoulli Society, Rietz Lecturer of IMS, and a COPSS E.
+L.
+Scott Prize winner.
+She is a member of the UC Berkeley Center for Computational Biology and serves as a scientific advisor at the Simons Institute for the Theory of Computing.
+She is a Chan-Zuckerberg Biohub Investigator and Weill Neurohub Investigator.
 
@@
 She was a Visiting Faculty at MIT, ETH, Poincare Institute, Peking University, INRIA-Paris, Fields Institute at University of Toronto, Newton Institute at Cambridge University, and the Flatiron Institute in NYC.
-She was Chair of the Department of Statistics at UC Berkeley from 2009 to 2012.
 Recently, she was a 50% consultant researcher in the deep learning group of MSR at Redmond (2022-2023).
 
-She is a Member of the U.S.
-National Academy of Sciences and of the American Academy of Arts and Sciences.
-She was President of the Institute of Mathematical Statistics (IMS), Guggenheim Fellow, Tukey Memorial Lecturer of the Bernoulli Society, Rietz Lecturer of IMS, and a COPSS E.
-L.
-Scott Prize winner.
 Recently, she delivered the Wald Memorial Lectures of IMS and COPSS Distinguished Achievement Award and Lecture (DAAL) (formerly Fisher Award and Lecture) at JSM in 2023.
@@
 
-# About the Research Group
+# About Our Research Group
 
@@
 The Yu Group and I have also developed an array of statistical and machine learning methods inspired by our interdisciplinary projects, including [stability-driven nonnegative matrix factorization (staNMF)](https://github.com/Yu-Group/staNMF) for unsupervised learning, [iterative Random Forests (iRF)](https://github.com/Yu-Group/iterative-Random-Forest) and [signed iRF (s-iRF)](https://github.com/karlkumbier/iRF2.0) for discovering predictive and stable high-order (Boolean) interactions in supervised learning, [contextual decomposition (CD)](https://github.com/jamie-murdoch/ContextualDecomposition) and [aggregated contextual decomposition (ACD)](https://github.com/csinva/hierarchical-dnn-interpretations) for phrase or patch importance extraction from Deep Neural Networks (DNNs).
+
+Our research covers several key areas:
+
+## Deep Learning and Machine Learning
+
+Our work in deep learning spans from theoretical understanding to practical applications.
+Key contributions include mechanistic interpretation through contextual decomposition in transformers, efficient fine-tuning methods like [LoRA+](https://github.com/nikhil-ghosh-berkeley/loraplus), and frameworks for understanding neural network dynamics.
+We've developed methods like [Adaptive Wavelet Distillation (AWD)](https://github.com/Yu-Group/adaptive-wavelets) for interpreting deep neural networks, and theoretical work on the three stages of dynamics in high-dimensional kernel methods.
+Our applications range from clinical decision-making in healthcare to cosmological analysis.
+
+Selected recent papers:
+- [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) (ICML 2024)
+- [Mechanistic Interpretation through Contextual Decomposition in Transformers](https://arxiv.org/pdf/2407.00886) (2024)
+- [Diagnosing transformers: illuminating feature space for clinical decision-making](https://arxiv.org/abs/2305.17588) (ICLR 2024)
+- [Adaptive Wavelet Distillation from Neural Networks through Interpretation](https://nips.cc/Conferences/2021/ScheduleMultitrack?event=28027) (NeurIPS 2021)
+
+## Veridical Data Science (PCS)
+
+The PCS (Predictability, Computability, Stability) framework represents our approach to responsible, reliable, and transparent data analysis.
+This framework unifies and expands on best practices in machine learning and statistics, ensuring that data science findings are both scientifically sound and practically actionable.
+Our work includes applications to genomics, clinical research, and epidemiology, always emphasizing the importance of stability and reproducibility in scientific discovery.
+
+Selected recent papers:
+- [Veridical data science](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf) (PNAS 2020) - foundational framework paper
+- [Epistasis regulates genetic control of cardiac hypertrophy](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) (2023) - PCS application to genomics
+- [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (Harvard Data Science Review 2024)
+- [Stable discovery of interpretable subgroups via calibration in causal studies (staDISC)](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427)
+
+## Interpretable Machine Learning
+
+We develop methods to make machine learning models interpretable and trustworthy, particularly for high-stakes applications in healthcare and science.
+Our work spans contextual decomposition for understanding neural networks, feature importance frameworks, and methods for aligning model explanations with prior knowledge.
+We emphasize the principle that interpretations should be both faithful to the model and useful for human decision-making.
+
+Selected recent papers:
+- [Mechanistic Interpretation through Contextual Decomposition in Transformers](https://arxiv.org/pdf/2407.00886) (2024)
+- [MDI+: a flexible random forest-based feature importance framework](https://arxiv.org/abs/2307.01932) (2023)
+- [Tell your model where to attend: post-hoc attention steering for LLMs](https://arxiv.org/abs/2311.02262) (ICLR 2024)
+- [Definitions, methods, and applications in interpretable machine learning](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) (PNAS 2019)
+
+## Tree-based Methods
+
+We develop both theoretical understanding and practical improvements for tree-based methods, including random forests and gradient boosting.
+Our contributions include the iterative Random Forests (iRF) algorithm for discovering high-order interactions, hierarchical shrinkage methods for improving accuracy and interpretability, and fast interpretable greedy-tree sums (FIGS).
+We also provide theoretical analysis of when and why tree-based methods succeed or fail.
+
+Selected recent papers:
+- [Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931) (2022)
+- [Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods](https://arxiv.org/abs/2202.00858) (ICML 2022)
+- [Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests](https://arxiv.org/abs/2102.11800) (PNAS 2022)
+- [iterative Random Forests to discover predictive and stable high-order interactions](https://www.stat.berkeley.edu/~binyu/ps/papers2018/iRF+SI18.pdf) (PNAS 2018)
+
+<!-- ## Interdisciplinary Research in Biomedicine
+
+Our biomedicine work applies statistical machine learning to problems in genomics, clinical prediction, and biomarker discovery.
+We collaborate closely with domain experts to develop methods that are both statistically rigorous and clinically meaningful.
+Recent work includes epistasis analysis for cardiac hypertrophy, metabolomic signatures for pancreatic cancer risk, and clinical AI modeling standards.
+
+Selected recent papers:
+- [Epistasis regulates genetic control of cardiac hypertrophy](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) (2023)
+- [A blood-based metabolomic signature predictive of risk for pancreatic cancer](https://pubmed.ncbi.nlm.nih.gov/37729870/) (Cell Reports Medicine 2023)
+- [Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y) (Nature Medicine 2020)
+- [Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) (2023) -->
 
@@
 
-In 2014, I was elected to the National Academy of Sciences based on my statistical and scientific contributions, as well as my broad vision of data science best described in my article [Veridical Data Science](https://www.pnas.org/content/117/8/3920), written together with my former student Karl Kumbier.
+My broad vision of data science best described in my article [Veridical Data Science](https://www.pnas.org/content/117/8/3920).
 In this work, I introduced a framework based on three principles: predictability, computability and stability (abbreviated to PCS).

### 2025-07-20 index.qmd
Refactor website navigation and update content
Added a new 'People' link to the navigation in _quarto.yml and streamlined the 'Papers' section to a single link. Updated the 'About' page with a comprehensive overview of Professor Bin Yu's background and research focus, while enhancing the teaching section with detailed course descriptions for STAT 154 and STAT 215A. Adjusted styles.css to comment out the background color for the column class, improving layout consistency.

@@
 
-CDSS Chancellor's Distinguished Professor
+Chancellor's Distinguished Professor of Statistics and Electrical Engineering and Computer Sciences by courtesy
 
-Departments of [Statistics](https://statistics.berkeley.edu/) and [Electrical Engineering and Computer Sciences](https://eecs.berkeley.edu/), Center for Computational Biology
+Statistics Department Chair, 2009 - 2012
 
-[UC Berkeley](https://www.berkeley.edu/)
+*mail: 367 Evans Hall #3860 • Berkeley, CA 94720 phone: 510-642-2781 • fax: 510-642-7892 • [binyu@berkeley.edu](mailto:binyu@berkeley.edu)*
 
-[Chan-Zuckerberg Biohub](https://www.czbiohub.org/) Investigator Alumnus • [Weill Neurohub](https://www.weillneurohub.org/) Investigator
-
-*mail: 367 Evans Hall #3860 • Berkeley, CA 94720*
-
-*phone: 510-642-2781 • fax: 510-642-7892 • [binyu@berkeley.edu](mailto:binyu@berkeley.edu)*
-
-<div class="two-column-container">
-
-<div class="column">
 ## Recent Publications & Talks
@@
 
-</div>
-
-<div class="column">
 ## Recent News
@@
 25, 2020
-
-</div>
-
-</div>

### 2025-07-20 papers.qmd
Refactor website navigation and update content
Added a new 'People' link to the navigation in _quarto.yml and streamlined the 'Papers' section to a single link. Updated the 'About' page with a comprehensive overview of Professor Bin Yu's background and research focus, while enhancing the teaching section with detailed course descriptions for STAT 154 and STAT 215A. Adjusted styles.css to comment out the background color for the column class, improving layout consistency.

@@
 
-# Papers
-
-## Recent Papers by Area
-
-- [Deep Learning and Machine Learning](papers/deep-learning-and-machine-learning.qmd)
-- [Veridical Data Science (PCS)](papers/veridical-data-science-pcs.qmd)
-- [Interpretable Machine Learning](papers/interpretable-machine-learning.qmd)
-- [Interdisciplinary Research in Biomedicine](papers/interdisciplinary-research-in-biomedicine.qmd)
-- [Tree-based Methods](papers/tree-based-methods.qmd)
-
----
-
-## Complete List by Reverse Chronological Order
+# Select Publications
 
@@
 
-### Publications
-
-1. A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contextual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886)
-1. Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958)
-1. O. Ronen, A. I. Humayun, R. Balestriero, R. Baraniuk, B. Yu (2024). [ScaLES: Scalable Latent Exploration Score for Pre-Trained Generative Networks](https://arxiv.org/pdf/2406.09657)
-1. S. Hayou, N. Ghosh, B. Yu (2024). [The Impact of Initialization on LoRA Fineuning Dynamics.](https://arxiv.org/pdf/2406.08447)
-1. B. Yu (2024). [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (Harvard Data Science Review)
-1. S. Hayou, N. Ghosh, B. Yu (2024). [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) (Proc. ICML)
-1. C. F. Elliott, J. Duncan, T. M. Tang, M. Behr, K. Kumbier, B. Yu (2024). [Designing a data science simulation with MERITS: a primer.](https://arxiv.org/abs/2403.08971)
-1. Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). [Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986)
-1. N. R. Mallinar, A. Zane, S. Frei, B. Yu (2024). Minimum-Norm Interpolation Under Covariate Shift. (Proc. ICML) [arXiv](https://arxiv.org/pdf/2404.00522)
-1.
+## 2024
+
+A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contextual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886)
+
+Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958)
+
+O. Ronen, A. I. Humayun, R. Balestriero, R. Baraniuk, B. Yu (2024). [ScaLES: Scalable Latent Exploration Score for Pre-Trained Generative Networks](https://arxiv.org/pdf/2406.09657)
+
+S. Hayou, N. Ghosh, B. Yu (2024). [The Impact of Initialization on LoRA Fineuning Dynamics.](https://arxiv.org/pdf/2406.08447)
+
+B. Yu (2024). [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (Harvard Data Science Review)
+
+S. Hayou, N. Ghosh, B. Yu (2024). [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) (Proc. ICML)
+
+C. F. Elliott, J. Duncan, T. M. Tang, M. Behr, K. Kumbier, B. Yu (2024). [Designing a data science simulation with MERITS: a primer.](https://arxiv.org/abs/2403.08971)
+
+Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). [Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986)
+
+N. R. Mallinar, A. Zane, S. Frei, B. Yu (2024). Minimum-Norm Interpolation Under Covariate Shift. (Proc. ICML) [arXiv](https://arxiv.org/pdf/2404.00522)
+
 L.
@@
 ICML) [arXiv](https://arxiv.org/abs/2402.13448)
-1. C. Singh*, A. R. Hsu*, R. Antonello, S. Jain, A. G. Huth, B. Yu, J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
-1. Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262)
-1.
+
+## 2023
+
+C. Singh*, A. R. Hsu*, R. Antonello, S. Jain, A. G. Huth, B. Yu, J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
+
+Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262)
+
 Q.
@@
 [medRxiv](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
-1.
+
 R.
@@
 [bioRxiv](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
-1.
+
 E.
@@
 (PCS related) ([Editorial](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10518497/))
-1. R. Dwivedi, C. Singh, B. Yu, M. Wainwright (2023). [Revisiting miniumu description length complexity in overparametrized models.](https://jmlr.org/papers/v24/21-1133.html) JMLR, 24(268): 1-59.
-1.
+
+R. Dwivedi, C. Singh, B. Yu, M. Wainwright (2023). [Revisiting miniumu description length complexity in overparametrized models.](https://jmlr.org/papers/v24/21-1133.html) JMLR, 24(268): 1-59.
+
 K.
@@
 [https://arxiv.org/abs/2309.10301](https://arxiv.org/abs/2309.10301)
-1.
+
 N.
@@
 [https://arxiv.org/abs/2308.03215](https://arxiv.org/abs/2308.03215)
-1.
+
 R.
@@
 [https://arxiv.org/abs/2307.03887](https://arxiv.org/abs/2307.03887)
-1.
+
 A.
@@
 [https://arxiv.org/abs/2307.01932](https://arxiv.org/abs/2307.01932) (PCS related)
-1.
+
 A.
@@
 [https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)
-1.
+
 C.
@@
 [https://arxiv.org/abs/2305.09863](https://arxiv.org/abs/2305.09863)
-1.
+
+## 2022
+
 D.
@@
 [https://arxiv.org/abs/2207.14481](https://arxiv.org/abs/2207.14481)
-1.
+
 B.
@@
 [Offline evaluation in RL: soft stability weighting to combine fitted Q-learning and model-based methods.](https://openreview.net/forum?id=R3h3-bt0mq) NeurIPS 3rd Offline Reinforcement Learning Workshop.
-1.
+
 Y.
@@
 ([imodels 🔎](https://github.com/csinva/imodels) contains code for FIGS)
-1.
+
 A.
@@
 ICML ([imodels 🔎](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS)).
-1.
+
 B.
@@
 Statistical Science, 36(2):266-269.
-1. N. Ghosh, S. Mei, and B. Yu (2022). [The three stages of dynamics in high-dimensional kernel methods.](https://arxiv.org/abs/2111.07167) Proc. ICLR, 2022.
-1. Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS.
-1.
+
+N. Ghosh, S. Mei, and B. Yu (2022). [The three stages of dynamics in high-dimensional kernel methods.](https://arxiv.org/abs/2111.07167) Proc. ICLR, 2022.
+
+## 2021
+
+Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS.
+
 N.
@@
 30 4(3).
-1.
+
 C.
@@
 Holzinger et al.).
-1.
+
 W.
@@
 ([code](https://github.com/Yu-Group/adaptive-wavelets))
-1.
+
 M.
@@
 ([theory for iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS-related)
-1.
+
 N.
@@
 [arXiv version](https://arxiv.org/abs/2012.08113)
-1.
+
+## 2020
+
 M.
@@
 [Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
-1.
+
 B.
@@
 [Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y), Nature Medicine, 26, 1320–1324.
-1. B. Yu (2020). [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/1). Harvard Data Science Review (PCS related)
-1. B. Yu and R. Barter (2020). [Data science process: one culture.](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20) JASA. (PCS related)
-1.
+
+B. Yu (2020). [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/1). Harvard Data Science Review (PCS related)
+
+B. Yu and R. Barter (2020). [Data science process: one culture.](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20) JASA. (PCS related)
+
 R.
@@
 [Stable discovery of interpretable subgroups via calibration in causal studies (staDISC).](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427) International Statistical Review ([code](https://github.com/Yu-Group/stadisc)) (PCS case study for causal inference)
-1.
+
 X.
@@
 NeurISP workshop on ML4H (Machine learning for Health) Extended Abstract.
-1.
+
 A.
@@
 [Natural language processing systems for pathology parsing in limited data environments with uncertainty estimation.](https://academic.oup.com/jamiaopen/article/3/3/431/5922788) JAMIA Open.
-1.
+
 L.
@@
 ([code](https://github.com/laura-rieger/deep-explanation-penalization))
-1.
+
 C.
@@
 ([code](https://github.com/csinva/transformation-importance))
-1.
+
 N.
@@
 (2020) [Curating a COVID-19 data repository and forecasting county-level death counts in the United States.](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1) Harvard Data Science Review ([code](https://github.com/Yu-Group/covid19-severity-prediction)) [7-day prediction results](https://covidseverity.com/) [Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4)
-1.
+
 B.
@@
 [QnAs with Bin Yu.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf)
-1.
+
 R.
@@
 Yu (2020) [Sharp Analysis of Expectation-Maximization for Weakly Identifiable Mixture Models](https://arxiv.org/abs/1902.00194) AISTATS.
-1. R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) [Singularity, Misspecification and the Convergence Rate of EM](https://arxiv.org/abs/1810.00828) Annals of Statistics.
-1.
+
+R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) [Singularity, Misspecification and the Convergence Rate of EM](https://arxiv.org/abs/1810.00828) Annals of Statistics.
+
 Y.
@@
 Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients,](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, [arXiv](https://arxiv.org/abs/1905.12247)
-1. R. Dwivedi, Y. Chen, M. J. Wainwright and B. Yu (2019) [Log-concave Sampling: Metropolis Hastings Algorithms are Fast](http://jmlr.org/papers/v20/19-306.html) JMLR.
-1. D. Rothenhäusler and B. Yu (2019). [Incremental causal effects](https://arxiv.org/abs/1907.13258).
-1. Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes](http://jmlr.org/papers/v19/18-158.html). JMLR . http://jmlr.org/papers/v19/18-158.html
-1.
+
+## 2019
+
+R. Dwivedi, Y. Chen, M. J. Wainwright and B. Yu (2019) [Log-concave Sampling: Metropolis Hastings Algorithms are Fast](http://jmlr.org/papers/v20/19-306.html) JMLR.
+
+D. Rothenhäusler and B. Yu (2019). [Incremental causal effects](https://arxiv.org/abs/1907.13258).
+
+## 2018
+
+Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes](http://jmlr.org/papers/v19/18-158.html). JMLR . http://jmlr.org/papers/v19/18-158.html
+
 Y.
@@
 Yu (2020) [Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier](https://ieeexplore.ieee.org/abstract/document/8262876/) Allerton Conference 2017 https://ieeexplore.ieee.org/abstract/document/8262876/
-1.
+
 W.
@@
 Yu* (2019) [Definitions, methods, and applications in interpretable machine learning.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) PNAS, 116 (44) 22071-22080.
-1.
+
 W.
@@
 ([code](https://github.com/csinva/hierarchical-dnn-interpretations))
-1.
+
 Y.
@@
 Also at https://arxiv.org/abs/1902.08380
-1.
+
 Y.
@@
 Yu* (2018) [The DeepTune framework for modeling and characterizing neurons in visual cortex area V4](https://www.biorxiv.org/content/10.1101/465534v1) https://www.biorxiv.org/content/10.1101/465534v1
-1.
+
 K.
@@
 Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
-1. Y. Chen C. Jin, and B. Yu (2018) [Stability and Convergence Trade-off of Iterative Optimization Algorithms.](https://arxiv.org/abs/1804.01619) https://arxiv.org/abs/1804.01619
-1.
+
+Y. Chen C. Jin, and B. Yu (2018) [Stability and Convergence Trade-off of Iterative Optimization Algorithms.](https://arxiv.org/abs/1804.01619) https://arxiv.org/abs/1804.01619
+
 J.
@@
 [https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code)](https://github.com/csinva/hierarchical-dnn-interpretations)
-1. R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309) https://arxiv.org/abs/1801.02309.
-1. Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) [Fast MCMC sampling algorithms on polytopes](https://arxiv.org/abs/1710.08165) https://arxiv.org/abs/1710.08165.
-1.
+
+R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309) https://arxiv.org/abs/1801.02309.
+
+## 2017
+
+Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) [Fast MCMC sampling algorithms on polytopes](https://arxiv.org/abs/1710.08165) https://arxiv.org/abs/1710.08165.
+
 B.
@@
 19(1), 6-9.
-1. R. Abbasi-Asl and B. Yu (2017) [Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning](https://arxiv.org/abs/1705.07356) https://arxiv.org/abs/1705.07356
-1.
+
+R. Abbasi-Asl and B. Yu (2017) [Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning](https://arxiv.org/abs/1705.07356) https://arxiv.org/abs/1705.07356
+
 R.
@@
 (also https://arxiv.org/abs/1711.02329)
-1.
+
 S.
@@
 [(code](https://github.com/soerenkuenzel/hte))
-1.
+
 S.
@@
 ([code](https://github.com/Yu-Group/iterative-Random-Forest)) (PCS related)
-1.
+
 S.
@@
 Yu (2017) [Statistical Guarantees for the EM algorithm: from population to sample-based analysis.](https://www.stat.berkeley.edu/~binyu/ps/papers2017/EM17.pdf) Annals of Statistics, 45(1), 77 - 120.
-1.
+
 R.
@@
 https://github.com/rlbarter/superheat
-1.
+
 H.
@@
 26: 740-750.
-1.
+
 C.
@@
 [UC Berkeley Data Science Planning Initiative Faculty Advisory Board (FAB) Report.](https://www.stat.berkeley.edu/~binyu/ps/FAB2016.pdf) [FAB Report Executive Summary](https://www.stat.berkeley.edu/~binyu/ps/FAB-Summary2016.pdf)
-1.
+
 S.
@@
 18, 1 - 56.
-1.
+
+## 2016
+
 K.
@@
 National Academy of Sciences (PNAS), 113(45), 12679 - 12684.
-1.
+
 R.
@@
 doi:10.1371/journal.pcbi.1004961
-1.
+
 Siqi Wu, Antony Joseph, Ann S.
@@
 ([code](https://github.com/yu-group/stanmf)) (PCS related)
-1.
+
 A.
@@
 of AISTATS, Barcelona, Spain.
-1. B. Yu (2015). [Data wisdom for data science.](http://www.odbms.org/2015/04/data-wisdom-for-data-science/) Operational Database Management Systems (ODBMS.ORG).
-1.
+
+## 2015
+
+B. Yu (2015). [Data wisdom for data science.](http://www.odbms.org/2015/04/data-wisdom-for-data-science/) Operational Database Management Systems (ODBMS.ORG).
+
 A.
@@
 113, 7383 - 7390.
-1.
+
 P.
@@
 [A Statistical Perspective on Algorithmic Leveraging.](https://www.stat.berkeley.edu/~binyu/ps/papers2015/MaMahoneyYu2015.pdf) Journal of Machine Learning Research, 16, (2015), 861-911.
-1.
+
 T.
@@
 [Evaluation of a MISR-based high-resolution aerosol retrieval method using AERONET DRAGON campaign data.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=7047927) IEEE Transactions on Geoscience and Remote Sensing, 53, 4328-4339.
-1.
+
+## 2014
+
 B.
@@
 [Let us own data science.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/IMS-pres-address14-yu.pdf) [video](https://www.youtube.com/watch?v=92OjsYQJC1U) [IMS Bulletin](http://bulletin.imstat.org/2014/10/ims-presidential-address-let-us-own-data-science/) Institute of Mathematical Statistics (IMS) Presidental Address, ASC-IMS Joint Conference, Sydney, July, 2014.
-1. G. Schiebinger, M. J. Wainwright and B. Yu (2014). [The geometry of kernelized spectral clustering.](http://arxiv.org/pdf/1404.7552v3.pdf) Annals of Statistics, 43, 819-846.
-1.
+
+G. Schiebinger, M. J. Wainwright and B. Yu (2014). [The geometry of kernelized spectral clustering.](http://arxiv.org/pdf/1404.7552v3.pdf) Annals of Statistics, 43, 819-846.
+
 L.
@@
 Applied Statist., 8, 499-529.
-1.
+
 Y.
@@
 [The shuttle estimator for explainable variance in fMRI experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/BenjaminiY12.pdf) Annals of Applied Statistics, 7, 2007-2033.
-1.
+
 D.
@@
 [Optimal M-estimation in high-dimensional regression.](http://www.pnas.org/content/early/2013/08/08/1307845110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1456314568.
-1.
+
 N.
@@
 [On robust regression with high-dimensional predictors.](http://www.pnas.org/content/early/2013/08/15/1307842110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1455714562.
-1.
+
 P.
@@
 (2015))
-1.
+
 A.
@@
 of RECOMB 2014 (to appear).
-1.
+
 Tao Shi (2013), [A conversation with Professor Bin Yu](http://www.yufamily.org/src/ShiTao_AnInterviewWithProfessorBinYu.php?xref=YuFamily_YuBin_interview_cn) International Chinese Statistical Association (ICSA) Bulletin, Vol 25, Issue 2, pp 85-98.
 ([Selected Parts in Statblogs](http://www.statsblogs.com/2013/07/09/a-conversation-with-professor-bin-yu/))
-1. A. Joseph and B. Yu (2016). [The impact of regularization on spectral clustering.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/reg-spectral16.pdf) Annals of Statistics. 4, 1765 - 1791.
-1.
+
+A. Joseph and B. Yu (2016). [The impact of regularization on spectral clustering.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/reg-spectral16.pdf) Annals of Statistics. 4, 1765 - 1791.
+
 C.
@@
 (First paper towards PCS)
-1.
+
+## 2013
+
 A.
@@
 [Spatial expression of transcription factors in Drosophila embryonic organ development.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Hammondsetal13.pdf) Genome Biology, 14(12), R140.
-1.
+
 H.
@@
 Statist., 7, 312-3169.
-1.
+
 J.
@@
 [Supervised Feature Selection in Graphs with Path Coding Penalties and Network Flows.](http://jmlr.org/papers/v14/mairal13a.html) Journal of Machine Learning Research, 14, 2449-2485.
-1.
+
 Y.
@@
 American Statistical Association, 108, 483-493.
-1.
+
 Y.
@@
 [Reversible MCMC on Markov equivalence classes of sparse directed acyclic graphs.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/rev-MCMC13.pdf) Annals of Statistics, 41(4), 1742-1779.
-1.
+
 B.
@@
 (Invited paper for the Special Issue commemorating the 300th anniversary of the publication of Jakob Bernoullis Ars Conjectandi in 1712) (Begining of PCS)
-1. J. Mairal and B. Yu (2013). Discussion on Grouping Strategies and Thresholding for High Dimensional Linear Models Journal of Statistical Planning and Inference, 143, 1451-1453.
-1.
+
+J. Mairal and B. Yu (2013). Discussion on Grouping Strategies and Thresholding for High Dimensional Linear Models Journal of Statistical Planning and Inference, 143, 1451-1453.
+
 C.
@@
 [Geometry of faithfulness assumption in causal inference.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/faithfulness13.pdf) Annals of Statistics, 41, 436-463.
-1.
+
 L.
@@
 [Adjusting Treatment Effect Estimates by Post-Stratification in Randomized Experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/post-stratification13.pdf) Journal of Royal Statistical Society, Series B, 75 (part 2), 369-396.
-1. J. Jia, K. Rohe and B. Yu (2013) [The Lasso under Poisson-like Heteroscadecity.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/lasso-poisson13.pdf) Statistica Sinica, 23, 99-118.
-1.
+
+J. Jia, K. Rohe and B. Yu (2013) [The Lasso under Poisson-like Heteroscadecity.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/lasso-poisson13.pdf) Statistica Sinica, 23, 99-118.
+
 S.
@@
 Yu (2012) [A unified framework for high-dimensional analysis of M-estimators with decomposable regularizers.](https://www.stat.berkeley.edu/~binyu/ps/unified-797.pdf) Statistical Science, 27, 538-557.
-1.
+
 G.
@@
 Machine Learning Research, 13, 389-427.
-1.
+
 J.
@@
 of International Conference on Machine Learning (ICML).
-1.
+
+## 2012
+
 Yanfeng Gu, Shizhe Wang, Tao Shi, Yinghui Lu, Eugene E.
@@
 of IEEE International Geoscience and Remote Sensing Symposium (IGRSS).
-1.
+
+## 2011
+
 S.
@@
 [related videos](https://sites.google.com/site/gallantlabucb/publications/nishimoto-et-al-2011)
-1.
+
 P.
@@
 [High-dimensional covariance estimation by minimizing l1-penalized log-determinant divergence.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RavikumarWRY11.pdf) Electronic Journal of Statistics, 5, 935-980.
-1.
+
 G.
@@
 Th., 57(10), 6976-6994.
-1.
+
 K.
@@
 [Spectral clustering and the high-dimensional Stochastic Block Model.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RoheCY11.pdf) Annals of Statistics, 39 (4), 1878-1915
-1.
+
 V.
@@
 (*First senior author as last author in biology tradition)
-1. S. N. Pakzad, G. Rocha, and B. Yu (2011). Distributed modal identification by regularized auto regressive models. International Journal of Systems Science, 42, 1473-1489.
-1.
+
+S. N. Pakzad, G. Rocha, and B. Yu (2011). Distributed modal identification by regularized auto regressive models. International Journal of Systems Science, 42, 1473-1489.
+
 J.
@@
 64.
-1.
+
 X.
@@
 International Conference on Semantic Computing.
-1.
+
 B.
@@
 33-36, Springer.
-1. B. Yu (2010). [Remembering Leo.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/Yu10.pdf) Annals of Applied Statistics, 4(4), 1657-1659.
-1.
+
+## 2010
+
+B. Yu (2010). [Remembering Leo.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/Yu10.pdf) Annals of Applied Statistics, 4(4), 1657-1659.
+
 J.
@@
 Chiaromonte.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaBLRY10.pdf) Statistica Sinica, 20, 961-967.
-1.
+
 G.
@@
 Yu (2010) [Restricted Eigenvalue Properties for Correlated Gaussian Designs.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/RaskuttiWY10.pdf) Journal of Machine Learning Research, 11, 2241-2259.
-1. J. Jia and B. Yu (2010). [On model selection consistency of elastic net when p >>n.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaY10.pdf) Statistica Sinica, 10, 595-611.
-1. P. Buhlmann and B. Yu (2010). [Boosting.](http://onlinelibrary.wiley.com/doi/10.1002/wics.55/abstract) Wiley Interdisciplinary Reviews: Computational Statistics, 2, 69-74.
-1.
+
+J. Jia and B. Yu (2010). [On model selection consistency of elastic net when p >>n.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaY10.pdf) Statistica Sinica, 10, 595-611.
+
+P. Buhlmann and B. Yu (2010). [Boosting.](http://onlinelibrary.wiley.com/doi/10.1002/wics.55/abstract) Wiley Interdisciplinary Reviews: Computational Statistics, 2, 69-74.
+
 L.
@@
 NIPS 2010.
-1.
+
 Y.
@@
 of The 24th AAAI Conference on Artificial Intelligence, July 11-15, Atlanta, GA.
-1.
+
 B.
@@
 11th ACM SIGMM International Confernece on Multimedia Information Retrieval (MIR).
-1.
+
+## 2009
+
 E.
@@
 Clothiaux (2009) [Maximum Likelihood Estimation of Cloud Height from Multi-Angle Satellite Imagery.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/AnderesYJMGBC09.pdf) Annals of Applied Statistics, 3, 902-921
-1.
+
 T.
@@
 Yu, (2009) [Data Spectroscopy: Eigenspace of Convolution Operator and Clustering](https://www.stat.berkeley.edu/~binyu/ps/shi.aos09.pdf) Annals of Statistics, 37 (6B), 3960-3984.
-1. Vincent Q. Vu, Bin Yu, Robert E. Kass (2009) [Information In The Non-Stationary Case](https://www.stat.berkeley.edu/~binyu/ps/papers2009/VuYK09.pdf) Neural computation 21, 688-703.
-1.
+
+Vincent Q. Vu, Bin Yu, Robert E. Kass (2009) [Information In The Non-Stationary Case](https://www.stat.berkeley.edu/~binyu/ps/papers2009/VuYK09.pdf) Neural computation 21, 688-703.
+
 N.
@@
 [Lasso-type recovery of sparse representations for high-dimensional data.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/MeinshausenY09.pdf) Annals of Statistics 37, 246-270.
-1.
+
 P.
@@
 Rep 703.)
-1.
+
 S.
@@
 2012).
-1.
+
 G.
@@
 2011).
-1.
+
 G.
@@
 2011).
-1.
+
+## 2008
+
 T.
@@
 103( 482), 584-593.
-1.
+
 Peter Buhlmann and Bin Yu (2008) Invited discussion on "Evidence contrary to the statistical view of boosting (D.
@@
 [(paper with discussion) ](https://www.stat.berkeley.edu/~binyu/ps/Mease08a_with_discussion.pdf) Journal of Machine Learning Research 9, 187-194.
-1.
+
 P.
@@
 It does not contain decoding results.)
-1.
+
 P.
@@
 Yu (2008) [Model selection in Gaussian graphical models: high-dimensional consistency of l1-regularized MLE.](https://www.stat.berkeley.edu/~binyu/ps/covsel.nips08.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
-1. T. Shi, M. Belkin, and B. Yu (2008). [Data spectroscopy: learning mixture models using eigenspaces of convolution operators.](https://www.stat.berkeley.edu/~binyu/ps/ICML08.pdf) Proc. of ICML 2008.
-1.
+
+T. Shi, M. Belkin, and B. Yu (2008). [Data spectroscopy: learning mixture models using eigenspaces of convolution operators.](https://www.stat.berkeley.edu/~binyu/ps/ICML08.pdf) Proc. of ICML 2008.
+
 M.
@@
 [Towards Robust Phoneme Classification Augmentation of PLP Models with Acoustic Waveforms.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=7080758) Proceedings of EUSIPCO.
-1.
+
 J.
@@
 [Combined PLP-Acoustic Waveform Classification for Robust Phoneme Recognition using Support Vector Machines.](http://www.eurasip.org/Proceedings/Eusipco/Eusipco2008/papers/1569105546.pdf) Proceedings of EUSIPCO.
-1.
+
+## 2007
+
 N.
@@
 [A tale of three cousins: Lasso, L2Boosting, and Danzig](https://www.stat.berkeley.edu/~binyu/ps/aos.dis07.pdf) Annals of Statistics (invited discussion on Candes and Tao's Danzig Selector paper)
-1. V. Vu, B. Yu, and R. Kass (2007). [Coverage Adjusted Entropy Estimation.](https://www.stat.berkeley.edu/~binyu/ps/entropy.sub.pdf) Statistics and Medicine, 26(21), 4039-4060.
-1.
+
+V. Vu, B. Yu, and R. Kass (2007). [Coverage Adjusted Entropy Estimation.](https://www.stat.berkeley.edu/~binyu/ps/entropy.sub.pdf) Statistics and Medicine, 26(21), 4039-4060.
+
 B.
@@
 49 (3), 237-248.
-1.
+
 X.
@@
 45-53.
-1.
+
 T.
@@
 172-184.
-1. Peng Zhao and Bin Yu (2006). [On Model Selection Consistency of Lasso.](https://www.stat.berkeley.edu/~binyu/ps/LassoConsi.pdf) J. Machine Learning Research, 7 (nov), 2541-2567.
-1. B. Yu (2006). [Comments on: Monitoring networked applications with incremental quantile estimation by Chambers et al.](http://arxiv.org/pdf/0708.0338.pdf) Statist. Sci., 21, 483-485.
-1. B. Yu (2006). [Comments on: Regularization in Statistics, by P. J. Bickel and B. Li.](https://www.stat.berkeley.edu/~binyu/ps/test06.pdf) Test, vol. 15 (2), pages 314-316.
-1.
+
+## 2006
+
+Peng Zhao and Bin Yu (2006). [On Model Selection Consistency of Lasso.](https://www.stat.berkeley.edu/~binyu/ps/LassoConsi.pdf) J. Machine Learning Research, 7 (nov), 2541-2567.
+
+B. Yu (2006). [Comments on: Monitoring networked applications with incremental quantile estimation by Chambers et al.](http://arxiv.org/pdf/0708.0338.pdf) Statist. Sci., 21, 483-485.
+
+B. Yu (2006). [Comments on: Regularization in Statistics, by P. J. Bickel and B. Li.](https://www.stat.berkeley.edu/~binyu/ps/test06.pdf) Test, vol. 15 (2), pages 314-316.
+
 P.
@@
 This is a shortened and more focused version of Buhlmann and Yu "Boosting, Model Selection, Lasso and Nonnegative Garotte" given below.
-1.
+
 J.
@@
 225-232, Sydney.
-1. T. Shi and B. Yu (2005). [Binning in Gaussian Kernel Regularization.](https://www.stat.berkeley.edu/~binyu/ps/binning.final.pdf) Statistica Sinica (special issue on machine learning), 16, 541-567.
-1.
+
+## 2005
+
+T. Shi and B. Yu (2005). [Binning in Gaussian Kernel Regularization.](https://www.stat.berkeley.edu/~binyu/ps/binning.final.pdf) Statistica Sinica (special issue on machine learning), 16, 541-567.
+
 G.
@@
 2006)
-1. Tong Zhang and B. Yu (2005). [Boosting with early stopping: convergence and consistency.](https://www.stat.berkeley.edu/~binyu/ps/zhang.final.ps) The Annals of Statistics. Vol. 33, 1538-1579.
-1. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2005) [Network tomography: recent developments.](http://nowak.ece.wisc.edu/StatSci04.pdf) Statistical Science, 19, 499-517.
-1.
+
+Tong Zhang and B. Yu (2005). [Boosting with early stopping: convergence and consistency.](https://www.stat.berkeley.edu/~binyu/ps/zhang.final.ps) The Annals of Statistics. Vol. 33, 1538-1579.
+
+Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2005) [Network tomography: recent developments.](http://nowak.ece.wisc.edu/StatSci04.pdf) Statistical Science, 19, 499-517.
+
 C.
@@
 2005))
-1.
+
+## 2004
+
 P.
@@
 Report #678, Statistics Department, UC Berkeley (December, 2004; revised in April, 2005)
-1.
+
 D.
@@
 [PARAGON: A Systematic, Integrated Approach to Aerosol Observation and Modeling.](https://www.stat.berkeley.edu/~binyu/ps/paragon.pdf) American Meterological Society, Oct., 1491-1501.
-1. P. Buhlmann and B. Yu (2004). [Discussion on three boosting papers by Jiang, Lugosi and Vayatis, and Zhang](https://www.stat.berkeley.edu/~binyu/ps/disc2.ps) Annals of Statistics. 32 (1): 96-101.
-1.
+
+P. Buhlmann and B. Yu (2004). [Discussion on three boosting papers by Jiang, Lugosi and Vayatis, and Zhang](https://www.stat.berkeley.edu/~binyu/ps/disc2.ps) Annals of Statistics. 32 (1): 96-101.
+
 R.
@@
 341 - 366.
-1.
+
 G.
@@
 [Maximum entropy models: convergence rates and application in dynamic system monitoring.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=1365207&sortType%3Dasc_p_Sequence%26filter%3DAND%28p_IS_Number%3A29909%29%26pageNumber%3D4%26rowsPerPage%3D50) International Symposium on Information Theory, Chicago.
-1. R. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2003). [Internet Tomography: Recent Developments](https://www.stat.berkeley.edu/~binyu/ps/cny.pdf) Statistical Science. Vol. 19(3), 499-517.
-1.
+
+## 2003
+
+R. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2003). [Internet Tomography: Recent Developments](https://www.stat.berkeley.edu/~binyu/ps/cny.pdf) Statistical Science. Vol. 19(3), 499-517.
+
 G.
@@
 51(8), 2043-2053
-1.
+
 Rebecka Jornsten and Bin Yu (2003).
@@
 19(9): 1100-1109.
-1. Peter Buhlmann and Bin Yu (2003). [Boosting with the L2 Loss: Regression and Classification.](https://www.stat.berkeley.edu/~binyu/ps/boostingl2.ps) J. Amer. Statist. Assoc. 98, 324-340.
-1.
+
+Peter Buhlmann and Bin Yu (2003). [Boosting with the L2 Loss: Regression and Classification.](https://www.stat.berkeley.edu/~binyu/ps/boostingl2.ps) J. Amer. Statist. Assoc. 98, 324-340.
+
 R.
@@
 83, 859-869.
-1. G. Liang and B. Yu (2003). [Pseudo Likelihood Estimation in Network Tomography.](http://infocom2003.ieee-infocom.org/papers/51_03.PDF) Proceedings of of Infocom, San Francisco.
-1. Peter Buhlmann and Bin Yu (2002). [Analyzing Bagging.](https://www.stat.berkeley.edu/~binyu/ps/bagging.ps) Annals of Statistics vol. 30, 927-961.
-1.
+
+G. Liang and B. Yu (2003). [Pseudo Likelihood Estimation in Network Tomography.](http://infocom2003.ieee-infocom.org/papers/51_03.PDF) Proceedings of of Infocom, San Francisco.
+
+## 2002
+
+Peter Buhlmann and Bin Yu (2002). [Analyzing Bagging.](https://www.stat.berkeley.edu/~binyu/ps/bagging.ps) Annals of Statistics vol. 30, 927-961.
+
 R.
@@
 295-321.
-1.
+
 Mark Hansen and Bin Yu (2002).
@@
 40.
-1.
+
 Rebecka Jornsten, and Bin Yu (2002).
 [Multiterminal Estimation: Extensions and a Geometric interpretation.](https://www.stat.berkeley.edu/~binyu/ps/isit02.ps) Proceedings of International Symposium on Information Theory (ISIT), June, 2002.
-1.
+
 Gerald Schuller, Bin Yu, Dawei Huang, and Bern Edler (2002).
@@
 10 (6), 379-390
-1. Mark Coates, Alfred Hero, Robert Nowak, and Bin Yu (2002). [Internet Tomography.](https://www.stat.berkeley.edu/~binyu/ps/spmag.ps) Signal Processing Magazine. vol. 19, No. 3 (May issue), 47-65.
-1.
-M.
-Hansen and B.
-Yu (2001).
-[Model selection and the principle of Minimum Description Length.](https://www.stat.berkeley.edu/~binyu/ps/mdl.ps) Journal of American Statistical Association.
-96, 746-774.
-1.
+
+Mark Coates, Alfred Hero, Robert Nowak, and Bin Yu (2002). [Internet Tomography.](https://www.stat.berkeley.edu/~binyu/ps/spmag.ps) Signal Processing Magazine. vol. 19, No. 3 (May issue), 47-65.
+
+## 2001
+
+M. Hansen and B. Yu (2001). [Model selection and the principle of Minimum Description Length.](https://www.stat.berkeley.edu/~binyu/ps/mdl.ps) Journal of American Statistical Association. 96, 746-774.
+
+## 2000
+
 Jin Cao, Drew Davis, Scott Vander Wiel and Bin Yu (2000).
@@
 95, 1063-1075.
-1.
-Peter Buhlmann and Bin Yu (2000a).
+
+Peter Buhlmann and Bin Yu (2000).
 [Discussion.
@@
 28, 377-386
-1.
+
 Mark Hansen and Bin Yu (2000).
@@
 46, 1778-1788.
-1.
+
 Jorma Rissanen and Bin Yu (2000).
@@
 95, 986-988.
-1.
+
 Lei Li and Bin Yu (2000).
@@
 46, 2683-2689.
-1.
+
 G.
@@
 9, 1532-1546.
-1.
+
 G.
@@
 9, 1522-1531.
-1. G. Chang, B. Yu and M. Vetterli (2000). [Wavelet thresholding for multiple noisy image copies.](https://www.stat.berkeley.edu/~binyu/ps/mt.ps) IEEE Trans. Image Processing, vol. 9, 1631-1635.
-1.
+
+G. Chang, B. Yu and M. Vetterli (2000). [Wavelet thresholding for multiple noisy image copies.](https://www.stat.berkeley.edu/~binyu/ps/mt.ps) IEEE Trans. Image Processing, vol. 9, 1631-1635.
+
+## 1999
+
 Y.
@@
 8, 1702-1215.
-1. B. Yu, M. Ostland, P. Gong and R. Pu (1999). Penalized discriminant analysis of in situ hyperspectral data for conifer species recognition. IEEE Trans. Geoscience and Remote Sensing, in press.
-1.
+
+B. Yu, M. Ostland, P. Gong and R. Pu (1999). Penalized discriminant analysis of in situ hyperspectral data for conifer species recognition. IEEE Trans. Geoscience and Remote Sensing, in press.
+
+## 1998
+
 A.
@@
 McLaughlin (eds), IEEE Press , 1999.
-1. B. Yu and P. Mykland (1998). Looking at Markov samplers through cusum path plots: a simple diagnostic idea. Statistics and Computing , 8, 275-286.
-1. P. Gong, R. Pu and B. Yu (1998) Conifer species recognition: effects of data transformation and band width (in Chinese) Journal of Remote Sensing, 2(3), 211-217.
-1.
+
+B. Yu and P. Mykland (1998). Looking at Markov samplers through cusum path plots: a simple diagnostic idea. Statistics and Computing , 8, 275-286.
+
+P. Gong, R. Pu and B. Yu (1998) Conifer species recognition: effects of data transformation and band width (in Chinese) Journal of Remote Sensing, 2(3), 211-217.
+
 G.
@@
 [Spatially adaptive wavelet thresholding for image denoising.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=862630) Proceedings of IEEE International Conference on Image Processing, October, Chicago.
-1.
+
 S.
@@
 604-607.
-1. M. Ostland and B. Yu (1997). [Exploring quasi Monte Carlo for marginal density approximation.](https://www.stat.berkeley.edu/~binyu/ps/quasiMC.pdf) Statistics and Computing, 7, 217-228.
-1. P. Gong, R. Pu, and B. Yu (1997). Conifer species recognition with in Situ hyperspectral data. Remote Sensing of Environment, 62, 189-200.
-1. B. Yu and T. P. Speed (1997). [Information and the clone mapping of chromosomes.](https://www.stat.berkeley.edu/~binyu/ps/clone.pdf) Ann. Statist. 25, 169-185.
-1. D. Nelson, T. Speed, and B. Yu (1997). The limits of random fingerprinting. Genomics, 40, 1-12.
-1.
-B.
-Yu (1997).
-[Assouad, Fano, and Le Cam.](https://www.stat.berkeley.edu/~binyu/ps/LeCam.pdf) Festschrift for Lucien Le Cam .
-D.
-Pollard, E.
-Torgersen, and G.
-Yang (eds), pp.
-423-435, Springer-Verlag.
-1. B. Yu (1996). Lower bounds on expected redundancy for nonparametric classes. IEEE Trans. on Information Theory, 42, 272-275.
-1.
+
+M. Ostland and B. Yu (1997). [Exploring quasi Monte Carlo for marginal density approximation.](https://www.stat.berkeley.edu/~binyu/ps/quasiMC.pdf) Statistics and Computing, 7, 217-228.
+
+P. Gong, R. Pu, and B. Yu (1997). Conifer species recognition with in Situ hyperspectral data. Remote Sensing of Environment, 62, 189-200.
+
+B. Yu and T. P. Speed (1997). [Information and the clone mapping of chromosomes.](https://www.stat.berkeley.edu/~binyu/ps/clone.pdf) Ann. Statist. 25, 169-185.
+
+## 1997
+
+D. Nelson, T. Speed, and B. Yu (1997). The limits of random fingerprinting. Genomics, 40, 1-12.
+
+B. Yu (1997). [Assouad, Fano, and Le Cam.](https://www.stat.berkeley.edu/~binyu/ps/LeCam.pdf) Festschrift for Lucien Le Cam . D. Pollard, E. Torgersen, and G. Yang (eds), pp. 423-435, Springer-Verlag.
+
+## 1996
+
+B. Yu (1996). Lower bounds on expected redundancy for nonparametric classes. IEEE Trans. on Information Theory, 42, 272-275.
+
 Y.
@@
 In Proceedings of IEEE International Conference on Image Processing, Lausanne, Switzerland.
-1.
+
 B.
@@
 [A Statistical analysis of adaptive scalar quantization based on quantized past data.](https://www.stat.berkeley.edu/~binyu/ps/quan.ps) In Proceedings of International Symposium on Information Theory and its Applications (ISITA96), Victoria, Canada.
-1. B. Yu (1995). Comment: Extracting more diagnostic information from a single run using cusum path plot. Statist. Sci., 10, 54-58.
-1.
+
+## 1995
+
+B. Yu (1995). Comment: Extracting more diagnostic information from a single run using cusum path plot. Statist. Sci., 10, 54-58.
+
 J.
@@
 3-19.
-1. P. Mykland, L. Tierney, and B. Yu (1995). Regeneration in Markov Chain samplers. J. Amer. Statist. Assoc., 90, 233-241.
-1. B. Yu (1994a). Rates of convergence for empirical processes of stationary mixing sequences. Ann. Probab. 22, 94-116.
-1. M. Arcones and B. Yu (1994). Central limit theorems for empirical and U-processes of stationary mixing sequences. J. Theor. Probab. 7, 47-71.
-1. B. Yu (1994). Lower bound on the expected redundancy for classes of continuous Markov sources. In Statistical Decision Theory and Related Topics V, S. S. Gupta and J. O. Berger (eds), 453-466.
-1. M. Arcones and B. Yu (1994). Limit theorems for empirical processes under dependence. In Proceedings in Chaos expansions, multiple Wiener integrals and their applications. 205-221.
-1.
+
+P. Mykland, L. Tierney, and B. Yu (1995). Regeneration in Markov Chain samplers. J. Amer. Statist. Assoc., 90, 233-241.
+
+## 1994
+
+B. Yu (1994). Rates of convergence for empirical processes of stationary mixing sequences. Ann. Probab. 22, 94-116.
+
+M. Arcones and B. Yu (1994). Central limit theorems for empirical and U-processes of stationary mixing sequences. J. Theor. Probab. 7, 47-71.
+
+B. Yu (1994). Lower bound on the expected redundancy for classes of continuous Markov sources. In Statistical Decision Theory and Related Topics V, S. S. Gupta and J. O. Berger (eds), 453-466.
+
+M. Arcones and B. Yu (1994). Limit theorems for empirical processes under dependence. In Proceedings in Chaos expansions, multiple Wiener integrals and their applications. 205-221.
+
 A.
@@
 38, Trondheim, Norway.
-1. B. Yu and T. Speed (1993). A rate of convergence result for a universal D-semifaithful code. IEEE Trans. on Information Theory 39, 8813-820.
-1. B. Yu (1993). Density estimation in the L∞ norm for dependent data with applications to the Gibbs sampler. Ann. Statist. 21, 711-735.
-1. T. Speed and B. Yu (1993). Model selection and prediction: normal regression. J. Inst. Statist. Math. 45, 35-54.
-1. J. Rissanen, T. Speed and B. Yu (1992). Density estimation by stochastic complexity. IEEE Trans. on Information Theory, 38, 315-323.
-1. B. Yu and T. Speed (1992) Data compression and histograms. Probability Theory and Related Fields, 92, 195-229.
-
----
+
+## 1993
+
+B. Yu and T. Speed (1993). A rate of convergence result for a universal D-semifaithful code. IEEE Trans. on Information Theory 39, 8813-820.
+
+B. Yu (1993). Density estimation in the L∞ norm for dependent data with applications to the Gibbs sampler. Ann. Statist. 21, 711-735.
+
+T. Speed and B. Yu (1993). Model selection and prediction: normal regression. J. Inst. Statist. Math. 45, 35-54.
+
+## 1992
+
+J. Rissanen, T. Speed and B. Yu (1992). Density estimation by stochastic complexity. IEEE Trans. on Information Theory, 38, 315-323.
+
+B. Yu and T. Speed (1992) Data compression and histograms. Probability Theory and Related Fields, 92, 195-229.

### 2025-07-20 people.qmd
Refactor website navigation and update content
Added a new 'People' link to the navigation in _quarto.yml and streamlined the 'Papers' section to a single link. Updated the 'About' page with a comprehensive overview of Professor Bin Yu's background and research focus, while enhancing the teaching section with detailed course descriptions for STAT 154 and STAT 215A. Adjusted styles.css to comment out the background color for the column class, improving layout consistency.

---
title: "People"
---

## Current Members (Role, Program)

- Abhineet Agarwal (Ph.D. Student, Statistics)
- Soufiane Hayou (Post-doc)
- Jakob Heiss (Post-doc)
- Aliyah Hsu (Ph.D. Student, Statistics)
- Yaxuan Huang (Ph.D. Student, Statistics)
- Nathan Benjamin McNaughton (Undergraduate Student)
- Robin Netzorg (Ph.D. Student, Statistics)
- Anthony Ozerov (Ph.D. Student, Statistics)
- Zachary Rewolinski (Ph.D. Student, Statistics)
- Omer Ronen (Ph.D. Student, Statistics)
- Jingfeng Wu (Post-doc)
- Chengzhong Ye (Ph.D. Student, Statistics)
- Zeyu Yun (Ph.D. Student, Statistics)
- Austin Zane (Ph.D. Student, Statistics)

## Former Ph.D. Students (Graduation Year)

- Corine Elliot (2024) - Statistical Scientist, Berry Consultants
- James Duncan (2024) - Climate ML Engineering, Allen Institute for AI (AI2)
- Tiffany Tang (2023) - Clare Boothe Luce Assistant Professor, University of Notre Dame
- Yeshwanth Cherapanamjeri (2023) - Postdoctoral Researcher, MIT
- Dennis Shen (2023) - Assistant Professor, USC
- Spencer Frei (2023) - Assistant Professor, UC Davis
- Rebecca L. Barter (2022) - Research Assistant Professor, University of Utah
- Luiz Chamon (2022) - Research Group Leader, University of Stuttgart
- Angela Zhou (2022) - Assistant Professor, University of Southern California
- Briton Park (2022) - Citadel Securities
- Chandan Singh (2022) - Microsoft Research
- Keyan Nasseri (2022) - Google
- Wooseok Ha (2022) - AWS
- Yan Shuo Tan (2022) - Assistant Profressor, Department of Statistics and Data Science, National University of Singapore
- Xiao Li (2021) - Voleon
- Raaz Dwivedi (2021) - Postdoctoral scholar, MIT / Harvard
- Yu Wang (2020) - Two Sigma
- Merle Behr (2020) - Scientific Expert, Bayer AG
- Nicholas Altieri (2020) - Genentech
- Yuansi Chen (2019) - Assistant Professor, Department of Statistical Sciences, Duke University
- Karl Kumbier (2019) - Postdoctoral Researcher, UC San Francisco
- Jamie Murdoch (2019) - Co-founder / President, clientelligent.ai
- Soren Kunzel (2019) - Data Scientist, Citadel
- Simon Walter (2019) - Data Scientist, Bridgewater
- Sujayam Saha (2018) - Data Scientist, Google
- Reza Abbasi-Asl (2018) - Scientist, Allen Institute for Brain Science
- Christine Kuang (2017) - Data Scientist, Facebook
- Hanzhong Liu (2016) - Assistant Professor, Department of Statistics, Tsinghua University
- Sumanta Basu (2016) - Assistant Professor, Department of Statistics, Cornell University
- Sivaraman Balakrishnan (2016) - Assistant Professor, Department of Statistics, Carnegie Mellon University
- Adam Bloniarz (2016) - Data Scientist, Google
- Siqi Wu (2016) - Data Scientist, Citadel
- Hongwei Li (2015) - Senior Data Scientist, UBER
- Antony Joseph (2014) - Staff Data Scientist, Walmart eCommerce
- Taesup Moon (2013) - Research Staff Member, Samsung Advanced Institute of Technology
- Yuval Benjamini (2013) - Stein fellow, Statistics department, Stanford University
- Julien Mairal (2012) - Research Scientist, INRIA
- Yueqing Wang (2012) - Research Scientist, Google
- Hau-tieng Wu (2012) - Assistant Professor, Mathematics Department, University of Toronto
- Garvesh Raskutti (2012) - Assistant Professor, Department of Statistics, Univ. Wisconsin-Madison
- Luke W. Miratrix (2012) - Assistant Professor, Department of Statistics, Harvard University
- Harry Kim (2011) - Product Marketing Manager, Google
- Chinghway Lim (2011) - Assistant Professor, Department of Statistics and Applied Probability, National University of Singapore
- Karl Rohe (2011) - Assistant Professor, Department, University of Wisconsin-Madison.
- Kyle Jia (2010) - Assistant Professor, Peking University, China.
- David Purdy (2009) - Data Scientist, Uber
- Pradeep Ravikumar (2009) - Associate Professor, Department of Computer Sciences, University of Texas, Austin.
- Vince Vu (2009) - Assistant Professor, Department of Statistics, The Ohio State University
- Ethan Anderes (2008) - Assistant Professor, Department of Statistics, University of California, Davis
- Guilherme Rocha (2008) - Assistant Professor, Department of Statistics, Indiana University, Bloomington
- Peng Zhao (2006) - CEO of Citadel Securities, Citadel Investment Group in Chicago, IL.
- Nicolai Meinshausen (2006) - Professor, Department of Statistics, ETH Zurich
- Tao Shi (2005) - Quantitative Researcher, Citadel Investment Group in Chicago, IL.
- Gang Liang (2004) - Quantitative Operations Associate, Bank of America
- Rebecka Jörnsten (2000) - Associate Professor, Mathematical Statistics, Chalmers University of Technology
- Grace Chang (2000) - Senior Manager of Product Development, Marketing Dept, MTN Irancell

## Former Post-docs, Visitors, and Associates (Starting Year)

- Arman Sabbaghi (2022)
- Yanjun Qi (2020)
- Ezequiel Smucler (2020)
- Laura Reiger (2019)
- Yanyan Lan (2018)
- Yahong Han (2016)
- Thibault Vatter
- Guoqiang Cai
- Trine Abrahamsen
- Xiaoling Lu
- Xiusheng Lu (2014)
- Xiangyu Chang (2012)
- Ling Hong (2012)
- Toshiyasu Matsushima (2012)
- Yanfeng Gu (2012) - Professor of Electronics Engineering, Harbin Institute of Technology
- Hai Zhang (2012)
- Rodolphe Jenatton (2010)
- Kenichi Hayashi (2010)
- Yangbo He (2010)
- Fei Wu (2010)
- Kei Kobayashi (2008)
- Xing Wang (2007)

### 2025-07-20 about.qmd
Update website content and navigation structure
Renamed the 'Code' section to 'Software' in _quarto.yml for clarity. Enhanced the 'About' page with a more detailed overview of Professor Bin Yu's achievements and research focus, while streamlining the content for better readability. Removed the 'code.qmd' file to consolidate software information into the new 'Software' section. Updated the index.qmd layout to improve the presentation of recent publications and news.

--- 2025-05-17 bio.qmd
@@
 ---
-title: Biography
+title: About
 ---
 
-# Biography
+# About Bin Yu
 
-<img src="images/bio1.jpg" alt="Bin Yu speaking" style="float:right; margin:0 0 1em 2em; width:200px; border-radius:8px;" />
+Bin Yu is the Chancellor's Distinguished Professor in the UC Berkeley Departments of Statistics and EECS.
+She was Chair of the Department of Statistics at UC Berkeley from 2009 to 2012.
+She is a member of National Academy of Sciences and currently serves on the editorial board of Proceedings of National Academy of Sciences (PNAS).
 
-Bin Yu is CDSS Chancellor's Distinguished Professor in the Departments of statistics and EECS, and Center for Computational Biology, and serves as a scientific advisor at the Simons Institute for the Theory of Computing, all at UC Berkeley.
+Professor Bin Yu recieved a BS Degree in Mathematics from Peking University, and MS and Ph.D.
+in Statistics from UC Berkeley.
+She was a Member of Technical Staff at Lucent Bell-Labs, Distinguished Researcher in the Deep Learning Group of Microsoft Research, Assistant Professor at UW-Madison, and Miller Research Professor at Berkeley.
+She was a Visiting Faculty at MIT, Peking University,  Newton Institute at Cambridge University, ETH, Yale University, Flatiron Institute, Poincare Institute, INRIA-Paris, and Fields Institute at University of Toronto.
 
-She obtained her BS Degree in Mathematics from Peking University, and MS and PhD Degrees in Statistics from UC Berkeley.
-She was Assistant Professor at UW-Madison, Visiting Assistant Professor at Yale University, Member of Technical Staff at Lucent Bell-Labs, and Miller Research Professor at Berkeley.
-She was a Visiting Faculty at MIT, ETH, Poincare Institute, Peking University, INRIA-Paris, Fields Institute at University of Toronto, Newton Institute at Cambridge University, and the Flatiron Institute in NYC.
-She was Chair of the Department of Statistics at UC Berkeley from 2009 to 2012.
-Recently, she was a 50% consultant researcher in the deep learning group of MSR at Redmond (2022-2023).
+Professor Bin Yu has published many research papers and one book, *Veridical Data Science* (MIT Press, 2024).
+Her research focuses on developing trustworthy and interpretable machine learning methods, with particular emphasis on the Predictability-Computability-Stability (PCS) framework for veridical data science.
+She has made fundamental contributions to statistical theory, including pioneering work on Vapnik-Chervonenkis (VC) theory for time series analysis, minimum description length (MDL) and entropy estimation, sparse modeling, boosting, spectral clustering, and MCMC convergence analysis.
+Her applied work spans neuroscience, genomics, remote sensing, and precision medicine, always emphasizing interdisciplinary collaboration with domain experts.
+Currently, she leads research in interpretable machine learning (including tree-based methods and deep learning interpretability), causal inference, and the development of stable, reproducible methods for scientific discovery.
+Her group has developed influential algorithms such as iterative random forests (iRF), contextual decomposition for transformers, and adaptive wavelet distillation for interpreting neural networks.
 
-She is a Member of the U.S.
-National Academy of Sciences and of the American Academy of Arts and Sciences.
-She was President of the Institute of Mathematical Statistics (IMS), Guggenheim Fellow, Tukey Memorial Lecturer of the Bernoulli Society, Rietz Lecturer of IMS, and a COPSS E.
+Professor Bin Yu has received many awards and honors throughout her career.
+She has been elected to the National Academy of Sciences and the American Academy of Arts and Sciences.
+Her major awards include the Guggenheim Fellowship, COPSS E.
 L.
-Scott Prize winner.
-Recently, she delivered the Wald Memorial Lectures of IMS and COPSS Distinguished Achievement Award and Lecture (DAAL) (formerly Fisher Award and Lecture) at JSM in 2023.
+Scott Prize, and most recently, the COPSS Distinguished Achievement Award and Lecture (DAAL) (formerly Fisher Award and Lecture) at JSM in 2023.
+She has delivered several distinguished lectures, including the Wald Memorial Lectures of the Institute of Mathematical Statistics (IMS), the Tukey Memorial Lecture of the Bernoulli Society, and the Rietz Lecture of IMS.
+She holds an Honorary Doctorate from the University of Lausanne in Switzerland.
+
+Professor Bin Yu has held many leadership positions in the statistical and data science communities.
+She served as President of the Institute of Mathematical Statistics (IMS) and was Chair of the Department of Statistics at UC Berkeley from 2009 to 2012.
 She served on the Inaugural Scientific Committee of the UK Turing Institute for Data Science and AI.
-She holds an Honorary Doctorate from the University of Lausanne in Switzerland.
-She is serving on the Editorial Board of Proceedings of National Academy of Sciences (PNAS).
+Her editorial leadership includes current service on the Editorial Board of Proceedings of National Academy of Sciences (PNAS), and previous service on editorial boards of Annals of Statistics, Journal of American Statistical Association, and Journal of Machine Learning Research.
+Her committee and advisory work includes co-chairing the National Scientific Committee of the Statistical and Applied Mathematical Sciences Institute (SAMSI), serving on scientific advisory committees of SAMSI and IPAM, and on the board of trustees of ICERM and the Board of Governors of IEEE-IT Society.
+She recently served on the scientific advisory committee for the IAS Special Year on optimization, statistics and theoretical machine learning, and the Scientific Advisory Boards of Canadian Statistical Sciences Institute (CANSSI).
+Currently, she serves on the advisory board of the AI Policy Hub at UC Berkeley, the Scientific Advisory Committee of the Department of Quantitative and Computational Biology at USC, and on the External Advisory Committee for Learning the Earth with Artificial Intelligence and Physics (LEAP), an NSF Science and Technology Center (STC), at Columbia University.
+She is a Chan-Zuckerberg Biohub Investigator and Weill Neurohub Investigator.
+She is a member of the UC Berkeley Center for Computational Biology and serves as a scientific advisor at the Simons Institute for the Theory of Computing.
+<!-- 
+# About Our Research Group
 
-She has published more than 170 papers in premier venues on statistical machine learning including deep learning and the Predictability-Computability-Stability (PCS) framework and documentation for [veridical (truthful) data science](https://vdsbook.com/) and these papers not only investigate a wide range of research topics from practice to algorithms and to theory, but also seek deep insights.
-The breadth and depth of her research experience enabled unique and novel solutions to interdisciplinary data problems in audio and image compression, network tomography, remote sensing, climate science, neuroscience, genomics, and precision medicine.
+The [Yu Group](https://www.stat.berkeley.edu/~yugroup/) at Berkeley consists of a small group of students and postdocs from Statistics and EECS, developing cutting-edge statistical machine learning methods that have proven highly valuable in theortical and applied diciplines spanning a broad range from genetics to quantitative finance.
+Our graduates have achieved exceptional success in academia and industry, with notable alumni including Peng Zhao (CEO of Citadel Securities), and senior quantitative researchers at Citadel, Two Sigma, Bridgewater, and Voleon.
 
-Currently, she is championing "in-context" research with experts in the subject knowledge and leading research in interpretable machine learning (e.g.
-tree-based methods and deep learning) and causal inference to design algorithms such as [iterative random forests (iRF)](https://www.pnas.org/doi/10.1073/pnas.1711236115), [Efficient Automated Circuit Discovery in Transformers using Contextual Decomposition (CD-T)](https://openreview.net/forum?id=41HlN8XYM5) and [adaptive wavelet distillation (AWD)](https://proceedings.neurips.cc/paper/2021/file/acaa23f71f963e96c8847585e71352d6-Paper.pdf) for interpreting deep neural networks and [X-learner for heterogeneous treatment effect estimation in causal inference](https://www.pnas.org/doi/10.1073/pnas.1804597116).
-Recently, she and her collaborators developed PCS-guided [low-signal signed iterative random forests (lo-siRF)](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v2) that recommends genetic targets for high-yield follow-up experiments with a case study showing epistasis regulation controls cardiac hypertrophy through gene-silencing experiment (4 out of 5 sets of experiments found causal genes or gene-gene interactions).
-She is also working on relevant deep learning theory and practical algorithms with her team (e.g.
-the development of [LoRA+ algorithm](https://github.com/nikhil-ghosh-berkeley/loraplus) for fine-tuning large language models).
+Our research focuses on developing stable, interpretable, and scalable methods.
+We have successfully built **real-time forecasting systems** for complex temporal data (including our [COVID-19 severity prediction](https://covidseverity.com/) system), developed **stability-driven machine learning frameworks** crucial for risk management, and created **interpretable deep learning methods** essential for regulatory compliance in financial applications.
 
-Previously, she pioneered Vapnik-Chervonenkis (VC) type theory needed for asymptotic analysis of time series and spatio-temporal processes, and made fundamental contributions to information theory and statistics through work on minimum description length (MDL) and entropy estimation, and through theory on sparse modeling, boosting and spectral clustering, EM algorithm, and MCMC convergence analysis.
-With her students and collaborators, she developed a highly cited spatially adaptive wavelet image denoising method and a low-complexity low-delay perceptually lossless audio coder that was incorporated in Bose wireless speakers, and developed a fast and well-validated Arctic cloud detection algorithm using NASA's MISR data.
-With the Jack Gallant Lab and her students, she developed predictive models of fMRI brain activity in vision neuroscience that made "mind-reading" possible (or reconstruction of movies using only fMRI signals).
+The Yu Group has developed many fundamental statistical and machine learning methods, including [**stability-driven nonnegative matrix factorization (staNMF)**](https://github.com/Yu-Group/staNMF) for regime detection and factor modeling, [**iterative Random Forests (iRF)**](https://github.com/Yu-Group/iterative-Random-Forest) and [**signed iRF (s-iRF)**](https://github.com/karlkumbier/iRF2.0) for discovering complex market interactions and non-linear relationships, [**hierarchical shrinkage methods**](https://arxiv.org/abs/2202.00858) for robust prediction in high-dimensional settings, and [**contextual decomposition (CD)**](https://github.com/jamie-murdoch/ContextualDecomposition) and [**aggregated contextual decomposition (ACD)**](https://github.com/csinva/hierarchical-dnn-interpretations) for interpreting complex deep learning models in trading applications.
 
-Moreover, she served on editorial boards including Annals of Statistics, Journal of American Statistical Association, and Journal of Machine Learning Research.
-Her leadership roles included co-chairing the National Scientific Committee of the Statistical and Applied Mathematical Sciences Institute (SAMSI), and serving on the scientific advisory committee of SAMSI and IPAM, and on the board of trustees of ICERM and the Board of Governors of IEEE-IT Society.
-She recently served on the scientific advisory committee for the IAS Special Year on optimization, statistics and theoretical machine learning, the Scientific Advisory Boards of Canadian Statistical Sciences Institute (CANSSI).
-She is serving on the advisory board of the AI Policy Hub at UC Berkeley, the Scientific Advisory Committee of the Department of Quantitative and Computational Biology at USC, and on the External Advisory Committee, Learning the Earth with Artificial Intelligence and Physics (LEAP), an NSF Science and Technology Center (STC), at Columbia University.
+Our research covers several key areas:
+
+## Deep Learning and Machine Learning
+
+Our work in deep learning spans from theoretical understanding to practical applications across diverse domains.
+Key contributions include mechanistic interpretation through contextual decomposition in transformers, efficient fine-tuning methods like [LoRA+](https://github.com/nikhil-ghosh-berkeley/loraplus), and frameworks for understanding neural network dynamics.
+We've developed methods like [Adaptive Wavelet Distillation (AWD)](https://github.com/Yu-Group/adaptive-wavelets) for interpreting deep neural networks, and theoretical work on the three stages of dynamics in high-dimensional kernel methods.
+Our applications range from clinical decision-making in healthcare to cosmological analysis and financial modeling.
+
+Selected recent papers:
+- [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) (ICML 2024)
+- [Mechanistic Interpretation through Contextual Decomposition in Transformers](https://arxiv.org/pdf/2407.00886) (2024)
+- [Minimum-Norm Interpolation Under Covariate Shift](https://arxiv.org/pdf/2404.00522) (ICML 2024)
+- [The three stages of dynamics in high-dimensional kernel methods](https://arxiv.org/abs/2111.07167) (ICLR 2022)
+
+## Veridical Data Science (PCS)
+
+The PCS (Predictability, Computability, Stability) framework represents our approach to responsible, reliable, and transparent data analysis.
+This framework unifies and expands on best practices in machine learning and statistics, ensuring that data science findings are both scientifically sound and practically actionable.
+The **Stability** component addresses model robustness and reproducibility, the **Predictability** component focuses on out-of-sample performance, and the **Computability** component ensures scalable implementation.
+Our work includes applications to genomics, clinical research, epidemiology, and quantitative finance, always emphasizing the importance of stability and reproducibility in scientific discovery.
+
+Selected recent papers:
+- [Veridical data science](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf) (PNAS 2020) — foundational framework paper
+- [Epistasis regulates genetic control of cardiac hypertrophy](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) (2023) — PCS application to genomics
+- [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (Harvard Data Science Review 2024)
+- [Stable discovery of interpretable subgroups via calibration in causal studies (staDISC)](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427)
+
+## Interpretable Machine Learning
+
+We develop methods to make machine learning models interpretable and trustworthy, particularly for high-stakes applications in healthcare, science, and finance.
+Our work spans contextual decomposition for understanding neural networks, feature importance frameworks, and methods for aligning model explanations with prior knowledge.
+We emphasize the principle that interpretations should be both faithful to the model and useful for human decision-making across diverse domains.
+
+Selected recent papers:
+- [Mechanistic Interpretation through Contextual Decomposition in Transformers](https://arxiv.org/pdf/2407.00886) (2024)
+- [MDI+: a flexible random forest-based feature importance framework](https://arxiv.org/abs/2307.01932) (2023)
+- [Tell your model where to attend: post-hoc attention steering for LLMs](https://arxiv.org/abs/2311.02262) (ICLR 2024)
+- [Definitions, methods, and applications in interpretable machine learning](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) (PNAS 2019)
+
+## Tree-based Methods
+
+We develop both theoretical understanding and practical improvements for tree-based methods, including random forests and gradient boosting.
+Our contributions include the iterative Random Forests (iRF) algorithm for discovering high-order interactions, hierarchical shrinkage methods for improving accuracy and interpretability, and fast interpretable greedy-tree sums (FIGS).
+We also provide theoretical analysis of when and why tree-based methods succeed or fail, with applications spanning from genomics to finance to clinical medicine.
+
+Selected recent papers:
+- [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis](https://arxiv.org/pdf/2406.19958) (2024)
+- [Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931) (2022)
+- [Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods](https://arxiv.org/abs/2202.00858) (ICML 2022)
+- [Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests](https://arxiv.org/abs/2102.11800) (PNAS 2022)
+- [iterative Random Forests to discover predictive and stable high-order interactions](https://www.stat.berkeley.edu/~binyu/ps/papers2018/iRF+SI18.pdf) (PNAS 2018)
+
+## Quantitative Finance Applications
+
+Our methods have proven particularly valuable in quantitative finance, where model stability, interpretability, and out-of-sample performance are crucial.
+Our graduates have achieved exceptional success at leading hedge funds including Citadel Securities (where Peng Zhao serves as CEO), Two Sigma, Bridgewater, and Voleon.
+We develop stability-driven approaches for regime detection, portfolio optimization, risk management, and alpha generation, always emphasizing robust performance across changing market conditions.
+
+Key applications and alumni outcomes:
+- **Real-time forecasting systems** for complex temporal data and market dynamics
+- **Stability-driven frameworks** crucial for live trading environments
+- **Interpretable models** essential for regulatory compliance and risk management
+- **High-dimensional interaction discovery** for complex market relationship modeling
+
+## Interdisciplinary Research in Biomedicine
+
+Our biomedicine work applies statistical machine learning to problems in genomics, clinical prediction, and biomarker discovery.
+We collaborate closely with domain experts to develop methods that are both statistically rigorous and clinically meaningful.
+Recent work includes epistasis analysis for cardiac hypertrophy, metabolomic signatures for pancreatic cancer risk, and clinical AI modeling standards.
+
+Selected recent papers:
+- [Epistasis regulates genetic control of cardiac hypertrophy](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) (2023)
+- [A blood-based metabolomic signature predictive of risk for pancreatic cancer](https://pubmed.ncbi.nlm.nih.gov/37729870/) (Cell Reports Medicine 2023)
+- [Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y) (Nature Medicine 2020)
+- [Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) (2023)
+
+Our graduates have achieved remarkable success across academia and industry, securing positions at leading institutions including top universities, major technology companies, and premier quantitative trading firms such as Citadel Securities, Two Sigma, Bridgewater, and Voleon.
+This success reflects the broad applicability of our research and the exceptional training our students receive in robust statistical methods, scalable machine learning, and rigorous mathematical foundations essential for tackling complex real-world problems.
+
+Research is supported in part by grants from NSF, NIH, the Weill Neurohub, and the Simons Foundation.
+
+- [Yu Group at Berkeley](https://www.stat.berkeley.edu/~yugroup/) for current group members and current projects
+- [Papers](https://binyu.stat.berkeley.edu/papers)
+- [Code](https://www.stat.berkeley.edu/~yugroup/code.html)
+- [Statistical Machine Learning at Berkeley](http://www.stat.berkeley.edu/~statlearning/)
+
+# Vision
+
+My broad vision of data science best described in my article [Veridical Data Science](https://www.pnas.org/content/117/8/3920).
+In this work, I introduced a framework based on three principles: predictability, computability and stability (abbreviated to PCS).
+This framework helps guide practitioners who solve domain data problems with data science tools to be creative in their analysis and properly validate their findings.
+I have written a book on the Veridical Data Science framework together with my former student [Rebecca Barter](https://www.rebeccabarter.com/).
+The book is being published by the MIT Press in 2024 with a free on-line copy available soon.
+
+She and her team have developed the PCS framework for veridical data science (or responsible, reliable, and transparent data analysis and decision-making).
+PCS stands for predictability, computability and stability, and it unifies, streamlines, and expands on ideas and best practices of machine learning and statistics.
+
+In order to augment empirical evidence for decision-making, they are investigating statistical machine learning methods/algorithms (and associated statistical inference problems) such as dictionary learning, non-negative matrix factorization (NMF), EM and deep learning (CNNs and LSTMs), and heterogeneous effect estimation in randomized experiments (X-learner).
+Their recent algorithms include staNMF for unsupervised learning, iterative Random Forests (iRF) and signed iRF (s-iRF) for discovering predictive and stable high-order interactions in supervised learning, next generation tree-based methods (e.g.
+fast and interpretable greedy-tree sums (FIGS) and hierarchical shrinked (HS) trees, and RF+ ), contextual decomposition (CD), aggregated contextual decomposition (ACD), and adaptive wavelet distillation (AWD) for interpretation of Deep Neural Networks (DNNs).
+-->

### 2025-07-20 index.qmd
Update website content and navigation structure
Renamed the 'Code' section to 'Software' in _quarto.yml for clarity. Enhanced the 'About' page with a more detailed overview of Professor Bin Yu's achievements and research focus, while streamlining the content for better readability. Removed the 'code.qmd' file to consolidate software information into the new 'Software' section. Updated the index.qmd layout to improve the presentation of recent publications and news.

@@
 
-<div style="text-align:center">
 # Bin Yu
+
+<div style="flex: 0 0 200px;">
+<img src="images/binyu.jpg" alt="Bin Yu" style="width:200px; border-radius:8px;" />
 </div>
 
-<img src="images/binyu.jpg" alt="Bin Yu" style="float:right; margin:0 0 1em 2em; width:200px; border-radius:8px;" />
+- Chancellor's Distinguished Professor of Statistics
+- Statistics Department Chair, 2009 - 2012
+- Professor by courtesy, Electrical Engineering and Computer Sciences
 
-Chancellor's Distinguished Professor of Statistics and Electrical Engineering and Computer Sciences by courtesy
+**Address:** 367 Evans Hall #3860, Berkeley, CA 94720  
+**Phone:** 510-642-2781  
+**Fax:** 510-642-7892  
+**Email:** [binyu@berkeley.edu](mailto:binyu@berkeley.edu)
 
-Statistics Department Chair, 2009 - 2012
+## Recent Publications, Talks & News
 
-*mail: 367 Evans Hall #3860 • Berkeley, CA 94720 phone: 510-642-2781 • fax: 510-642-7892 • [binyu@berkeley.edu](mailto:binyu@berkeley.edu)*
-
-## Recent Publications & Talks
-
-- [New paper: PCS workflow for veridical data science in the age of AI (Z. Rewolinski and B. Yu, 2025)](https://www.stat.berkeley.edu/~yugroup/pubs/pcs_workflow-6.pdf)
-- [Veridical data science and medical foundation models](https://arxiv.org/abs/2409.10580) on arXiv by Alaa and Yu.
-- [VDS book review](https://hdsr.mitpress.mit.edu/pub/5322mn1e/release/3) by Yuval and Yoav Benjamini in Harvard Data Science Review (HDSR)-- "pedagogical excellence, diverse examples, and projects make Veridical Data Science a suitable textbook for students of all levels, in addition to being a valuable resource for data scientists in general" (review summary in HDSR Editor-in-Chief's note), June, 2024.
-- ["Veridical data science towards trustworthy AI"](https://ww2.amstat.org/meetings/jsm/2023/webcasts/index.cfm) (Talk video of COPSS DAAL (formerly Fisher Award and Lecture), scroll down), Aug.
+- *2025* [New paper: PCS workflow for veridical data science in the age of AI (Z. Rewolinski and B. Yu, 2025)](https://www.stat.berkeley.edu/~yugroup/pubs/pcs_workflow-6.pdf)
+- *2025* [Veridical Data Science in Biology on July 11, 2025 at UC Berkeley (Submission deadline July 4)](https://www.eventbrite.com/e/veridical-data-science-for-biology-2025-tickets-1384456339179)
+- *2025* [Rome Workshop on Veridical Data Science, June 20, 2025](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html)
+- *2024* [Veridical data science and medical foundation models](https://arxiv.org/abs/2409.10580) on arXiv by Alaa and Yu.
+- *2024* [VDS book review](https://hdsr.mitpress.mit.edu/pub/5322mn1e/release/3) by Yuval and Yoav Benjamini in Harvard Data Science Review (HDSR)-- "pedagogical excellence, diverse examples, and projects make Veridical Data Science a suitable textbook for students of all levels, in addition to being a valuable resource for data scientists in general" (review summary in HDSR Editor-in-Chief's note), June, 2024.
+- *2024* [Inaugural Berkeley-Stanford Workshop on Veridical Data Science at UC Berkeley](https://na.eventscloud.com/website/69057/) (May 31, 2024) ([talk videos available](https://www.youtube.com/playlist?list=PLKW2Azk23ZtSrg4jwLSioaV1bwmFnQ1Bx))
+- *2024* Our MIT Press book ["Veridical Data Science: The Practice of Responsible Data Analysis and Decision Making"](https://mitpress.mit.edu/9780262049191/veridical-data-science/), has been released [online](http://vdsbook.com/).
+- *2023* ["Veridical data science towards trustworthy AI"](https://ww2.amstat.org/meetings/jsm/2023/webcasts/index.cfm) (Talk video of COPSS DAAL (formerly Fisher Award and Lecture), scroll down), Aug.
 JSM in Toronto, 2023.
-- [Veridical data science](https://www.pnas.org/content/117/8/3920) (PCS framework: [v-flow code](https://github.com/Yu-Group/veridical-flow) and [documentation template](https://yu-group.github.io/vdocs/PCSDoc-Template.html)), PNAS, 2020 ([QnAs with Bin Yu](https://www.pnas.org/content/117/8/3893))
-- My co-author [Rebecca Barter](https://rebeccabarter.com/) and I are thrilled to announce the [online release](http://vdsbook.com/) of our MIT Press book ["Veridical Data Science: The Practice of Responsible Data Analysis and Decision Making"](https://mitpress.mit.edu/9780262049191/veridical-data-science/), an essential source for producing trustworthy data-driven results (Feb.
-28, 2024).
+- *2023* IMS Wald [Lecture I](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1029) and [Lecture II](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1031), and [COPSS Distinguished Award and Lecture (DAAL)](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1374) delivered at [Joint Statistical Meeting (JSM)](https://ww2.amstat.org/meetings/jsm/2023/) in Toronto, August 2023
+- *2022* [CDSS news: Statistics-Computer Science team reflects on tackling covid outbreaks](https://data.berkeley.edu/news/statistics-computer-sciences-team-reflects-tackling-covid-outbreaks), May, 2022
+- *2021* Honorary Doctorate, University of Lausanne (UNIL) (Faculty of Business and Economics), June 4, 2021 ([Interview of Bin Yu](https://www.youtube.com/watch?v=1JRGPGhcYzU) by journalist Nathalie Randin, with an introduction by Dean Jean-Philippe Bonardi of UNIL in French ([English translation](https://www.stat.berkeley.edu/~binyu/Intro-DeanBonardi-UNIL.pdf)))
+- *2020* [Veridical data science](https://www.pnas.org/content/117/8/3920) (PCS framework: [v-flow code](https://github.com/Yu-Group/veridical-flow) and [documentation template](https://yu-group.github.io/vdocs/PCSDoc-Template.html)), PNAS, 2020 ([QnAs with Bin Yu](https://www.pnas.org/content/117/8/3893))
+- *2020* [CDSS news on our PCS framework: "A better framework for more robust, trustworthy data science"](https://data.berkeley.edu/people/bin-yu), Oct. 2020
+- *2020* [UC Berkeley to lead $10M NSF/Simons Foundation program to investigate theoretical underpinnings of deep learning](https://data.berkeley.edu/news/uc-berkeley-lead-10m-nsfsimons-foundation-program-investigate-theoretical-underpinnings-deep), Aug.
+25, 2020
+- *2020* UC Berkeley team part of the new NSF AI Center for Cybersecurity [ACTION](https://action.ucsb.edu/) led by UCSB.
 
 [View all papers →](papers.qmd)
-
-## Recent News
-
-- [Veridical Data Science in Biology on July 11, 2025 at UC Berkeley (Submission deadline July 4)](https://www.eventbrite.com/e/veridical-data-science-for-biology-2025-tickets-1384456339179)
-- [Rome Workshop on Veridical Data Science, June 20, 2025](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html)
-- IMS Wald [Lecture I](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1029) and [Lecture II](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1031), and [COPSS Distinguished Award and Lecture (DAAL)](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1374) delivered at [Joint Statistical Meeting (JSM)](https://ww2.amstat.org/meetings/jsm/2023/) in Toronto, August 2023
-- [Inaugural Berkeley-Stanford Workshop on Veridical Data Science at UC Berkeley](https://na.eventscloud.com/website/69057/) (May 31, 2024) ([talk videos available](https://www.youtube.com/playlist?list=PLKW2Azk23ZtSrg4jwLSioaV1bwmFnQ1Bx))
-- UC Berkeley team part of the new NSF AI Center for Cybersecurity [ACTION](https://action.ucsb.edu/) led by UCSB.
-- [CDSS news: Statistics-Computer Science team reflects on tackling covid outbreaks](https://data.berkeley.edu/news/statistics-computer-sciences-team-reflects-tackling-covid-outbreaks), May, 2022
-- Honorary Doctorate, University of Lausanne (UNIL) (Faculty of Business and Economics), June 4, 2021 ([Interview of Bin Yu](https://www.youtube.com/watch?v=1JRGPGhcYzU) by journalist Nathalie Randin, with an introduction by Dean Jean-Philippe Bonardi of UNIL in French ([English translation](https://www.stat.berkeley.edu/~binyu/Intro-DeanBonardi-UNIL.pdf)))
-- [CDSS news on our PCS framework: "A better framework for more robust, trustworthy data science"](https://data.berkeley.edu/people/bin-yu), Oct. 2020
-- [UC Berkeley to lead $10M NSF/Simons Foundation program to investigate theoretical underpinnings of deep learning](https://data.berkeley.edu/news/uc-berkeley-lead-10m-nsfsimons-foundation-program-investigate-theoretical-underpinnings-deep), Aug.
-25, 2020

### 2025-07-20 papers.qmd
Update website content and navigation structure
Renamed the 'Code' section to 'Software' in _quarto.yml for clarity. Enhanced the 'About' page with a more detailed overview of Professor Bin Yu's achievements and research focus, while streamlining the content for better readability. Removed the 'code.qmd' file to consolidate software information into the new 'Software' section. Updated the index.qmd layout to improve the presentation of recent publications and news.

@@
 Ashley* (2023).
-Epistasis regulates genetic control of cardiac hypertrophy.
-[medRxiv](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
+[Epistasis regulates genetic control of cardiac hypertrophy.](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
 
@@
 Abbasi-Asl (2023).
-Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology.
-[bioRxiv](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
+[Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology.](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
 
@@
 
-K.
-Wu, Y.
-Chen, W.
-Ha, B.
-Yu (2023).
-[Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms.](https://arxiv.org/abs/2309.10301) JMLR (accepted).
-[https://arxiv.org/abs/2309.10301](https://arxiv.org/abs/2309.10301)
-
-N.
-Ghosh, S.
-Frei, W.
-Ha, B.
-Yu (2023).
-The effect of SGD batch size on autoencoder learning: sparsity, sharpness and feature learning.
-[https://arxiv.org/abs/2308.03215](https://arxiv.org/abs/2308.03215)
-
-R.
-Netzorg, J.
-Li, B.
-Yu (2024).
-Improving prototypical part networks with reward reweighting, reselection, and retraining.
-Proc.
-ICML.
-[https://arxiv.org/abs/2307.03887](https://arxiv.org/abs/2307.03887)
-
-A.
-Agarwal, A.
-M.
-Kenny, Y.
-S.
-Tan, T.
-M.
-Tang, B.
-Yu (2023).
-MDI+: a flexible random forest-based feature importance framework.
-[https://arxiv.org/abs/2307.01932](https://arxiv.org/abs/2307.01932) (PCS related)
+K. Wu, Y. Chen, W. Ha, B. Yu (2023). [Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms.](https://arxiv.org/abs/2309.10301) JMLR (accepted).
+
+N. Ghosh, S. Frei, W. Ha, B. Yu (2023). [The effect of SGD batch size on autoencoder learning: sparsity, sharpness and feature learning.](https://arxiv.org/abs/2308.03215)
+
+R. Netzorg, J. Li, B. Yu (2024). [Improving prototypical part networks with reward reweighting, reselection, and retraining.](https://arxiv.org/abs/2307.03887) Proc. ICML.
+
+A. Agarwal, A. M. Kenny, Y. S. Tan, T. M. Tang, B. Yu (2023). [MDI+: a flexible random forest-based feature importance framework.](https://arxiv.org/abs/2307.01932) (PCS related)
 
@@
 Yu (2023).
-Diagnosing transformers: illuminating feature space for clinical decison-making.
-Proc.
+[Diagnosing transformers: illuminating feature space for clinical decison-making.](https://arxiv.org/abs/2305.17588) Proc.
 ICLR.
-[https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)
-
-C.
-Singh, A.
-R.
-Hsu, R.
-Antonello, S.
-Jain, A.
-G.
-Huth, B.
-Yu and J.
-Gao (2023).
-Explaining black box text modules in natural language with language models.
-[https://arxiv.org/abs/2305.09863](https://arxiv.org/abs/2305.09863)
+
+C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
 
@@
 
-D.
-Shen, P.
-Ding, J.
-Sekhon, B.
-Yu (2022).
-Same root different leaves: time series and cross-sectional methods in panel data.
-Econometrica (accepted).
-[https://arxiv.org/abs/2207.14481](https://arxiv.org/abs/2207.14481)
+D. Shen, P. Ding, J. Sekhon, B. Yu (2022). [Same root different leaves: time series and cross-sectional methods in panel data.](https://arxiv.org/abs/2207.14481) Econometrica (accepted).
 
@@
 (2021).
-Supervised line attention for tumor attribute classification from pathology reports: Higher performance with less data.
-Journal of Biomedical Informatics.
+[Supervised line attention for tumor attribute classification from pathology reports: Higher performance with less data.](https://arxiv.org/abs/2012.08113) Journal of Biomedical Informatics.
 122 (2021) 103872.
-[arXiv version](https://arxiv.org/abs/2012.08113)
 
@@
 Yu* (2020).
-[Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
+[Learning epistatic polygenic phenotypes with Boolean interactions.](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
 
@@
 Yu (2020).
-[A stability-driven protocol for drug response interpretable prediction (staDRIP)](https://arxiv.org/abs/2011.06593).
-NeurISP workshop on ML4H (Machine learning for Health) Extended Abstract.
+[A stability-driven protocol for drug response interpretable prediction (staDRIP).](https://arxiv.org/abs/2011.06593) NeurISP workshop on ML4H (Machine learning for Health) Extended Abstract.
 
@@
 Yu*.
-(2020) [Curating a COVID-19 data repository and forecasting county-level death counts in the United States.](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1) Harvard Data Science Review ([code](https://github.com/Yu-Group/covid19-severity-prediction)) [7-day prediction results](https://covidseverity.com/) [Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4)
+(2020) [Curating a COVID-19 data repository and forecasting county-level death counts in the United States.](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1) Harvard Data Science Review ([code](https://github.com/Yu-Group/covid19-severity-prediction)) ([7-day prediction results](https://covidseverity.com/)) ([Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4))
 
@@
 117 (8), 3920-3929.
-[QnAs with Bin Yu.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf)
+([QnAs with Bin Yu](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf))
 
@@
 Wainwright and B.
-Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients,](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, [arXiv](https://arxiv.org/abs/1905.12247)
+Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients.](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, ([arXiv](https://arxiv.org/abs/1905.12247))
 
@@
 
-Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes](http://jmlr.org/papers/v19/18-158.html). JMLR . http://jmlr.org/papers/v19/18-158.html
+Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes.](http://jmlr.org/papers/v19/18-158.html) JMLR.
 
@@
 Wainwright and B.
-Yu (2020) [Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier](https://ieeexplore.ieee.org/abstract/document/8262876/) Allerton Conference 2017 https://ieeexplore.ieee.org/abstract/document/8262876/
+Yu (2020) [Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier.](https://ieeexplore.ieee.org/abstract/document/8262876/) Allerton Conference 2017.
 
@@
 1-52.
-Also at https://arxiv.org/abs/1902.08380
+([arXiv](https://arxiv.org/abs/1902.08380))
 
@@
 Gallant*, and B.
-Yu* (2018) [The DeepTune framework for modeling and characterizing neurons in visual cortex area V4](https://www.biorxiv.org/content/10.1101/465534v1) https://www.biorxiv.org/content/10.1101/465534v1
+Yu* (2018) [The DeepTune framework for modeling and characterizing neurons in visual cortex area V4.](https://www.biorxiv.org/content/10.1101/465534v1)
 
@@
 Celniker, and B.
-Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
+Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
 
@@
 ICLR 2018.
-[https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code)](https://github.com/csinva/hierarchical-dnn-interpretations)
-
-R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309) https://arxiv.org/abs/1801.02309.
+([code](https://github.com/csinva/hierarchical-dnn-interpretations))
+
+R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309)
 
@@
 
-Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) [Fast MCMC sampling algorithms on polytopes](https://arxiv.org/abs/1710.08165) https://arxiv.org/abs/1710.08165.
+Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) [Fast MCMC sampling algorithms on polytopes.](https://arxiv.org/abs/1710.08165)
 
@@
 
-R. Abbasi-Asl and B. Yu (2017) [Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning](https://arxiv.org/abs/1705.07356) https://arxiv.org/abs/1705.07356
-
-R.
-Abbasi-Asl and B.
-Yu (2017) [Interpreting Convolutional Neural Networks Through Compression.](https://arxiv.org/abs/1711.02329) NIPS 2017.
-Symposium on Interpretable Machine Learning.
-(also https://arxiv.org/abs/1711.02329)
+R. Abbasi-Asl and B. Yu (2017) [Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning.](https://arxiv.org/abs/1705.07356)
+
+R. Abbasi-Asl and B. Yu (2017) [Interpreting Convolutional Neural Networks Through Compression.](https://arxiv.org/abs/1711.02329) NIPS 2017. Symposium on Interpretable Machine Learning.
 
@@
 Bickel, and B.
-Yu* (2019) [Meta-learners for Estimating Heterogeneous Treatment Effects using Machine Learning,](https://www.pnas.org/content/116/10/4156) PNAS.
+Yu* (2019) [Meta-learners for Estimating Heterogeneous Treatment Effects using Machine Learning.](https://www.pnas.org/content/116/10/4156) PNAS.
 116 (10) 4156-4165.
-https://arxiv.org/abs/1706.03461.
-[(code](https://github.com/soerenkuenzel/hte))
+([arXiv](https://arxiv.org/abs/1706.03461)) ([code](https://github.com/soerenkuenzel/hte))
 

### 2025-07-20 papers/interpretable-machine-learning.qmd
Update website content and navigation structure
Renamed the 'Code' section to 'Software' in _quarto.yml for clarity. Enhanced the 'About' page with a more detailed overview of Professor Bin Yu's achievements and research focus, while streamlining the content for better readability. Removed the 'code.qmd' file to consolidate software information into the new 'Software' section. Updated the index.qmd layout to improve the presentation of recent publications and news.

@@
 
-1.
-A.
-R.
-Hsu, Y.
-Cherapanamjeri, A.
-Y.
-Odisho, P.
-R.
-Carroll, B.
-Yu (2024).
-[Mechanistic Interpretation through Contexual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886) [https://arxiv.org/pdf/2407.00886](https://arxiv.org/pdf/2407.00886).
-1.
-Y.
-Chen, C.
-Singh, X.
-Liu, S.
-Zuo, B.
-Yu, H.
-He, J.
-Gao (2024).
-[Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986) [https://arxiv.org/abs/2401.13986](https://arxiv.org/abs/2401.13986)
-1.
-Q.
-Zhang, C.
-Singh, L.
-Liu, X.
-Liu, B.
-Yu, J.
-Gao, T.
-Zhao (2023).
-[Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262) ICLR 2024.
-https://arxiv.org/abs/2311.02262
-1.
-A.
-Agarwal, A.
-M.
-Kenny, Y.
-S.
-Tan, T.
-M.
-Tang, B.
-Yu (2023).
-MDI+: a flexible random forest-based feature importance framework.
-[https://arxiv.org/abs/2307.01932](https://arxiv.org/abs/2307.01932) (PCS related)
+1. A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contextual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886)
+1. Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). [Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986)
+1. Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262) ICLR 2024.
+1. A. Agarwal, A. M. Kenny, Y. S. Tan, T. M. Tang, B. Yu (2023). [MDI+: a flexible random forest-based feature importance framework.](https://arxiv.org/abs/2307.01932) (PCS related)
 1.
@@
 Yu (2023).
-[Diagnosing transformers: illuminating feature space for clinical decison-making.](https://arxiv.org/abs/2305.17588) ICLR (2024) [https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)
+[Diagnosing transformers: illuminating feature space for clinical decision-making.](https://arxiv.org/abs/2305.17588) ICLR (2024)
 1. C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
@@
 Yu (2021).
-[Interpreting and Improving Deep-Learning Models with Reality Checks](https://arxiv.org/abs/2108.06847).
-[https://arxiv.org/abs/2108.06847](https://arxiv.org/abs/2108.06847) to appear in the book entitled "xxAI - Beyond Explainable AI" (eds.
+[Interpreting and Improving Deep-Learning Models with Reality Checks.](https://arxiv.org/abs/2108.06847) To appear in the book entitled "xxAI - Beyond Explainable AI" (eds.
 Andreas Holzinger, Randy Goebel, Ruth Fong, Taesup Moon, Klaus-Robert Müller, and Wojciech Samek).
@@
 ICLR 2018.
-[https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code](https://github.com/csinva/hierarchical-dnn-interpretations))
+([code](https://github.com/csinva/hierarchical-dnn-interpretations))

### 2025-07-20 papers/tree-based-methods.qmd
Update website content and navigation structure
Renamed the 'Code' section to 'Software' in _quarto.yml for clarity. Enhanced the 'About' page with a more detailed overview of Professor Bin Yu's achievements and research focus, while streamlining the content for better readability. Removed the 'code.qmd' file to consolidate software information into the new 'Software' section. Updated the index.qmd layout to improve the presentation of recent publications and news.

@@
 
-1.
-Y.
-S.
-Tan, O.
-Ronen, T.
-Saarinen, B.
-Yu (2024).
-[The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958) [https://arxiv.org/pdf/2406.19958](https://arxiv.org/pdf/2406.19958).
+1. Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958)
 1.
@@
 Yu (2022).
-[Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931).
-https://arxiv.org/abs/2201.11931 ([imodels 🔎: a python package for fitting interpretable models](https://github.com/csinva/imodels) contains code for FIGS).
+[Fast interpretable greedy-tree sums (FIGS).](https://arxiv.org/abs/2201.11931) ([imodels 🔎: a python package for fitting interpretable models](https://github.com/csinva/imodels) contains code for FIGS).
 1.
@@
 Yu (2022).
-[Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.](https://arxiv.org/abs/2102.11800) PNAS, [https://arxiv.org/abs/2102.11800](https://arxiv.org/abs/2102.11800) (theory for a tractable version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS-related)
+[Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.](https://arxiv.org/abs/2102.11800) PNAS, (theory for a tractable version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS-related)
 1.
@@
 [Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.](https://arxiv.org/abs/2202.00858) Proc.
-ICML [https://arxiv.org/abs/2202.00858](https://arxiv.org/abs/2202.00858) ([imodels 🔎: a python package for fitting interpretable models](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS))
-1.
-Y.
-Tan, A.
-Agarwal, and B.
-Yu (2021).
-[A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc.
-AISTATS, [https://arxiv.org/abs/2110.09626](https://arxiv.org/abs/2110.09626)
+ICML ([imodels 🔎: a python package for fitting interpretable models](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS))
+1. Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS.
 1.
@@
 Yu* (2020).
-[Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) [https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
+[Learning epistatic polygenic phenotypes with Boolean interactions.](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
 1.
@@
 Celniker, and B.
-Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
+Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
 1.

### 2025-07-20 papers/veridical-data-science-pcs.qmd
Update website content and navigation structure
Renamed the 'Code' section to 'Software' in _quarto.yml for clarity. Enhanced the 'About' page with a more detailed overview of Professor Bin Yu's achievements and research focus, while streamlining the content for better readability. Removed the 'code.qmd' file to consolidate software information into the new 'Software' section. Updated the index.qmd layout to improve the presentation of recent publications and news.

@@
 Ashley (2023).
-Epistasis regulates genetic control of cardiac hypertrophy.
-[https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
+[Epistasis regulates genetic control of cardiac hypertrophy.](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
 1.
@@
 Abbasi-Asl (2023).
-Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology.
-[https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
-1.
-A.
-Agarwal, A.
-M.
-Kenny, Y.
-S.
-Tan, T.
-M.
-Tang, B.
-Yu (2023).
-MDI+: a flexible random forest-based feature importance framework.
-[https://arxiv.org/abs/2307.01932](https://arxiv.org/abs/2307.01932) (PCS related)
+[Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology.](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
+1. A. Agarwal, A. M. Kenny, Y. S. Tan, T. M. Tang, B. Yu (2023). [MDI+: a flexible random forest-based feature importance framework.](https://arxiv.org/abs/2307.01932) (PCS related)
 1.
@@
 Yu* (2020).
-[Stable discovery of interpretable subgroups via calibration in causal studies (staDISC).](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427) International Statistical Review and also at [arxiv.org/abs/2008.10109](https://arxiv.org/abs/2008.10109) ([code](https://github.com/Yu-Group/stadisc)) (PCS case study for causal inference)
+[Stable discovery of interpretable subgroups via calibration in causal studies (staDISC).](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427) International Statistical Review ([arXiv](https://arxiv.org/abs/2008.10109)) ([code](https://github.com/Yu-Group/stadisc)) (PCS case study for causal inference)
 1.
@@
 Gallant*, and B.
-Yu* (2018) [The DeepTune framework for modeling and characterizing neurons in visual cortex area V4](https://www.biorxiv.org/content/10.1101/465534v1) https://www.biorxiv.org/content/10.1101/465534v1
+Yu* (2018) [The DeepTune framework for modeling and characterizing neurons in visual cortex area V4.](https://www.biorxiv.org/content/10.1101/465534v1)
 1.

### 2025-07-20 software.qmd
Update website content and navigation structure
Renamed the 'Code' section to 'Software' in _quarto.yml for clarity. Enhanced the 'About' page with a more detailed overview of Professor Bin Yu's achievements and research focus, while streamlining the content for better readability. Removed the 'code.qmd' file to consolidate software information into the new 'Software' section. Updated the index.qmd layout to improve the presentation of recent publications and news.

---
title: Code
---

# Software

*Also see our group's public repos on [GitHub](https://github.com/Yu-Group).*

* **[VeridicalFlow](https://github.com/Yu-Group/veridical-flow)**: Library for building stable, trustworthy data-science pipelines, PCS framework, [paper](https://www.pnas.org/content/117/8/3920), [docs](https://vflow.csinva.io/)

* **[simChef](https://github.com/Yu-Group/simChef)**: R package to facilitate PCS simulation studies, data science workflows

* **[imodels](https://github.com/csinva/imodels)**: Python package for interpretable machine learning models, FIGS, hierarchical shrinkage, MDI+, [FIGS paper](https://arxiv.org/abs/2201.11931), [hierarchical shrinkage paper](https://arxiv.org/abs/2202.00858), [MDI+ paper](https://arxiv.org/pdf/2307.01932)

* **[iRF](https://github.com/Yu-Group/iterative-Random-Forest)**: Iterative Random Forests, stable high-order interactions, PCS-guided, [paper](https://www.pnas.org/content/115/8/1943)

* **[Adaptive wavelets](https://github.com/Yu-Group/adaptive-wavelets)**: Adaptive interpretable wavelets and wavelet distillation, domain-agnostic, [paper](https://www.nature.com/articles/s41467-021-25759-1)

* **[COVID-19 severity prediction](https://github.com/Yu-Group/covid19-severity-prediction)**: Extensive COVID-19 data and forecasting for counties and hospitals, pandemic severity index, [paper](https://hdsr.mitpress.mit.edu/pub/p6isyf0g), [website](http://covidseverity.com/)

* **[Epistasis cardiac hypertrophy](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)**: Code for epistasis in genetic control of cardiac hypertrophy, PCS-guided, [preprint](https://www.biorxiv.org/content/10.1101/2021.12.22.473882v2), [PCS docs](https://yu-group.github.io/epistasis-cardiac-hypertrophy/)

* **[Molecular partner prediction](https://github.com/Yu-Group/molecular-partner-prediction)**: Predicting successful CME events using clathrin markers, cell biology

* **[sMPS2](https://github.com/Yu-Group/sMPS2)**: Simplified MyProstateScore2.0 for high-grade prostate cancer detection, clinical decision rules

* **[MS-analysis-NMF](https://github.com/Yu-Group/MS-analysis-NMF)**: Non-negative matrix factorization for deconvolving complex mass spectra, simulation study

* **[VDS book supplementary](https://github.com/Yu-Group/vds-book-supplementary)**: Supplementary materials for Veridical Data Science book, educational resources

* **[imodels-experiments](https://github.com/Yu-Group/imodels-experiments)**: Experimental interpretable models to accompany imodels package, rule-based models

* **[Yu Group website](https://github.com/Yu-Group/yugroup-website)**: Source code for the Yu Group website, web development

<!-- * **escv**: Selection of regularization for lasso, sparser interpretable models, first work related to PCS, [paper](https://www.tandfonline.com/doi/full/10.1080/10618600.2015.1092978)

* **stanmf**: Stability driven non-negative matrix factorization, PCS-guided dimensionality reduction, [paper](https://www.pnas.org/content/113/16/4290)

* **Causal inference**: X-learner for CATE prediction, staDISC for discovering stable subgroups, PCS-guided causal methods, [X-learner paper](https://arxiv.org/abs/1706.03461), [staDISC paper](https://arxiv.org/abs/2008.10109)

* **epiTree**: Learning epistatic polygenic phenotypes with boolean interactions, PCS inference, genetics, [paper](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1)

* **staDRIP**: Drug-response prediction using stability-driven methods, PCS-guided precision medicine, [paper](https://arxiv.org/abs/2011.06593)

* **Superheat**: R package for generating beautiful and customizable heatmaps, data visualization, [paper](https://www.tandfonline.com/doi/full/10.1080/10618600.2018.1473780)

* **SUFO**: Embedding space interpretations for mechanistic neural network understanding, transformers, [paper](https://arxiv.org/abs/2305.17588)

* **ACD**: Hierarchical interpretations for neural networks, TRIM, CDEP, SPEX for feature attribution and LLMs, [ACD paper](https://arxiv.org/abs/1806.05337), [CD-T paper](https://arxiv.org/abs/2407.00886)

* **MDI OOB**: Debiased random forest feature importance, statistical inference, [MDI+ paper](https://arxiv.org/abs/2307.01932), [MDI OOB paper](https://arxiv.org/abs/1906.10845)

* **MDL-Complexity**: Model complexity theory, information theory applications, [paper](https://jmlr.org/papers/v24/21-1133.html) -->

### 2025-07-20 papers.qmd
Update website content and structure
Renamed sections in various files for clarity, changing 'Bin Yu' to 'Professor Bin Yu' in index.qmd and 'Select Publications' to 'Papers' in papers.qmd. Enhanced publication entries with direct links to papers for better accessibility. Updated the 'People' section title in people.qmd and changed 'Code' to 'Software' in software.qmd for consistency. Removed the outdated bio1.jpg image file.

--- 2025-07-20 papers.qmd
@@
 
-# Select Publications
+# Papers
 
@@
 
-A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contextual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886)
-
-Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958)
-
-O. Ronen, A. I. Humayun, R. Balestriero, R. Baraniuk, B. Yu (2024). [ScaLES: Scalable Latent Exploration Score for Pre-Trained Generative Networks](https://arxiv.org/pdf/2406.09657)
-
-S. Hayou, N. Ghosh, B. Yu (2024). [The Impact of Initialization on LoRA Fineuning Dynamics.](https://arxiv.org/pdf/2406.08447)
-
-B. Yu (2024). [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (Harvard Data Science Review)
-
-S. Hayou, N. Ghosh, B. Yu (2024). [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) (Proc. ICML)
-
-C. F. Elliott, J. Duncan, T. M. Tang, M. Behr, K. Kumbier, B. Yu (2024). [Designing a data science simulation with MERITS: a primer.](https://arxiv.org/abs/2403.08971)
-
-Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). [Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986)
-
-N. R. Mallinar, A. Zane, S. Frei, B. Yu (2024). Minimum-Norm Interpolation Under Covariate Shift. (Proc. ICML) [arXiv](https://arxiv.org/pdf/2404.00522)
+A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). Mechanistic Interpretation through Contextual Decomposition in Transformers. ([paper](https://arxiv.org/pdf/2407.00886))
+
+Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis. ([paper](https://arxiv.org/pdf/2406.19958))
+
+O. Ronen, A. I. Humayun, R. Balestriero, R. Baraniuk, B. Yu (2024). ScaLES: Scalable Latent Exploration Score for Pre-Trained Generative Networks. ([paper](https://arxiv.org/pdf/2406.09657))
+
+S. Hayou, N. Ghosh, B. Yu (2024). The Impact of Initialization on LoRA Fineuning Dynamics. ([paper](https://arxiv.org/pdf/2406.08447))
+
+B. Yu (2024). After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI. (Harvard Data Science Review) ([paper](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1))
+
+S. Hayou, N. Ghosh, B. Yu (2024). LoRA+: Efficient Low Rank Adaptation of Large Models. (Proc. ICML) ([paper](https://arxiv.org/abs/2402.12354))
+
+C. F. Elliott, J. Duncan, T. M. Tang, M. Behr, K. Kumbier, B. Yu (2024). Designing a data science simulation with MERITS: a primer. ([paper](https://arxiv.org/abs/2403.08971))
+
+Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). Towards consistent natural-language explanations via explanation-consistent finetuning. ([paper](https://arxiv.org/abs/2401.13986))
+
+N. R. Mallinar, A. Zane, S. Frei, B. Yu (2024). Minimum-Norm Interpolation Under Covariate Shift. (Proc. ICML) ([paper](https://arxiv.org/pdf/2404.00522))
 
@@
 (Proc.
-ICML) [arXiv](https://arxiv.org/abs/2402.13448)
+ICML) ([paper](https://arxiv.org/abs/2402.13448))
 
@@
 
-C. Singh*, A. R. Hsu*, R. Antonello, S. Jain, A. G. Huth, B. Yu, J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
-
-Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262)
+C. Singh*, A. R. Hsu*, R. Antonello, S. Jain, A. G. Huth, B. Yu, J. Gao (2023). Explaining black box text modules in natural language with language models. ([paper](https://arxiv.org/abs/2305.09863))
+
+Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). Tell your model where to attend: post-hoc attention steering for LLMs. ([paper](https://arxiv.org/abs/2311.02262))
 
@@
 Epistasis regulates genetic control of cardiac hypertrophy.
-[medRxiv](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
+([paper](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1)) ([code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))
 
@@
 Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology.
-[bioRxiv](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))
+([paper](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2)) ([code](https://github.com/abbasilab/osNMF))
 
@@
 (2023).
-[A blood-based metabolomic signature predictive of risk for pancreatic cancer](https://pubmed.ncbi.nlm.nih.gov/37729870/).
+A blood-based metabolomic signature predictive of risk for pancreatic cancer.
 Cell Reports Medicine 4(9): 101194.
 doi: 10.1016/j.xcrm.2023.101194.
-(PCS related) ([Editorial](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10518497/))
-
-R. Dwivedi, C. Singh, B. Yu, M. Wainwright (2023). [Revisiting miniumu description length complexity in overparametrized models.](https://jmlr.org/papers/v24/21-1133.html) JMLR, 24(268): 1-59.
-
-K.
-Wu, Y.
-Chen, W.
-Ha, B.
-Yu (2023).
-[Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms.](https://arxiv.org/abs/2309.10301) JMLR (accepted).
-[https://arxiv.org/abs/2309.10301](https://arxiv.org/abs/2309.10301)
-
-N.
-Ghosh, S.
-Frei, W.
-Ha, B.
-Yu (2023).
-The effect of SGD batch size on autoencoder learning: sparsity, sharpness and feature learning.
-[https://arxiv.org/abs/2308.03215](https://arxiv.org/abs/2308.03215)
-
-R.
-Netzorg, J.
-Li, B.
-Yu (2024).
-Improving prototypical part networks with reward reweighting, reselection, and retraining.
-Proc.
-ICML.
-[https://arxiv.org/abs/2307.03887](https://arxiv.org/abs/2307.03887)
-
-A.
-Agarwal, A.
-M.
-Kenny, Y.
-S.
-Tan, T.
-M.
-Tang, B.
-Yu (2023).
-MDI+: a flexible random forest-based feature importance framework.
-[https://arxiv.org/abs/2307.01932](https://arxiv.org/abs/2307.01932) (PCS related)
+(PCS related) ([paper](https://pubmed.ncbi.nlm.nih.gov/37729870/)) ([Editorial](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10518497/))
+
+R. Dwivedi, C. Singh, B. Yu, M. Wainwright (2023). Revisiting miniumu description length complexity in overparametrized models. JMLR, 24(268): 1-59. ([paper](https://jmlr.org/papers/v24/21-1133.html))
+
+K. Wu, Y. Chen, W. Ha, B. Yu (2023). Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms. JMLR (accepted). ([paper](https://arxiv.org/abs/2309.10301))
+
+N. Ghosh, S. Frei, W. Ha, B. Yu (2023). The effect of SGD batch size on autoencoder learning: sparsity, sharpness and feature learning. ([paper](https://arxiv.org/abs/2308.03215))
+
+R. Netzorg, J. Li, B. Yu (2024). Improving prototypical part networks with reward reweighting, reselection, and retraining. Proc. ICML. ([paper](https://arxiv.org/abs/2307.03887))
+
+A. Agarwal, A. M. Kenny, Y. S. Tan, T. M. Tang, B. Yu (2023). MDI+: a flexible random forest-based feature importance framework. (PCS related) ([paper](https://arxiv.org/abs/2307.01932))
 
@@
 ICLR.
-[https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)
-
-C.
-Singh, A.
-R.
-Hsu, R.
-Antonello, S.
-Jain, A.
-G.
-Huth, B.
-Yu and J.
-Gao (2023).
-Explaining black box text modules in natural language with language models.
-[https://arxiv.org/abs/2305.09863](https://arxiv.org/abs/2305.09863)
+([paper](https://arxiv.org/abs/2305.17588))
+
+C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). Explaining black box text modules in natural language with language models. ([paper](https://arxiv.org/abs/2305.09863))
 
@@
 
-D.
-Shen, P.
-Ding, J.
-Sekhon, B.
-Yu (2022).
-Same root different leaves: time series and cross-sectional methods in panel data.
-Econometrica (accepted).
-[https://arxiv.org/abs/2207.14481](https://arxiv.org/abs/2207.14481)
+D. Shen, P. Ding, J. Sekhon, B. Yu (2022). Same root different leaves: time series and cross-sectional methods in panel data. Econometrica (accepted). ([paper](https://arxiv.org/abs/2207.14481))
 
@@
 Zhou (2022).
-[Offline evaluation in RL: soft stability weighting to combine fitted Q-learning and model-based methods.](https://openreview.net/forum?id=R3h3-bt0mq) NeurIPS 3rd Offline Reinforcement Learning Workshop.
+Offline evaluation in RL: soft stability weighting to combine fitted Q-learning and model-based methods.
+NeurIPS 3rd Offline Reinforcement Learning Workshop.
+([paper](https://openreview.net/forum?id=R3h3-bt0mq))
 
@@
 Yu (2022).
-[Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931).
-([imodels 🔎](https://github.com/csinva/imodels) contains code for FIGS)
+Fast interpretable greedy-tree sums (FIGS).
+([paper](https://arxiv.org/abs/2201.11931)) ([code](https://github.com/csinva/imodels))
 
@@
 Yu (2022).
-[Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.](https://arxiv.org/abs/2202.00858) Proc.
-ICML ([imodels 🔎](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS)).
+Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.
+Proc.
+ICML ([paper](https://arxiv.org/abs/2202.00858)) ([code](https://github.com/csinva/imodels)).
 
@@
 Singh (2022).
-[Seven principles for rapid-response data science: lessons learned from covid-19 forecasting](https://projecteuclid.org/journals/statistical-science/volume-37/issue-2/Seven-Principles-for-Rapid-Response-Data-Science--Lessons-Learned/10.1214/22-STS855.full).
+Seven principles for rapid-response data science: lessons learned from covid-19 forecasting.
 Statistical Science, 36(2):266-269.
-
-N. Ghosh, S. Mei, and B. Yu (2022). [The three stages of dynamics in high-dimensional kernel methods.](https://arxiv.org/abs/2111.07167) Proc. ICLR, 2022.
+([paper](https://projecteuclid.org/journals/statistical-science/volume-37/issue-2/Seven-Principles-for-Rapid-Response-Data-Science--Lessons-Learned/10.1214/22-STS855.full))
+
+N. Ghosh, S. Mei, and B. Yu (2022). The three stages of dynamics in high-dimensional kernel methods. Proc. ICLR, 2022. ([paper](https://arxiv.org/abs/2111.07167))
 
@@
 
-Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS.
+Y. Tan, A. Agarwal, and B. Yu (2021). A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds. Proc. AISTATS. ([paper](https://arxiv.org/abs/2110.09626))
 
@@
 (2021).
-[Improving natural language information extraction from cancer pathology reports using transfer learning and zero-shot string similarity.](https://pubmed.ncbi.nlm.nih.gov/34604711/) JAMIA Open.
+Improving natural language information extraction from cancer pathology reports using transfer learning and zero-shot string similarity.
+JAMIA Open.
 2021 Sept.
 30 4(3).
+([paper](https://pubmed.ncbi.nlm.nih.gov/34604711/))
 
@@
 Yu (2021).
-[Interpreting and Improving Deep-Learning Models with Reality Checks](https://arxiv.org/abs/2108.06847).
+Interpreting and Improving Deep-Learning Models with Reality Checks.
 To appear in "xxAI - Beyond Explainable AI" (eds.
 Holzinger et al.).
+([paper](https://arxiv.org/abs/2108.06847))
 
@@
 Yu (2021).
-[Adaptive Wavelet Distillation from Neural Networks through Interpretation.](https://nips.cc/Conferences/2021/ScheduleMultitrack?event=28027) Proc.
+Adaptive Wavelet Distillation from Neural Networks through Interpretation.
+Proc.
 NeurIPS 2021.
-([code](https://github.com/Yu-Group/adaptive-wavelets))
+([paper](https://nips.cc/Conferences/2021/ScheduleMultitrack?event=28027)) ([code](https://github.com/Yu-Group/adaptive-wavelets))
 
@@
 Yu (2022).
-[Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.](https://arxiv.org/abs/2102.11800) PNAS.
-([theory for iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS-related)
+Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.
+PNAS.
+(PCS-related) ([paper](https://arxiv.org/abs/2102.11800)) ([theory for iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115))
 
@@
 122 (2021) 103872.
-[arXiv version](https://arxiv.org/abs/2012.08113)
+([paper](https://arxiv.org/abs/2012.08113))
 
@@
 Yu* (2020).
-[Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
+Learning epistatic polygenic phenotypes with Boolean interactions.
+(PCS inference case study) ([paper](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1)) ([code](https://github.com/merlebehr/epiTree))
 
@@
 Butte* (2020).
-[Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y), Nature Medicine, 26, 1320–1324.
-
-B. Yu (2020). [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/1). Harvard Data Science Review (PCS related)
-
-B. Yu and R. Barter (2020). [Data science process: one culture.](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20) JASA. (PCS related)
+Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist, Nature Medicine, 26, 1320–1324.
+([paper](https://www.nature.com/articles/s41591-020-1041-y))
+
+B. Yu (2020). Stability expanded, in reality. Harvard Data Science Review (PCS related) ([paper](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/1))
+
+B. Yu and R. Barter (2020). Data science process: one culture. JASA. (PCS related) ([paper](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20))
 
@@
 Yu (2020).
-[Stable discovery of interpretable subgroups via calibration in causal studies (staDISC).](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427) International Statistical Review ([code](https://github.com/Yu-Group/stadisc)) (PCS case study for causal inference)
+Stable discovery of interpretable subgroups via calibration in causal studies (staDISC).
+International Statistical Review (PCS case study for causal inference) ([paper](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427)) ([code](https://github.com/Yu-Group/stadisc))
 
@@
 Yu (2020).
-[A stability-driven protocol for drug response interpretable prediction (staDRIP)](https://arxiv.org/abs/2011.06593).
+A stability-driven protocol for drug response interpretable prediction (staDRIP).
 NeurISP workshop on ML4H (Machine learning for Health) Extended Abstract.
+([paper](https://arxiv.org/abs/2011.06593))
 
@@
 Yu (2020).
-[Natural language processing systems for pathology parsing in limited data environments with uncertainty estimation.](https://academic.oup.com/jamiaopen/article/3/3/431/5922788) JAMIA Open.
+Natural language processing systems for pathology parsing in limited data environments with uncertainty estimation.
+JAMIA Open.
+([paper](https://academic.oup.com/jamiaopen/article/3/3/431/5922788))
 
@@
 Yu (2020).
-[Interpretations are Useful: Penalizing Explanations to Align Neural Networks with Prior Knowledge](https://proceedings.icml.cc/static/paper_files/icml/2020/992-Paper.pdf).
+Interpretations are Useful: Penalizing Explanations to Align Neural Networks with Prior Knowledge.
 ICML Proceedings.
-([code](https://github.com/laura-rieger/deep-explanation-penalization))
+([paper](https://proceedings.icml.cc/static/paper_files/icml/2020/992-Paper.pdf)) ([code](https://github.com/laura-rieger/deep-explanation-penalization))
 
@@
 Yu (2020).
-[Transformation Importance with Applications to Cosmology](https://arxiv.org/pdf/2003.01926.pdf) ICLR Workshop paper.
-([code](https://github.com/csinva/transformation-importance))
+Transformation Importance with Applications to Cosmology.
+ICLR Workshop paper.
+([paper](https://arxiv.org/pdf/2003.01926.pdf)) ([code](https://github.com/csinva/transformation-importance))
 
@@
 Yu*.
-(2020) [Curating a COVID-19 data repository and forecasting county-level death counts in the United States.](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1) Harvard Data Science Review ([code](https://github.com/Yu-Group/covid19-severity-prediction)) [7-day prediction results](https://covidseverity.com/) [Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4)
+(2020) Curating a COVID-19 data repository and forecasting county-level death counts in the United States.
+Harvard Data Science Review ([paper](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1)) ([code](https://github.com/Yu-Group/covid19-severity-prediction)) ([7-day prediction results](https://covidseverity.com/)) ([Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4))
 
@@
 Yu and K.
-Kumbier (2020) [Veridical data science](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf) (PCS framework), PNAS.
+Kumbier (2020) Veridical data science (PCS framework), PNAS.
 117 (8), 3920-3929.
-[QnAs with Bin Yu.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf)
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf)) ([QnAs with Bin Yu](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf))
 
@@
 Jordan and B.
-Yu (2020) [Sharp Analysis of Expectation-Maximization for Weakly Identifiable Mixture Models](https://arxiv.org/abs/1902.00194) AISTATS.
-
-R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) [Singularity, Misspecification and the Convergence Rate of EM](https://arxiv.org/abs/1810.00828) Annals of Statistics.
+Yu (2020) Sharp Analysis of Expectation-Maximization for Weakly Identifiable Mixture Models AISTATS.
+([paper](https://arxiv.org/abs/1902.00194))
+
+R.
+Dwivedi, N.
+Ho, K.
+Khamaru, M.
+J.
+Wainwright, M.
+I.
+Jordan and B.
+Yu (2020) Singularity, Misspecification and the Convergence Rate of EM Annals of Statistics.
+([paper](https://arxiv.org/abs/1810.00828))
 
@@
 Wainwright and B.
-Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients,](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, [arXiv](https://arxiv.org/abs/1905.12247)
+Yu (2020) Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients.
+JMLR, ([paper](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf)) ([arXiv](https://arxiv.org/abs/1905.12247))
 
@@
 
-R. Dwivedi, Y. Chen, M. J. Wainwright and B. Yu (2019) [Log-concave Sampling: Metropolis Hastings Algorithms are Fast](http://jmlr.org/papers/v20/19-306.html) JMLR.
-
-D. Rothenhäusler and B. Yu (2019). [Incremental causal effects](https://arxiv.org/abs/1907.13258).
+R. Dwivedi, Y. Chen, M. J. Wainwright and B. Yu (2019) Log-concave Sampling: Metropolis Hastings Algorithms are Fast JMLR. ([paper](http://jmlr.org/papers/v20/19-306.html))
+
+D. Rothenhäusler and B. Yu (2019). Incremental causal effects. ([paper](https://arxiv.org/abs/1907.13258))
 
@@
 Wainwright and B.
-Yu (2020) [Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier](https://ieeexplore.ieee.org/abstract/document/8262876/) Allerton Conference 2017 https://ieeexplore.ieee.org/abstract/document/8262876/
+Yu (2020) Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier.
+Allerton Conference 2017.
+([paper](https://ieeexplore.ieee.org/abstract/document/8262876/))
 
@@
 Abbasi-Asl, and B.
-Yu* (2019) [Definitions, methods, and applications in interpretable machine learning.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) PNAS, 116 (44) 22071-22080.
+Yu* (2019) Definitions, methods, and applications in interpretable machine learning.
+PNAS, 116 (44) 22071-22080.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf))
 
@@
 Yu (2019).
-[Hierarchical interpretations for neural network predictions.](https://openreview.net/pdf?id=SkEqro0ctQ) ICLR.
-([code](https://github.com/csinva/hierarchical-dnn-interpretations))
+Hierarchical interpretations for neural network predictions.
+ICLR.
+([paper](https://openreview.net/pdf?id=SkEqro0ctQ)) ([code](https://github.com/csinva/hierarchical-dnn-interpretations))
 
@@
 Wu and B.
-Yu (2020) [Unique Sharp Local Minimum in l1-minimization Complete Dictionary Learning.](https://jmlr.org/papers/volume21/19-169/19-169.pdf) JMLR.
+Yu (2020) Unique Sharp Local Minimum in l1-minimization Complete Dictionary Learning.
+JMLR.
 21(63), pp.
 1-52.
-Also at https://arxiv.org/abs/1902.08380
+([paper](https://jmlr.org/papers/volume21/19-169/19-169.pdf)) ([arXiv](https://arxiv.org/abs/1902.08380))
 
@@
 Gallant*, and B.
-Yu* (2018) [The DeepTune framework for modeling and characterizing neurons in visual cortex area V4](https://www.biorxiv.org/content/10.1101/465534v1) https://www.biorxiv.org/content/10.1101/465534v1
+Yu* (2018) The DeepTune framework for modeling and characterizing neurons in visual cortex area V4.
+([paper](https://www.biorxiv.org/content/10.1101/465534v1))
 
@@
 Celniker, and B.
-Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
-
-Y. Chen C. Jin, and B. Yu (2018) [Stability and Convergence Trade-off of Iterative Optimization Algorithms.](https://arxiv.org/abs/1804.01619) https://arxiv.org/abs/1804.01619
+Yu* (2018) Refining interaction search through signed iterative Random Forests.
+(an enhanced version of iRF, PCS related) ([paper](https://arxiv.org/abs/1810.07287)) ([iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115))
+
+Y. Chen C. Jin, and B. Yu (2018) Stability and Convergence Trade-off of Iterative Optimization Algorithms. ([paper](https://arxiv.org/abs/1804.01619))
 
@@
 Liu, and B.
-Yu (2018) [Beyond word importance: contextual decomposition to extract interactions from LSTMs.](https://arxiv.org/abs/1801.05453) Proc.
+Yu (2018) Beyond word importance: contextual decomposition to extract interactions from LSTMs.
+Proc.
 ICLR 2018.
-[https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code)](https://github.com/csinva/hierarchical-dnn-interpretations)
-
-R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309) https://arxiv.org/abs/1801.02309.
+([paper](https://arxiv.org/abs/1801.05453)) ([code](https://github.com/csinva/hierarchical-dnn-interpretations))
+
+R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) Log-concave sampling: Metropolis-Hastings algorithms are fast! ([paper](https://arxiv.org/abs/1801.02309))
 
@@
 
-Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) [Fast MCMC sampling algorithms on polytopes](https://arxiv.org/abs/1710.08165) https://arxiv.org/abs/1710.08165.
+Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) Fast MCMC sampling algorithms on polytopes. ([paper](https://arxiv.org/abs/1710.08165))
 
@@
 Yu and K.
-Kumbier (2018) [Artificial Intelligence and Statistics](https://www.stat.berkeley.edu/~binyu/ps/papers2018/AI+Stat18.pdf) Frontiers of Information Technology and Electronic Engineering.
+Kumbier (2018) Artificial Intelligence and Statistics.
+Frontiers of Information Technology and Electronic Engineering.
 19(1), 6-9.
-
-R. Abbasi-Asl and B. Yu (2017) [Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning](https://arxiv.org/abs/1705.07356) https://arxiv.org/abs/1705.07356
-
-R.
-Abbasi-Asl and B.
-Yu (2017) [Interpreting Convolutional Neural Networks Through Compression.](https://arxiv.org/abs/1711.02329) NIPS 2017.
-Symposium on Interpretable Machine Learning.
-(also https://arxiv.org/abs/1711.02329)
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2018/AI+Stat18.pdf))
+
+R. Abbasi-Asl and B. Yu (2017) Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning. ([paper](https://arxiv.org/abs/1705.07356))
+
+R. Abbasi-Asl and B. Yu (2017) Interpreting Convolutional Neural Networks Through Compression. NIPS 2017. Symposium on Interpretable Machine Learning. ([paper](https://arxiv.org/abs/1711.02329))
 
@@
 Bickel, and B.
-Yu* (2019) [Meta-learners for Estimating Heterogeneous Treatment Effects using Machine Learning,](https://www.pnas.org/content/116/10/4156) PNAS.
+Yu* (2019) Meta-learners for Estimating Heterogeneous Treatment Effects using Machine Learning.
+PNAS.
 116 (10) 4156-4165.
-https://arxiv.org/abs/1706.03461.
-[(code](https://github.com/soerenkuenzel/hte))
+([paper](https://www.pnas.org/content/116/10/4156)) ([arXiv](https://arxiv.org/abs/1706.03461)) ([code](https://github.com/soerenkuenzel/hte))
 
@@
 Brown*, and B.
-Yu* (2018) [iterative Random Forests to discover predictive and stable high-order interactions](https://www.stat.berkeley.edu/~binyu/ps/papers2018/iRF+SI18.pdf) PNAS, 115 (8), 1943-1948.
-([code](https://github.com/Yu-Group/iterative-Random-Forest)) (PCS related)
+Yu* (2018) iterative Random Forests to discover predictive and stable high-order interactions PNAS, 115 (8), 1943-1948.
+(PCS related) ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2018/iRF+SI18.pdf)) ([code](https://github.com/Yu-Group/iterative-Random-Forest))
 
@@
 Wainwright, B.
-Yu (2017) [Statistical Guarantees for the EM algorithm: from population to sample-based analysis.](https://www.stat.berkeley.edu/~binyu/ps/papers2017/EM17.pdf) Annals of Statistics, 45(1), 77 - 120.
+Yu (2017) Statistical Guarantees for the EM algorithm: from population to sample-based analysis.
+Annals of Statistics, 45(1), 77 - 120.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2017/EM17.pdf))
 
@@
 Barter and B.
-Yu (2017) [Superheat: An R package for creating beautiful and extendable heatmaps for visualizing complex data](https://www.stat.berkeley.edu/~binyu/ps/papers2017/superheat17.pdf) JCGS (revised).
-https://github.com/rlbarter/superheat
+Yu (2017) Superheat: An R package for creating beautiful and extendable heatmaps for visualizing complex data.
+JCGS (revised).
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2017/superheat17.pdf)) ([code](https://github.com/rlbarter/superheat))
 
@@
 Liu and B.
-Yu (2017) [Comments on: High-dimensional simultaneous inference with the bootstrap by Dezeure et al](https://www.stat.berkeley.edu/~binyu/ps/papers2017/LiuYu-test17.pdf) Test.
+Yu (2017) Comments on: High-dimensional simultaneous inference with the bootstrap by Dezeure et al Test.
 26: 740-750.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2017/LiuYu-test17.pdf))
 
@@
 Carson et al (2016).
-[UC Berkeley Data Science Planning Initiative Faculty Advisory Board (FAB) Report.](https://www.stat.berkeley.edu/~binyu/ps/FAB2016.pdf) [FAB Report Executive Summary](https://www.stat.berkeley.edu/~binyu/ps/FAB-Summary2016.pdf)
+UC Berkeley Data Science Planning Initiative Faculty Advisory Board (FAB) Report.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/FAB2016.pdf)) ([FAB Report Executive Summary](https://www.stat.berkeley.edu/~binyu/ps/FAB-Summary2016.pdf))
 
@@
 Yu (2018).
-[Local identifiability of l1-minimization dictionary learning: a sufficient and almost necessary condition.](https://www.stat.berkeley.edu/~binyu/ps/papers2018/local-iden18.pdf) JMLR.
+Local identifiability of l1-minimization dictionary learning: a sufficient and almost necessary condition.
+JMLR.
 18, 1 - 56.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2018/local-iden18.pdf))
 
@@
 Yu* (2016).
-[Co-clustering directed graphs to discover asymmetries and directional communities.](http://www.pnas.org/content/113/45/12679.full.pdf?with-ds=yes) Proc.
+Co-clustering directed graphs to discover asymmetries and directional communities.
+Proc.
 National Academy of Sciences (PNAS), 113(45), 12679 - 12684.
+([paper](http://www.pnas.org/content/113/45/12679.full.pdf?with-ds=yes))
 
@@
 Yu, Nancy Reid* (2016).
-[Ten simple rules for effective statistical practice.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/Ten-Simple-Rules.pdf) PLoS Comput.
+Ten simple rules for effective statistical practice.
+PLoS Comput.
 Biol., 12(6): e1004961.
-doi:10.1371/journal.pcbi.1004961
+doi:10.1371/journal.pcbi.1004961 ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2016/Ten-Simple-Rules.pdf))
 
@@
 Celniker, Bin Yu*, and Erwin Frise* (2016).
-[Stability-driven nonnegative matrix factorization to interpret spatial gene expression and build local gene networks (with support information).](https://www.stat.berkeley.edu/~binyu/ps/papers2016/staNMF+SI.pdf) PNAS, pp.
+Stability-driven nonnegative matrix factorization to interpret spatial gene expression and build local gene networks (with support information).
+PNAS, pp.
 4290 - 4295.
-([code](https://github.com/yu-group/stanmf)) (PCS related)
+(PCS related) ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2016/staNMF+SI.pdf)) ([code](https://github.com/yu-group/stanmf))
 
@@
 Talwalkar (2016).
-[Supervised neighborhoods for distributed nonparametric regression.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/AISTATS16.pdf) Proc.
+Supervised neighborhoods for distributed nonparametric regression.
+Proc.
 of AISTATS, Barcelona, Spain.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2016/AISTATS16.pdf))
 
@@
 
-B. Yu (2015). [Data wisdom for data science.](http://www.odbms.org/2015/04/data-wisdom-for-data-science/) Operational Database Management Systems (ODBMS.ORG).
+B. Yu (2015). Data wisdom for data science. Operational Database Management Systems (ODBMS.ORG). ([paper](http://www.odbms.org/2015/04/data-wisdom-for-data-science/))
 
@@
 Yu* (2015).
-[Lasso adjustments of treatment effect estimates in randomized experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/lasso-adj+SI16.pdf) PNAS.
+Lasso adjustments of treatment effect estimates in randomized experiments.
+PNAS.
 113, 7383 - 7390.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2016/lasso-adj+SI16.pdf))
 
@@
 Yu (2015).
-[A Statistical Perspective on Algorithmic Leveraging.](https://www.stat.berkeley.edu/~binyu/ps/papers2015/MaMahoneyYu2015.pdf) Journal of Machine Learning Research, 16, (2015), 861-911.
+A Statistical Perspective on Algorithmic Leveraging.
+Journal of Machine Learning Research, 16, (2015), 861-911.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2015/MaMahoneyYu2015.pdf))
 
@@
 Yu (2015).
-[Evaluation of a MISR-based high-resolution aerosol retrieval method using AERONET DRAGON campaign data.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=7047927) IEEE Transactions on Geoscience and Remote Sensing, 53, 4328-4339.
+Evaluation of a MISR-based high-resolution aerosol retrieval method using AERONET DRAGON campaign data.
+IEEE Transactions on Geoscience and Remote Sensing, 53, 4328-4339.
+([paper](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=7047927))
 
@@
 Yu (2014).
-[Let us own data science.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/IMS-pres-address14-yu.pdf) [video](https://www.youtube.com/watch?v=92OjsYQJC1U) [IMS Bulletin](http://bulletin.imstat.org/2014/10/ims-presidential-address-let-us-own-data-science/) Institute of Mathematical Statistics (IMS) Presidental Address, ASC-IMS Joint Conference, Sydney, July, 2014.
-
-G. Schiebinger, M. J. Wainwright and B. Yu (2014). [The geometry of kernelized spectral clustering.](http://arxiv.org/pdf/1404.7552v3.pdf) Annals of Statistics, 43, 819-846.
+Let us own data science.
+Institute of Mathematical Statistics (IMS) Presidental Address, ASC-IMS Joint Conference, Sydney, July, 2014.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2014/IMS-pres-address14-yu.pdf)) ([video](https://www.youtube.com/watch?v=92OjsYQJC1U)) ([IMS Bulletin](http://bulletin.imstat.org/2014/10/ims-presidential-address-let-us-own-data-science/))
+
+G. Schiebinger, M. J. Wainwright and B. Yu (2014). The geometry of kernelized spectral clustering. Annals of Statistics, 43, 819-846. ([paper](http://arxiv.org/pdf/1404.7552v3.pdf))
 
@@
 Clavier (2014).
-[Concise comparative summaries (CCS) of large text corpora with a human experiment.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/CCS14.pdf) Ann.
+Concise comparative summaries (CCS) of large text corpora with a human experiment.
+Ann.
 Applied Statist., 8, 499-529.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2014/CCS14.pdf))
 
@@
 Yu (2014).
-[The shuttle estimator for explainable variance in fMRI experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/BenjaminiY12.pdf) Annals of Applied Statistics, 7, 2007-2033.
+The shuttle estimator for explainable variance in fMRI experiments.
+Annals of Applied Statistics, 7, 2007-2033.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2012/BenjaminiY12.pdf))
 
@@
 Yu (2014).
-[Optimal M-estimation in high-dimensional regression.](http://www.pnas.org/content/early/2013/08/08/1307845110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1456314568.
+Optimal M-estimation in high-dimensional regression.
+Proceedings of National Academy of Sciences, 110, 1456314568.
+([paper](http://www.pnas.org/content/early/2013/08/08/1307845110.full.pdf+html))
 
@@
 Yu (2014).
-[On robust regression with high-dimensional predictors.](http://www.pnas.org/content/early/2013/08/15/1307842110.full.pdf+html) Proceedings of National Academy of Sciences, 110, 1455714562.
+On robust regression with high-dimensional predictors.
+Proceedings of National Academy of Sciences, 110, 1455714562.
+([paper](http://www.pnas.org/content/early/2013/08/15/1307842110.full.pdf+html))
 
@@
 Yu (2014).
-[A Statistical Perspective on Algorithmic Leveraging.](http://arxiv.org/abs/1306.5362) Proc.
+A Statistical Perspective on Algorithmic Leveraging.
+Proc.
 of International Conference on Machine Learning (ICML) (This conference paper contains some of preliminary results of the journal submission Ma et al.
-(2015))
+(2015)) ([paper](http://arxiv.org/abs/1306.5362))
 
@@
 Song (2014).
-[Changepoint Analysis for Efficient Variant Calling.](https://www.stat.berkeley.edu/~binyu/ps/papers2014/Bloniarzetal14.pdf) Proc.
+Changepoint Analysis for Efficient Variant Calling.
+Proc.
 of RECOMB 2014 (to appear).
-
-Tao Shi (2013), [A conversation with Professor Bin Yu](http://www.yufamily.org/src/ShiTao_AnInterviewWithProfessorBinYu.php?xref=YuFamily_YuBin_interview_cn) International Chinese Statistical Association (ICSA) Bulletin, Vol 25, Issue 2, pp 85-98.
-([Selected Parts in Statblogs](http://www.statsblogs.com/2013/07/09/a-conversation-with-professor-bin-yu/))
-
-A. Joseph and B. Yu (2016). [The impact of regularization on spectral clustering.](https://www.stat.berkeley.edu/~binyu/ps/papers2016/reg-spectral16.pdf) Annals of Statistics. 4, 1765 - 1791.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2014/Bloniarzetal14.pdf))
+
+Tao Shi (2013), A conversation with Professor Bin Yu International Chinese Statistical Association (ICSA) Bulletin, Vol 25, Issue 2, pp 85-98.
+([paper](http://www.yufamily.org/src/ShiTao_AnInterviewWithProfessorBinYu.php?xref=YuFamily_YuBin_interview_cn)) ([Selected Parts in Statblogs](http://www.statsblogs.com/2013/07/09/a-conversation-with-professor-bin-yu/))
+
+A. Joseph and B. Yu (2016). The impact of regularization on spectral clustering. Annals of Statistics. 4, 1765 - 1791. ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2016/reg-spectral16.pdf))
 
@@
 Yu (2016).
-[Estimation Stability with Cross Validation (ESCV)](https://www.stat.berkeley.edu/~binyu/ps/papers2016/ESCV16.pdf) Journal of Computational and Graphical Statistics.
+Estimation Stability with Cross Validation (ESCV) Journal of Computational and Graphical Statistics.
 25, 464 - 492.
-(First paper towards PCS)
+(First paper towards PCS) ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2016/ESCV16.pdf))
 
@@
 Celniker (2013).
-[Spatial expression of transcription factors in Drosophila embryonic organ development.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Hammondsetal13.pdf) Genome Biology, 14(12), R140.
+Spatial expression of transcription factors in Drosophila embryonic organ development.
+Genome Biology, 14(12), R140.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Hammondsetal13.pdf))
 
@@
 Yu (2013).
-[Asymptotic properties of Lasso+mLS and Lasso+Ridge in sparse high-dimensional linear regression.](https://www.stat.berkeley.edu/~binyu/ps/LassoOLSBootstrap13.pdf) Electron.
+Asymptotic properties of Lasso+mLS and Lasso+Ridge in sparse high-dimensional linear regression.
+Electron.
 J.
 Statist., 7, 312-3169.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/LassoOLSBootstrap13.pdf))
 
@@
 Yu (2013).
-[Supervised Feature Selection in Graphs with Path Coding Penalties and Network Flows.](http://jmlr.org/papers/v14/mairal13a.html) Journal of Machine Learning Research, 14, 2449-2485.
+Supervised Feature Selection in Graphs with Path Coding Penalties and Network Flows.
+Journal of Machine Learning Research, 14, 2449-2485.
+([paper](http://jmlr.org/papers/v14/mairal13a.html))
 
@@
 Jiang (2013).
-[A Hierarchical Bayesian Approach for Aerosol Retrieval Using MISR Data.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/WangJiangYuJiang2013.pdf) J.
+A Hierarchical Bayesian Approach for Aerosol Retrieval Using MISR Data.
+J.
 American Statistical Association, 108, 483-493.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2013/WangJiangYuJiang2013.pdf))
 
@@
 Yu (2013).
-[Reversible MCMC on Markov equivalence classes of sparse directed acyclic graphs.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/rev-MCMC13.pdf) Annals of Statistics, 41(4), 1742-1779.
+Reversible MCMC on Markov equivalence classes of sparse directed acyclic graphs.
+Annals of Statistics, 41(4), 1742-1779.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2013/rev-MCMC13.pdf))
 
@@
 Yu (2013).
-[Stability.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Yu13.pdf) Bernoulli, 19 (4), 1484-1500.
-(Invited paper for the Special Issue commemorating the 300th anniversary of the publication of Jakob Bernoullis Ars Conjectandi in 1712) (Begining of PCS)
+Stability.
+Bernoulli, 19 (4), 1484-1500.
+(Invited paper for the Special Issue commemorating the 300th anniversary of the publication of Jakob Bernoullis Ars Conjectandi in 1712) (Begining of PCS) ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2013/Yu13.pdf))
 
@@
 Yu (2013).
-[Geometry of faithfulness assumption in causal inference.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/faithfulness13.pdf) Annals of Statistics, 41, 436-463.
+Geometry of faithfulness assumption in causal inference.
+Annals of Statistics, 41, 436-463.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2013/faithfulness13.pdf))
 
@@
 Yu (2013).
-[Adjusting Treatment Effect Estimates by Post-Stratification in Randomized Experiments.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/post-stratification13.pdf) Journal of Royal Statistical Society, Series B, 75 (part 2), 369-396.
-
-J. Jia, K. Rohe and B. Yu (2013) [The Lasso under Poisson-like Heteroscadecity.](https://www.stat.berkeley.edu/~binyu/ps/papers2013/lasso-poisson13.pdf) Statistica Sinica, 23, 99-118.
+Adjusting Treatment Effect Estimates by Post-Stratification in Randomized Experiments.
+Journal of Royal Statistical Society, Series B, 75 (part 2), 369-396.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2013/post-stratification13.pdf))
+
+J. Jia, K. Rohe and B. Yu (2013) The Lasso under Poisson-like Heteroscadecity. Statistica Sinica, 23, 99-118. ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2013/lasso-poisson13.pdf))
 
@@
 Wainwrigt, and B.
-Yu (2012) [A unified framework for high-dimensional analysis of M-estimators with decomposable regularizers.](https://www.stat.berkeley.edu/~binyu/ps/unified-797.pdf) Statistical Science, 27, 538-557.
+Yu (2012) A unified framework for high-dimensional analysis of M-estimators with decomposable regularizers.
+Statistical Science, 27, 538-557.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/unified-797.pdf))
 
@@
 Wainwrigt, and B.
-Yu (2012) [Minimax-optimal rates for sparse additive models over kernel classes via convex programming.](https://www.stat.berkeley.edu/~binyu/ps/papers2012/RaskuttiWY12.pdf) J.
+Yu (2012) Minimax-optimal rates for sparse additive models over kernel classes via convex programming.
+J.
 Machine Learning Research, 13, 389-427.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2012/RaskuttiWY12.pdf))
 
@@
 Yu (2012).
-[Complexity analysis of the Lasso regularization path.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/MairalY12.pdf) Proc.
+Complexity analysis of the Lasso regularization path.
+Proc.
 of International Conference on Machine Learning (ICML).
+([paper](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/MairalY12.pdf))
 
@@
 Clothiaux, and Bin Yu (2012).
-[Multiple-kernel learning-based unmixing algorithm for estimation of cloud fractions with MODIS and CLOUDSAT data.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GuWSLCY12.pdf) Proc.
+Multiple-kernel learning-based unmixing algorithm for estimation of cloud fractions with MODIS and CLOUDSAT data.
+Proc.
 of IEEE International Geoscience and Remote Sensing Symposium (IGRSS).
+([paper](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GuWSLCY12.pdf))
 
@@
 Gallant (2011).
-[Reconstructing visual experiences from brain activity evoked by natural movies.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/NishimotoVNBYG11.pdf) Current Biology, 21(19), 1641-1646.
-[related videos](https://sites.google.com/site/gallantlabucb/publications/nishimoto-et-al-2011)
+Reconstructing visual experiences from brain activity evoked by natural movies.
+Current Biology, 21(19), 1641-1646.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2011/NishimotoVNBYG11.pdf)) ([related videos](https://sites.google.com/site/gallantlabucb/publications/nishimoto-et-al-2011))
 
@@
 Yu (2011).
-[High-dimensional covariance estimation by minimizing l1-penalized log-determinant divergence.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RavikumarWRY11.pdf) Electronic Journal of Statistics, 5, 935-980.
+High-dimensional covariance estimation by minimizing l1-penalized log-determinant divergence.
+Electronic Journal of Statistics, 5, 935-980.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RavikumarWRY11.pdf))
 
@@
 Yu (2011).
-[Minimax rates of estimation for high-dimensional linear regression over lq-balls.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RaskuttiWainwrightYu2011.pdf) IEEE Trans.
+Minimax rates of estimation for high-dimensional linear regression over lq-balls.
+IEEE Trans.
 Inform.
 Th., 57(10), 6976-6994.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RaskuttiWainwrightYu2011.pdf))
 
@@
 Yu (2011).
-[Spectral clustering and the high-dimensional Stochastic Block Model.](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RoheCY11.pdf) Annals of Statistics, 39 (4), 1878-1915
+Spectral clustering and the high-dimensional Stochastic Block Model.
+Annals of Statistics, 39 (4), 1878-1915 ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2011/RoheCY11.pdf))
 
@@
 Yu* (2011).
-[Encoding and decoding V1 fMRI responses to natural images with sparse nonparametric models.](http://arxiv.org/pdf/1104.2805.pdf) Annals of Applied Statistics, 5, 1150-1182.
-(*First senior author as last author in biology tradition)
+Encoding and decoding V1 fMRI responses to natural images with sparse nonparametric models.
+Annals of Applied Statistics, 5, 1150-1182.
+(*First senior author as last author in biology tradition) ([paper](http://arxiv.org/pdf/1104.2805.pdf))
 
@@
 Yu (2011).
-[Combined Features and Kernel Design for Robust Phoneme Classification Using Support Vector Machines.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=5618550) IEEE Trans.
+Combined Features and Kernel Design for Robust Phoneme Classification Using Support Vector Machines.
+IEEE Trans.
 Audio, Speech and Language Processing (to appear).
 64.
+([paper](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=5618550))
 
@@
 Jia, B.
-Yu, El Ghaoui (2011) [SBA-term: Sparse Bilingual Association for terms.](http://www.eecs.berkeley.edu/~elghaoui/Pubs/icsc2011.pdf) Proc.
+Yu, El Ghaoui (2011) SBA-term: Sparse Bilingual Association for terms.
+Proc.
 International Conference on Semantic Computing.
+([paper](http://www.eecs.berkeley.edu/~elghaoui/Pubs/icsc2011.pdf))
 
@@
 Yu (2011).
-[Asymptotics and Coding Theory: One of the n - 1 Dimensions of Terry.](http://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/Yu11.pdf) In Selected Works of Terry Speed (ed.
+Asymptotics and Coding Theory: One of the n - 1 Dimensions of Terry.
+In Selected Works of Terry Speed (ed.
 S.
@@
 33-36, Springer.
+([paper](http://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/Yu11.pdf))
 
@@
 
-B. Yu (2010). [Remembering Leo.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/Yu10.pdf) Annals of Applied Statistics, 4(4), 1657-1659.
+B. Yu (2010). Remembering Leo. Annals of Applied Statistics, 4(4), 1657-1659. ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2010/Yu10.pdf))
 
@@
 Yu (2010).
-[Comment on "Envelope models for parsimonious and efficient multivariate linear regression" by R.
+Comment on "Envelope models for parsimonious and efficient multivariate linear regression" by R.
 D.
@@
 Li, and F.
-Chiaromonte.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaBLRY10.pdf) Statistica Sinica, 20, 961-967.
+Chiaromonte.
+Statistica Sinica, 20, 961-967.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaBLRY10.pdf))
 
@@
 Wainwrigt, and B.
-Yu (2010) [Restricted Eigenvalue Properties for Correlated Gaussian Designs.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/RaskuttiWY10.pdf) Journal of Machine Learning Research, 11, 2241-2259.
-
-J. Jia and B. Yu (2010). [On model selection consistency of elastic net when p >>n.](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaY10.pdf) Statistica Sinica, 10, 595-611.
-
-P. Buhlmann and B. Yu (2010). [Boosting.](http://onlinelibrary.wiley.com/doi/10.1002/wics.55/abstract) Wiley Interdisciplinary Reviews: Computational Statistics, 2, 69-74.
+Yu (2010) Restricted Eigenvalue Properties for Correlated Gaussian Designs.
+Journal of Machine Learning Research, 11, 2241-2259.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2010/RaskuttiWY10.pdf))
+
+J. Jia and B. Yu (2010). On model selection consistency of elastic net when p >>n. Statistica Sinica, 10, 595-611. ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2010/JiaY10.pdf))
+
+P. Buhlmann and B. Yu (2010). Boosting. Wiley Interdisciplinary Reviews: Computational Statistics, 2, 69-74. ([paper](http://onlinelibrary.wiley.com/doi/10.1002/wics.55/abstract))
 
@@
 Naik (2010).
-[Predicting Execution Time of Computer Programs Using Sparse Polynomial Regression.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HuangJYCMN10.pdf) Proc.
+Predicting Execution Time of Computer Programs Using Sparse Polynomial Regression.
+Proc.
 NIPS 2010.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HuangJYCMN10.pdf))
 
@@
 Yu (2010).
-[Multi-task Sparse Discriminant Analysis (MtSDA) with Overlapping Categories.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HanWJZY10.pdf) Proc.
+Multi-task Sparse Discriminant Analysis (MtSDA) with Overlapping Categories.
+Proc.
 of The 24th AAAI Conference on Artificial Intelligence, July 11-15, Atlanta, GA.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/HanWJZY10.pdf))
 
@@
 Clavier (2010).
-[Discovering Word Associations in News Media via Feature Selection and Sparse Classification.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GawaltJMGYC10.pdf) Proc.
+Discovering Word Associations in News Media via Feature Selection and Sparse Classification.
+Proc.
 11th ACM SIGMM International Confernece on Multimedia Information Retrieval (MIR).
+([paper](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/GawaltJMGYC10.pdf))
 
@@
 Braverman, E.
-Clothiaux (2009) [Maximum Likelihood Estimation of Cloud Height from Multi-Angle Satellite Imagery.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/AnderesYJMGBC09.pdf) Annals of Applied Statistics, 3, 902-921
+Clothiaux (2009) Maximum Likelihood Estimation of Cloud Height from Multi-Angle Satellite Imagery.
+Annals of Applied Statistics, 3, 902-921 ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2009/AnderesYJMGBC09.pdf))
 
@@
 Belkin, and B.
-Yu, (2009) [Data Spectroscopy: Eigenspace of Convolution Operator and Clustering](https://www.stat.berkeley.edu/~binyu/ps/shi.aos09.pdf) Annals of Statistics, 37 (6B), 3960-3984.
-
-Vincent Q. Vu, Bin Yu, Robert E. Kass (2009) [Information In The Non-Stationary Case](https://www.stat.berkeley.edu/~binyu/ps/papers2009/VuYK09.pdf) Neural computation 21, 688-703.
+Yu, (2009) Data Spectroscopy: Eigenspace of Convolution Operator and Clustering Annals of Statistics, 37 (6B), 3960-3984.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/shi.aos09.pdf))
+
+Vincent Q. Vu, Bin Yu, Robert E. Kass (2009) Information In The Non-Stationary Case Neural computation 21, 688-703. ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2009/VuYK09.pdf))
 
@@
 Yu (2009).
-[Lasso-type recovery of sparse representations for high-dimensional data.](https://www.stat.berkeley.edu/~binyu/ps/papers2009/MeinshausenY09.pdf) Annals of Statistics 37, 246-270.
+Lasso-type recovery of sparse representations for high-dimensional data.
+Annals of Statistics 37, 246-270.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2009/MeinshausenY09.pdf))
 
@@
 Yu (2009).
-[The composite absolute penalties family for grouped and hierarchical variable selection](https://www.stat.berkeley.edu/~binyu/ps/papers2009/ZhaoRY09.pdf) Annals of Statistics 37, 3468-3497.
+The composite absolute penalties family for grouped and hierarchical variable selection Annals of Statistics 37, 3468-3497.
 (An earlier version 'appeared as Grouped and hierarchical model selection through composite absolute penalties' by P.
@@
 Yu, Department of Statistics, UC Berkeley, Tech.
-Rep 703.)
+Rep 703.) ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2009/ZhaoRY09.pdf))
 
@@
 Yu (2009).
-[A unified framework for high-dimensional analysis of $M$-estimators with decomposable regularizers](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/NegahbanRWY09.pdf) Proc.
+A unified framework for high-dimensional analysis of $M$-estimators with decomposable regularizers Proc.
 NIPS, 2009.
@@
 2012).
+([paper](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/NegahbanRWY09.pdf))
 
@@
 Wainwright, B.
-Yu (2009) [High-dimensional regression under lq-ball sparsity: Optimal rates of convergence.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09b.pdf) Proc.
+Yu (2009) High-dimensional regression under lq-ball sparsity: Optimal rates of convergence.
+Proc.
 of Allerton Conference on Communication, Control, and Computing.
@@
 2011).
+([paper](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09b.pdf))
 
@@
 Wainwrigt, and B.
-Yu (2009) [Lower bounds on minimax rates for nonparametric regression with additive sparsity and smoothness.](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09a.pdf) Proc.
+Yu (2009) Lower bounds on minimax rates for nonparametric regression with additive sparsity and smoothness.
+Proc.
 NIPS, 2009.
@@
 2011).
+([paper](https://www.stat.berkeley.edu/~binyu/ps/Conferencepapers/RaskuttiWY09a.pdf))
 
@@
 Braverman (2008).
-[Daytime Arctic Cloud Detection based on Multi-angle Satellite Data with Case Studies.](https://www.stat.berkeley.edu/~binyu/ps/jasa_resub.pdf) Journal of American Statistical Association.
+Daytime Arctic Cloud Detection based on Multi-angle Satellite Data with Case Studies.
+Journal of American Statistical Association.
 103( 482), 584-593.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/jasa_resub.pdf))
 
@@
 Wyner)".
-[(paper with discussion) ](https://www.stat.berkeley.edu/~binyu/ps/Mease08a_with_discussion.pdf) Journal of Machine Learning Research 9, 187-194.
+Journal of Machine Learning Research 9, 187-194.
+([paper with discussion](https://www.stat.berkeley.edu/~binyu/ps/Mease08a_with_discussion.pdf))
 
@@
 Gallant (2008).
-[Nonparametric sparse hiearchical models describe V1 fMRI responses to natural images](https://www.stat.berkeley.edu/~binyu/ps/rocha.pseudo.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
+Nonparametric sparse hiearchical models describe V1 fMRI responses to natural images In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
 (This conference paper contains some preliminary results of journal paper Vu et al.
@@
 (2011).
-It does not contain decoding results.)
+It does not contain decoding results.) ([paper](https://www.stat.berkeley.edu/~binyu/ps/rocha.pseudo.pdf))
 
@@
 Wainwright, B.
-Yu (2008) [Model selection in Gaussian graphical models: high-dimensional consistency of l1-regularized MLE.](https://www.stat.berkeley.edu/~binyu/ps/covsel.nips08.pdf) In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
-
-T. Shi, M. Belkin, and B. Yu (2008). [Data spectroscopy: learning mixture models using eigenspaces of convolution operators.](https://www.stat.berkeley.edu/~binyu/ps/ICML08.pdf) Proc. of ICML 2008.
+Yu (2008) Model selection in Gaussian graphical models: high-dimensional consistency of l1-regularized MLE.
+In Adavances in Neural Information Processing Systems (NIPS) 21, (2008).
+([paper](https://www.stat.berkeley.edu/~binyu/ps/covsel.nips08.pdf))
+
+T.
+Shi, M.
+Belkin, and B.
+Yu (2008).
+Data spectroscopy: learning mixture models using eigenspaces of convolution operators.
+Proc.
+of ICML 2008.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/ICML08.pdf))
 
@@
 Yu (2008).
-[Towards Robust Phoneme Classification Augmentation of PLP Models with Acoustic Waveforms.](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=7080758) Proceedings of EUSIPCO.
+Towards Robust Phoneme Classification Augmentation of PLP Models with Acoustic Waveforms.
+Proceedings of EUSIPCO.
+([paper](http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=7080758))
 
@@
 Yu (2008).
-[Combined PLP-Acoustic Waveform Classification for Robust Phoneme Recognition using Support Vector Machines.](http://www.eurasip.org/Proceedings/Eusipco/Eusipco2008/papers/1569105546.pdf) Proceedings of EUSIPCO.
+Combined PLP-Acoustic Waveform Classification for Robust Phoneme Recognition using Support Vector Machines.
+Proceedings of EUSIPCO.
+([paper](http://www.eurasip.org/Proceedings/Eusipco/Eusipco2008/papers/1569105546.pdf))
 
@@
 Yu (2007).
-[A tale of three cousins: Lasso, L2Boosting, and Danzig](https://www.stat.berkeley.edu/~binyu/ps/aos.dis07.pdf) Annals of Statistics (invited discussion on Candes and Tao's Danzig Selector paper)
-
-V. Vu, B. Yu, and R. Kass (2007). [Coverage Adjusted Entropy Estimation.](https://www.stat.berkeley.edu/~binyu/ps/entropy.sub.pdf) Statistics and Medicine, 26(21), 4039-4060.
+A tale of three cousins: Lasso, L2Boosting, and Danzig Annals of Statistics (invited discussion on Candes and Tao's Danzig Selector paper) ([paper](https://www.stat.berkeley.edu/~binyu/ps/aos.dis07.pdf))
+
+V. Vu, B. Yu, and R. Kass (2007). Coverage Adjusted Entropy Estimation. Statistics and Medicine, 26(21), 4039-4060. ([paper](https://www.stat.berkeley.edu/~binyu/ps/entropy.sub.pdf))
 
@@
 Yu (2007).
-[Embracing Statistical Challenges in the Information Technology Age](https://www.stat.berkeley.edu/~binyu/ps/embracing.pdf) Technometrics (special issue on statistics and information technologies).
+Embracing Statistical Challenges in the Information Technology Age.
+Technometrics (special issue on statistics and information technologies).
 vol.
 49 (3), 237-248.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/embracing.pdf))
 
@@
 Jiang (2007).
-[Comparison of MISR aerosol optical thickness with AERONET measurements in Beijing metropolitan area.](https://www.stat.berkeley.edu/~binyu/ps/xin.pdf) Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol.
+Comparison of MISR aerosol optical thickness with AERONET measurements in Beijing metropolitan area.
+Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol.
 107, pp.
 45-53.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/xin.pdf))
 
@@
 Groff (2007).
-[Detection of Daytime Arctic Clouds using MISR and MODIS Data.](https://www.stat.berkeley.edu/~binyu/ps/misr-modis.pdf) Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol.
+Detection of Daytime Arctic Clouds using MISR and MODIS Data.
+Remote Sensing of Environment (Special Issue on Multi-angle Imaging SpectroRadiometer), vol.
 107, pp.
 172-184.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/misr-modis.pdf))
 
@@
 
-Peng Zhao and Bin Yu (2006). [On Model Selection Consistency of Lasso.](https://www.stat.berkeley.edu/~binyu/ps/LassoConsi.pdf) J. Machine Learning Research, 7 (nov), 2541-2567.
-
-B. Yu (2006). [Comments on: Monitoring networked applications with incremental quantile estimation by Chambers et al.](http://arxiv.org/pdf/0708.0338.pdf) Statist. Sci., 21, 483-485.
-
-B. Yu (2006). [Comments on: Regularization in Statistics, by P. J. Bickel and B. Li.](https://www.stat.berkeley.edu/~binyu/ps/test06.pdf) Test, vol. 15 (2), pages 314-316.
+Peng Zhao and Bin Yu (2006). On Model Selection Consistency of Lasso. J. Machine Learning Research, 7 (nov), 2541-2567. ([paper](https://www.stat.berkeley.edu/~binyu/ps/LassoConsi.pdf))
+
+B. Yu (2006). Comments on: Monitoring networked applications with incremental quantile estimation by Chambers et al. Statist. Sci., 21, 483-485. ([paper](http://arxiv.org/pdf/0708.0338.pdf))
+
+B. Yu (2006). Comments on: Regularization in Statistics, by P. J. Bickel and B. Li. Test, vol. 15 (2), pages 314-316. ([paper](https://www.stat.berkeley.edu/~binyu/ps/test06.pdf))
 
@@
 Yu (2006).
-[Sparse Boosing](https://www.stat.berkeley.edu/~binyu/ps/rev.pdf) Journal of Machine Learning Research ( 7 (June), 1001-1024).
+Sparse Boosing Journal of Machine Learning Research ( 7 (June), 1001-1024).
 This is a shortened and more focused version of Buhlmann and Yu "Boosting, Model Selection, Lasso and Nonnegative Garotte" given below.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/rev.pdf))
 
@@
 Yu (2006).
-[Approximation Lasso Methods for Language Modeling.](https://www.stat.berkeley.edu/~binyu/ps/acl.06.pdf) Proceedings of the 21st International Conference on Computational Linguistics and 44th Annual Meeting of the ACL, pp.
+Approximation Lasso Methods for Language Modeling.
+Proceedings of the 21st International Conference on Computational Linguistics and 44th Annual Meeting of the ACL, pp.
 225-232, Sydney.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/acl.06.pdf))
 
@@
 
-T. Shi and B. Yu (2005). [Binning in Gaussian Kernel Regularization.](https://www.stat.berkeley.edu/~binyu/ps/binning.final.pdf) Statistica Sinica (special issue on machine learning), 16, 541-567.
+T.
+Shi and B.
+Yu (2005).
+Binning in Gaussian Kernel Regularization.
+Statistica Sinica (special issue on machine learning), 16, 541-567.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/binning.final.pdf))
 
@@
 Yu (2005).
-[A fast lightweight approach to origin-destination IP traffic estimation using partial measurements.](https://www.stat.berkeley.edu/~binyu/ps/pamtram.final.pdf) Tech Report 687, Statistics Department, UCB (accepted for Special Issue of IEEE-IT and ACM Networks on data networks, Jan.
-2006)
-
-Tong Zhang and B. Yu (2005). [Boosting with early stopping: convergence and consistency.](https://www.stat.berkeley.edu/~binyu/ps/zhang.final.ps) The Annals of Statistics. Vol. 33, 1538-1579.
-
-Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2005) [Network tomography: recent developments.](http://nowak.ece.wisc.edu/StatSci04.pdf) Statistical Science, 19, 499-517.
+A fast lightweight approach to origin-destination IP traffic estimation using partial measurements.
+Tech Report 687, Statistics Department, UCB (accepted for Special Issue of IEEE-IT and ACM Networks on data networks, Jan.
+2006) ([paper](https://www.stat.berkeley.edu/~binyu/ps/pamtram.final.pdf))
+
+Tong Zhang and B. Yu (2005). Boosting with early stopping: convergence and consistency. The Annals of Statistics. Vol. 33, 1538-1579. ([paper](https://www.stat.berkeley.edu/~binyu/ps/zhang.final.ps))
+
+Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2005) Network tomography: recent developments. Statistical Science, 19, 499-517. ([paper](http://nowak.ece.wisc.edu/StatSci04.pdf))
 
@@
 Yu (2005).
-[Efficient algorithms for discrete universal denoising for channels with memeory.](https://www.stat.berkeley.edu/~binyu/ps/isit05.pdf) Proceedings of International Symposium on Information Theory, Australia.
+Efficient algorithms for discrete universal denoising for channels with memeory.
+Proceedings of International Symposium on Information Theory, Australia.
 (Also as Tech.
@@
 ISIT, Sept.
-2005))
+2005)) ([paper](https://www.stat.berkeley.edu/~binyu/ps/isit05.pdf))
 
@@
 Yu (2004).
-[Stagewise Lasso (old title: Boosted Lasso)](https://www.stat.berkeley.edu/~binyu/ps/StagewiseLasso.pdf) Journal of Machine Learning Research, 8, 2701-2726.
+Stagewise Lasso (old title: Boosted Lasso) Journal of Machine Learning Research, 8, 2701-2726.
 (An earlier version appeared as Tech.
-Report #678, Statistics Department, UC Berkeley (December, 2004; revised in April, 2005)
+Report #678, Statistics Department, UC Berkeley (December, 2004; revised in April, 2005) ([paper](https://www.stat.berkeley.edu/~binyu/ps/StagewiseLasso.pdf))
 
@@
 Diner et al (2004).
-[PARAGON: A Systematic, Integrated Approach to Aerosol Observation and Modeling.](https://www.stat.berkeley.edu/~binyu/ps/paragon.pdf) American Meterological Society, Oct., 1491-1501.
-
-P. Buhlmann and B. Yu (2004). [Discussion on three boosting papers by Jiang, Lugosi and Vayatis, and Zhang](https://www.stat.berkeley.edu/~binyu/ps/disc2.ps) Annals of Statistics. 32 (1): 96-101.
+PARAGON: A Systematic, Integrated Approach to Aerosol Observation and Modeling.
+American Meterological Society, Oct., 1491-1501.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/paragon.pdf))
+
+P.
+Buhlmann and B.
+Yu (2004).
+Discussion on three boosting papers by Jiang, Lugosi and Vayatis, and Zhang Annals of Statistics.
+32 (1): 96-101.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/disc2.ps))
 
@@
 Yu (2004).
-[Compressing genomic and proteomic array images for statistical analyses.](https://www.stat.berkeley.edu/~binyu/ps/sig.chapter.ps) Invited chapter in a book on Genomic signal processing and statistics, edited by E.
+Compressing genomic and proteomic array images for statistical analyses.
+Invited chapter in a book on Genomic signal processing and statistics, edited by E.
 R.
@@
 341 - 366.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/sig.chapter.ps))
 
@@
 Taft (2004).
-[Maximum entropy models: convergence rates and application in dynamic system monitoring.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=1365207&sortType%3Dasc_p_Sequence%26filter%3DAND%28p_IS_Number%3A29909%29%26pageNumber%3D4%26rowsPerPage%3D50) International Symposium on Information Theory, Chicago.
+Maximum entropy models: convergence rates and application in dynamic system monitoring.
+International Symposium on Information Theory, Chicago.
+([paper](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=1365207&sortType%3Dasc_p_Sequence%26filter%3DAND%28p_IS_Number%3A29909%29%26pageNumber%3D4%26rowsPerPage%3D50))
 
@@
 
-R. Castro, M. Coates, G. Liang, R. Nowak, and B. Yu (2003). [Internet Tomography: Recent Developments](https://www.stat.berkeley.edu/~binyu/ps/cny.pdf) Statistical Science. Vol. 19(3), 499-517.
+R.
+Castro, M.
+Coates, G.
+Liang, R.
+Nowak, and B.
+Yu (2003).
+Internet Tomography: Recent Developments Statistical Science.
+Vol.
+19(3), 499-517.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/cny.pdf))
 
@@
 Yu (2003).
-[Maximum Pseudo Likelihood Estimation in Network Tomography.](https://www.stat.berkeley.edu/~binyu/ps/pseudo-ieee.ps) IEEE Trans.
+Maximum Pseudo Likelihood Estimation in Network Tomography.
+IEEE Trans.
 on Signal Processing (Special Issue on Data Networks).
-51(8), 2043-2053
+51(8), 2043-2053 ([paper](https://www.stat.berkeley.edu/~binyu/ps/pseudo-ieee.ps))
 
 Rebecka Jornsten and Bin Yu (2003).
-[Simultaneous Gene Clustering and Subset Selection for Classification via MDL.](https://www.stat.berkeley.edu/~binyu/ps/bioinformatics.ps) Bioinformatics.
+Simultaneous Gene Clustering and Subset Selection for Classification via MDL.
+Bioinformatics.
 19(9): 1100-1109.
-
-Peter Buhlmann and Bin Yu (2003). [Boosting with the L2 Loss: Regression and Classification.](https://www.stat.berkeley.edu/~binyu/ps/boostingl2.ps) J. Amer. Statist. Assoc. 98, 324-340.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/bioinformatics.ps))
+
+Peter Buhlmann and Bin Yu (2003). Boosting with the L2 Loss: Regression and Classification. J. Amer. Statist. Assoc. 98, 324-340. ([paper](https://www.stat.berkeley.edu/~binyu/ps/boostingl2.ps))
 
@@
 Ramchandran (2003).
-[Microarray image compression: SLOCO and the effects of information loss.](https://www.stat.berkeley.edu/~binyu/ps/spj.ps) Signal Processing Journal (Special Issue on Genomic Signal Processing).
+Microarray image compression: SLOCO and the effects of information loss.
+Signal Processing Journal (Special Issue on Genomic Signal Processing).
 83, 859-869.
-
-G. Liang and B. Yu (2003). [Pseudo Likelihood Estimation in Network Tomography.](http://infocom2003.ieee-infocom.org/papers/51_03.PDF) Proceedings of of Infocom, San Francisco.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/spj.ps))
+
+G. Liang and B. Yu (2003). Pseudo Likelihood Estimation in Network Tomography. Proceedings of of Infocom, San Francisco. ([paper](http://infocom2003.ieee-infocom.org/papers/51_03.PDF))
 
@@
 
-Peter Buhlmann and Bin Yu (2002). [Analyzing Bagging.](https://www.stat.berkeley.edu/~binyu/ps/bagging.ps) Annals of Statistics vol. 30, 927-961.
+Peter Buhlmann and Bin Yu (2002). Analyzing Bagging. Annals of Statistics vol. 30, 927-961. ([paper](https://www.stat.berkeley.edu/~binyu/ps/bagging.ps))
 
@@
 Mark Hansen and Bin Yu (2002).
-[Minimum Description Length Model Selection Criteria for Generalized Linear Models.](https://www.stat.berkeley.edu/~binyu/ps/mdl_glm.ps){\em Science and Statistics: Festschrift for Terry Speed}, IMS Lecture Notes -- Monograph Series, Vol.
+Minimum Description Length Model Selection Criteria for Generalized Linear Models.{\em Science and Statistics: Festschrift for Terry Speed}, IMS Lecture Notes -- Monograph Series, Vol.
 40.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/mdl_glm.ps))
 
 Rebecka Jornsten, and Bin Yu (2002).
-[Multiterminal Estimation: Extensions and a Geometric interpretation.](https://www.stat.berkeley.edu/~binyu/ps/isit02.ps) Proceedings of International Symposium on Information Theory (ISIT), June, 2002.
+Multiterminal Estimation: Extensions and a Geometric interpretation.
+Proceedings of International Symposium on Information Theory (ISIT), June, 2002.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/isit02.ps))
 
 Gerald Schuller, Bin Yu, Dawei Huang, and Bern Edler (2002).
-[Perceptual Audio Coding using Pre- and Poster- Filters and Lossless Compression.](https://www.stat.berkeley.edu/~binyu/ps/coding.ps) IEEE Trans.
+Perceptual Audio Coding using Pre- and Poster- Filters and Lossless Compression.
+IEEE Trans.
 Speech and Audio Processing.
 Vol.
-10 (6), 379-390
-
-Mark Coates, Alfred Hero, Robert Nowak, and Bin Yu (2002). [Internet Tomography.](https://www.stat.berkeley.edu/~binyu/ps/spmag.ps) Signal Processing Magazine. vol. 19, No. 3 (May issue), 47-65.
+10 (6), 379-390 ([paper](https://www.stat.berkeley.edu/~binyu/ps/coding.ps))
+
+Mark Coates, Alfred Hero, Robert Nowak, and Bin Yu (2002).
+Internet Tomography.
+Signal Processing Magazine.
+vol.
+19, No.
+3 (May issue), 47-65.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/spmag.ps))
 
@@
 
-M. Hansen and B. Yu (2001). [Model selection and the principle of Minimum Description Length.](https://www.stat.berkeley.edu/~binyu/ps/mdl.ps) Journal of American Statistical Association. 96, 746-774.
+M.
+Hansen and B.
+Yu (2001).
+Model selection and the principle of Minimum Description Length.
+Journal of American Statistical Association.
+96, 746-774.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/mdl.ps))
 
@@
 Jin Cao, Drew Davis, Scott Vander Wiel and Bin Yu (2000).
-[[ PDF ](https://www.stat.berkeley.edu/~binyu/Site/ps/net.pdf)| [Time-varying network tomography: router link data.](https://www.stat.berkeley.edu/~binyu/ps/net.ps) J.
+Time-varying network tomography: router link data.
+J.
 Amer.
@@
 95, 1063-1075.
+([PDF](https://www.stat.berkeley.edu/~binyu/Site/ps/net.pdf)) ([paper](https://www.stat.berkeley.edu/~binyu/ps/net.ps))
 
 Peter Buhlmann and Bin Yu (2000).
-[Discussion.
+Discussion.
 Additive logistic regression: a statistical view of boosting, by Friedman, J., Hastie, T.
-and Tibshirani, R.](https://www.stat.berkeley.edu/~binyu/ps/disc.ps) Annals of Statistics.
+and Tibshirani, R.
+Annals of Statistics.
 Vol.
-28, 377-386
+28, 377-386 ([paper](https://www.stat.berkeley.edu/~binyu/ps/disc.ps))
 
 Mark Hansen and Bin Yu (2000).
-[Wavelet thresholding via MDL for natural images.](https://www.stat.berkeley.edu/~binyu/ps/lmdl.ps) IEEE Trans.
+Wavelet thresholding via MDL for natural images.
+IEEE Trans.
 Inform.
@@
 46, 1778-1788.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/lmdl.ps))
 
 Jorma Rissanen and Bin Yu (2000).
-[Coding and compression: a happy union of theory and practice.](https://www.stat.berkeley.edu/~binyu/ps/vig.ps) J.
+Coding and compression: a happy union of theory and practice.
+J.
 Amer.
@@
 95, 986-988.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/vig.ps))
 
 Lei Li and Bin Yu (2000).
-[Iterated logarithm expansions of the pathwise code lengths for exponential families.](https://www.stat.berkeley.edu/~binyu/ps/pred.ps) IEEE Trans.
+Iterated logarithm expansions of the pathwise code lengths for exponential families.
+IEEE Trans.
 Inform.
@@
 46, 2683-2689.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/pred.ps))
 
@@
 Vetterli (2000).
-[Adaptive wavelet thresholding for image denoising and compression.](https://www.stat.berkeley.edu/~binyu/ps/jMDLQ.ps) IEEE Trans.
+Adaptive wavelet thresholding for image denoising and compression.
+IEEE Trans.
 Image Processing, vol.
 9, 1532-1546.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/jMDLQ.ps))
 
@@
 Vetterli (2000).
-[Spatially adaptive wavelet thresholding based on context modeling for image denoising.](https://www.stat.berkeley.edu/~binyu/ps/spatThr.ps) IEEE Trans.
+Spatially adaptive wavelet thresholding based on context modeling for image denoising.
+IEEE Trans.
 Image Processing, vol.
 9, 1522-1531.
-
-G. Chang, B. Yu and M. Vetterli (2000). [Wavelet thresholding for multiple noisy image copies.](https://www.stat.berkeley.edu/~binyu/ps/mt.ps) IEEE Trans. Image Processing, vol. 9, 1631-1635.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/spatThr.ps))
+
+G. Chang, B. Yu and M. Vetterli (2000). Wavelet thresholding for multiple noisy image copies. IEEE Trans. Image Processing, vol. 9, 1631-1635. ([paper](https://www.stat.berkeley.edu/~binyu/ps/mt.ps))
 
@@
 Yu (1999).
-[Image subband coding using context-based classification and adaptive quantization.](https://www.stat.berkeley.edu/~binyu/ps/yoo.ps) IEEE Trans.
+Image subband coding using context-based classification and adaptive quantization.
+IEEE Trans.
 Image Processing, vol.
 8, 1702-1215.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/yoo.ps))
 
@@
 Vetterli (1998).
-[Spatially adaptive wavelet thresholding for image denoising.](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=862630) Proceedings of IEEE International Conference on Image Processing, October, Chicago.
+Spatially adaptive wavelet thresholding for image denoising.
+Proceedings of IEEE International Conference on Image Processing, October, Chicago.
+([paper](http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=862630))
 
@@
 Vetterli (1998).
-[Image denoising via lossy compression and wavelet thresholding.](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=647985) Proceedings of International Conference on Image Processing.
+Image denoising via lossy compression and wavelet thresholding.
+Proceedings of International Conference on Image Processing.
 Santa Barbara, California, vol.
@@
 604-607.
-
-M. Ostland and B. Yu (1997). [Exploring quasi Monte Carlo for marginal density approximation.](https://www.stat.berkeley.edu/~binyu/ps/quasiMC.pdf) Statistics and Computing, 7, 217-228.
+([paper](http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=647985))
+
+M. Ostland and B. Yu (1997). Exploring quasi Monte Carlo for marginal density approximation. Statistics and Computing, 7, 217-228. ([paper](https://www.stat.berkeley.edu/~binyu/ps/quasiMC.pdf))
 
@@
 
-B. Yu and T. P. Speed (1997). [Information and the clone mapping of chromosomes.](https://www.stat.berkeley.edu/~binyu/ps/clone.pdf) Ann. Statist. 25, 169-185.
+B. Yu and T. P. Speed (1997). Information and the clone mapping of chromosomes. Ann. Statist. 25, 169-185. ([paper](https://www.stat.berkeley.edu/~binyu/ps/clone.pdf))
 
@@
 
-B. Yu (1997). [Assouad, Fano, and Le Cam.](https://www.stat.berkeley.edu/~binyu/ps/LeCam.pdf) Festschrift for Lucien Le Cam . D. Pollard, E. Torgersen, and G. Yang (eds), pp. 423-435, Springer-Verlag.
+B.
+Yu (1997).
+Assouad, Fano, and Le Cam.
+Festschrift for Lucien Le Cam .
+D.
+Pollard, E.
+Torgersen, and G.
+Yang (eds), pp.
+423-435, Springer-Verlag.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/LeCam.pdf))
 
@@
 Yu (1996).
-[A Statistical analysis of adaptive scalar quantization based on quantized past data.](https://www.stat.berkeley.edu/~binyu/ps/quan.ps) In Proceedings of International Symposium on Information Theory and its Applications (ISITA96), Victoria, Canada.
+A Statistical analysis of adaptive scalar quantization based on quantized past data.
+In Proceedings of International Symposium on Information Theory and its Applications (ISITA96), Victoria, Canada.
+([paper](https://www.stat.berkeley.edu/~binyu/ps/quan.ps))
 

### 2025-07-20 index.qmd
Update website content and structure
Renamed sections in various files for clarity, changing 'Bin Yu' to 'Professor Bin Yu' in index.qmd and 'Select Publications' to 'Papers' in papers.qmd. Enhanced publication entries with direct links to papers for better accessibility. Updated the 'People' section title in people.qmd and changed 'Code' to 'Software' in software.qmd for consistency. Removed the outdated bio1.jpg image file.
Update website content and layout
Changed the page footer in _quarto.yml to center the copyright notice for 2025. Revised the 'About' page in about.qmd to enhance clarity

@@
 
-# Bin Yu
+:::: {.columns}
 
-<div style="flex: 0 0 200px;">
-<img src="images/binyu.jpg" alt="Bin Yu" style="width:200px; border-radius:8px;" />
-</div>
+::: {.column width="40%"}
+![](images/binyu.jpg)
+:::
 
-- Chancellor's Distinguished Professor of Statistics
-- Statistics Department Chair, 2009 - 2012
-- Professor by courtesy, Electrical Engineering and Computer Sciences
+::: {.column width="60%"}
+## Professor Bin Yu
 
-**Address:** 367 Evans Hall #3860, Berkeley, CA 94720  
-**Phone:** 510-642-2781  
-**Fax:** 510-642-7892  
-**Email:** [binyu@berkeley.edu](mailto:binyu@berkeley.edu)
+Chancellor's Distinguished Professor of Statistics  
+Statistics Department Chair, 2009 - 2012  
+Professor of Electrical Engineering and Computer Sciences, by courtesy
+
+## Contact
+
+Address: 367 Evans Hall #3860, Berkeley, CA 94720  
+Phone: 510-642-2781  
+Fax: 510-642-7892  
+Email: [binyu@berkeley.edu](mailto:binyu@berkeley.edu)
+:::
+
+::::
 
@@
 
-- *2025* [New paper: PCS workflow for veridical data science in the age of AI (Z. Rewolinski and B. Yu, 2025)](https://www.stat.berkeley.edu/~yugroup/pubs/pcs_workflow-6.pdf)
-- *2025* [Veridical Data Science in Biology on July 11, 2025 at UC Berkeley (Submission deadline July 4)](https://www.eventbrite.com/e/veridical-data-science-for-biology-2025-tickets-1384456339179)
-- *2025* [Rome Workshop on Veridical Data Science, June 20, 2025](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html)
-- *2024* [Veridical data science and medical foundation models](https://arxiv.org/abs/2409.10580) on arXiv by Alaa and Yu.
-- *2024* [VDS book review](https://hdsr.mitpress.mit.edu/pub/5322mn1e/release/3) by Yuval and Yoav Benjamini in Harvard Data Science Review (HDSR)-- "pedagogical excellence, diverse examples, and projects make Veridical Data Science a suitable textbook for students of all levels, in addition to being a valuable resource for data scientists in general" (review summary in HDSR Editor-in-Chief's note), June, 2024.
-- *2024* [Inaugural Berkeley-Stanford Workshop on Veridical Data Science at UC Berkeley](https://na.eventscloud.com/website/69057/) (May 31, 2024) ([talk videos available](https://www.youtube.com/playlist?list=PLKW2Azk23ZtSrg4jwLSioaV1bwmFnQ1Bx))
-- *2024* Our MIT Press book ["Veridical Data Science: The Practice of Responsible Data Analysis and Decision Making"](https://mitpress.mit.edu/9780262049191/veridical-data-science/), has been released [online](http://vdsbook.com/).
-- *2023* ["Veridical data science towards trustworthy AI"](https://ww2.amstat.org/meetings/jsm/2023/webcasts/index.cfm) (Talk video of COPSS DAAL (formerly Fisher Award and Lecture), scroll down), Aug.
-JSM in Toronto, 2023.
-- *2023* IMS Wald [Lecture I](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1029) and [Lecture II](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1031), and [COPSS Distinguished Award and Lecture (DAAL)](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1374) delivered at [Joint Statistical Meeting (JSM)](https://ww2.amstat.org/meetings/jsm/2023/) in Toronto, August 2023
-- *2022* [CDSS news: Statistics-Computer Science team reflects on tackling covid outbreaks](https://data.berkeley.edu/news/statistics-computer-sciences-team-reflects-tackling-covid-outbreaks), May, 2022
-- *2021* Honorary Doctorate, University of Lausanne (UNIL) (Faculty of Business and Economics), June 4, 2021 ([Interview of Bin Yu](https://www.youtube.com/watch?v=1JRGPGhcYzU) by journalist Nathalie Randin, with an introduction by Dean Jean-Philippe Bonardi of UNIL in French ([English translation](https://www.stat.berkeley.edu/~binyu/Intro-DeanBonardi-UNIL.pdf)))
-- *2020* [Veridical data science](https://www.pnas.org/content/117/8/3920) (PCS framework: [v-flow code](https://github.com/Yu-Group/veridical-flow) and [documentation template](https://yu-group.github.io/vdocs/PCSDoc-Template.html)), PNAS, 2020 ([QnAs with Bin Yu](https://www.pnas.org/content/117/8/3893))
-- *2020* [CDSS news on our PCS framework: "A better framework for more robust, trustworthy data science"](https://data.berkeley.edu/people/bin-yu), Oct. 2020
-- *2020* [UC Berkeley to lead $10M NSF/Simons Foundation program to investigate theoretical underpinnings of deep learning](https://data.berkeley.edu/news/uc-berkeley-lead-10m-nsfsimons-foundation-program-investigate-theoretical-underpinnings-deep), Aug.
-25, 2020
-- *2020* UC Berkeley team part of the new NSF AI Center for Cybersecurity [ACTION](https://action.ucsb.edu/) led by UCSB.
+- <span class="year-entry">2025</span>[PCS workflow for veridical data science in the age of AI](https://www.stat.berkeley.edu/~yugroup/pubs/pcs_workflow-6.pdf) - Framework for responsible AI development and deployment
+- <span class="year-entry">2025</span>[Veridical Data Science in Biology workshop](https://www.eventbrite.com/e/veridical-data-science-for-biology-2025-tickets-1384456339179), UC Berkeley, July 11 - Applying trustworthy data science to biological research
+- <span class="year-entry">2025</span>[Rome Workshop on Veridical Data Science](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html), June 20 - International workshop on responsible data analysis
+- <span class="year-entry">2024</span>[Veridical data science and medical foundation models](https://arxiv.org/abs/2409.10580) - Guidelines for trustworthy medical AI systems
+- <span class="year-entry">2024</span>[Mechanistic Interpretation through Contextual Decomposition in Transformers](https://arxiv.org/pdf/2407.00886) - Method for understanding transformer decision-making processes
+- <span class="year-entry">2024</span>[LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) - Improved technique for fine-tuning large language models
+- <span class="year-entry">2024</span>[VDS book review](https://hdsr.mitpress.mit.edu/pub/5322mn1e/release/3) in Harvard Data Science Review - Praise for pedagogical approach to responsible data science
+- <span class="year-entry">2024</span>[Berkeley-Stanford Workshop on Veridical Data Science](https://na.eventscloud.com/website/69057/) ([videos](https://www.youtube.com/playlist?list=PLKW2Azk23ZtSrg4jwLSioaV1bwmFnQ1Bx)) - Inaugural academic collaboration on trustworthy AI
+- <span class="year-entry">2024</span>[Veridical Data Science book](https://mitpress.mit.edu/9780262049191/veridical-data-science/) released ([online](http://vdsbook.com/)) - Comprehensive guide to responsible data analysis and decision making
+- <span class="year-entry">2023</span>[Explaining black box text modules in natural language with language models](https://arxiv.org/abs/2305.09863) - Natural language explanations for neural network text processing
+- <span class="year-entry">2023</span>[Diagnosing transformers: illuminating feature space for clinical decision-making](https://arxiv.org/abs/2305.17588) - Interpretability methods for medical transformer applications
+- <span class="year-entry">2023</span>[COPSS Distinguished Award and Lecture](https://ww2.amstat.org/meetings/jsm/2023/webcasts/index.cfm), JSM Toronto - Recognition for contributions to statistical science and AI
 

### 2025-07-20 papers.qmd
Update content in papers.qmd and software.qmd
Revised the text in papers.qmd to clarify the reference to Google Scholar and arXiv. Simplified the statement in software.qmd regarding GitHub for consistency and brevity.

@@
 
-*For the most up-to-date and complete list, see [Google Scholar](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en) or [arXiv](https://arxiv.org/search/?query=bin+yu&searchtype=author).*
+*Also see [Google Scholar](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en) and [arXiv](https://arxiv.org/search/?query=bin+yu&searchtype=author)*
 

### 2025-07-20 people.qmd
Update website content and structure
Renamed sections in various files for clarity, changing 'Bin Yu' to 'Professor Bin Yu' in index.qmd and 'Select Publications' to 'Papers' in papers.qmd. Enhanced publication entries with direct links to papers for better accessibility. Updated the 'People' section title in people.qmd and changed 'Code' to 'Software' in software.qmd for consistency. Removed the outdated bio1.jpg image file.
Update 'People' section in people.qmd to relocate Yeshwanth Cherapanamjeri's entry
Moved Yeshwanth Cherapanamjeri's listing from the current post-docs section to the form

@@
 ---
+
+# People
 
@@
 - Tiffany Tang (2023) - Clare Boothe Luce Assistant Professor, University of Notre Dame
-- Yeshwanth Cherapanamjeri (2023) - Postdoctoral Researcher, MIT
 - Dennis Shen (2023) - Assistant Professor, USC
@@
 
+- Yeshwanth Cherapanamjeri (2023)
 - Arman Sabbaghi (2022)

### 2025-07-20 index.qmd
Enhance index.qmd and styles.css for improved layout and responsiveness
Updated index.qmd to consolidate Professor Bin Yu's titles for clarity. Added responsive styles in styles.css to ensure a mobile-friendly layout, including adjustments for column stacking and image proportions.
Update index.qmd

@@
 
-Chancellor's Distinguished Professor of Statistics  
+CDSS Chancellor's Distinguished Professor of Statistics, Electrical Engineering and Computer Sciences, and Center for Computational Biology
 Statistics Department Chair, 2009 - 2012
-Professor of Electrical Engineering and Computer Sciences, by courtesy
 

### 2025-07-21 index.qmd
Fix titles across multiple lines

--- 2025-07-20 index.qmd
@@
 
-Chancellor's Distinguished Professor of Statistics  
+CDSS Chancellor's Distinguished Professor of Statistics
+Electrical Engineering and Computer Sciences, and Center for Computational Biology
 Statistics Department Chair, 2009 - 2012
-Professor of Electrical Engineering and Computer Sciences, by courtesy
 

### 2025-07-21 people.qmd
Fix student positions.

@@
 - Soufiane Hayou (Post-doc)
+- David Deriso (Ph.D. student, CS)
 - Jakob Heiss (Post-doc)
-- Aliyah Hsu (Ph.D. Student, Statistics)
 - Yaxuan Huang (Ph.D. Student, Statistics)
-- Nathan Benjamin McNaughton (Undergraduate Student)
-- Robin Netzorg (Ph.D. Student, Statistics)
+- Nathan Benjamin McNaughton (MEng)
+- Robin Netzorg (Ph.D. Student, CS)
 - Anthony Ozerov (Ph.D. Student, Statistics)
@@
 - Chengzhong Ye (Ph.D. Student, Statistics)
-- Zeyu Yun (Ph.D. Student, Statistics)
+- Zeyu Yun (Ph.D. Student, CS)
 - Austin Zane (Ph.D. Student, Statistics)
@@
 ## Former Ph.D. Students (Graduation Year)
-
+- Aliyah Hsu (2025) -  Software Engineer, Salesforce
 - Corine Elliot (2024) - Statistical Scientist, Berry Consultants

### 2025-11-18 about/index.qmd
put qmd files into folders for urls without .html at end

--- 2025-07-20 about.qmd
@@
 She is a member of the UC Berkeley Center for Computational Biology and serves as a scientific advisor at the Simons Institute for the Theory of Computing.
-<!-- 
-# About Our Research Group
 
-The [Yu Group](https://www.stat.berkeley.edu/~yugroup/) at Berkeley consists of a small group of students and postdocs from Statistics and EECS, developing cutting-edge statistical machine learning methods that have proven highly valuable in theortical and applied diciplines spanning a broad range from genetics to quantitative finance.
-Our graduates have achieved exceptional success in academia and industry, with notable alumni including Peng Zhao (CEO of Citadel Securities), and senior quantitative researchers at Citadel, Two Sigma, Bridgewater, and Voleon.
-
-Our research focuses on developing stable, interpretable, and scalable methods.
-We have successfully built **real-time forecasting systems** for complex temporal data (including our [COVID-19 severity prediction](https://covidseverity.com/) system), developed **stability-driven machine learning frameworks** crucial for risk management, and created **interpretable deep learning methods** essential for regulatory compliance in financial applications.
-
-The Yu Group has developed many fundamental statistical and machine learning methods, including [**stability-driven nonnegative matrix factorization (staNMF)**](https://github.com/Yu-Group/staNMF) for regime detection and factor modeling, [**iterative Random Forests (iRF)**](https://github.com/Yu-Group/iterative-Random-Forest) and [**signed iRF (s-iRF)**](https://github.com/karlkumbier/iRF2.0) for discovering complex market interactions and non-linear relationships, [**hierarchical shrinkage methods**](https://arxiv.org/abs/2202.00858) for robust prediction in high-dimensional settings, and [**contextual decomposition (CD)**](https://github.com/jamie-murdoch/ContextualDecomposition) and [**aggregated contextual decomposition (ACD)**](https://github.com/csinva/hierarchical-dnn-interpretations) for interpreting complex deep learning models in trading applications.
-
-Our research covers several key areas:
+# Research Themes
 
@@
 
-Our work in deep learning spans from theoretical understanding to practical applications across diverse domains.
-Key contributions include mechanistic interpretation through contextual decomposition in transformers, efficient fine-tuning methods like [LoRA+](https://github.com/nikhil-ghosh-berkeley/loraplus), and frameworks for understanding neural network dynamics.
-We've developed methods like [Adaptive Wavelet Distillation (AWD)](https://github.com/Yu-Group/adaptive-wavelets) for interpreting deep neural networks, and theoretical work on the three stages of dynamics in high-dimensional kernel methods.
-Our applications range from clinical decision-making in healthcare to cosmological analysis and financial modeling.
+- A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contexual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886)
+- S. Hayou, N. Ghosh, B. Yu (2024). [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354). Proc. ICML.
+- A.
+R.
+Hsu, Y.
+Cherapanamjeri, B.
+Park, T.
+Naumann, A.
+Odisho, and B.
+Yu (2023).
+[Diagnosing transformers: illuminating feature space for clinical decison-making.](https://arxiv.org/abs/2305.17588) ICLR 2023.
+- J. Murdoch, P. Liu, and B. Yu (2018) [Beyond word importance: contextual decomposition to extract interactions from LSTMs.](https://arxiv.org/abs/1801.05453) Proc. ICLR 2018.
 
-Selected recent papers:
-- [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) (ICML 2024)
-- [Mechanistic Interpretation through Contextual Decomposition in Transformers](https://arxiv.org/pdf/2407.00886) (2024)
-- [Minimum-Norm Interpolation Under Covariate Shift](https://arxiv.org/pdf/2404.00522) (ICML 2024)
-- [The three stages of dynamics in high-dimensional kernel methods](https://arxiv.org/abs/2111.07167) (ICLR 2022)
+## Interdisciplinary Research in Biomedicine
+
+- Q.
+Wang,* T.
+M.
+Tang*, N.
+Youlton, C.
+S.
+Weldy, A.
+M.
+Kenney, O.
+Ronen, J.
+W.
+Hughes, E.
+T.
+Chin, S.
+C.
+Sutton.
+A.
+Agarwal, X.
+Li, M.
+Behr, K.
+Kumbier, C.
+S.
+Moravec, W.
+H.
+W.
+Tang, K.
+B.
+Margulies, T.
+P.
+Cappola, A.
+J.
+Buitte, R.
+Arnaout, J.
+B.
+Brown, J.
+R.
+Priest, V.
+N.
+Parikh, B.
+Yu*, E.
+Ashley* (2023).
+[Epistasis regulates genetic control of cardiac hypertrophy.](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1)
+- E.
+Irajizad, A.
+Kenney, T.
+Tang, J.
+Vykoukal, R.
+Wu, E.
+Murage, J.
+B.
+Dennison, M.
+Sans, J.
+P.
+Long, M.
+Loftus, J.
+A.
+Chabot, M.
+D.
+Kluger, F.
+Kastrinos, L.
+Brais, A.
+Babic, K.
+Jajoo, L.
+S.
+Lee, T.
+E.
+Clancy, K.
+Ng, A.
+Bullock, J.
+M.
+Genkinger, A.
+Maitra, K.
+A.
+Do, B.
+Yu, B.
+W.
+Wolpin, S.
+Hanash, J.
+F.
+Fahrmann.
+(2023).
+[A blood-based metabolomic signature predictive of risk for pancreatic cancer](https://pubmed.ncbi.nlm.nih.gov/37729870/).
+Cell Reports Medicine 4(9): 101194.
+- B.
+Norgeot*, G.
+Quer, B.
+K.
+Beaulieu-Jones, A.
+Torkamani, R.
+Dias, M.
+Gianfrancesco, R.
+Arnaout, I.
+S.
+Kohane, S.
+Saria, E.
+Topol, Z.
+Obermeyer, B.
+Yu & A.
+Butte* (2020).
+[Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y), Nature Medicine, 26, 1320–1324.
+
+## Interpretable Machine Learning
+
+- Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262) ICLR 2024.
+- A. Agarwal, A. M. Kenny, Y. S. Tan, T. M. Tang, B. Yu (2023). [MDI+: a flexible random forest-based feature importance framework.](https://arxiv.org/abs/2307.01932)
+- C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
+- W.
+J.
+Murdoch, C.
+Singh, K.
+Kumbier, R.
+Abbasi-Asl, and B.
+Yu* (2019) [Definitions, methods, and applications in interpretable machine learning.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) PNAS, 116 (44) 22071-22080.
+
+## Tree-based Methods
+
+- Y. S. Tan, C. Singh, K. Nasseri, A. Agarwal, J. Duncan, O. Ronen, M. Epland, A. Kornblith, B. Yu (2022). [Fast interpretable greedy-tree sums (FIGS).](https://arxiv.org/abs/2201.11931)
+- A. Agarwal, Y. S. Tan, O. Ronen, C. Singh, B. Yu (2022). [Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.](https://arxiv.org/abs/2202.00858) Proc. ICML
+- M. Behr, Y. Wang, X. Li, B. Yu (2022). [Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.](https://arxiv.org/abs/2102.11800) PNAS.
+- S.
+Basu, K.
+Kumbier, J.
+B.
+Brown*, and B.
+Yu* (2018) [iterative Random Forests to discover predictive and stable high-order interactions](https://www.stat.berkeley.edu/~binyu/ps/papers2018/iRF+SI18.pdf) PNAS, 115 (8), 1943-1948.
 
@@
 
-The PCS (Predictability, Computability, Stability) framework represents our approach to responsible, reliable, and transparent data analysis.
-This framework unifies and expands on best practices in machine learning and statistics, ensuring that data science findings are both scientifically sound and practically actionable.
-The **Stability** component addresses model robustness and reproducibility, the **Predictability** component focuses on out-of-sample performance, and the **Computability** component ensures scalable implementation.
-Our work includes applications to genomics, clinical research, epidemiology, and quantitative finance, always emphasizing the importance of stability and reproducibility in scientific discovery.
-
-Selected recent papers:
-- [Veridical data science](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf) (PNAS 2020) — foundational framework paper
-- [Epistasis regulates genetic control of cardiac hypertrophy](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) (2023) — PCS application to genomics
-- [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (Harvard Data Science Review 2024)
-- [Stable discovery of interpretable subgroups via calibration in causal studies (staDISC)](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427)
-
-## Interpretable Machine Learning
-
-We develop methods to make machine learning models interpretable and trustworthy, particularly for high-stakes applications in healthcare, science, and finance.
-Our work spans contextual decomposition for understanding neural networks, feature importance frameworks, and methods for aligning model explanations with prior knowledge.
-We emphasize the principle that interpretations should be both faithful to the model and useful for human decision-making across diverse domains.
-
-Selected recent papers:
-- [Mechanistic Interpretation through Contextual Decomposition in Transformers](https://arxiv.org/pdf/2407.00886) (2024)
-- [MDI+: a flexible random forest-based feature importance framework](https://arxiv.org/abs/2307.01932) (2023)
-- [Tell your model where to attend: post-hoc attention steering for LLMs](https://arxiv.org/abs/2311.02262) (ICLR 2024)
-- [Definitions, methods, and applications in interpretable machine learning](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) (PNAS 2019)
-
-## Tree-based Methods
-
-We develop both theoretical understanding and practical improvements for tree-based methods, including random forests and gradient boosting.
-Our contributions include the iterative Random Forests (iRF) algorithm for discovering high-order interactions, hierarchical shrinkage methods for improving accuracy and interpretability, and fast interpretable greedy-tree sums (FIGS).
-We also provide theoretical analysis of when and why tree-based methods succeed or fail, with applications spanning from genomics to finance to clinical medicine.
-
-Selected recent papers:
-- [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis](https://arxiv.org/pdf/2406.19958) (2024)
-- [Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931) (2022)
-- [Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods](https://arxiv.org/abs/2202.00858) (ICML 2022)
-- [Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests](https://arxiv.org/abs/2102.11800) (PNAS 2022)
-- [iterative Random Forests to discover predictive and stable high-order interactions](https://www.stat.berkeley.edu/~binyu/ps/papers2018/iRF+SI18.pdf) (PNAS 2018)
-
-## Quantitative Finance Applications
-
-Our methods have proven particularly valuable in quantitative finance, where model stability, interpretability, and out-of-sample performance are crucial.
-Our graduates have achieved exceptional success at leading hedge funds including Citadel Securities (where Peng Zhao serves as CEO), Two Sigma, Bridgewater, and Voleon.
-We develop stability-driven approaches for regime detection, portfolio optimization, risk management, and alpha generation, always emphasizing robust performance across changing market conditions.
-
-Key applications and alumni outcomes:
-- **Real-time forecasting systems** for complex temporal data and market dynamics
-- **Stability-driven frameworks** crucial for live trading environments
-- **Interpretable models** essential for regulatory compliance and risk management
-- **High-dimensional interaction discovery** for complex market relationship modeling
-
-## Interdisciplinary Research in Biomedicine
-
-Our biomedicine work applies statistical machine learning to problems in genomics, clinical prediction, and biomarker discovery.
-We collaborate closely with domain experts to develop methods that are both statistically rigorous and clinically meaningful.
-Recent work includes epistasis analysis for cardiac hypertrophy, metabolomic signatures for pancreatic cancer risk, and clinical AI modeling standards.
-
-Selected recent papers:
-- [Epistasis regulates genetic control of cardiac hypertrophy](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) (2023)
-- [A blood-based metabolomic signature predictive of risk for pancreatic cancer](https://pubmed.ncbi.nlm.nih.gov/37729870/) (Cell Reports Medicine 2023)
-- [Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y) (Nature Medicine 2020)
-- [Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) (2023)
-
-Our graduates have achieved remarkable success across academia and industry, securing positions at leading institutions including top universities, major technology companies, and premier quantitative trading firms such as Citadel Securities, Two Sigma, Bridgewater, and Voleon.
-This success reflects the broad applicability of our research and the exceptional training our students receive in robust statistical methods, scalable machine learning, and rigorous mathematical foundations essential for tackling complex real-world problems.
-
-Research is supported in part by grants from NSF, NIH, the Weill Neurohub, and the Simons Foundation.
-
-- [Yu Group at Berkeley](https://www.stat.berkeley.edu/~yugroup/) for current group members and current projects
-- [Papers](https://binyu.stat.berkeley.edu/papers)
-- [Code](https://www.stat.berkeley.edu/~yugroup/code.html)
-- [Statistical Machine Learning at Berkeley](http://www.stat.berkeley.edu/~statlearning/)
-
-# Vision
-
-My broad vision of data science best described in my article [Veridical Data Science](https://www.pnas.org/content/117/8/3920).
-In this work, I introduced a framework based on three principles: predictability, computability and stability (abbreviated to PCS).
-This framework helps guide practitioners who solve domain data problems with data science tools to be creative in their analysis and properly validate their findings.
-I have written a book on the Veridical Data Science framework together with my former student [Rebecca Barter](https://www.rebeccabarter.com/).
-The book is being published by the MIT Press in 2024 with a free on-line copy available soon.
-
-She and her team have developed the PCS framework for veridical data science (or responsible, reliable, and transparent data analysis and decision-making).
-PCS stands for predictability, computability and stability, and it unifies, streamlines, and expands on ideas and best practices of machine learning and statistics.
-
-In order to augment empirical evidence for decision-making, they are investigating statistical machine learning methods/algorithms (and associated statistical inference problems) such as dictionary learning, non-negative matrix factorization (NMF), EM and deep learning (CNNs and LSTMs), and heterogeneous effect estimation in randomized experiments (X-learner).
-Their recent algorithms include staNMF for unsupervised learning, iterative Random Forests (iRF) and signed iRF (s-iRF) for discovering predictive and stable high-order interactions in supervised learning, next generation tree-based methods (e.g.
-fast and interpretable greedy-tree sums (FIGS) and hierarchical shrinked (HS) trees, and RF+ ), contextual decomposition (CD), aggregated contextual decomposition (ACD), and adaptive wavelet distillation (AWD) for interpretation of Deep Neural Networks (DNNs).
--->
+- B. Yu (2024). [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) Harvard Data Science Review (HDSR).
+- B. Yu and K. Kumbier (2020) [Veridical data science](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf) PNAS. 117 (8), 3920-3929.
+- B. Yu (2023). [What is uncertainty in today's practice of data science?](https://www.sciencedirect.com/science/article/abs/pii/S030440762300235X?dgcid=author) J. Econometrics. 237, 105519.

### 2025-11-18 books/index.qmd
put qmd files into folders for urls without .html at end

---
title: Books
---

# Books

## Veridical Data Science

<div style="display: flex; align-items: flex-start; margin-bottom: 2em;">

<img src="images/veridical-data-science-cover.jpg" alt="Veridical Data Science Book Cover" style="float:left; margin:0 2em 1em 0; width:200px; border-radius:8px;" />

<div>

*Published by MIT Press, 2024*

*Veridical Data Science* presents the PCS (Predictability, Computability, and Stability) framework that prioritizes reproducibility, interpretability, and reliability in data analysis. 
The book covers essential topics including statistical modeling, machine learning, causal inference, and ethical considerations in data science. Through real-world case studies and practical examples, readers learn how to apply the PCS principles to ensure their analyses are not only accurate but also robust and interpretable.

- **[Web](https://vdsbook.com/)** (free online access)
- **[Printed](https://mitpress.mit.edu/9780262049191/veridical-data-science/)**

</div>

</div>

### 2025-11-18 people/index.qmd
put qmd files into folders for urls without .html at end

---
title: "People"
---

# People

## Current Members (Role, Program)

- Abhineet Agarwal (Ph.D. Student, Statistics)
- David Deriso (Ph.D. student, CS)
- Jakob Heiss (Post-doc)
- Yaxuan Huang (Ph.D. Student, Statistics)
- Nathan Benjamin McNaughton (MEng)
- Robin Netzorg (Ph.D. Student, CS)
- Anthony Ozerov (Ph.D. Student, Statistics)
- Zachary Rewolinski (Ph.D. Student, Statistics)
- Omer Ronen (Ph.D. Student, Statistics)
- Jingfeng Wu (Post-doc)
- Chengzhong Ye (Ph.D. Student, Statistics)
- Zeyu Yun (Ph.D. Student, CS)
- Austin Zane (Ph.D. Student, Statistics)

## Former Ph.D. Students and Postdocs (Graduation Year)
- Soufiane Hayou (2025) - Assistant Professor, Johns Hopkins University
- Aliyah Hsu (2025) -  Software Engineer, Salesforce
- Corine Elliot (2024) - Statistical Scientist, Berry Consultants
- James Duncan (2024) - Climate ML Engineering, Allen Institute for AI (AI2)
- Tiffany Tang (2023) - Clare Boothe Luce Assistant Professor, University of Notre Dame
- Dennis Shen (2023) - Assistant Professor, USC
- Spencer Frei (2023) - Assistant Professor, UC Davis
- Rebecca L. Barter (2022) - Research Assistant Professor, University of Utah
- Luiz Chamon (2022) - Research Group Leader, University of Stuttgart
- Angela Zhou (2022) - Assistant Professor, University of Southern California
- Briton Park (2022) - Citadel Securities
- Chandan Singh (2022) - Microsoft Research
- Keyan Nasseri (2022) - Google
- Wooseok Ha (2022) - Assistant Professor, KAIST, Korea
- Yan Shuo Tan (2022) - Assistant Profressor, Department of Statistics and Data Science, National University of Singapore
- Xiao Li (2021) - Voleon
- Raaz Dwivedi (2021) - Assistant Professor, Cornell Tech
- Yu Wang (2020) - Two Sigma
- Merle Behr (2020) - Professor of Informatics, Regensburg University, Germany
- Nicholas Altieri (2020) - Genentech
- Yuansi Chen (2019) - Associate Professor, ETH, Zurich
- Karl Kumbier (2019) - Postdoctoral Researcher, UC San Francisco
- Jamie Murdoch (2019) - Co-founder / President, clientelligent.ai
- Soren Kunzel (2019) - Data Scientist, Citadel
- Simon Walter (2019) - Data Scientist, Google
- Sujayam Saha (2018) - Data Scientist, Google
- Reza Abbasi-Asl (2018) - Associate Professor of Neuroscience, UCSF
- Christine Kuang (2017) - Data Scientist, Facebook
- Hanzhong Liu (2016) - Associate Professor, Department of Statistics, Tsinghua University
- Sumanta Basu (2016) - Associate Professor, Department of Statistics, Cornell University
- Sivaraman Balakrishnan (2016) - Professor, Department of Statistics, Carnegie Mellon University
- Adam Bloniarz (2016) - Data Scientist, Google
- Siqi Wu (2016) - Data Scientist, Citadel
- Hongwei Li (2015) - Senior Data Scientist, UBER
- Antony Joseph (2014) - Staff Data Scientist, Walmart eCommerce
- Taesup Moon (2013) - Research Staff Member, Samsung Advanced Institute of Technology
- Yuval Benjamini (2013) - Professor, Department of Statistics, Hebrew University
- Julien Mairal (2012) - Senior Research Scientist, INRIA
- Yueqing Wang (2012) - Research Scientist, Google
- Hau-tieng Wu (2012) - Professor, Mathematics Department, Courant Institute, NYU
- Garvesh Raskutti (2012) - Associate Professor, Department of Statistics, Univ. Wisconsin-Madison
- Luke W. Miratrix (2012) - Associate Professor, School of Education, Harvard University
- Harry Kim (2011) - Product Marketing Manager, Google
- Chinghway Lim (2011) - Assistant Professor, Department of Statistics and Applied Probability, National University of Singapore
- Karl Rohe (2011) - Professor, Department, University of Wisconsin-Madison.
- Kyle Jia (2010) - Associate Professor, Peking University, China.
- David Purdy (2009) - Data Scientist, Uber
- Pradeep Ravikumar (2009) - Professor, Department of Computer Sciences, University of Texas, Austin.
- Vince Vu (2009) - Associate Professor, Department of Statistics, The Ohio State University
- Ethan Anderes (2008) - Professor, Department of Statistics, University of California, Davis
- Guilherme Rocha (2008) - Assistant Professor, Department of Statistics, Indiana University, Bloomington
- Peng Zhao (2006) - CEO of Citadel Securities, Citadel Investment Group in Chicago, IL.
- Nicolai Meinshausen (2006) - Professor, Department of Statistics, ETH Zurich
- Tao Shi (2005) - Quantitative Researcher, Citadel Investment Group in Chicago, IL.
- Gang Liang (2004) - Quantitative Operations Associate, Wells Fargo
- Rebecka Jörnsten (2000) - Professor, Biostatistics and Applied Statistics, Chalmers University of Technology, Sweden
- Grace Chang (2000) - Senior Manager of Product Development, Marketing Dept, MTN Irancell

## Former Visitors, and Associates (Starting Year)
- Yeshwanth Cherapanamjeri (2023)
- Arman Sabbaghi (2022)
- Yanjun Qi (2020)
- Ezequiel Smucler (2020)
- Laura Reiger (2019)
- Yanyan Lan (2018)
- Yahong Han (2016)
- Thibault Vatter
- Guoqiang Cai
- Trine Abrahamsen
- Xiaoling Lu
- Xiusheng Lu (2014)
- Xiangyu Chang (2012)
- Ling Hong (2012)
- Toshiyasu Matsushima (2012)
- Yanfeng Gu (2012) - Professor of Electronics Engineering, Harbin Institute of Technology
- Hai Zhang (2012)
- Rodolphe Jenatton (2010)
- Kenichi Hayashi (2010)
- Yangbo He (2010)
- Fei Wu (2010)
- Kei Kobayashi (2008)
- Xing Wang (2007)

### 2025-11-18 teaching/index.qmd
put qmd files into folders for urls without .html at end

---
title: "Teaching"
---

# Teaching

## STAT 154 - Modern Statistical Prediction and Machine Learning

**Course Description:** Theory and practice of statistical prediction. Contemporary methods as extensions of classical methods. Topics: optimal prediction rules, the curse of dimensionality, empirical risk, linear regression and classification, basis expansions, regularization, splines, the bootstrap, model selection, classification and regression trees, boosting, support vector machines. Computational efficiency versus predictive performance. Emphasis on experience with real data and assessing statistical assumptions. This course uses Python as its primary computing language; details are determined by the instructor.

This is an introductory-level course in supervised learning, with a focus on regression and classification methods. The syllabus includes: linear regression, model assessment, model selection, regularization methods (PCR, PLSR, ridge and lasso); logistic regression and discriminant analysis; cross-validation and the bootstrap; tree-based methods, random forests and boosting; support-vector machines. Some unsupervised learning methods are discussed: principal components and clustering (k-means and hierarchical).

In this course, students explore the predictive modeling lifecycle, including question formulation, data preprocessing, exploratory data analysis and visualization, model building, model assessment/validation, model selection, and decision-making. The course focuses on quantitative critical thinking and key principles needed to carry out this cycle: 1) Foundational principles for building predictive models; 2) Intuitive explanations of many commonly used predictive modeling techniques for both classification and regression problems; 3) Principles and steps for validating a predictive model; and 4) write and use computer code to perform the necessary foundational work to build and validate predictive models.

**Prerequisites:** Mathematics 53 or equivalent; Mathematics 54, Electrical Engineering 16A, Statistics 89A, Mathematics 110 or equivalent linear algebra; Statistics 135, the combination of Data/Stat C140 and Data/Stat/Compsci C100, or equivalent; experience with some programming language. Recommended prerequisite: Mathematics 55 or equivalent exposure to counting arguments.

**Course Website:** [[STAT 154](https://classes.berkeley.edu/content/2019-Spring-STAT-154-001-LEC-001)]

## STAT 215A - Statistical Models: Theory and Application

**Course Description:** Applied statistics and machine learning, focusing on answering scientific questions using data, the data science life cycle, critical thinking, reasoning, methodology, and trustworthy and reproducible computational practice. Hands-on experience in open-ended data labs, using programming languages such as R and Python. Emphasis on understanding and examining the assumptions behind standard statistical models and methods and the match between the assumptions and the scientific question. Exploratory data analysis. Model formulation, fitting, model testing and validation, interpretation, and communication of results. Methods include linear regression and generalizations, decision trees, random forests, simulation, and randomization methods.

**Prerequisites:** Linear algebra, calculus, upper division probability and statistics, and familiarity with high-level programming languages. Statistics 133, 134, and 135 recommended.

**Course Website:** [[STAT 215A](https://classes.berkeley.edu/content/2019-Fall-STAT-215A-001-LEC-001)]

### 2025-11-18 books/index.qmd
fixed book image link, added welcome info, and added 214 to teaching page

@@
 
-<img src="images/veridical-data-science-cover.jpg" alt="Veridical Data Science Book Cover" style="float:left; margin:0 2em 1em 0; width:200px; border-radius:8px;" />
+<img src="../images/veridical-data-science-cover.jpg" alt="Veridical Data Science Book Cover" style="float:left; margin:0 2em 1em 0; width:200px; border-radius:8px;" />
 

### 2025-11-18 index.qmd
Add spaces to impose newlines.
fixed book image link, added welcome info, and added 214 to teaching page

@@
 Email: [binyu@berkeley.edu](mailto:binyu@berkeley.edu)
+
 :::
@@
 ::::
+
+## Welcome
+
+Professor Bin Yu is the head of the Yu Group at Berkeley, which consists of
+12-15 students and postdocs from Statistics and EECS. She was formally trained
+as a statistician, but her research interests and achievements extend beyond
+the realm of statistics. Together with her group,  Bin Yu has leveraged new
+computational developments to solve important scientific problems by combining
+novel and often interpretable statistical machine learning approaches with the
+domain expertise of my many collaborators in neuroscience, genomics and
+precision medicine. She also develops relevant theory to understand random
+forests and deep learning for insight into and guidance for practice.  Her work
+has been recongized by many awards. In particular, she was inducted to the
+National Academy of Sciences in 2014 and to the American Academy of Arts and
+Sciences in 2013. She delivered the IMS Wald Lectures and COPSS Distinguished
+Achievement and Award Lecture (DAAL, formerly Fisher Award and Lecture) in 2023.
+
+She and her team have developed the PCS framework for veridical data science (or
+responsible, reliable, and transparent data analysis and decision-making). PCS
+stands for predictability, computability and stability, and it unifies,
+streamlines, and expands on ideas and best practices of machine learning and
+statistics.
+
+In order to augment empirical evidence for decision-making, they are
+investigating statistical machine learning methods/algorithms (and associated
+statistical inference problems) such as dictionary learning, non-negative matrix
+factorization (NMF), EM and deep learning (CNNs and LSTMs), and heterogeneous
+effect estimation in randomized experiments (X-learner). Their recent algorithms
+include staNMF for unsupervised learning, iterative Random Forests (iRF) and
+signed iRF (s-iRF) for discovering predictive and stable high-order interactions
+in supervised learning, next generation tree-based methods (e.g. fast and
+interpretable greedy-tree sums (FIGS) and hierarchical shrinked (HS) trees, and
+RF+), contextual decomposition (CD), aggregated contextual decomposition (ACD),
+and adaptive wavelet distillation (AWD) for interpretation of Deep Neural
+Networks (DNNs).
 

### 2025-11-18 teaching/index.qmd
fixed book image link, added welcome info, and added 214 to teaching page

@@
 # Teaching
+
+## STAT 215A - Applied Statistics and Machine Learning
+
+**Course Description:** Applied statistics and machine learning, focusing on answering scientific questions using data, the data science life cycle, critical thinking, reasoning, methodology, and trustworthy and reproducible computational practice.
+Hands-on experience in open-ended data labs, using programming languages such as R and Python.
+Emphasis on understanding and examining the assumptions behind standard statistical models and methods and the match between the assumptions and the scientific question.
+Exploratory data analysis.
+Model formulation, fitting, model testing and validation, interpretation, and communication of results.
+Methods include linear regression and generalizations, decision trees, random forests, simulation, and randomization methods.
+
+**Prerequisites:** Linear algebra, calculus, upper division probability and statistics, and familiarity with high-level programming languages. Statistics 133, 134, and 135 recommended.
+
+**Course Website:** [[STAT 215A](https://classes.berkeley.edu/content/2025-fall-stat-215a-001-lec-001)]
+
+## STAT 214 - Data Analysis and Machine Learning for Real-World Decision Making
+
+**Course Description:** Students will be engaged in open-ended data projects for decision making to solve domain problems.
+It mirrors the entire data science life cycle in practice, including problem formulation, data cleaning, exploratory data analysis, statistical and machine learning modeling and computational techniques, and interpretation of results in context.
+It is guided by the Predictability-Computability-Stability (PCS) framework for veridical data science and emphasizes critical thinking and documenting human judgment calls and code.
+It coaches not only the technical but also communication and teamwork skills in order to obtain responsible and reliable data-driven conclusions for solving complex real world problems.
+
+**Prerequisites:** Linear algebra, calculus, upper division probability and statistics, and familiarity with high-level programming languages.
+
+**Course Website:** [[STAT 214](https://classes.berkeley.edu/content/2026-spring-stat-214-001-lec-001)]
 
@@
 **Course Website:** [[STAT 154](https://classes.berkeley.edu/content/2019-Spring-STAT-154-001-LEC-001)]
-
-## STAT 215A - Statistical Models: Theory and Application
-
-**Course Description:** Applied statistics and machine learning, focusing on answering scientific questions using data, the data science life cycle, critical thinking, reasoning, methodology, and trustworthy and reproducible computational practice.
-Hands-on experience in open-ended data labs, using programming languages such as R and Python.
-Emphasis on understanding and examining the assumptions behind standard statistical models and methods and the match between the assumptions and the scientific question.
-Exploratory data analysis.
-Model formulation, fitting, model testing and validation, interpretation, and communication of results.
-Methods include linear regression and generalizations, decision trees, random forests, simulation, and randomization methods.
-
-**Prerequisites:** Linear algebra, calculus, upper division probability and statistics, and familiarity with high-level programming languages. Statistics 133, 134, and 135 recommended.
-
-**Course Website:** [[STAT 215A](https://classes.berkeley.edu/content/2019-Fall-STAT-215A-001-LEC-001)]

### 2025-11-18 index.qmd
shortened welcome section and fixed paper link at bottom of home page

--- 2025-07-21 index.qmd
@@
 ::::
+
+## Welcome
+
+Professor Bin Yu leads the Yu Group at UC Berkeley, a team of researchers in
+Statistics and EECS focused on advancing statistical machine learning and
+responsible data science. Her group develops interpretable methods and theory
+for modern techniques such as random forests and deep learning, and applies them
+to scientific domains including neuroscience, genomics, and precision medicine.
+
+She is a member of the National Academy of Sciences and the American Academy of
+Arts and Sciences, and delivered the 2023 IMS Wald Lectures and COPSS DAAL
+Lecture. Her team created the PCS framework (predictability, computability, and
+stability) to guide transparent and reliable data analysis.
 
@@
 
-[View all papers →](papers.qmd)
+[View all papers →](papers/index.qmd)

### 2025-11-18 people/index.qmd
shortened welcome section and fixed paper link at bottom of home page

@@
 
-- Abhineet Agarwal (Ph.D. Student, Statistics)
-- David Deriso (Ph.D. student, CS)
+- David Deriso (Ph.D. Student, CS)
 - Jakob Heiss (Post-doc)
+- Hao Huang (MEng, EECS)
 - Yaxuan Huang (Ph.D. Student, Statistics)
-- Nathan Benjamin McNaughton (MEng)
+- Nathan Benjamin McNaughton (MEng, EECS)
 - Robin Netzorg (Ph.D. Student, CS)
@@
 ## Former Ph.D. Students and Postdocs (Graduation Year)
+- Abhineet Agarwal (2025) - Technical Staff, Traversal
 - Soufiane Hayou (2025) - Assistant Professor, Johns Hopkins University

### 2025-11-18 index.qmd
changed paper link to google scholar and updated welcome

--- 2025-07-21 index.qmd
@@
 ::::
+
+## Welcome
+
+Professor Bin Yu leads the Yu Group at UC Berkeley, an interdisciplinary team in
+Statistics and EECS dedicated to advancing machine learning, artificial
+intelligence, and veridical data science. Her group develops efficient and
+interpretable ML/AI methods and theory—ranging from iterative random forests
+(iRF) and FIGS to LoRA+ for model adaptation and CD-T and SPEX for interpreting
+deep models. The Yu Group collaborates closely with domain experts in
+neuroscience, genomics, and precision medicine.
+
+A member of both the National Academy of Sciences and the American Academy of
+Arts and Sciences, she has delivered major invited lectures, including the 2019
+Breiman Lecture at NeurIPS, 2023 IMS Wald Lecture, and the COPSS DAAL Lecture
+(formerly Fisher Lecture). Her group’s PCS framework (predictability,
+computability, and stability) for veridical data science has become an
+influential guide for transparent, trustworthy data science and AI.
 
@@
 
-[View all papers →](papers.qmd)
+[View all papers →](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en)

### 2025-11-18 index.qmd
added year to copss lecture

@@
 Arts and Sciences, she has delivered major invited lectures, including the 2019
-Breiman Lecture at NeurIPS, 2023 IMS Wald Lecture, and the COPSS DAAL Lecture
-(formerly Fisher Lecture). Her group’s PCS framework (predictability,
+Breiman Lecture at NeurIPS, 2023 IMS Wald Lecture, and the 2023 COPSS DAAL
+Lecture (formerly Fisher Lecture). Her group’s PCS framework (predictability,
 computability, and stability) for veridical data science has become an

### 2025-11-18 index.qmd
fixed small grammar error

--- 2025-11-18 index.qmd
@@
 Arts and Sciences, she has delivered major invited lectures, including the 2019
-Breiman Lecture at NeurIPS, 2023 IMS Wald Lecture, and the COPSS DAAL Lecture
-(formerly Fisher Lecture). Her group’s PCS framework (predictability,
+Breiman Lecture at NeurIPS, the 2023 IMS Wald Lecture, and the 2023 COPSS DAAL
+Lecture (formerly Fisher Lecture). Her group’s PCS framework (predictability,
 computability, and stability) for veridical data science has become an

### 2025-11-18 index.qmd
edit to welcome and specified google scholar for papers after 2025

--- 2025-11-18 index.qmd
@@
 interpretable ML/AI methods and theory—ranging from iterative random forests
-(iRF) and FIGS to LoRA+ for model adaptation and CD-T and SPEX for interpreting
-deep models. The Yu Group collaborates closely with domain experts in
-neuroscience, genomics, and precision medicine.
+(iRF) and tree-based FIGS to LoRA+ for fine-tuning deep learning and CD-T and
+SPEX for interpreting deep models. The Yu Group collaborates closely with domain
+experts in medical AI, genomics, and neuroscience.
 
 A member of both the National Academy of Sciences and the American Academy of
-Arts and Sciences, she has delivered major invited lectures, including the 2019
-Breiman Lecture at NeurIPS, 2023 IMS Wald Lecture, and the COPSS DAAL Lecture
-(formerly Fisher Lecture). Her group’s PCS framework (predictability,
-computability, and stability) for veridical data science has become an
-influential guide for transparent, trustworthy data science and AI.
+Arts and Sciences, she has delivered major keynotes, including the 2019 Breiman
+Lecture at NeurIPS, 2023 IMS Wald Lectures and the COPSS DAAL Lecture (formerly
+Fisher Lecture). She and her team pioneered the PCS framework (predictability,
+computability, and stability) for veridical (truthful) data science (VDS),
+which has become an influential guide for transparent, trustworthy data science
+and AI.
 

### 2025-11-18 papers/index.qmd
edit to welcome and specified google scholar for papers after 2025

--- 2025-07-20 papers.qmd
@@
 
-*Also see [Google Scholar](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en) and [arXiv](https://arxiv.org/search/?query=bin+yu&searchtype=author)*
+*For papers after 2025, also see [Google Scholar](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en) and [arXiv](https://arxiv.org/search/?query=bin+yu&searchtype=author)*
 
